### 2010-08-04 docs/tex/model.tex
Commit for the tex files

%Chapter describing the model
\chapter{Modeling the evolution of mimicry}

### 2010-08-04 docs/tex/review.tex
Commit for the tex files

%Review Chapter
\chapter{Review}

\section{Evolutionary Programming}

\section{Genetic Algorithm}

\section{Co-evolution}

\section{Artificial Life}

\subsection{Cellular Automata}

### 2010-08-04 docs/tex/application.tex
Commit for the tex files

\chapter{Application}

Part of this thesis was to think about whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions. Predator-prey co-evolution has also been used for solving interesting problems \cite{hillis1990}, giving better result than conventional methodologies.

\paragraph{}
The biggest challenge faced while searching for the appropriate problem to be optimized is the idea of associating palatability with CA pattern with which the prey species has been represented. If we consider the CA pattern to be a certain solution to a problem then the set of 2D CA pattern among which the prey species vary could be considered as the solution set of the problem. And if we consider that the predator species are responsible for selecting the appropriate pattern based on their palatability, then we can consider palatability as the criteria for selection of the pattern (or the evaluation/fitness function for the case of Evolutionary Programming/Genetic Algorithm).

\paragraph{}
If the predator associates the CA pattern with palatability then it does not make any sense of having a mimic in the solution space as mimics will have the same pattern with opposite palatability. So using the evolution of mimicry to solve an optimization problem is futile if we try conventional problems which already can be solved with the help of evolutionary programming or genetic algorithm. 
So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods. We should be looking for a problem where the idea of deception can be useful in term of solving it. Unfortunately during the time of this research we were unable to find such a problem.

### 2010-08-04 docs/tex/mimicry.tex
Commit for the tex files

%Chapter describing the mimetic process
\chapter{Mimicry}

### 2010-08-04 docs/tex/result.tex
Commit for the tex files

% All the result and analysis
\chapter{Results and Analysis}

\section{Initial configuration with two prey species}

% Put the table here
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \includegraphics[scale=0.50]{images/CARule110} & 108 & \multicolumn{2}{|c|}{10} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \includegraphics[scale=0.50]{images/CARule30}  & 108 & \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{0.03} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline

\end{tabular}

\paragraph{}
The above set of parameters were carefully selected to be the initial condition for this run of the simulation. This test has been done with two sets of prey species with very different CA pattern and with opposite palatability and equal population. To control reproduction of the prey species their age limit has been set to 100 iterations into the time the species were alive. And the reproduction interval was set to 1000 iterations.

\paragraph{}
Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation. The Genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents. As mentioned earlier the genome mutation rate has been separated from the pattern mutation rate to bring more control to the number of mimicry rings generated.

\paragraph{}
Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500. But later in the following results predator demise age has been increased to 5000 iterations. Predators in this simulation generates selection pressure for the evolution of mimicry. So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid. But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.

\paragraph{}
Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation. The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die accept their natural cause of death, that is to reach their demise age. So predator population can explode very easily. That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.

\paragraph{}
The memory configuration size for predators are a very interesting parameter. The minimum memory size is directly associated with the number of prey species with which we initiate the simulation. Otherwise evolution of mimicry is not observed. As mentioned earlier the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species. After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgement. At this point its memory size is zero. As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank. No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species. When catching a prey if its memory tells that it is palatable, it will consume that prey. Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.

\paragraph{}
Now as we know the behaviour of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory. So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern previously captured and the patterns stored in memory.

% Put the image
\begin{figure}
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-2Prey}
	\caption{Population distribution of mimicry rings, initialized with 2 prey species.}
\end{figure}

\paragraph{}
The above plot is simulation time verses prey population after running it for above 10000 iterations. With the initial configuration in the above table we can observe that multiple rings of prey population has been created. Two prey species are in a ring if their CA pattern have a hamming distance within 10 bits. Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve. Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population. The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.

\paragraph{}
By closely observing the graph we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species. At around time 1000 the prey population starts reproducing as the population increases. At around the same time different other species of prey population gets to be born with mutated CA patterns. Over time the population of CA Rule 110 dominates the population as most predators recognizes it as unpalatable. And similarly a population of CA Rule 110 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 30 (Time: 5000 approx.) which was initially considered as a set of palatable species.

\paragraph{}
We can observe from the above results that the evolution of mimicry has taken effect. A population of mimics were successfully able to exceed the population of other prey species the reason being avoidance by predators of prey pattern similar to unpalatable ones. We can conclude that Batesian mimicry has taken effect in the simulation.

\paragraph{}
The above configuration is also the most appropriate condition for Mullerian Mimicry. We can observe that a single pattern of unpalatable species dominate the entire population. These effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviours of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.

%Put the number of rings picture:
\begin{figure}
	\centering
	\includegraphics[scale=0.40]{images/ringSize10k-2Prey}
	\caption{Number of mimicry rings, initialized with 2 prey species.}
\end{figure}

\paragraph{}
The number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations. We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented. For example if we observe the following set of patterns genotype with very different phenotype:

%CARule table

\paragraph{}
All the above set of patterns have a genetic bit difference of 1. So by a single mutation there can be three different set of phenotype for a child organism from its parent. This is largely the reason for the increased number of Rings created in the simulation. Only the 8 most populous rings have presented in the graph above with population verses simulation time.

%Screenshot of the simulation
\begin{figure}
	\centering
	\includegraphics[scale=0.50]{images/simTime7600}
	\caption{Graphical representation of the model, simulation time: 7600.}
\end{figure}

\paragraph{}
The above screen shot is for one instance of time of the simulation. The red agents are predators while the black agents with different textured patterns are the prey species. According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.

\section{Initial configuration with four prey species}

\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}
\paragraph{}

### 2010-08-04 docs/tex/result.tex
Documentation update

@@
 % Put the table here
+\begin{table}
+\centering
+\caption{Agent configuration of 2 prey species}
+\label{tab:config-table-2-prey}
 \begin{tabular}{|l|l|c|c|l|c|}
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \includegraphics[scale=0.50]{images/CARule110} & 108 & \multicolumn{2}{|c|}{10} \\ \cline{2-4}
-  					 									& Rule30 (Unpalatable)& \includegraphics[scale=0.50]{images/CARule30}  & 108 & \multicolumn{2}{|c|}{}\\ \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \includegraphics[scale=0.50]{images/CARule110} & 108 
+  														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
+  					 									& Rule30 (Unpalatable)& \includegraphics[scale=0.50]{images/CARule30}  & 108 
+  					 									& \multicolumn{2}{|c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
   						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{0.03} \\ \cline{2-4}
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
@@
    																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
-
 \end{tabular}
+\end{table}
 
 \paragraph{}
-The above set of parameters were carefully selected to be the initial condition for this run of the simulation.
+The set of parameters in Table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
 This test has been done with two sets of prey species with very different CA pattern and with opposite palatability and equal population.
@@
 	\caption{Population distribution of mimicry rings, initialized with 2 prey species.}
+	\label{fig:plot-2-prey}
 \end{figure}
@@
 \paragraph{}
-The above plot is simulation time verses prey population after running it for above 10000 iterations.
+The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for above 10000 iterations.
 With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
@@
 \paragraph{}
-The above configuration is also the most appropriate condition for Mullerian Mimicry.
+The above configuration in Table \ref{tab:config-table-2-prey} is also the most appropriate condition for Mullerian Mimicry.
 We can observe that a single pattern of unpalatable species dominate the entire population.
-These effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviours of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.
+These effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviors of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.
 
@@
 	\caption{Number of mimicry rings, initialized with 2 prey species.}
+	\label{fig:ringSize10k-2Prey}
 \end{figure}
@@
 \paragraph{}
-The number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations.
+As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations.
 We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
@@
 %CARule table
+\begin{table}
+\centering
+\caption{Difference in prey pattern genotype and phenotype}
+\label{tab:diff-in-pattern}
+\begin{tabular}{|l|c|c|c|}
+  \hline
+  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
+  Pattern & \includegraphics[scale=0.50]{images/CARule60} & \includegraphics[scale=0.50]{images/CARule61} & \includegraphics[scale=0.50]{images/CARule62}\\
+  \hline
+\end{tabular}
+\end{table}
 
 \paragraph{}
-All the above set of patterns have a genetic bit difference of 1.
+All the patterns in Table \ref{tab:diff-in-pattern} have a genetic bit difference of 1.
 So by a single mutation there can be three different set of phenotype for a child organism from its parent.
@@
 	\centering
-	\includegraphics[scale=0.50]{images/simTime7600}
+	\label{fig:screenshot-simTime7600-2-prey}
+	\includegraphics[scale=0.65]{images/simTime7600}
 	\caption{Graphical representation of the model, simulation time: 7600.}
@@
 \paragraph{}
-The above screen shot is for one instance of time of the simulation.
+The screen shot in Figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
 The red agents are predators while the black agents with different textured patterns are the prey species.

### 2010-08-04 docs/tex/application.tex
Documentation update

@@
 
-\paragraph{}
 The biggest challenge faced while searching for the appropriate problem to be optimized is the idea of associating palatability with CA pattern with which the prey species has been represented.
@@
 
-\paragraph{}
 If the predator associates the CA pattern with palatability then it does not make any sense of having a mimic in the solution space as mimics will have the same pattern with opposite palatability.

### 2010-08-04 docs/tex/model.tex
Documentation update

@@
 \chapter{Modeling the evolution of mimicry}
+
+\section{Past Work}
+
+\subsection{Sherratt's Model}
+
+\subsection{Models by Frank and Noble}
+
+\section{FormAL Framework}
+
+\subsection{Spatial representation of the environment}
+
+\subsection{3D Visualization}
+
+\subsection{Agents}
+
+\subsection{Mobility}
+
+\section{Mimics and Model}
+
+\subsection{Pattern representation by Cellular Automata}
+
+\subsection{Species diversity}
+
+\subsection{Genetic representation of palatability}
+The palatability of each prey species is fixed and has been represented with 2 bit of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+			Gene (Index 8 to 9) &	Palatable \\ \hline
+			00									& True 			\\ \hline
+			01									& True 			\\ \hline
+			10									& False 		\\ \hline
+			11									& False 		\\
+		\hline
+	\end{tabular}
+	\caption{Genetic representation of Palatability}
+	\label{tab:genetic-representation-palatability}
+\end{table}
+
+This representation in Table \ref{tab:genetic-representation-palatability} is unlike \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+
+\subsection{Interaction between Mimics and Models}
+
+\subsection{Interaction with predators}
+
+\section{Predator}
+
+\subsection{Learning}
+
+\subsubsection{Hebbian Learning}
+
+\subsection{Design of Memory with Hopfield Network}
+
+\subsubsection{Hopfield Network}
+
+\subsection{Genetic representation of mobility and reproduction capability}
+Each predator in the simulation has a genetic representation. The genome of the predator is represented with a 5 bits binary value.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+			\multicolumn{4}{|c|}{Mobility} &	Reproduction Capability \\ \hline
+			1	& 0 &	1	& 0 								&	1\\
+		\hline
+	\end{tabular}
+	\caption{Genetic representation of Mobility and Reproduction capability}
+	\label{tab:genetic-representation-mobility-reproduction}
+\end{table}
+
+Movement behavior of a Predator calculated from its Genome.
+The first 4 bits of the genome of this species are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of Prey present within its neighborhood.
+So mobility of a predator varies within a range of 0-15 units.
+If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells.
+A predator chooses the neighborhood cell which contains the least number of predators.
+When the neighborhood contains zero predators, it would select any one of them randomly and move towards that cell.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/predators-40}
+	\caption{A population of 40 predators distributed over the environment.}
+	\label{fig:predators-40}
+\end{figure}
+
+The screen shot in Figure \ref{fig:predators-40} is from the simulation with only 40 predator species.
+It is presented to show the behavior of predator species in the simulation in absence of any prey species.
+As it can be observed the predator are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
+This behavior of predator has been designed to enforce the predatory behavior of this species and also to have increase predator prey interaction in the simulation in terms of one species chasing the other for search of food.
+
+The  fifth gene of the predator is used to represent their capability of reproduction.
+Depending on its binary value a predator in the simulation will or will not be able to reproduce in the simulation.
+
+\subsection{Reproduction process}
+The reproduction process for predators is similar to prey species.
+As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability behavior takes effect in the reproductive process of predator species from one generation to another.
+
+There are two control parameters that effect reproduction of predator species in the simulation.
+The first is the "Reproduction Age Limit".
+This the minimum age a predator has to reach before starting to involve itself for reproduction.
+This parameter has been set to 500 iterations during the result and analysis section of the thesis.
+The second parameter is "Reproduction Interval" which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatability of the prey species.
+This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment.
+Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.
+
+When the above two conditions are met, meaning the predator reaches it age for reproduction and also crosses every age interval, it randomly select another predator residing in the same cell.
+If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species in born which also resides on the same cell and initializes with zero memory configuration.
+Similarly when the new born predator reaches its maturity of reproductive age and if its capable to reproduce then the process iterates itself.
+
+\subsection{Interaction with Models and Mimics}

### 2010-08-04 docs/tex/result.tex
Documentation update

@@
 \chapter{Results and Analysis}
-
 \section{Initial configuration with two prey species}
-
 % Put the table here
-\begin{table}
+\begin{table}[H]
 \centering
@@
    														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \includegraphics[scale=0.50]{images/CARule110} & 108 
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
   														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Unpalatable)& \includegraphics[scale=0.50]{images/CARule30}  & 108 
+  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
   					 									& \multicolumn{2}{|c|}{}\\ \hline
@@
 
-\paragraph{}
 The set of parameters in Table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
@@
 
-\paragraph{}
 Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation.
@@
 
-\paragraph{}
 Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500.
@@
 
-\paragraph{}
 Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation.
@@
 
-\paragraph{}
 The memory configuration size for predators are a very interesting parameter.
@@
 
-\paragraph{}
 Now as we know the behaviour of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
@@
 % Put the image
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 
-\paragraph{}
 The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for above 10000 iterations.
@@
 
-\paragraph{}
 By closely observing the graph we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species.
@@
 
-\paragraph{}
 We can observe from the above results that the evolution of mimicry has taken effect.
@@
 
-\paragraph{}
 The above configuration in Table \ref{tab:config-table-2-prey} is also the most appropriate condition for Mullerian Mimicry.
@@
 %Put the number of rings picture:
-\begin{figure}
+\begin{figure}[H]
 	\centering
-	\includegraphics[scale=0.40]{images/ringSize10k-2Prey}
+	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
 	\caption{Number of mimicry rings, initialized with 2 prey species.}
@@
 
-\paragraph{}
 As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations.
 We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
-For example if we observe the following set of patterns genotype with very different phenotype:
+For example if we observe the set of pattern genotype with very different phenotype in Table \ref{tab:diff-in-pattern}.
 
 %CARule table
-\begin{table}
+\begin{table}[H]
 \centering
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \includegraphics[scale=0.50]{images/CARule60} & \includegraphics[scale=0.50]{images/CARule61} & \includegraphics[scale=0.50]{images/CARule62}\\
+  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule60}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule61}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule62}}\\
   \hline
@@
 
-\paragraph{}
 All the patterns in Table \ref{tab:diff-in-pattern} have a genetic bit difference of 1.
@@
 %Screenshot of the simulation
-\begin{figure}
+\begin{figure}[H]
 	\centering
 	\label{fig:screenshot-simTime7600-2-prey}
-	\includegraphics[scale=0.65]{images/simTime7600}
+	\includegraphics[scale=0.55]{images/simTime7600}
 	\caption{Graphical representation of the model, simulation time: 7600.}
@@
 
-\paragraph{}
 The screen shot in Figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
@@
 \section{Initial configuration with four prey species}
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 4 prey species}
+\label{tab:config-table-4-prey}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  																										& 50 & \multicolumn{2}{|c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
+  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}
+  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}
+  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}
+  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1400} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
 
-\paragraph{}
-\paragraph{}
-\paragraph{}
-\paragraph{}
-\paragraph{}
-\paragraph{}
-\paragraph{}
+This run of the simulation has been initialized with four prey species with very different CA pattern configuration.
+The predator reproduction interval has been increased to 1400, while the minimum memory size has been increased to 4 instead of 2 as the predator is expected to memorize four different species of prey before starting to make intelligent decision about consuming them.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
+	\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
+	\label{fig:plot-4-prey}
+\end{figure}
+
+By observing the graph in Figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species which was put at the initial sate of the simulation has dominated after 10000 iterations.
+CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve).
+Also the palatable prey species with similar patterns to CA rule 55 and 110 are taking full advantage of their deceiving pattern and increasing their population (represented with line curve).
+The two unpalatable set of patterns CA Rule 90 and 130 are unable to dominate the population.
+Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in Figure \ref{fig:ringSize10k-4Prey}, the total number of rings reached somewhere near 33 while each of them has comparatively low representative population.
+Batesian mimicry is in full effect in this simulated environment.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
+	\caption{Number of mimicry rings, initialized with 4 prey species.}
+	\label{fig:ringSize10k-4Prey}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\label{fig:screenshot-simTime11K-4Prey}
+	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
+	\caption{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
+\end{figure}
+
+\section{Increased initial population with four prey species}
+
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 4 prey species with increased population}
+\label{tab:config-table-4-more-prey}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  	 & 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}  & 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+In this run of the simulation some significant parameters have been updated.
+One is the initial population of prey species.
+It has been increased from 50 to 150 for each of the prey species increasing the overall population from 200 to 600.
+Secondly the number of predator population has been increased from 20 to 30.
+Thirdly, Predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
+Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will increased selection pressure from the entire population of predators.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime9K-4MorePrey}
+	\caption{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
+	\label{fig:plot-4-more-prey}
+\end{figure}
+
+Some very interesting diversity of rings can be observed in the simulation for updating the parameters.
+The unpalatable rings and their deceptive counterparts(palatable prey with similar pattern) still have their dominance.
+We can observe CA Rule 55 and 190 are the highest number of population.
+Interestingly enough CA Rule 110 which started as a palatable prey species has also taken dominance in the population which is the second highest.
+Both palatable and unpalatable version of CA Rule 110 are present with equal population density.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize10k-4MorePrey}
+	\caption{Number of mimicry rings, initialized with 4 prey species with increased population.}
+	\label{fig:ringSize10k-4MorePrey}
+\end{figure}
+
+The total number of rings had much increment in this run compared to the previous one.
+To summarize we can observe increased diversity of prey population and much more interaction between predators and prey.
+
+\section{Initial population with six prey species}
+
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 6 prey species.}
+\label{tab:config-table-6-prey}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  																									& 150 & \multicolumn{2}{|c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
+  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}} 
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule57}}    
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule105}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 6 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime10k-6Prey}
+	\caption{Population distribution of mimicry rings, initialized with 6 prey species.}
+	\label{fig:plot-6-prey}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
+	\caption{Number of mimicry rings, initialized with 6 prey species.}
+	\label{fig:ringSize10k-6-Prey}
+\end{figure}
+
+\section{Initial configuration with only unpalatable species}
+
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 4 prey species all unpalatable.}
+\label{tab:config-table-4-prey-unpalatable}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{30}} \\ \cline{2-4}
+  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-unp}
+	\caption{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\label{fig:plot-4-prey-unp}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize9k-4Prey-unp}
+	\caption{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\label{fig:ringSize10k-4-Prey-unp}
+\end{figure}
+
+\section{Initial configuration with only palatable species}
+
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 4 prey species all palatable.}
+\label{tab:config-table-4-prey-palatable}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{30}} \\ \cline{2-4}
+  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
+	\caption{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
+	\label{fig:plot-4-prey-p}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
+	\caption{Number of mimicry rings, initialized with 4 prey species all palatable.}
+	\label{fig:ringSize8k-4-Prey-p}
+\end{figure}
+
+\section{Initial configuration with single prey species}
+
+\subsection{Unpalatable}
+
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 1 prey species unpalatable.}
+\label{tab:config-table-1-prey-unpalatable}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
+  																									& 216 & \multicolumn{2}{|c|}{10} \\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
+	\caption{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
+	\label{fig:plot-1-prey-unp}
+\end{figure}
+
+From unpalatable species we see a bunch of rings with majority of unpalatable species created.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
+	\caption{Number of mimicry rings, initialized with 1 prey species unpalatable.}
+	\label{fig:ringSize8k-1-Prey-unp}
+\end{figure}
+
+\subsection{Palatable}
+\begin{table}[H]
+\centering
+\caption{Agent configuration of 1 prey species palatable.}
+\label{tab:config-table-1-prey-palatable}
+\begin{tabular}{|l|l|c|c|l|c|}
+  \hline
+   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
+  																									& 216 & \multicolumn{2}{|c|}{8} \\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
+   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime9k-1-p}
+	\caption{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
+	\label{fig:plot-1-prey-p}
+\end{figure}
+
+From Palatable population we see a bunch of palatable rings created. 
+Major difference is the total number of prey population created.
+For unpalatable species total population reaches above 12 thousand.
+But for palatable species total population reaches nearly above 5000.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
+	\caption{Number of mimicry rings, initialized with 1 prey species palatable.}
+	\label{fig:ringSize8k-1-Prey-p}
+\end{figure}

### 2010-08-07 docs/tex/model.tex
Thesis: updates to predator description

@@
 
+\section{Introduction}
+%Entire section until past work needs to be revised when the model has been fully described.
+The objective of this thesis is to design an agent based artificial life model for simulating the natural process of the evolution of mimicry.
+
+There are mainly two species of agents.
+These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry.
+We represent evolution of pattern for the model and the mimic with the help of Cellular Automata(CA).
+Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string.
+The predator will be equipped with a Hopfield network, to be able to have pattern recognition capability.
+The process of evolution will of course be running at the genetic level.
+
+The choice of Hopfield Network memory for a predator can be considered appropriate as the number of patterns which can be recognized by this network is inversely proportional to the accuracy of recall.
+As more patterns are memorized, Hopfiled network tends to make more errors.
+This behavior will be appropriate for the simulation of Mullerian mimicry.
+Mullerian mimicry happens because of limited memory of the predators.
+Because of this limited memory, multiple inedible butterflies seems to converge to a single ring.
+
+The environment will be designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the Laws and Life project by Peter Grogono \cite{grogono2003}.
+
 \section{Past Work}
+Various models of mimicry has been simulated and explored.
+The model by Turner \cite{turner1996} and the mathematical model of Huheey \cite{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.
 
-\subsection{Sherratt's Model}
+Sherratt \cite{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations.
+The model's predators are deterministic, in that they have a fixed behavioral strategy over their lifetime, and cannot learn from experience.
+For both cryptic and conspicuous prey, each predator has fixed policy of either attacking or avoiding.
+
+The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Frank and Noble.
+Their initial work \cite{franks2002} seems of focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
+
+On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Frank and Noble.
+Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics.
+So an evolutionary simulation to observe the above mentioned phenomenon has been presented in this piece of work.
+
+Frank and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}.
+Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
+In this model prey colorations are free to evolve.
+This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.
 
 \subsection{Models by Frank and Noble}
+%Explain more about the first model by Frank and Noble
+The first model by Frank and Noble \cite{franks2002} is where ``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed." Each individual had a single gene: a value representing their external appearance or phenotype.
+The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors).
+The distance of one phenotype from another represents their levels of similarity.
+
+A single abstract predator was modeled with a simple reinforcement learning system.
+The predator's experience of each phenotype was represented by a score, which would be maintained by probability to consume the next prey species depending on similarity or difference in phenotype.
+
+The existence of mimetic effect were measured with the initial and final distances between prey species' phenotypes.
+Three experiments were noted.
+Firstly, with one palatable and one unpalatable species.
+For this Batesian mimicry was evolved.
+For the second experiment, with two unpalatable species, Mullerian mimicry was evolved if the two prey species have some initial resemblance.
+Experiment 3 was carried out with two unpalatable and one palatable species, where the phenotype of the palatable species moved towards that of one of the unpalatable species, which is in other words Batesian Mimicry.
+
+\paragraph{}
+The second model by Frank and Noble \cite{franks2003} is based on two working hypothesis:
+
+\begin{itemize}
+	\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
+	\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
+\end{itemize}
+
+Although there are many mathematical and stochastic models of mimicry in the biological literature, this model gives attention to the evolution of mimicry ring phenomenon from an artificial life perspective.
+
+%\subsubsection{Model Description}
+\paragraph{Prey}
+Similar to the first model this also contains a population of prey species each having an appearance and palatability level.
+Different species of prey were each assigned a fixed palatability level on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+Palatable species have values greater than 0.5, and unpalatable species have values lower than 0.5.
+Each prey species has used two genes with values compositely representing their external appearance or phenotype.
+Both of these genes were constrained to values from 1 - 200.
+The Euclidean distance of one phenotype from another represented their level of similarity.
+
+\paragraph{Predator}
+Similar to Turner's stochastic model \cite{turner_et_al1984},  predators were modeled with a Monte Carlo reinforcement learning system.
+The predator's experience of each phenotype was represented by an attack probability, which was initialized to ambivalence at 0.5.
+After eating prey of a particular phenotype, the predator would make a post-attack update of the relevant probability according to the palatability of the prey consumed.
+The predator would use its experience of different prey appearances to help it decide on whether or not to attack at the next opportunity.
+
+In contrary to the stochastic model \cite{turner_et_al1984},  predators would generalize on the basis of experience.
+A set of probability formula was used to come up with the current probability to consume a prey species based on its palatability and the previous probability of consumption based on experience using generalization rate and the Euclidean distance between the experienced phenotype and the consumed prey phenotype.
+
+%Explain the results for the second model by Frank and Noble
+\paragraph{Results}
+According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established.
+Their was existence of multiple mimicry rings of very different frequency.
+Second experiment was carried out with some palatable species along with the unpalatable once which was able able to reach conditions of Batesian mimicry also with less mimicry rings, were hypothesis 2 borne out.
+
+\begin{quote}
+\textsl{The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
+Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them.}
+\end{quote}
 
 \section{FormAL Framework}
+The FormAL framework is a collection of ideas and concepts taken from \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The framework consists of a 3-D visual environment where agents of the individual based simulation gets complete freedom of movement following a certain pattern.
 
@@
 
-\section{Mimics and Model}
+\section{The Prey: Mimics and Models}
 
@@
 \subsection{Species diversity}
+Franks and Noble have used different models to diversify species.
+In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
+Here the distance of one phenotype from another represents their level of similarity.
 
@@
 \subsection{Learning}
+The objective of a predator's interaction with the prey is always to consume it.
+But based on the species of the prey and depending on its palatability, the predator will either be able to consume it or to throw it back to the environment.
+At this event the predator needs to learn the pattern with which the prey has been represented.
+The pattern represents palatability of the prey species, at least to the predator.
+To store this new pattern into memory, each predator is equipped with a Hopfield Network Memory.
+Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
+The learning procedure used for this memory will be Hebbian Learning.
 
 \subsubsection{Hebbian Learning}
+\textit{Hebb's postulate of learning} is the oldest and most famous of all learning rules; it is named in honor of the neuropsychologist Donald Hebb(1949).
+Hebb's book \textit{The Organization of Behavior} (1949) states the following (p.62):
+
+\begin{quote}
+\textsl{When an axon of cell A is near enough to excite a cell B and repeatedly or persistently takes part in firing it, some growth process or metabolic changes take place in one or both cells such that A's efficiency as one of the cells firing B is increased.}
+\end{quote}
+
+The following \textit{general learning rule} is adopted in neural network studies: \textit{The weight vector} \( \textbf{w}_i = [w_{i1} \> w_{i2} \> ...
+\> w_{in}]^t \) \textit{increases in proportion to the product of input} \textbf{x} \textit{and learning signal r}.
+The learning signal r is in general a function of \(\textbf{w}_i,\textbf{x}\), and sometimes of the teacher's signal \(d_i\).
+Thus we have,
+
+\begin{equation}
+	r = r(\textbf{w}_i,\textbf{x},d_i)
+%\label{eq:}
+\end{equation}
+
+The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
+
+\begin{equation}
+	\Delta\textbf{w}_i(t)=cr[\textbf{w}_i(t),\textbf{x}(t),d_i(t)]\textbf{x}(t)
+%\label{eq:}
+\end{equation}
+
+when c is a positive number called the \textit{learning constant} that determines the rate of learning.
+
+For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
+
+\begin{equation}
+	r \overset{\Delta}{=} f(\textbf{w}_i^t \textbf{x})
+%\label{eq:}
+\end{equation}
+
+The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
+
+\begin{equation}
+	\Delta\textbf{w}_i = cf(\textbf{w}_i^t \textbf{x})\textbf{x}
+%\label{eq:}
+\end{equation}
+
+The single weight \( w_{ij} \) is adapted using the following increment:
+
+\begin{equation}
+	\Delta\textit{w}_{ij} = cf(\textbf{w}_i^t \textbf{x})x_j
+%\label{eq:}
+\end{equation}
+
+This can be written briefly as
+
+\begin{equation}
+	\Delta\textit{w}_{ij} = c o_i x_j, \> for \> j = 1, 2, ..., n
+%\label{eq:}
+\end{equation}
+
+The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning.
+The Hebbian learning rule represents a purely feed-forward, unsupervised learning.
+The rule implements the interpretation of the classic \textit{Hebb's postulate of learning} stated above.
+
+The rule states that if the cross product of output and input, or correlation term \(o_ix_j\) is positive, this results in an increase of weight \(w_{ij}\); otherwise the weight decreases.
+It can be seen that the output is strengthened in turn for each input presented.
+Therefore, frequent input patterns will have most influence at the neuron's weight vector and will eventually produce the largest output.
+
+Training for Hopfield Network used for predator's memory is done by Hebbian Learning.
+Initially the weights are all set to zero.
+Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern.
+As Hopfield is a feedback network, the output of the network is also the input.
+The outer vector matrix of all the patterns are summed to come up with the final weight matrix.
+Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
+
+\begin{equation}
+w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
+%\label{eq:}
+\end{equation}
+
+\[
+w_{ij} = 0, i = j
+\]
+
+where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
 
 \subsection{Design of Memory with Hopfield Network}
+
+\subsubsection{Input to memory}
+Each prey will contain an evolving cellular automata which will be represented by a binary gene.
+This two dimensional pattern will be serialized to be available as a one dimensional binary array, which will be taken as input for any predator organism trying to interact with the prey.
+This binary representation of the pattern will have to be converted to a bipolar representation.
+Each input pattern will consist of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
+The \textit{m} by \textit{n} pattern configuration will be flattened by putting all row vectors in one single row sequentially.
 

### 2010-08-10 docs/tex/model.tex
Documentation update.

@@
 
-\begin{itemize}
+\begin{enumerate}
 	\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
 	\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
-\end{itemize}
+\end{enumerate}
 
@@
 \section{FormAL Framework}
-The FormAL framework is a collection of ideas and concepts taken from \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
-The framework consists of a 3-D visual environment where agents of the individual based simulation gets complete freedom of movement following a certain pattern.
+The ``FormAL framework" is a collection of ideas and concepts taken from Peter Grogono's FormAL(Formal Artificial Life) project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}".
+While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}".
+We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.
+
+\subsection{Agents}
+In FormAL, an \textbf{Agent} is a simulated organism. It is designed simply, but with the following qualities:
+
+\begin{itemize}
+	\item It has behaviors to be able to reproduce itself using genetic information.
+	\item Capable of modifying the structure of genome between generations.
+	\item Able to interact with other agents.
+	\item And also to survive and reproduce in a challenging environment.
+\end{itemize}
 
 \subsection{Spatial representation of the environment}
+The framework consists of a three dimensional visual environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.
 
-\subsection{3D Visualization}
+\paragraph{Space}
+The space of the environment is a three-dimensional lattice of discrete points.
+The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
+\(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in Table \ref{tab:environment-control-parameters}).
 
-\subsection{Agents}
+\paragraph{Time}
+Time, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.
+
+\paragraph{Cell}
+The entire three dimensional toroidal environment is divided in multiple cells.
+A cell is a three dimensional cubical section of the hyperspace.
+Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
+The size of a cell is evaluated from the entire world size.
+And the total number of cell is calculated as \(ISize^3 = 216\).
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{3cm} | p{7.5cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		ISize & 6 & \\ \hline
+		World Size & 20 & \\ \hline
+		Cell Size & \( World Size / ISize \) & \\ \hline
+		Total Number of Cells & \( ISize^3  = 216\) & \\ 
+	\hline
+\end{tabular}
+\caption{Parameters to control the environment.}
+\label{tab:environment-control-parameters}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{cc}
+		\multicolumn{2}{c}{ \includegraphics[scale=0.50]{images/cells-front} } \\
+		\includegraphics[scale=0.40]{images/cells-top} & \includegraphics[scale=0.40]{images/cells-side} \\
+\end{tabular}
+\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
+\label{tab:3-d-environment-images}
+\end{table}
 
 \subsection{Mobility}
+An agents position is calculated once during each step of update in time.
+The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
+The \(force\) component is calculated from agent's mobility gene.
+And it is used to compute agent's \(acceleration\).
+If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion.
+Otherwise, Newton's law is used to obtain the \(acceleration\), which is integrated to obtain the new \(velocity\) and new \(position\).
+
+\begin{algorithm}
+	\caption{Algorithm for updating movement of the Agents}
+	\label{algo:algorithm-movement-agents}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\STATE $accelaration \gets ForceFactor * force - Friction * velocity$
+			\STATE $velocity \gets DT*accelaration$ \COMMENT{DT is considered as Differential Time Set}
+			\STATE $deltaPos \gets DT*velocity$
+			\STATE $position \gets position + deltaPos$
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{1.3cm} | p{9cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
+		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
+		Friction & 5 & The friction constant used for motion calculations.\\ \hline
+		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
+	\hline
+\end{tabular}
+\caption{Parameters to control mobility of agents.}
+\label{tab:mobility-control-parameters}
+\end{table}
+
+Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while Table \ref{tab:mobility-control-parameters} contains the values of the parameters used for this simulation.
 
 \section{The Prey: Mimics and Models}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{1.5cm} | p{9cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
+		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
+		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
+		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
+		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
+		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
+	\hline
+\end{tabular}
+\caption{Parameters to control prey population and visibility.}
+\label{tab:prey-control-parameters}
+\end{table}
+
+\subsection{Genome}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|c|c|c|}
+	\hline
+		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
+		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
+\end{tabular}
+\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
+\label{tab:prey-genome}
+\end{table}
 
@@
 		\hline
-			Gene (Index 8 to 9) &	Palatable \\ \hline
+			\textbf{Gene (Index 8 to 9)} &	\textbf{Palatable} \\ \hline
 			00									& True 			\\ \hline
@@
 
+Predators in the system are designed to provide selection pressure to \textit{models} and \textit{mimics} for the evolution of mimicry.
+Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction.
+In addition to that these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
+Their mobility and reproduction capability is controlled at the genetic level, but their memory is not, as it was not possible to come up with a genetic representation for Hopfield Network.
+A set of parameters are defined to control predators' population and learning ability in the environment.
+Details of the parameters are given in Table \ref{tab:predator-control-parameters}.
+
+\subsection{Genome}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|c|}
+	\hline
+		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
+				 1101					   &					1						 		\\ \hline
+\end{tabular}
+\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
+\label{tab:predator-genome}
+\end{table}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{2.2cm} | p{8cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
+		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
+		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
+Usually the network reaches a steady state before that.
+But this restriction is to avoid infinite loop in case the network never reaches a steady state.
+\\ \hline
+		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
+		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
+		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
+		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
+		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
+		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
+	\hline
+\end{tabular}
+\caption{Parameters to control predator population and pattern recognition capability.}
+\label{tab:predator-control-parameters}
+\end{table}
+
+\subsection{Interaction with Models and Mimics}
+
 \subsection{Learning}
@@
 Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
-The learning procedure used for this memory will be Hebbian Learning.
+The learning procedure used for this memory is Hebbian Learning.
 
@@
 \begin{equation}
-	\Delta\textit{w}_{ij} = c o_i x_j, \> for \> j = 1, 2, ..., n
+	\Delta\textit{w}_{ij} = c o_i x_j, \> \text{for} \> j = 1, 2, ..., n
 %\label{eq:}
@@
 
+\subsubsection{Hopfield Network}
+
+Algorithm for the Hopfield model is described in the following:
+
+\begin{enumerate}
+	\item \textit{Learning.} Let \( \boldsymbol{\xi}_1, \boldsymbol{\xi}_2, ..., \boldsymbol{\xi}_{\mu} \) denote a known set of N-dimensional fundamental memories.
+Use the outer-product rule (i.e.
+Hebb's postulate of learning) to compute the synaptic weights of the network as
+
+	\begin{equation}
+		w_{ji} =
+			\begin{cases}
+				\frac{1}{N} \sum_{\mu=1}^{M}\xi_{\mu,j}\xi_{\mu,i}	& j \neq i \\
+				0																										& j = i 
+			\end{cases}
+	%\label{eq:}
+	\end{equation}
+
+	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\).
+The elements of the vector \( \boldsymbol{\xi}_\mu \) equal \(\pm 1\) (bipolar).
+Once they are computed, the synaptic weights are kept fixed.
+
+	\item \textit{Initialization.} Let \( \boldsymbol{\xi}_{probe} \) denote an unknown N-dimensional input vector (probe) presented to the network. The algorithm is initialized by setting
+	\begin{equation}
+		x_j(0) = \xi_{j,probe}, \> j = 1,...,N
+	%\label{eq:}
+	\end{equation}
+
+	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).
+
+	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
+
+	\begin{equation}
+		x_j(n+1)=sgn \Bigg(\sum_{i=1}^{N} w_{ji}x_i(n) \Bigg), \> j = 1,2, ..., N
+	%\label{eq:}
+	\end{equation}
+
+	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.
+
+	\item \textit{Outputting.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
+
+	\begin{equation}
+		\boldsymbol{y} = \boldsymbol{x}_{fixed}
+	\label{eq:}
+	\end{equation}
+
+	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
+\end{enumerate}
+
 \subsubsection{Input to memory}
@@
 The \textit{m} by \textit{n} pattern configuration will be flattened by putting all row vectors in one single row sequentially.
-
-\subsubsection{Hopfield Network}
 
@@
 Similarly when the new born predator reaches its maturity of reproductive age and if its capable to reproduce then the process iterates itself.
-
-\subsection{Interaction with Models and Mimics}

### 2010-08-10 docs/tex/model.tex
Documentation update

@@
 		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		ISize & 6 & \\ \hline
-		World Size & 20 & \\ \hline
-		Cell Size & \( World Size / ISize \) & \\ \hline
-		Total Number of Cells & \( ISize^3  = 216\) & \\ 
+		ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
+		World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
+		Cell Size & \( World Size / ISize \) & Size of each cell\\ \hline
+		Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
 	\hline
@@
 
-Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while Table \ref{tab:mobility-control-parameters} contains the values of the parameters used for this simulation.
+Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while Table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.
 
 \section{The Prey: Mimics and Models}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{1.5cm} | p{9cm} |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
-		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
-		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
-		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
-		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
-		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
-	\hline
-\end{tabular}
-\caption{Parameters to control prey population and visibility.}
-\label{tab:prey-control-parameters}
-\end{table}
 
@@
 
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{1.5cm} | p{9cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
+		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
+		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
+		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
+		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
+		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
+	\hline
+\end{tabular}
+\caption{Parameters to control prey population and visibility.}
+\label{tab:prey-control-parameters}
+\end{table}
+
 \section{Predator}
@@
 \label{tab:predator-genome}
-\end{table}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{2.2cm} | p{8cm} |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
-		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
-		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
-Usually the network reaches a steady state before that.
-But this restriction is to avoid infinite loop in case the network never reaches a steady state.
-\\ \hline
-		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
-		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
-		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
-		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
-		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
-		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
-	\hline
-\end{tabular}
-\caption{Parameters to control predator population and pattern recognition capability.}
-\label{tab:predator-control-parameters}
 \end{table}
@@
 Similarly when the new born predator reaches its maturity of reproductive age and if its capable to reproduce then the process iterates itself.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.2cm} | >{\centering} p{2.2cm} | p{8cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
+		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
+		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
+Usually the network reaches a steady state before that.
+But this restriction is to avoid infinite loop in case the network never reaches a steady state.
+\\ \hline
+		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
+		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
+		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
+		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
+		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
+		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
+	\hline
+\end{tabular}
+\caption{Parameters to control predator population and pattern recognition capability.}
+\label{tab:predator-control-parameters}
+\end{table}
+
+\section{Conclusion}

### 2010-08-12 docs/tex/model.tex
Chapter for Modelling the evolution of mimicry almost complete.

@@
 
+\subsection{Pattern representation by Cellular Automata}
+Only the significant characteristics which are required for a successful model of mimicry is implemented.
+As for this simulation we are considering heliconius butterfly, the representation of their wing pattern is with the help of cellular automata.
+So basically every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.
+
+%More content needs to be added for cellular automata.
+\subsubsection{Cellular Automata}
+
+Cellular automata are computer generated patterns applying very simple rules.
+First invented by Jon von Neuman and later extended by Stephen Wolfram, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules.
+We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=5]{images/CA_rule30s}
+	\caption{Cellular Automata Rule 30.
+	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
+	\label{fig:cellular-automata-rule-30}
+\end{figure}
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
+	  \hline
+	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
+	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
+	  \hline
+	\end{tabular}
+	\caption{Cellular Automata Rule}
+	\label{tab:cellular-automata-rule}
+\end{table}
+
+In generating the pattern of Figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the 'New state of center cell'.
+As Figure \ref{fig:cellular-automata-rule-30} is a rule 30 cellular automata, the eight bit binary representation of 30 would be the genetic representation for this pattern.
+Generation of automata pattern from this binary string can be considered analogous to the complex pathway between the genotype and the phenotype that exists in all living organism.
+
+\subsection{Species diversity}
+Franks and Noble have used different models to diversify species.
+In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
+Here the distance of one phenotype from another represents their level of similarity.
+
+To use CA as prey pattern, its genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
+Each of this 256 values have a unique CA pattern associated with it.
+When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.
+
+With CA based pattern representation, population of prey species with a specific CA pattern can be grouped as one single species.
+And by restricting inter species reproduction we can control the diversity of patterns.
+But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species.
+So that is why we have two separate mutation rate while reproducing prey species.
+One being the ``Pattern Mutation Rate" (default values are mentioned in Table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (Table \ref{tab:prey-genome}).
+
 \subsection{Genome}
+The Genome of the prey species consists of 17 bits as presented in Table \ref{tab:prey-genome}.
+The first eight bit is the rule, which is used to generate Cellular Automata pattern.
+The next two bits are used to represent palatability of the organism explained detail in Section \ref{sec:genetic-palatability-representation}.
+The next six bits is the force with which mobility of the organism is calculated.
+The 17th bit is used to evaluate reproduction capability of the organism, depending on which the prey species is either capable or not capable to participate in reproduction.
 
@@
 
-\subsection{Pattern representation by Cellular Automata}
-
-\subsection{Species diversity}
-Franks and Noble have used different models to diversify species.
-In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
-Here the distance of one phenotype from another represents their level of similarity.
-
 \subsection{Genetic representation of palatability}
+\label{sec:genetic-palatability-representation}
 The palatability of each prey species is fixed and has been represented with 2 bit of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
@@
 
-This representation in Table \ref{tab:genetic-representation-palatability} is unlike \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+This representation in Table \ref{tab:genetic-representation-palatability} is unlike Frank and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
 
-\subsection{Interaction between Mimics and Models}
+\subsection{Interaction between other Prey and Predators}
+The prey have been defined to have many conglomerate behavior in the environment.
+Prey interaction with other prey species and with predators make the evolution of mimicry possible.
+Mobility of prey species and their reproduction capability are two important behaviors which result from interaction.
 
-\subsection{Interaction with predators}
+\subsubsection{Mobility}
+The mobility genes of the prey consist of 6 bits.
+These six bits are used to calculate the force with which each prey try to move towards any neighborhood cell.
+The algorithm sorts all neighboring cell descending to the number of prey species.
+Then it selects the cell which contains the highest number of prey with zero predator.
+If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least.
+Algorithm \ref{algo:algorithm-movement-prey} explains in detail.
+
+\begin{algorithm}[H]
+	\caption{Algorithm for updating position of the Prey species}
+	\label{algo:algorithm-movement-prey}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
+			\STATE Get list of neighborhood cells, sorted by population of prey species.
+			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
+			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+\subsubsection{Reproduction}
+Every prey species starts reproducing when it reaches the ``Reproductive age limit".
+If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it.
+Now the other prey also needs to be genetically capable of reproduction and needs to reach its age limit.
+A new genome is created from the existing genome of the two prey by applying single point crossover operation.
+Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in Table \ref{tab:prey-control-parameters}.
+So there is two point mutation for the genome.
+
+\begin{algorithm}[H]
+	\caption{Algorithm for reproduction of the Prey species}
+	\label{algo:algorithm-reproduction-prey}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\STATE $capableToReproduce \gets$ true or false depending on the 17th bit of the genome, and maturity on reproduction age.
+			\IF {$capableToReproduce == true$ and $currentCellPopulation > 1$ } 
+				\STATE $anotherPrey \gets$ Select random prey from same cell.
+				\IF {$anotherPrey$ is alive and $capableToReproduce$ and of similar $pattern$ and $palatability$}
+					\STATE Perform genetic cross over and mutation to create new genome.
+					\STATE Create new prey with new genome, and release into environment.
+					\STATE Record reproduction time for both prey.
+				\ENDIF
+			\ENDIF
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
-\subsection{Genome}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{|c|c|}
-	\hline
-		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
-				 1101					   &					1						 		\\ \hline
-\end{tabular}
-\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
-\label{tab:predator-genome}
-\end{table}
-
-\subsection{Interaction with Models and Mimics}
-
 \subsection{Learning}
@@
 Thus we have,
-
 \begin{equation}
@@
 \end{equation}
-
 The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
-
 \begin{equation}
@@
 \end{equation}
-
 when c is a positive number called the \textit{learning constant} that determines the rate of learning.
@@
 For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
-
 \begin{equation}
@@
 \end{equation}
-
 The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
-
 \begin{equation}
@@
 \end{equation}
-
 The single weight \( w_{ij} \) is adapted using the following increment:
-
 \begin{equation}
@@
 \end{equation}
-
 This can be written briefly as 
-
 \begin{equation}
@@
 \end{equation}
-
 The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning.
@@
 Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
-
 \begin{equation}
@@
 \end{equation}
-
 \[
@@
 \]
-
 where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
@@
 Hebb's postulate of learning) to compute the synaptic weights of the network as
-
 	\begin{equation}
@@
 	\end{equation}
-
 	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\).
@@
 	\end{equation}
-
 	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).
@@
 	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
-
 	\begin{equation}
@@
 	\end{equation}
-
 	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.
@@
 	\item \textit{Outputting.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
-
 	\begin{equation}
@@
 	\end{equation}
-
 	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
@@
 \subsubsection{Input to memory}
-Each prey will contain an evolving cellular automata which will be represented by a binary gene.
-This two dimensional pattern will be serialized to be available as a one dimensional binary array, which will be taken as input for any predator organism trying to interact with the prey.
-This binary representation of the pattern will have to be converted to a bipolar representation.
+Each prey contains an evolving cellular automata which is represented by a binary gene.
+This two dimensional pattern is serialized to be available as a one dimensional binary array, which is taken as input for any predator organism trying to interact with the prey.
+This binary representation of the pattern gets converted to a bipolar representation.
 Each input pattern will consist of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
-The \textit{m} by \textit{n} pattern configuration will be flattened by putting all row vectors in one single row sequentially.
+The \textit{m} by \textit{n} pattern configuration will be serialized by putting all row vectors in one single row sequentially.
 
-\subsection{Genetic representation of mobility and reproduction capability}
-Each predator in the simulation has a genetic representation. The genome of the predator is represented with a 5 bits binary value.
+\subsubsection{Predator attack algorithm}
+As soon as a predator reaches its attack age it selects random prey species around its vicinity and starts attacking them.
+This attack process also involves recognition of prey pattern, which is at the heart of mimicry simulation for this research.
+Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive.
+The ``Hopfield Minimum Memory Size" (default value in Table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
+After a predator is born, it start attacking prey without any caution.
+But after every attack the predator will store its pattern and palatability level inside its memory.
+As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next species.
+It will try to recognize the pattern and if found palatable, prey will be consumed.
+Otherwise prey will be thrown back into the environment.
+If the pattern is not recognized predator will try to consume it and in the process will store its palatability and pattern into memory.
+
+In this way the predator memory is limited to ``Hopfield Maximum Memory Size".
+After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored.
+Algorithm \ref{algo:algorithm-attack-prey} and \ref{algo:algorithm-attemptToKill} explains the process in every detail.
+
+\begin{algorithm}
+	\caption{Algorithm for attacking Prey species}
+	\label{algo:algorithm-attack-prey}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\IF {Predator has reached Minimum attack age}
+				\STATE $preyToAttack \gets$ select random prey species from the same cell.
+				\IF {$currentMemorySize < MinimumMemorySize$}
+					\STATE $attemptToKill(preyToAttack);$ \COMMENT {Function defined in Algorithm \ref{algo:algorithm-attemptToKill}}
+				\ELSE
+					\STATE recognize $preyToAttack$ pattern from memory.
+					\IF {prey is not recognized or prey is palatable}
+						\STATE $attemptToKill(preyToAttack)$
+					\ELSE 
+						\STATE Prey is recognized as unpalatable, so release it back into environment.
+					\ENDIF
+				\ENDIF
+			\ENDIF
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+	\caption{$attemptToKill(preyToAttack)$}
+	\label{algo:algorithm-attemptToKill}
+	\begin{algorithmic}
+		\STATE Kill $preyToAttack$.
+		\IF {Memory size $< MaxMemorySize$}
+			\STATE Associate $preyToAttack$ pattern and palatability and store into memory.
+			\STATE Recalculate Hopfield Memory Weights using Hebbian Learning outer product rule.
+		\ENDIF
+	\end{algorithmic}	
+\end{algorithm}
+
+\subsection{Genome}
+Each predators has a 5 bit genome as explained in Table \ref{tab:predator-genome}.
+The first four bit represents its mobility and the magnitude of the force component with which it moves around the environment.
+The last bit controls reproduction capability of the specific species.
 
@@
 \centering
-	\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|}
 	\hline
-			\multicolumn{4}{|c|}{Mobility} &	Reproduction Capability \\ \hline
-			1	& 0 &	1	& 0 								&	1\\
-		\hline
+		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
+				 1101					   &					1						 		\\ \hline
 \end{tabular}
-	\caption{Genetic representation of Mobility and Reproduction capability}
-	\label{tab:genetic-representation-mobility-reproduction}
+\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
+\label{tab:predator-genome}
 \end{table}
 
-Movement behavior of a Predator calculated from its Genome.
-The first 4 bits of the genome of this species are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of Prey present within its neighborhood.
-So mobility of a predator varies within a range of 0-15 units.
+\subsection{Mobility and reproduction capability}
+Movement behavior of a predator is calculated from its genome.
+The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of prey present within its neighborhood.
+So magnitude of movement of a predator varies within a range of 0-15 units.
 If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells.
@@
 When the neighborhood contains zero predators, it would select any one of them randomly and move towards that cell.
+
+\begin{algorithm}[h]
+	\caption{Algorithm for updating position of the Predator species}
+	\label{algo:algorithm-movement-predator}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\STATE $forceMagnitude \gets convertToDecimal(genome[0-3])$
+			\STATE Get list of sorted neighborhood cells. Sorted by population of prey species.
+			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
+			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
 
@@
 
+\subsection{Reproduction process}
 The  fifth gene of the predator is used to represent their capability of reproduction.
-Depending on its binary value a predator in the simulation will or will not be able to reproduce in the simulation.
+Depending on its binary value a predator in the simulation will or will not be able to reproduce.
+The reproduction process for predators is similar to prey species.
+As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability takes effect in the reproductive process from one generation to another.
 
-\subsection{Reproduction process}
-The reproduction process for predators is similar to prey species.
-As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability behavior takes effect in the reproductive process of predator species from one generation to another.
-
-There are two control parameters that effect reproduction of predator species in the simulation.
-The first is the "Reproduction Age Limit".
-This the minimum age a predator has to reach before starting to involve itself for reproduction.
+There are two control parameters that effect the reproduction of predator species.
+The first is "Reproduction Age Limit".
+This is the minimum age a predator has to reach before starting to involve itself for reproduction.
 This parameter has been set to 500 iterations during the result and analysis section of the thesis.
-The second parameter is "Reproduction Interval" which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatability of the prey species.
+The second parameter is "Reproduction Interval" which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
 This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment.
 Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.
+
+\begin{algorithm}[H]
+	\caption{Algorithm for reproduction of the Predator species}
+	\label{algo:algorithm-reproduction-predator}
+	\begin{algorithmic}
+		\FOR{each step in time}
+			\STATE $capableToReproduce \gets$ true or false depending on the 5th bit of the genome, and maturity on reproduction age.
+			\IF {$capableToReproduce == true$ and $currentCellPopulationOfPredators > 1$ } 
+				\STATE $anotherPredator \gets$ Select random predator from same cell.
+				\IF {$anotherPredator$ is alive and $capableToReproduce$ and also reached reproduction maturity age}
+					\STATE Perform genetic cross over and mutation to create new genome.
+					\STATE Create new predator with new genome and zero memory, and release into environment.
+					\STATE Record reproduction time for both predators.
+				\ENDIF
+			\ENDIF
+		\ENDFOR
+	\end{algorithmic}
+\end{algorithm}
 

### 2010-08-12 docs/tex/model.tex
Documentation updates.

@@
 
-When the above two conditions are met, meaning the predator reaches it age for reproduction and also crosses every age interval, it randomly select another predator residing in the same cell.
+When the above two conditions are met, meaning the predator reaches its age for reproduction and also crosses its age interval, it randomly select another predator residing in the same cell.
 If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species in born which also resides on the same cell and initializes with zero memory configuration.

### 2010-08-12 docs/tex/result.tex
Thesis: updates to predator description
Documentation update.
Documentation updates.

@@
 \chapter{Results and Analysis}
+
+\section{Introduction}
+It is always a challenge to extract and analyze data from an Artificial Life simulation.
+
+\section{Mimicry Rings Reports}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{| p{2.0cm} | >{\centering} p{2.2cm} | p{8cm} |}
+	\hline
+		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
+		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
+	\hline
+\end{tabular}
+\caption{Parameters to Mimicry Ring Report.}
+\label{tab:ring-report-control-parameters}
+\end{table}
+
 \section{Initial configuration with two prey species}
@@
 \centering
-\caption{Agent configuration of 2 prey species}
-\label{tab:config-table-2-prey}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 2 prey species}
+\label{tab:config-table-2-prey}
 \end{table}
@@
 \centering
-\caption{Difference in prey pattern genotype and phenotype}
-\label{tab:diff-in-pattern}
 \begin{tabular}{|l|c|c|c|}
@@
 \end{tabular}
+\caption{Difference in prey pattern genotype and phenotype}
+\label{tab:diff-in-pattern}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 4 prey species}
-\label{tab:config-table-4-prey}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 4 prey species}
+\label{tab:config-table-4-prey}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 4 prey species with increased population}
-\label{tab:config-table-4-more-prey}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 4 prey species with increased population}
+\label{tab:config-table-4-more-prey}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 6 prey species.}
-\label{tab:config-table-6-prey}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 6 prey species.}
+\label{tab:config-table-6-prey}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 4 prey species all unpalatable.}
-\label{tab:config-table-4-prey-unpalatable}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 4 prey species all unpalatable.}
+\label{tab:config-table-4-prey-unpalatable}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 4 prey species all palatable.}
-\label{tab:config-table-4-prey-palatable}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 4 prey species all palatable.}
+\label{tab:config-table-4-prey-palatable}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 1 prey species unpalatable.}
-\label{tab:config-table-1-prey-unpalatable}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 1 prey species unpalatable.}
+\label{tab:config-table-1-prey-unpalatable}
 \end{table}
@@
 \centering
-\caption{Agent configuration of 1 prey species palatable.}
-\label{tab:config-table-1-prey-palatable}
 \begin{tabular}{|l|l|c|c|l|c|}
@@
 \end{tabular}
+\caption{Agent configuration of 1 prey species palatable.}
+\label{tab:config-table-1-prey-palatable}
 \end{table}
@@
 \end{figure}
+
+\section{Conclusion}

### 2010-08-18 docs/tex/mimicry.tex
Documentation update

@@
 \chapter{Mimicry}
+
+\section{History}
+Henry W.
+Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies, after 10 years of research in the Brazilian rain forest.
+For the next hundred years, it simulated heated discussion among all groups of people, scientists, philosophers, theologians, teachers and amateur naturalists.
+Bates collected ninety-four pieces of butterfly.
+He grouped them according to their similar appearance.
+He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families.
+Out of the ninety four species sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.
+
+\section{Batesian Mimicry}
+Even though Heliconiids are conspicuously colored, they are extremely abundant.
+They were also slow in mobility.
+Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature.
+Also because of this phenomenon other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.
+
+Repulsive animals, such as heliconiids are very conspicuously colored.
+Having this noticeable property, they are easily recalled by predators.
+Their wing pattern works as a warning to them.
+Once a predator has the knowledge of their inedible and unpalatable property, they would probably never attempt to try it again.
+As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators.
+Wickler \cite{wickler1986} expresses,
+\begin{quote}
+``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they 'act a part'.
+An actor is a mime, and so the representation of a false warning pattern was called \textit{mimicry}.
+Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."
+\end{quote}
+In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.
+
+\section{Mullerian Mimicry}
+Bates was not able to explain some phenomenon of mimicry.
+Occasionally two inedible unrelated butterfly species are amazingly similar in appearance.
+An explanation for this was provided by Fritz Muller in 1878.
+Like Bates, Muller observed and caught butterflies in Brazil.
+When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
+Because of predator's limited memory, all these species still loose their number even after being inedible.
+So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different family also tend to evolve to have similar appearance.
+This phenomenon is referred to as Mullerian Mimicry in the name of Fritz Muller.
+
+\section{Formation of Mimicry Rings}
+
+\section{Other form of mimicry}

### 2010-08-18 docs/tex/result.tex
Documentation update

@@
 It is always a challenge to extract and analyze data from an Artificial Life simulation.
+Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place.
+This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
+Also it can be established whether Batesian Mimicry and Mullerian Mimicry has taken effect by analyzing the data set of these populations.
 
-\section{Mimicry Rings Reports}
+\section{Mimicry Ring Reports}
+The mimicry ring reports consists entirely of the population of prey species categorized according to patterns and palatability.
+Data is stored at every instance of time of the simulation keeping an interval of 10 iterations.
+As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
+Parameters are mentioned in Table \ref{tab:ring-report-control-parameters}.
 
@@
 \centering
-\begin{tabular}{| p{2.0cm} | >{\centering} p{2.2cm} | p{8cm} |}
+\begin{tabular}{| p{2cm} | >{\centering} p{2.2cm} | p{8cm} |}
 	\hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-2Prey}
+	\includegraphics[scale=0.50]{images/simTime10k-2Prey}
 	\caption{Population distribution of mimicry rings, initialized with 2 prey species.}
@@
 
-The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for above 10000 iterations.
+The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for over 10000 iterations.
 With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
@@
 One is the initial population of prey species.
-It has been increased from 50 to 150 for each of the prey species increasing the overall population from 200 to 600.
+It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600.
 Secondly the number of predator population has been increased from 20 to 30.
 Thirdly, Predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
-Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will increased selection pressure from the entire population of predators.
+Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.
 
@@
 \section{Initial population with six prey species}
-
 \begin{table}[H]
@@
 
+To evaluate the simulation at a more complex level we increase the prey population to 900, consisting of 6 different species with very different pattern configuration.
+Similarly to increase predator-prey interaction we also increase the number of predator population to 30.
+Predator reproduction interval has been set comparatively lower in this simulation to 2000 iteration similar to the demise age which is set to 5000.
+As the initial population of prey species is very high, over time we are expecting even larger number of prey species.
+If predator population does not increase at similar rate there might be a prey population explosion were predator will have no effect on providing selection pressure for the evolution of mimicry.
+So that is why predator population control parameter has been set to this level.
+For memory configuration, the minimum number is set to 6, meaning the predator will have to store 6 different prey pattern configuration before starting to make intelligent decision about consuming them.
+As previously mention this number is always set in accordance with the initial number of different prey configuration.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+With the above set of parameters we can receive the plot of Figure \ref{fig:plot-6-prey}.
 
@@
 \section{Initial configuration with only unpalatable species}
-
+\label{sec:init-conf-only-unp}
 \begin{table}[H]
@@
 
+To further observe the effects of mimicry ring we initialize the simulation with four unpalatable population of prey species.
+As explained earlier the minimum memory configuration is set to 4 as the initial population of prey has four different species.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+The results according to Figure \ref{fig:plot-4-prey-unp} are expected as it can be observed the population of unpalatable species has prevailed.
+After nearly 9000 iterations we can see unpalatable species CA rule 55 has prevailed with the most population.
+Its palatable counter part is following this population.
+Unpalatable CA Rule 110 and its palatable counter part are also following the above.
+Similarly the other two species are increasing its population with dominance where the palatable population of deceivers are following them.
 
@@
 \section{Initial configuration with only palatable species}
+\label{sec:init-only-palatable-species}
 
@@
 
+The parameters for this simulation has been set with exactly the same as in the Table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
+All predator configuration has also been set to the exactly same as before.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+The results for the configuration in Table \ref{tab:config-table-4-prey-palatable} can be observed in Figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
+By analyzing details we can see, around simulation time 500 all population of species comes to a steady downfall as at this point initial predator species reaches its age for consumption.
+Around simulation time 1000 all population of prey species start increasing steadily because they reaches the maturity level of reproduction.
+At iteration time 2000 a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
+By this time the population of unpalatable species deceiving the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey comes to its demise.
+Predator population, from the beginning of the simulation has taken a very dominant effect.
+As all the species are palatable, their consumption and reproduction rate is extremely high and it keeps increasing in a geometric rate.
 
@@
 
+Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-unp}.
+The number of rings keep increasing but comes to a sudden drop around simulation time 7000 to reach at zero.
+
 \section{Initial configuration with single prey species}
+Until now all experiments have been initialized with both palatable and unpalatable species.
+The following set of experiments have been done with only a single prey species, for both cases of palatable and unpalatable.
 
 \subsection{Unpalatable}
+\label{subsec:single-prey-unpalatable}
 
@@
 
+This configuration has only one unpalatable species, one in each of the 216 cells, equally distributed all over the environment.
+Also have a set of 10 predators.
+Their minimum memory configuration has been set to 2 as any value below 2 will not help the Hopfield Network Memory to differentiate between two patterns.
+
 \begin{figure}[H]
@@
 
-From unpalatable species we see a bunch of rings with majority of unpalatable species created.
+From Figure \ref{fig:plot-1-prey-unp}, it can be observed, the initial set of unpalatable species is dominant as expected.
+And the palatable population mimicking that set is following it.
+Also a bunch of other rings with majority of unpalatable species have been created.
+Mainly because the initial population started with a bunch of unpalatable species, so their evolving generations have similar behavior as well.
 
@@
 
+This configuration is set exactly as according to Section \ref{subsec:single-prey-unpalatable} but with a single set of palatable species.
+The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of Section \ref{sec:init-only-palatable-species}.
+
 \begin{figure}[H]
@@
 
-From Palatable population we see a bunch of palatable rings created. 
-Major difference is the total number of prey population created.
-For unpalatable species total population reaches above 12 thousand.
-But for palatable species total population reaches nearly above 5000.
+From the initial palatable population we see a bunch of palatable rings created.
+Major difference from Section \ref{subsec:single-prey-unpalatable} is the total number of prey population created.
+For the unpalatable species section, total population reaches above 12 thousand.
+But for palatable species total population reaches nearly above 5000 prey species.
 
@@
 	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
-	\caption{Number of mimicry rings, initialized with 1 prey species palatable.}
+	\caption{Number of mimicry rings, initialized with 1 palatable prey species.}
 	\label{fig:ringSize8k-1-Prey-p}
@@
 
+\section{Analysis of Batesian Mimicry}
+For all possible initial conditions above, Batesian mimicry has taken effect.
+
+\section{Analysis of Mullerian Mimicry}
+
 \section{Conclusion}

### 2010-10-06 docs/tex/intro.tex
Very little intro

%Introductory Chapter
\chapter{Introduction}
Throughout history mankind has learned from nature. Human aspiration to fly in the sky comes from observing birds in the sky. Aspiration leads to inspiration, and airplanes are invented.

### 2010-10-12 docs/tex/model.tex
Some quotations added.

@@
 \chapter{Modeling the evolution of mimicry}
+
+\begin{quotation}
+``Modeling, it should be clear is an art form.
+It depends on the experience and taste of the modeler.
+In this it is much like cartooning.
+The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" \cite{holland1996}.
+\end{quotation}
 
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in Table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (Table \ref{tab:prey-genome}).
+Similar efforts of multiple mutation rate at varying location has been used in developing ``The Ecology of Echo" \cite{hraber1997}.
 

### 2010-10-27 docs/tex/model.tex
Updates on proof reading.

@@
 
-The environment will be designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the Laws and Life project by Peter Grogono \cite{grogono2003}.
+The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the Laws and Life project by Peter Grogono \cite{grogono2003}.
 
@@
 Their was existence of multiple mimicry rings of very different frequency.
-Second experiment was carried out with some palatable species along with the unpalatable once which was able able to reach conditions of Batesian mimicry also with less mimicry rings, were hypothesis 2 borne out.
+Second experiment was carried out with some palatable species along with the unpalatable once which was able to reach conditions of Batesian mimicry also with less mimicry rings, were hypothesis 2 borne out.
+It can be observed that,
 
@@
 \textsl{The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
-Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them.}
+Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them.
+\cite{franks2003}}
 \end{quote}
@@
 
-To use CA as prey pattern, its genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
+To use CA as prey pattern, an agent's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
 Each of this 256 values have a unique CA pattern associated with it.
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in Table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (Table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing ``The Ecology of Echo" \cite{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in \cite{hraber1997}.
 
@@
 The next two bits are used to represent palatability of the organism explained detail in Section \ref{sec:genetic-palatability-representation}.
-The next six bits is the force with which mobility of the organism is calculated.
+The next six bits is the magnitude of the force with which mobility of the organism is calculated.
 The 17th bit is used to evaluate reproduction capability of the organism, depending on which the prey species is either capable or not capable to participate in reproduction.
@@
 Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction.
-In addition to that these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
-Their mobility and reproduction capability is controlled at the genetic level, but their memory is not, as it was not possible to come up with a genetic representation for Hopfield Network.
+In addition to it, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
+Their mobility and reproduction capability is controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
+So every new predator species gets to born with zero memory and with no inharitance from parents.
 A set of parameters are defined to control predators' population and learning ability in the environment.
-Details of the parameters are given in Table \ref{tab:predator-control-parameters}.
+Details of these parameters are given in Table \ref{tab:predator-control-parameters}.
 
 \subsection{Learning}
-The objective of a predator's interaction with the prey is always to consume it.
-But based on the species of the prey and depending on its palatability, the predator will either be able to consume it or to throw it back to the environment.
+The objective of a predator's interaction with prey is always to consume it.
+But based on the prey's pattern and palatability, the predator will either be able to consume it or throw it back to the environment.
 At this event the predator needs to learn the pattern with which the prey has been represented.
@@
 
+%This section needs to use similar variables as mentioned in the above section on Hopfield Network.
 \subsubsection{Input to memory}
@@
 As it can be observed the predator are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
-This behavior of predator has been designed to enforce the predatory behavior of this species and also to have increase predator prey interaction in the simulation in terms of one species chasing the other for search of food.
+This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increase predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
 
@@
 \section{Conclusion}
+This model has been desinged from a pratical point of view; to come up with efficient results and achive the main objective, \textit{evolution of mimicry}; instead of the past therotical work done on the topic of mimicry.
+Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achive interesting results.
+This model can also be considered as a complex adaptive system similar to Hollands work on ``Echo" \cite{holland1996}.
+The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks are present in this model.

### 2010-10-27 docs/tex/result.tex
Updates on proof reading.

@@
 Otherwise evolution of mimicry is not observed.
-As mentioned earlier the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
+As mentioned in Table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
 After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgement.
@@
 With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
-Two prey species are in a ring if their CA pattern have a hamming distance within 10 bits.
+Two prey species are in a ring if their CA pattern have a hamming distance within 10 bits, parameter mentioned in Table \ref{tab:ring-report-control-parameters}.
 Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve.
@@
 
-Some very interesting diversity of rings can be observed in the simulation for updating the parameters.
+Some very interesting diversity of rings can be observed in the simulation for updating these parameters.
 The unpalatable rings and their deceptive counterparts(palatable prey with similar pattern) still have their dominance.
@@
 
-The parameters for this simulation has been set with exactly the same as in the Table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
-All predator configuration has also been set to the exactly same as before.
+The parameters for this simulation has been set exactly the same as in Table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
+All predator configuration has also been set to exactly same as before.
 
@@
 Predator population, from the beginning of the simulation has taken a very dominant effect.
-As all the species are palatable, their consumption and reproduction rate is extremely high and it keeps increasing in a geometric rate.
+As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keeps increasing in a geometric rate.
 
@@
 Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-unp}.
-The number of rings keep increasing but comes to a sudden drop around simulation time 7000 to reach at zero.
+The number of rings keep increasing but comes to a sudden drop around simulation time 7000 it goes to zero.
 
 \section{Initial configuration with single prey species}
-Until now all experiments have been initialized with both palatable and unpalatable species.
+Until now all experiments have been initialized with multiple prey species.
 The following set of experiments have been done with only a single prey species, for both cases of palatable and unpalatable.

### 2010-11-05 docs/tex/mimicry.tex
Updates on proof reading.
Mimicry chapter updated

@@
 \chapter{Mimicry}
+
+\begin{quote}
+``It is not the strongest of the species that survives, nor the most intelligent that survives. It is the one that is the most adaptable to change. - Charles Darwin"
+\end{quote}
 
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=1]{images/Batesplate_ArM}
+	\caption{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
+	\label{fig:plot-2-prey}
+\end{figure}
+
+\subsection{Definitions of Mimicry}
+The definition of mimicry provided by Bates is quite restricted and is similar to the following
+
+\begin{quote}
+``resemblance in external appearance, shapes and colours between members of widely distinct families."
+\end{quote}
+
+The following more sophisticated definition was provided at the international Zoological Congress in Washington, 1963,
+
+\begin{quote}
+``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."
+\end{quote}
+
+The best known defintion of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}.
+The clauses are presented in the following:
+
+\begin{itemize}
+	\item ``that the imitative species occur in the same area and occupy the same station as the immitated".
+This increases the probability that a predator will affect both parties concerned.
+Neverthless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
+	\item ``that the imitators are always the more defenceless".
+It will be seen later on in the discussion of Mertensian mimicry among coral snakes that the more offensive party may occasionally be the mimic.
+	\item ``that the imitators are always less numerous in individuals".
+What is meant here is that the deceived animal should encounter the mimic less often than the model.
+This is true when the deceived animal must learn to recognize model and mimic and when positive and negetive experiences carry equal weight.
+But it is known from various learning experiments that when an animal has learn about warning coloration, negetive experiences or punishment stimuli (such as iedibility) can have a stronger and more lasting effect than positive experiences.
+Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces.
+When the deceptive animal possesses an innate reaction to the model the number of mimics can be virtually unlimited.
+	\item ``that the imitators differ from the bulk of their allies".
+When this condition applies, our attention is of course most easily attracted.
+The most remarkable cases of mimicry are those where close relatives form divergent models.
+It is neverthless highly possible that groups of closely related species may be similar mimics of the same model.
+Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry.
+	\item ``that the imitation, however minute, is external and visible only, never extending to internal charecters or to such as do not affect the external appearance." This criteria, like the previous one is aimed at defining mimmicry as a special adaptation.
+But if one of two closely related species both of which are posinous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
+\end{itemize}
+
+These five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
+But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.
+
 \section{Mullerian Mimicry}
@@
 \section{Other form of mimicry}
+
+\section{Conclusion}

### 2010-11-05 docs/tex/model.tex
Mimicry chapter updated

@@
 In this it is much like cartooning.
-The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" \cite{holland1996}.
+The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point) - John H.
+Holland" \cite{holland1996}.
 \end{quotation}

### 2010-11-05 docs/tex/mimicry.tex
More addition to Mullerian Mimicry

@@
 	\caption{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
-	\label{fig:plot-2-prey}
+	\label{fig:batesian-butterfly}
 \end{figure}
@@
 
+According to Muller \cite{muller1879} Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution.
+In Muller's view, this convergence or sharing of the warning signal reduces the predation load on each species.
+The entry of a naive young predator into the population has usually been considered the primary cause of learning predation.
+In such a case, both Mullerian species should benefit from mutual advertising.
+In any event, a mutant that more strongly resembles a warningly colored species is expected to be more likely to survive predation than one that changes in the opposite direction.
+Predators of warningly colored species are encouraged to generalize; that is, it is to their benefit to recognize similar patterns as signaling unpalatability.
+Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance confer some protection.
+Note that Mullerian mimicry is not deceptive since it is to the predator's advantage to be able to recognize all deterrent and trauma-inducing species.
+The mimicry does not have to be close enough to cause misidentification on the part of the predator, merely close enough to remind it of a past experience with similar prey.
+Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
+Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.75]{images/BatesMimButter}
+	\caption{Perhaps one of the most well-known examples of mimicry, the viceroy butterfly (top) appears very similar to the noxious tasting monarch butterfly (bottom).
+Although it was for a long time purported to be an example of Batesian mimicry, it has recently been discovered that the viceroy is actually just as unpalatable as the monarch, making this a case of Mullerian mimicry.
+\cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
+	\label{fig:mullerian-butterfly}
+\end{figure}
+
 \section{Formation of Mimicry Rings}

### 2010-11-07 docs/tex/mimicry.tex
Dynamics of mimicry

@@
 \begin{itemize}
-	\item ``that the imitative species occur in the same area and occupy the same station as the immitated".
+	\item ``that the imitative species occur in the same area and occupy the same station as the imitated".
 This increases the probability that a predator will affect both parties concerned.
-Neverthless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
-	\item ``that the imitators are always the more defenceless".
+Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
+	\item ``that the imitators are always the more defenseless".
 It will be seen later on in the discussion of Mertensian mimicry among coral snakes that the more offensive party may occasionally be the mimic.
@@
 What is meant here is that the deceived animal should encounter the mimic less often than the model.
-This is true when the deceived animal must learn to recognize model and mimic and when positive and negetive experiences carry equal weight.
-But it is known from various learning experiments that when an animal has learn about warning coloration, negetive experiences or punishment stimuli (such as iedibility) can have a stronger and more lasting effect than positive experiences.
+This is true when the deceived animal must learn to recognize model and mimic and when positive and negative experiences carry equal weight.
+But it is known from various learning experiments that when an animal has learn about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences.
 Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces.
@@
 	\item ``that the imitators differ from the bulk of their allies".
-When this condition applies, our attention is of course most easily attracted.
 The most remarkable cases of mimicry are those where close relatives form divergent models.
-It is neverthless highly possible that groups of closely related species may be similar mimics of the same model.
+It is nevertheless highly possible that groups of closely related species may be similar mimics of the same model.
 Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry.
-	\item ``that the imitation, however minute, is external and visible only, never extending to internal charecters or to such as do not affect the external appearance." This criteria, like the previous one is aimed at defining mimmicry as a special adaptation.
-But if one of two closely related species both of which are posinous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
+	\item ``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance." This criteria, like the previous one is aimed at defining mimicry as a special adaptation.
+But if one of two closely related species both of which are poisonous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
 \end{itemize}
@@
 
-\section{Formation of Mimicry Rings}
+\section{Evolutionary Dynamics of Mimicry}
+There has been many explanations on the dynamics of mimicry.
+
+The dynamics of mimicry has been explained in detail by Turner, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
+As Turner states,
+
+``According to punctuated equilibrium, there, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories.
+Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
+The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" - J.
+R.
+G.
+Turner \cite{turner1988}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.5]{images/Punctuated-equilibrium}
+	\caption{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
+Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
+	\label{fig:punctuated-equilibrium}
+\end{figure}
+
+\subsection{Mimicry Ring}
+
+\subsection{Formation of Mimicry Rings}
 

### 2010-11-08 docs/tex/model.tex
Dynamics of mimicry
Mimicry chapter mostly complete

--- 2010-10-27 docs/tex/model.tex
@@
 In this it is much like cartooning.
-The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" \cite{holland1996}.
+The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" - John H.
+Holland \cite{holland1996}.
 \end{quotation}
@@
 Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in \cite{hraber1997}.
+
+%Content needs to be added.....
+\subsection{Reflection of punctuated equilibrium}
 

### 2010-11-08 docs/tex/mimicry.tex
Mimicry chapter mostly complete

@@
 \section{Evolutionary Dynamics of Mimicry}
-There has been many explanations on the dynamics of mimicry.
+The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
 
-The dynamics of mimicry has been explained in detail by Turner, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
-As Turner states,
+\paragraph{Punctuated Equilibrium}
+Punctuated equilibrium is a theory in evolutionary biology which proposes that most sexually reproducing species will experience little evolutionary change for most of their geological history, remaining in an extended state called \textit{stasis}.
+When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis.
+Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another.
+Thus, ``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}.
+
+\paragraph{Phyletic Gradualism}
+In contrast to punctuated equilibrium, phyletic gradualism states that species continue to adapt to new environmental and biological selection pressures over the course of their history, gradually becoming new species.
+Phyletic gradualism holds that a species population changes gradually; that is there is no clear line of demarcation between an ancestral species and a descendant species unless a splitting (cladogenetic) event occurs or the gradually-changing lineage is divided arbitrarily.
+During this process, evolution occurs at a smooth, steady and incremental (but not necessarily constant and slow) rate on a geological time scale.
+
+On this issue Turner states,
 
@@
 
+To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \cite{turner1988}, which was originated by Poulton \cite{poulton1912} and Nicholson \cite{nicholson1927}, termed as the \textbf{two stage model}.
+This theory states that mimicry normally arises in two steps.
+A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \cite{sheppard1972} \cite{ford1964}.
+This two-stage theory has been for the explanation of Mullerian mimicry as well.
+
 \subsection{Mimicry Ring}
+Any theory of Mullerian mimicry has to take into account the phenomenon of the coexistence of multiple mimicry rings.
+If we examine the local butterfly fauna in any area of the world, we will find that between all the aposomatic (warningly colored and defended) species present there are normally only a limited number of different patterns, normally far smaller than the number of species.
+Each cluster of species, all sharing a common pattern, is termed as Mullerian mimicry ring.
+Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.
 
-\subsection{Formation of Mimicry Rings}
+\subsubsection{Formation of Mimicry Rings}
+In regards to the formation of mimicry ring Turner \cite{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns.
+Different level of variation of these two parameter can give us very different formation of mimicry ring evolution.
+The cases are considered below.
 
-\section{Other form of mimicry}
+\begin{itemize}
+	\item If we imagine two different rings of similar warning patterns in one single habitat, similar enough that the envelop of protection afforded to one gives some protection to the more extreme variant of the other (in a simplified language, suppose that predators that have sampled species A sometimes avoid the more extreme members of species B because they mistake them as A), then these two species are subject to natural protection for mutual convergence of their patterns.
+Eventually they will form a rather accurate Mullerian mimicry ring.
+	\item By contrast, if the two species have patterns so dissimilar that predators encountering one never imagine that it might be the other (the envelop of protection do not overlap the other species' phenotype distribution), then there is no selection whatever for convergence, and the two patterns will remain distinct indefinitely.
+ \item But mutations of color patterns are occurring all the time.
+Suppose that species B happens to produce a mutation whole pattern falls within the envelop of protection afforded to species A.
+The mimicry need not be perfect, but if it is good enough, the mutation will have an advantage and will spread.
+In this way species B may, by a single mutation, become a Mullerian mimic of species A; in other word species B may switch from one Mullerian mimicry ring to another.
+Clearly, if the mimicry is not perfect, the two patterns will then gradually converge, making the resemblance ever closer.
+\end{itemize}
+
+Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.
+It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.
 
 \section{Conclusion}
+Mimicry is one of the most fascinating cases of evolutionary biology.
+This phenomenon has been studied extensively as infinite number of evidence exists in nature.
+One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
+And this figure has been taken from Wilcker \cite{wickler1986} which has been published in 1986.
+It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.
+Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \cite{cott1957}.

### 2010-11-13 docs/tex/model.tex
Review updates

@@
 %Explain more about the first model by Frank and Noble
-The first model by Frank and Noble \cite{franks2002} is where ``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed." Each individual had a single gene: a value representing their external appearance or phenotype.
+The \textbf{first} model by Frank and Noble \cite{franks2002} is where ``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed." Each individual had a single gene: a value representing their external appearance or phenotype.
 The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors).
@@
 \paragraph{}
-The second model by Frank and Noble \cite{franks2003} is based on two working hypothesis:
+The \textbf{second} model by Frank and Noble \cite{franks2003} is based on two working hypothesis:
 
@@
 \textit{Hebb's postulate of learning} is the oldest and most famous of all learning rules; it is named in honor of the neuropsychologist Donald Hebb(1949).
-Hebb's book \textit{The Organization of Behavior} (1949) states the following (p.62):
+Hebb's book \textit{The Organization of Behavior} \cite{hebb1949} states the following:
 
@@
 It is presented to show the behavior of predator species in the simulation in absence of any prey species.
-As it can be observed the predator are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
+As it can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
 This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increase predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
@@
 \section{Conclusion}
-This model has been desinged from a pratical point of view; to come up with efficient results and achive the main objective, \textit{evolution of mimicry}; instead of the past therotical work done on the topic of mimicry.
-Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achive interesting results.
+This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
+Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
 This model can also be considered as a complex adaptive system similar to Hollands work on ``Echo" \cite{holland1996}.

### 2010-11-13 docs/tex/mimicry.tex
Review updates

@@
 
-These five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
+According to Wickler \cite{wickler1986}, these five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
 But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.
@@
 One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
-And this figure has been taken from Wilcker \cite{wickler1986} which has been published in 1986.
+And this figure is more than 20 years old as it has been taken from Wilcker \cite{wickler1986}, published in 1986.
 It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.

### 2010-11-13 docs/tex/result.tex
Review updates

@@
 By analyzing details we can see, around simulation time 500 all population of species comes to a steady downfall as at this point initial predator species reaches its age for consumption.
-Around simulation time 1000 all population of prey species start increasing steadily because they reaches the maturity level of reproduction.
+Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction.
 At iteration time 2000 a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
@@
 
-Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-unp}.
+Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-p}.
 The number of rings keep increasing but comes to a sudden drop around simulation time 7000 it goes to zero.

### 2010-11-13 docs/tex/model.tex
Results chapter finally completed

@@
 \subsection{Models by Frank and Noble}
+\label{subsec:models-by-frank-and-noble}
 %Explain more about the first model by Frank and Noble
@@
 
-%Content needs to be added.....
-\subsection{Reflection of punctuated equilibrium}
-
 \subsection{Genome}
@@
 \end{table}
+
+\subsection{Reflection of punctuated equilibrium}
+\label{subsec:reflection-of-punctuated-equilibrium}
+Punctuated equilibrium has been defined in section \ref{sec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism.
+Also Turner \cite{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
+The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry.
+As it can observed new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
+Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation.
+The mutations that are favored, helps the mimics to survive while the unfavored ones fail to persist.
+It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene.
 

### 2010-11-13 docs/tex/result.tex
Results chapter finally completed

@@
 \section{Analysis of Batesian Mimicry}
-For all possible initial conditions above, Batesian mimicry has taken effect.
+For all possible initial conditions, Batesian mimicry has taken effect.
+It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
+Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{sec:init-only-palatable-species}).
+This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
+So from the analysis it can be concluded that the model under discussion has successfully simulated the evolution of Batesian mimicry.
 
 \section{Analysis of Mullerian Mimicry}
+Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}.
+In this experiment we initialize the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations we can observe that all of the initial unpalatable rings have survived with dominance.
+So we can be conclude that our results match with the one from Frank and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
 
 \section{Conclusion}
+Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
+In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings.
+Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
+This model also proves the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.

### 2010-11-13 docs/tex/mimicry.tex
Results chapter finally completed

@@
 \subsection{Definitions of Mimicry}
-The definition of mimicry provided by Bates is quite restricted and is similar to the following
+The following account on the definition of Mimicry is mostly extracted from Wickler's \textit{Mimicry in plants and animals} \cite{wickler1986}.
+
+According to him the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following
 
 \begin{quote}
-``resemblance in external appearance, shapes and colours between members of widely distinct families."
+``resemblance in external appearance, shapes and colors between members of widely distinct families."
 \end{quote}
@@
 
-The best known defintion of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}.
+The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}.
 The clauses are presented in the following:
@@
 Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
-	\item ``that the imitators are always the more defenseless".
-It will be seen later on in the discussion of Mertensian mimicry among coral snakes that the more offensive party may occasionally be the mimic.
+	\item ``that the imitators are always the more defenseless". On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
 	\item ``that the imitators are always less numerous in individuals".
@@
 \section{Evolutionary Dynamics of Mimicry}
+\label{sec:evolutionary-dynamics-of-mimicry}
 The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
@@
 Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
-The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" - J.
-R.
-G.
-Turner \cite{turner1988}
+The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}
 
@@
 A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \cite{sheppard1972} \cite{ford1964}.
-This two-stage theory has been for the explanation of Mullerian mimicry as well.
+This two-stage theory has been applied for the explanation of Mullerian mimicry as well.
 

### 2010-11-14 docs/tex/mimicry.tex
Changed the name of the chapters.
Small updates

@@
 %Chapter describing the mimetic process
-\chapter{Mimicry}
+\chapter{The Inspiration: Mimicry}
 
@@
 
-``According to punctuated equilibrium, there, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories.
+``According to punctuated equilibrium, therefore, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories.
 Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.

### 2010-11-15 docs/tex/mimicry.tex
Paraphrasing fixed.

@@
 
-According to Muller \cite{muller1879} Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution.
-In Muller's view, this convergence or sharing of the warning signal reduces the predation load on each species.
-The entry of a naive young predator into the population has usually been considered the primary cause of learning predation.
-In such a case, both Mullerian species should benefit from mutual advertising.
-In any event, a mutant that more strongly resembles a warningly colored species is expected to be more likely to survive predation than one that changes in the opposite direction.
-Predators of warningly colored species are encouraged to generalize; that is, it is to their benefit to recognize similar patterns as signaling unpalatability.
-Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance confer some protection.
-Note that Mullerian mimicry is not deceptive since it is to the predator's advantage to be able to recognize all deterrent and trauma-inducing species.
-The mimicry does not have to be close enough to cause misidentification on the part of the predator, merely close enough to remind it of a past experience with similar prey.
-Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
+According to Huheey \cite{huheey1988} ``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution \cite{muller1879}." In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
+Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species.
+For cases like these, all unpalatable species should benefit from mutual advertising.
+If mutation gives opportunity for a single unpalatable prey to resemble a warningly colored species, it is expected to be more likely to survive predation than if the change was in opposite direction.
+Predators surviving on warningly colored species need to generalize; meaning if similar patterns signal unpalatability, predators recognition rate becomes much higher.
+Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance provides some protection.
+
+It is worth observing the fact that Mullerian mimicry is not deception, as it is to the predator's advantage to be able to recognize all deterrent and noxious species.
+Preys resemblance does not have to be close enough to cause misidentification on the part of the predator, but merely similar enough to remind it of a bitter past experience with similar prey.
+As Huheey continues ``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
 Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian.
+"
 
@@
 	\includegraphics[scale=0.75]{images/BatesMimButter}
-	\caption{Perhaps one of the most well-known examples of mimicry, the viceroy butterfly (top) appears very similar to the noxious tasting monarch butterfly (bottom).
-Although it was for a long time purported to be an example of Batesian mimicry, it has recently been discovered that the viceroy is actually just as unpalatable as the monarch, making this a case of Mullerian mimicry.
+	\caption{A very well-known examples of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom).
+It was considered for a long time that this is an ideal example of Batesian mimicry.
+But recently Brower discovered that the viceroy is actually just as noxious as the monarch, making this a case of Mullerian mimicry.
 \cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
@@
 \paragraph{Punctuated Equilibrium}
-Punctuated equilibrium is a theory in evolutionary biology which proposes that most sexually reproducing species will experience little evolutionary change for most of their geological history, remaining in an extended state called \textit{stasis}.
+In evolutionary biology, punctuated equilibrium is the theory which proposes that most sexually reproducing species will remain in an extended state called \textit{stasis} while experiencing little evolutionary change for most of their geological history.
 When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis.

### 2010-11-16 docs/tex/review.tex
Some quotations added.
new section added to review.tex
Changed the name of the chapters.
Review section updated.

@@
 
-\section{Evolutionary Programming}
+\section{Introduction}
 
-\section{Genetic Algorithm}
+\section{Evolutionary Computation}
 
-\section{Co-evolution}
+``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}
+
+\subsection{History}
+
+\paragraph{1948: Turing}
+Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled ``Intelligent Machinery" where the expression of ``genetical or evolutionary search"  was used \cite{turing1948}.
+He suggested a range of ideas for systems which could be said to modify their own programs.
+
+\paragraph{1962: Bremermann}
+Bremermann was the first to apply the concept of biological evolution to execute computer experiments for solving optimization problems \cite{bremermann1962}.
+He was the first to consider the problem of minimizing a real-valued fitness function.
+He selected very simple functions to optimize in order to provide a more tractable analysis of the evolutionary process.
+
+\paragraph{1964: Rechenberg}
+Rechenberg's contribution is considered mostly in providing Evolutionary Strategies.
+He invented a highly influential set of optimization method which were successfully applied to challenging problems such as aerodynamic wing design.
+\cite{rechenberg1973}
+
+\paragraph{1965: L. Fogel, Owens and Walsh}
+A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in ``Artificial Intelligence through a simulation of evolution" \cite{fogel1966}.
+In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series.
+Evolutionary prediction of such kind was motivated by the concept that prediction is a keystone to intelligent behavior (defined in terms of adaptive behavior, in that the intelligent organism must anticipate events in order to adapt behavior in light of a goal).
+
+\paragraph{1975: Holland}
+Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H.
+Holland.
+His ground breaking book ``Adaptation in natural and artificial systems" \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.
+
+\paragraph{1992: Koza}
+Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem.
+Starting from a high-level statement of ``what needs to be done" it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.
+
+Contemporary terminology denotes the fields of \textbf{Evolutionary Strategy}, \textbf{Evolutionary Programming}, \textbf{Genetic Algorithm} and \textbf{Genetic Programming} to be under one umbrella termed as \textbf{Evolutionary Computation} while the algorithms are called \textbf{Evolutionary Algorithms}.
+
+\subsection{Evolutionary Algorithms}
+
+\subsection{Evolutionary Strategies}
+
+\subsection{Evolutionary Programming}
+
+\subsection{Genetic Algorithm}
+
+\subsection{Genetic Programming}
 
@@
 
-\subsection{Cellular Automata}
+\subsection{Complex Adaptive System}
+
+\subsubsection{Echo}
+
+\section{Cellular Automata}
+
+\section{Conclusion}

### 2010-11-17 docs/tex/review.tex
Some Quotations Added
Evolutionary algorithms.

@@
 \chapter{Review}
+
+\begin{quote}
+``The theory of evolution by cumulative natural selection is the only theory we know of that is in principle capable of explaining the existence of organized complexity" - Richard Dawkins \cite{dawkins1996}
+\end{quote}
 
@@
 
-\paragraph{1948: Turing}
+\paragraph{Turing(1948)}
 Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled ``Intelligent Machinery" where the expression of ``genetical or evolutionary search"  was used \cite{turing1948}.
@@
 
-\paragraph{1962: Bremermann}
+\paragraph{Bremermann(1962)}
 Bremermann was the first to apply the concept of biological evolution to execute computer experiments for solving optimization problems \cite{bremermann1962}.
@@
 
-\paragraph{1964: Rechenberg}
+\paragraph{Rechenberg(1964)}
 Rechenberg's contribution is considered mostly in providing Evolutionary Strategies.
@@
 
-\paragraph{1965: L. Fogel, Owens and Walsh}
+\paragraph{L. Fogel, Owens and Walsh (1965)}
 A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in ``Artificial Intelligence through a simulation of evolution" \cite{fogel1966}.
@@
 
-\paragraph{1975: Holland}
+\paragraph{Holland(1975)}
 Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H.
@@
 
-\paragraph{1992: Koza}
+\paragraph{Koza(1992)}
 Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem.
@@
 \subsection{Evolutionary Algorithms}
+Algorithms which are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions from a possible pool of population of solutions, can be defined as evolutionary algorithms.
+There are many different forms of evolutionary algorithms.
+All of which can be generalized to follow a certain pattern.
+The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual of the set of existing solution space.
+An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment.
+So given a problem the algorithm initializes the environment with a random set of population or solutions.
+Then it uses the fitness function to select a better set of solutions from the existing once.
+After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set or population born from the existing ones.
+Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.
+
+According to Eiben \cite{eiben2003} this process has two fundamental forces that form the basis of evolutionary systems:
+
+\begin{itemize}
+	\item ``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."
+	\item ``Selection acts as a force pushing quality."
+\end{itemize}
+
+Important components of evolutionary algorithms are
+
+\paragraph{Representation (Individuals or Solution Space)}
+Evolutionary Algorithms(EA) are considered as robust problem solvers as it provides evenly good performance over a wide range of problems.
+To apply evolutionary algorithm to this wide range the most important part is representation of the solution space.
+In EA representation is analogous to the complex pathway that exits between \textbf{genotype} and \textbf{phenotype} of a biological organism.
+
+\paragraph{Evaluation Function (Fitness Function)}
+This is the function with which the solution is evaluated.
+The outcome of applying evolutionary algorithm to the problem depends on this function.
+It is defined to evaluate each of the solutions of the problem.
+In biology evaluation function is analogous to the decision of survival of any species in an environment.
+
+\paragraph{Population}
+The population is the solution set of the problem over which EA will be applied.
+It is literally analogous to the same meaning in biology.
+The diversity of the population is very important.
+If the initial random population of solutions are diverse then there is more possibility of reaching an optimal solution space very quickly, and it also avoids reaching local optimum instead of the global optimum.
+
+\paragraph{Variation operators, recombination and mutation}
+Considering arity (number of object as input) variation operators are divided into two kinds.
+The mutation operator accepts only one operand.
+The process of mutation is similar to the way it happens in biology.
+It is a stochastic process, meaning, its output the child depends on the outcomes of a series of random choices.
+The operator is responsible for causing a random unbiased change.
+Mutation has very different roles in different fields of EC, for example in Genetic Programming it is not used at all, while in genetic algorithms it is a very pivotal process as it provides fresh blood to the existing set of solutions.
+Getting a new mutated child is like stepping into a new solution space outside of the ones which already exist in the parent pool.
+A recombination operator is responsible for merging two parent genotypes into one or two offspring genotypes.
+It is also a stochastic process depending on the choice of the parts of the parent individuals.
+Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent.
+According to Eiben \cite{eiben2003} ``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features." It is important that variation operators are defined based on the representation of the problem under consideration.
 

### 2010-11-18 docs/tex/review.tex
Evolutionary Strategy.

@@
 \subsection{Evolutionary Strategies}
+The key important property of these set of algorithms is \textbf{self-adaptation} of strategy parameters.
+The  parameters of Evolutionary Algorithm are included in the chromosomes and they co-evolve with the solution set while running the algorithm.
+To summarize these set of algorithms, they usually have real-valued vectors, their recombination process is discrete or intermediary, their mutation process uses Gaussian perturbation while parent selection is uniform random.
+In terms of their attribute feature they are fast and good optimizer for real-valued optimization.
 

### 2010-11-19 docs/tex/review.tex
Some updates. Nothing significant.
Genetic Algorithms in progress...

@@
 
+\subsection{Genetic Algorithm}
+Genetic Algorithms(GA) have the most wide set of applications.
+It was first conceived by John H.
+Holland for studying adaptive behavior as in \textit{Adaptation in natural and artificial systems} \cite{holland1975}.
+They are mainly considered as function optimizers.
+In general GA have many diverse representation schemes considering the solution set of the problem.
+Depending on the problem scenario an appropriate representation could be Binary, Grey Code, Integer, Real-Valued, Floating-point or Permutation based.
+
+Using GA for a binary representation mutation can be single point or multiple point, where a random location is selected from the binary genome and the bit is flipped.
+For integer representation random resetting is used instead of bit flipping.
+Creep mutation is another scheme which was designed for ordinal attributes and works by adding a small (positive or negative) value to each gene with a random probability.
+For a real-valued or floating-point mutation none of the above strategy is applicable.
+As for this case mutation is applied to a random gene maintaining a certain range of value within an upper and a lower bound and using a standard for randomization, such as Uniform, Gaussian or Cauchy distribution.
+For permutation representation swap mutation is a strategy used by simply swapping the location of two randomly selected genes.
+Insert mutation is another strategy where a random gene is selected and inserted to a different location in the genome, causing the other genes to move a single space.
+In scramble mutation, location of a collection of randomly selected genes are scrambled, while in inversion mutation serialized location of a set of genes are inverted.
+
+GA also have many different recombination operators for each representation.
+For binary and integer representation one-point crossover and \textit{N}-point-crossover are the most frequently used.
+These two operators work by dividing the parent genome at one or multiple random points and combining them to create an offspring.
+Uniform-crossover \cite{sywerda1989} is another method which works by treating each gene independently and making a random choice at to which parent it should inherit from.
+Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination.
+Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome but instead their genomes are derived from their using an arithmetic formula.
+Permutation representation has many interesting recombination operators out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems.
+Other useful operators for permutation representation are Edge crossover, Order crossover and Cycle crossover, where their name provides more or less an appropriate description of their operation.
+
 \subsection{Evolutionary Strategies}
@@
 \subsection{Evolutionary Programming}
-
-\subsection{Genetic Algorithm}
 

### 2010-11-19 docs/tex/review.tex
Genetic Algorithms fairly completed.

@@
 \subsection{Evolutionary Algorithms}
-Algorithms which are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions from a possible pool of population of solutions, can be defined as evolutionary algorithms.
-There are many different forms of evolutionary algorithms.
-All of which can be generalized to follow a certain pattern.
-The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual of the set of existing solution space.
+Algorithms which are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generation, can be defined as evolutionary algorithms.
+There are many different forms of evolutionary algorithm.
+All of which can be generalized to follow their pattern from natural selection.
+The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space.
 An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment.
@@
 Then it uses the fitness function to select a better set of solutions from the existing once.
-After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set or population born from the existing ones.
+After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set born from the existing ones.
 Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.
@@
 As for this case mutation is applied to a random gene maintaining a certain range of value within an upper and a lower bound and using a standard for randomization, such as Uniform, Gaussian or Cauchy distribution.
-For permutation representation swap mutation is a strategy used by simply swapping the location of two randomly selected genes.
-Insert mutation is another strategy where a random gene is selected and inserted to a different location in the genome, causing the other genes to move a single space.
+For permutation representation, swap mutation is a strategy used by simply swapping the location of two randomly selected genes.
+Insert mutation is another strategy where a random gene is selected and inserted to a random location in the genome, causing the other genes to move a single space.
 In scramble mutation, location of a collection of randomly selected genes are scrambled, while in inversion mutation serialized location of a set of genes are inverted.
@@
 Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination.
-Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome but instead their genomes are derived from their using an arithmetic formula.
-Permutation representation has many interesting recombination operators out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems.
+Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome but instead their genomes are derived from their parent using an arithmetic formula.
+Permutation representation has many interesting recombination operators, out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems.
 Other useful operators for permutation representation are Edge crossover, Order crossover and Cycle crossover, where their name provides more or less an appropriate description of their operation.
+
+In regards to parent selection the most commonly used process by GA is fitness proportion selection, where the selection probability of a parent depends on the absolute fitness value of the individual compared to the absolute fitness values of the rest of the population.
+A fitness value is evaluated from the evaluation or the fitness function.
+Introduced by Holland \cite{holland1975} this procedure has a few problems.
+Premature convergence being one where individuals that are a lot better than the rest take over the entire population.
+Also when fitness values are all very close there is almost no selection pressure in evolution of the fittest.
+Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection.
+This procedure preserves a constant selection pressure by sorting the population on the basis on fitness, and then allocating selection probabilities to individuals according to their rank.
+Both of the above mentioned selection procedures requires knowledge of the entire population.
+But when the population size is very large Tournament selection is an effective process.
+In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.
+
+Genetic Algorithms are one of the most effective strategy used in the field of evolutionary computation to solve optimization problems.
+Then again there are limitations.
+When the solution set of a problem do not have a gnomic representation, genetic algorithms cannot play any role in improving it.
+So the set of problems to which GA can be applied is not universal.
 

### 2010-11-20 docs/tex/review.tex
Small updates...
Genetic Programming.

@@
 When the solution set of a problem do not have a gnomic representation, genetic algorithms cannot play any role in improving it.
-So the set of problems to which GA can be applied is not universal.
+So the set of optimization problems to which GA can be applied is not universal.
 
 \subsection{Evolutionary Strategies}
-The key important property of these set of algorithms is \textbf{self-adaptation} of strategy parameters.
+The key important property of the set of algorithms termed as ``Evolutionary Strategy" is \textbf{self-adaptation} of strategy parameters.
 The  parameters of Evolutionary Algorithm are included in the chromosomes and they co-evolve with the solution set while running the algorithm.
@@
 \subsection{Genetic Programming}
+Genetic programming is typically applied to machine learning tasks such as prediction and classification.
+Its attribute feature behaves similar to neural network and usually has huge populations of solution combination.
+The algorithm itself is a very slow process.
+These sets of algorithms use non-linear chromosomes such as trees and graphs.
+Mutation is mostly avoided for genetic programming.
+Recombination operators work by exchanging subtrees.
+Mutation if applied will be a random changing process in the tree.
+Parent selection process is usually fitness proportional while the survivor selection process is usually replacement of generations.
+From a technical point of view, genetic programming is simply a variant of genetic algorithm working with a different data structure: the chromosomes are trees.
 

### 2010-11-20 docs/tex/mimicry.tex
Small updates...
Genetic Programming.

@@
 
-According to him the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following
+According to Wickler the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following
 
@@
 One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
-And this figure is more than 20 years old as it has been taken from Wilcker \cite{wickler1986}, published in 1986.
+And this figure is more than 40 years old as it has been taken from Wilcker \cite{wickler1986}, published in 1968.
 It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.

### 2010-11-20 docs/tex/review.tex
Evolutionary Programming.

@@
 \end{quote}
-
-\section{Introduction}
 
@@
 \subsection{Evolutionary Programming}
+The primary objective of evolutionary programming was to generate artificial intelligence by simulating evolution as a learning process \cite{fogel1966}.
+Capability of a system to adapt its behavior to meet some specified goal in the environment was considered as intelligence.
+Fogel used finite state machines as predictors and evolved them.
+Usually representation for evolutionary programming is with real-valued vectors.
+Its parent selection is deterministic, where each parent creates one offspring via mutation.
+There is no recombination operator for evolutionary programming.
+Mutation is applied with Gaussian perturbation.
+While survivor selection is probabilistic.
 
@@
 \section{Cellular Automata}
-
-\section{Conclusion}

### 2010-11-20 docs/tex/review.tex
Artificial Life.

@@
 \section{Artificial Life}
+As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
+In contrast to that in Artificial Life scientist take concepts from Biology specially Evolutionary Biology and genetics and implement into computer science.
+
+In defining Artificial Life Christopher G. Langton states the following,
+
+\begin{quote}
+`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature.
+Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts.
+The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."
+\end{quote}
+
+\section{History}
+
+%\paragraph{Jon Von Neumann}
+
+%\paragraph{Tierra}
+
+%\paragraph{Avida}
+
+The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}.
+While providing a brief survey over different AL models he talks about \textbf{wetware systems} which work at the molecular level, the \textbf{software systems} which work at the cellular level and the \textbf{hardware systems} which works at the organism level.
 

### 2010-11-29 docs/tex/application.tex
Update in the applications chapter. Simple text formatting.
Modified with Dr. Grogono's comments

@@
 
-Part of this thesis was to think about whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions.
+The goal of this thesis is to think about whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions.
 Predator-prey co-evolution has also been used for solving interesting problems \cite{hillis1990}, giving better result than conventional methodologies.
@@
 And if we consider that the predator species are responsible for selecting the appropriate pattern based on their palatability, then we can consider palatability as the criteria for selection of the pattern (or the evaluation/fitness function for the case of Evolutionary Programming/Genetic Algorithm).
-
 If the predator associates the CA pattern with palatability then it does not make any sense of having a mimic in the solution space as mimics will have the same pattern with opposite palatability.
 So using the evolution of mimicry to solve an optimization problem is futile if we try conventional problems which already can be solved with the help of evolutionary programming or genetic algorithm.
+
 So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods.

### 2010-11-29 docs/tex/mimicry.tex
Modified with Dr. Grogono's comments

@@
 \begin{quote}
-``It is not the strongest of the species that survives, nor the most intelligent that survives. It is the one that is the most adaptable to change. - Charles Darwin"
+\textsl{``It is not the strongest of the species that survives, nor the most intelligent that survives. It is the one that is the most adaptable to change." - Charles Darwin}
 \end{quote}
@@
 He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families.
-Out of the ninety four species sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.
+Out of the ninety four species, sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.
 
@@
 Even though Heliconiids are conspicuously colored, they are extremely abundant.
-They were also slow in mobility.
+They are also slow in mobility.
 Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature.
@@
 Having this noticeable property, they are easily recalled by predators.
-Their wing pattern works as a warning to them.
+Their wing pattern works as a warning to predators.
 Once a predator has the knowledge of their inedible and unpalatable property, they would probably never attempt to try it again.
@@
 \begin{quote}
-``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they 'act a part'.
+\textsl{``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they 'act a part'.
 An actor is a mime, and so the representation of a false warning pattern was called \textit{mimicry}.
-Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."
+Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."}
 \end{quote}
@@
 	\includegraphics[scale=1]{images/Batesplate_ArM}
-	\caption{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
+	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
+\cite{bates1862}}
 	\label{fig:batesian-butterfly}
@@
 \begin{quote}
-``resemblance in external appearance, shapes and colors between members of widely distinct families."
+\textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
 \end{quote}
@@
 \begin{quote}
-``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."
+\textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
 \end{quote}
@@
 \begin{itemize}
-	\item ``that the imitative species occur in the same area and occupy the same station as the imitated".
-This increases the probability that a predator will affect both parties concerned.
+	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".} This increases the probability that a predator will affect both parties concerned.
 Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
-	\item ``that the imitators are always the more defenseless". On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
-	\item ``that the imitators are always less numerous in individuals".
-What is meant here is that the deceived animal should encounter the mimic less often than the model.
+	\item \textsl{``that the imitators are always the more defenseless".} On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
+	\item \textsl{``that the imitators are always less numerous in individuals".} What is meant here is that the deceived animal should encounter the mimic less often than the model.
 This is true when the deceived animal must learn to recognize model and mimic and when positive and negative experiences carry equal weight.
-But it is known from various learning experiments that when an animal has learn about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences.
+But it is known from various learning experiments that when an animal has learned about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences.
 Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces.
 When the deceptive animal possesses an innate reaction to the model the number of mimics can be virtually unlimited.
-	\item ``that the imitators differ from the bulk of their allies".
-The most remarkable cases of mimicry are those where close relatives form divergent models.
+	\item \textsl{``that the imitators differ from the bulk of their allies".} The most remarkable cases of mimicry are those where close relatives form divergent models.
 It is nevertheless highly possible that groups of closely related species may be similar mimics of the same model.
 Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry.
-	\item ``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance." This criteria, like the previous one is aimed at defining mimicry as a special adaptation.
+	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} This criteria, like the previous one is aimed at defining mimicry as a special adaptation.
 But if one of two closely related species both of which are poisonous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
@@
 \section{Mullerian Mimicry}
-Bates was not able to explain some phenomenon of mimicry.
+Bates was not able to explain some phenomena of mimicry.
 Occasionally two inedible unrelated butterfly species are amazingly similar in appearance.
@@
 When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
-Because of predator's limited memory, all these species still loose their number even after being inedible.
+Because of predator's limited memory, all these species still lose their number even after being inedible.
 So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different family also tend to evolve to have similar appearance.
-This phenomenon is referred to as Mullerian Mimicry in the name of Fritz Muller.
+This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.
 
-According to Huheey \cite{huheey1988} ``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution \cite{muller1879}." In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
+According to Huheey \cite{huheey1988} \textsl{``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution" \cite{muller1879}.} In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
 Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species.
@@
 Preys resemblance does not have to be close enough to cause misidentification on the part of the predator, but merely similar enough to remind it of a bitter past experience with similar prey.
-As Huheey continues ``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
-Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian.
-"
+As Huheey continues \textsl{``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
+Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian."}
 
@@
 	\includegraphics[scale=0.75]{images/BatesMimButter}
-	\caption{A very well-known examples of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom).
+	\caption[A very well-known example of mimicry, the viceroy butterfly]{A very well-known example of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom).
 It was considered for a long time that this is an ideal example of Batesian mimicry.
@@
 Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another.
-Thus, ``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}.
+Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}}.
 
@@
 
-``According to punctuated equilibrium, therefore, evolution is not more of less both, gradual, and continual, as has been supposed for most purposes in most post-Darwinian theories.
-Rather, most morphological change is held to take place with in geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
-The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}
+\textsl{``According to punctuated equilibrium, therefore, evolution is not more of less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories.
+Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
+The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}}
 
@@
 	\includegraphics[scale=0.5]{images/Punctuated-equilibrium}
-	\caption{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
+	\caption[Punctuated equilibrium vs.
+phyletic gradualism]{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
 Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}

### 2010-11-29 docs/tex/model.tex
Changed the name of the chapters.
Some updates. Nothing significant.
Modified with Dr. Grogono's comments

@@
 %Chapter describing the model
-\chapter{Modeling the evolution of mimicry}
+\chapter{The Model: Evolution of Mimicry}
 
-\begin{quotation}
-``Modeling, it should be clear is an art form.
+\begin{quote}
+\textsl{``Modeling, it should be clear is an art form.
 It depends on the experience and taste of the modeler.
@@
 The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" - John H.
-Holland \cite{holland1996}.
-\end{quotation}
+Holland \cite{holland1996}.}
+\end{quote}
 
@@
 
-The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the Laws and Life project by Peter Grogono \cite{grogono2003}.
+The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \cite{grogono2003}.
 
@@
 According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established.
-Their was existence of multiple mimicry rings of very different frequency.
-Second experiment was carried out with some palatable species along with the unpalatable once which was able to reach conditions of Batesian mimicry also with less mimicry rings, were hypothesis 2 borne out.
+There was existence of multiple mimicry rings of very different frequency (population).
+Second experiment was carried out with some palatable species along with the unpalatable once which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out.
 It can be observed that,
@@
 \begin{quote}
-\textsl{The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
-Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them.
-\cite{franks2003}}
+\textsl{``The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
+Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them." \cite{franks2003}}
 \end{quote}
@@
 \section{FormAL Framework}
-The ``FormAL framework" is a collection of ideas and concepts taken from Peter Grogono's FormAL(Formal Artificial Life) project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's FormAL(Formal Artificial Life) project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
 The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}".
@@
 \begin{tabular}{cc}
-		\multicolumn{2}{c}{ \includegraphics[scale=0.50]{images/cells-front} } \\
-		\includegraphics[scale=0.40]{images/cells-top} & \includegraphics[scale=0.40]{images/cells-side} \\
+		\multicolumn{2}{c}{ \includegraphics[scale=0.60]{images/cells-front} } \\
+		\includegraphics[scale=0.50]{images/cells-top} & \includegraphics[scale=0.50]{images/cells-side} \\
 \end{tabular}
-\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
+\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
 \label{tab:3-d-environment-images}
@@
 	\includegraphics[scale=5]{images/CA_rule30s}
-	\caption{Cellular Automata Rule 30.
+	\caption[Cellular Automata]{Cellular Automata Rule 30.
 	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
@@
 	\end{tabular}
-	\caption{Cellular Automata Rule}
+	\caption{Cellular Automata rule}
 	\label{tab:cellular-automata-rule}
@@
 The Genome of the prey species consists of 17 bits as presented in Table \ref{tab:prey-genome}.
-The first eight bit is the rule, which is used to generate Cellular Automata pattern.
+The first eight bits is the rule, which is used to generate Cellular Automata pattern.
 The next two bits are used to represent palatability of the organism explained detail in Section \ref{sec:genetic-palatability-representation}.
@@
 \label{sec:genetic-palatability-representation}
-The palatability of each prey species is fixed and has been represented with 2 bit of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
+The palatability of each prey species is fixed and has been represented with 2 bits of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
 
@@
 	\end{tabular}
-	\caption{Genetic representation of Palatability}
+	\caption{Genetic representation of palatability}
 	\label{tab:genetic-representation-palatability}
@@
 \subsubsection{Reproduction}
-Every prey species starts reproducing when it reaches the ``Reproductive age limit".
+Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}.
 If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it.
@@
 Their mobility and reproduction capability is controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
-So every new predator species gets to born with zero memory and with no inharitance from parents.
+So every new predator species gets to born with zero memory and with no inheritance from parents.
 A set of parameters are defined to control predators' population and learning ability in the environment.
@@
 \begin{quote}
-\textsl{When an axon of cell A is near enough to excite a cell B and repeatedly or persistently takes part in firing it, some growth process or metabolic changes take place in one or both cells such that A's efficiency as one of the cells firing B is increased.}
+\textsl{``When an axon of cell A is near enough to excite a cell B and repeatedly or persistently takes part in firing it, some growth process or metabolic changes take place in one or both cells such that A's efficiency as one of the cells firing B is increased."}
 \end{quote}
@@
 
-In this way the predator memory is limited to ``Hopfield Maximum Memory Size".
+In this way the predator memory is limited to \textsl{``Hopfield Maximum Memory Size"}.
 After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored.
@@
 \subsection{Genome}
-Each predators has a 5 bit genome as explained in Table \ref{tab:predator-genome}.
-The first four bit represents its mobility and the magnitude of the force component with which it moves around the environment.
-The last bit controls reproduction capability of the specific species.
+Each predator has a 5 bit genome as explained in Table \ref{tab:predator-genome}.
+The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment.
+The last bit controls reproduction capability of each species.
 
@@
 	\centering
-	\includegraphics[scale=0.40]{images/predators-40}
-	\caption{A population of 40 predators distributed over the environment.}
+	\includegraphics[scale=0.60]{images/predators-40}
+	\caption[A population of predators]{A population of 40 predators distributed over the environment.}
 	\label{fig:predators-40}
@@
 There are two control parameters that effect the reproduction of predator species.
-The first is "Reproduction Age Limit".
+The first is \textsl{"Reproduction Age Limit"}.
 This is the minimum age a predator has to reach before starting to involve itself for reproduction.
 This parameter has been set to 500 iterations during the result and analysis section of the thesis.
-The second parameter is "Reproduction Interval" which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
+The second parameter is \textsl{"Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
 This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment.

### 2010-11-29 docs/tex/result.tex
Changed the name of the chapters.
Small updates
Some Quotations Added
Modified with Dr. Grogono's comments

@@
 % All the result and analysis
-\chapter{Results and Analysis}
+\chapter{The Results}
+
+\begin{quote}
+\textsl{``The most incomprehensible thing about the world is that it is comprehensible." - Albert Einstein}
+\end{quote}
 
@@
 \end{tabular}
-\caption{Parameters to Mimicry Ring Report.}
+\caption{Parameters to mimicry ring report.}
 \label{tab:ring-report-control-parameters}
@@
 
-The memory configuration size for predators are a very interesting parameter.
+The memory configuration size for predators is a very interesting parameter.
 The minimum memory size is directly associated with the number of prey species with which we initiate the simulation.
@@
 As mentioned in Table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
-After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgement.
+After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment.
 At this point its memory size is zero.
@@
 
-Now as we know the behaviour of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
+Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
 So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern previously captured and the patterns stored in memory.
@@
 	\includegraphics[scale=0.50]{images/simTime10k-2Prey}
-	\caption{Population distribution of mimicry rings, initialized with 2 prey species.}
+	\caption[Population distribution of mimicry rings (2 prey species)]{Population distribution of mimicry rings, initialized with 2 prey species.}
 	\label{fig:plot-2-prey}
@@
 	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
-	\caption{Number of mimicry rings, initialized with 2 prey species.}
+	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
 	\label{fig:ringSize10k-2Prey}
@@
 	\includegraphics[scale=0.55]{images/simTime7600}
-	\caption{Graphical representation of the model, simulation time: 7600.}
+	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
 \end{figure}
@@
 	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
-	\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
+	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
 	\label{fig:plot-4-prey}
@@
 	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
-	\caption{Number of mimicry rings, initialized with 4 prey species.}
+	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
 	\label{fig:ringSize10k-4Prey}
@@
 	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
-	\caption{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
+	\caption[Graphical representation of the model (simulation time: 11200)]{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
 \end{figure}
@@
 	\includegraphics[scale=0.40]{images/simTime9K-4MorePrey}
-	\caption{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
+	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
 	\label{fig:plot-4-more-prey}
@@
 	\includegraphics[scale=0.50]{images/ringSize10k-4MorePrey}
-	\caption{Number of mimicry rings, initialized with 4 prey species with increased population.}
+	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
 	\label{fig:ringSize10k-4MorePrey}
@@
 	\includegraphics[scale=0.40]{images/simTime10k-6Prey}
-	\caption{Population distribution of mimicry rings, initialized with 6 prey species.}
+	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
 	\label{fig:plot-6-prey}
@@
 	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
-	\caption{Number of mimicry rings, initialized with 6 prey species.}
+	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
 	\label{fig:ringSize10k-6-Prey}
@@
 	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-unp}
-	\caption{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
 	\label{fig:plot-4-prey-unp}
@@
 	\includegraphics[scale=0.50]{images/ringSize9k-4Prey-unp}
-	\caption{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
 	\label{fig:ringSize10k-4-Prey-unp}
@@
 	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
-	\caption{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
+	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
 	\label{fig:plot-4-prey-p}
@@
 	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
-	\caption{Number of mimicry rings, initialized with 4 prey species all palatable.}
+	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
 	\label{fig:ringSize8k-4-Prey-p}
@@
 	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
-	\caption{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
+	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
 	\label{fig:plot-1-prey-unp}
@@
 	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
-	\caption{Number of mimicry rings, initialized with 1 prey species unpalatable.}
+	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
 	\label{fig:ringSize8k-1-Prey-unp}
@@
 	\includegraphics[scale=0.40]{images/simTime9k-1-p}
-	\caption{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
+	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
 	\label{fig:plot-1-prey-p}
@@
 	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
-	\caption{Number of mimicry rings, initialized with 1 palatable prey species.}
+	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
 	\label{fig:ringSize8k-1-Prey-p}

### 2010-11-29 docs/tex/review.tex
Modified with Dr. Grogono's comments

@@
 \begin{quote}
-``The theory of evolution by cumulative natural selection is the only theory we know of that is in principle capable of explaining the existence of organized complexity" - Richard Dawkins \cite{dawkins1996}
+\textsl{``The theory of evolution by cumulative natural selection is the only theory we know of that is in principle capable of explaining the existence of organized complexity" - Richard Dawkins \cite{dawkins1996}}
 \end{quote}
@@
 
-``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}
+\textsl{``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}}
 
@@
 \paragraph{Turing(1948)}
-Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled ``Intelligent Machinery" where the expression of ``genetical or evolutionary search"  was used \cite{turing1948}.
+Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled \textsl{``Intelligent Machinery"} where the expression of \textsl{``genetical or evolutionary search"}  was used \cite{turing1948}.
 He suggested a range of ideas for systems which could be said to modify their own programs.
@@
 \paragraph{L. Fogel, Owens and Walsh (1965)}
-A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in ``Artificial Intelligence through a simulation of evolution" \cite{fogel1966}.
+A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in \textsl{``Artificial Intelligence through a simulation of evolution"} \cite{fogel1966}.
 In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series.
@@
 Holland.
-His ground breaking book ``Adaptation in natural and artificial systems" \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.
+His ground breaking book \textsl{``Adaptation in natural and artificial systems"} \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.
 
@@
 Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem.
-Starting from a high-level statement of ``what needs to be done" it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.
+Starting from a high-level statement of \textsl{``what needs to be done"} it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.
 
@@
 \begin{itemize}
-	\item ``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."
-	\item ``Selection acts as a force pushing quality."
+	\item \textsl{``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."}
+	\item \textsl{``Selection acts as a force pushing quality."}
 \end{itemize}
@@
 Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent.
-According to Eiben \cite{eiben2003} ``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features." It is important that variation operators are defined based on the representation of the problem under consideration.
+According to Eiben \cite{eiben2003} \textsl{``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features."} It is important that variation operators are defined based on the representation of the problem under consideration.
 
@@
 As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
-In contrast to that in Artificial Life scientist take concepts from Biology specially Evolutionary Biology and genetics and implement into computer science.
+In contrast to that in Artificial Life scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.
 
@@
 \begin{quote}
-`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature.
+\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature.
 Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts.
-The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."
+The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment." - Christopher G.
+Langton}
 \end{quote}
 
-\section{History}
+%\section{History}
 

### 2010-12-04 docs/tex/review.tex
References fixed.
Unfinished Artificial Life section

@@
 \end{quote}
+
+\section{Introduction}
 
@@
 
+Christopher G.
+Langton is considered as one of the founders of the filed of Artificial Life.
+He invented the term in the late 1980's when he organized the first ``International Conference on the Synthesis and Simulation of Living Systems" at the Los Alamos National Laboratory in 1987.
+
 In defining Artificial Life Christopher G. Langton states the following,
@@
 The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}.
-While providing a brief survey over different AL models he talks about \textbf{wetware systems} which work at the molecular level, the \textbf{software systems} which work at the cellular level and the \textbf{hardware systems} which works at the organism level.
+While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.
+
+%Describe Wetware, Software and Hardware systems of artificial life.
 
@@
 
-\subsubsection{Echo}
+\subsection{Echo}
+Echo is a gedanken experiment rather than a precise simulation.
+
+\subsubsection{Criteria}
+Echo has been constructed on a certain set of criteria. The following is a short summary on it extracted from \cite{holland1996}.
+
+\begin{itemize}
+	\item Simplicity is considered as the first and foremost criteria.
+Instead of emulating a real system Echo is more of a thought experiment.
+Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model.
+	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting, while mobility is also part of a wide range of geographical setting.
+Input to the environment which are considered as stimuli or resource can also be diversified.
+	\item Fitness of each of the agents is an evolving criteria.
+Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents.
+Instead of being a constant value it should evolve along with the system.
+	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}.
+Interpretation of results from the Echo model should be direct and ready-made.
+As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point.
+So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation.
+5
+	\item 
+	\item 
+\end{itemize}
+
+\subsubsection{Organization}
+
+\subsubsection{Agents}
+Individual agents in echo
+
+\subsubsection{Replication}
+
+\subsubsection{Interactions}
+\paragraph{Combat}
+\paragraph{Trading}
+\paragraph{Mating}
+\subsubsection{Results}
+
+\paragraph{Criteria}
 
 \section{Cellular Automata}
+
+\section{Conclusion}

### 2010-12-05 report/ringsAllData.m
Colour plot marker added, with increased font size.

@@ -9,19 +9,23 @@ i = 1;
 plotHandles = [];
 legends = {};
 %markers = {'+k';'ok';'*k';'xk';'sk';'dk';'vk';'^k';'>k';'<k';'pk';'hk'};
-markers = {'<k';'>k';'^k';'vk';'dk';'sk';'*k';'ok';'+k'};
+%markers = {'<k';'>k';'^k';'vk';'dk';'sk';'*k';'ok';'+k'};
+markers = {'<';'>';'^';'v';'d';'s';'*';'o'};
+grey = [0.5 0.5 0.5];
+pink = [0.5 0 0];
+markerFaceCol = {'y';'m';'c';pink;'g';'b';'w';grey};
 
 %Plot predator population
 plot(T, logs(:, 2), '-k');
-p0 = plot(T(1:35:timeSize), logs(1:35:timeSize, 2), 'hk');
+p0 = plot(T(1:35:timeSize), logs(1:35:timeSize, 2), 'h', 'MarkerEdgeColor','k','MarkerFaceColor','r');
 
 %Plot all the 8 rings of prey population both palatable and unpalatable.
 for c = 3:3:size(logs, 2)
     p1 = plot(T, logs(:, c + 1), '-k');
-    p2 = plot(T(1:50:timeSize), logs(1:50:timeSize, c + 1), markers{i});
+    p2 = plot(T(1:50:timeSize), logs(1:50:timeSize, c + 1), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i});
 %    p2 = plot(T(1:c*3:timeSize), logs(1:c*3:timeSize, c + 1), markers{i});
     p3 = plot(T, logs(:, c + 2), ':k');
-    plot(T(1:75:timeSize), logs(1:75:timeSize, c + 2), markers{i});
+    plot(T(1:75:timeSize), logs(1:75:timeSize, c + 2), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i});
 %    plot(T(1:c*7:timeSize), logs(1:c*7:timeSize, c + 2), markers{i});
     plotHandles = [plotHandles p2];
     legends = [legends; strcat( 'CA Rule: ', num2str(logs(1, c)))];
@@ -36,8 +40,9 @@ hold off;
 plotHandles = [plotHandles p1 p3 p0];
 legends = [legends;'Palatable';'Unpalatable';'Predator'];
 
-legend(plotHandles, legends);
[…]

### 2010-12-05 docs/tex/result.tex
New image update.

@@
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2400} \\ \hline
   Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
@@
 
-Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500.
+Prey demise age has been kept to 2000 iterations while predator demise age is set to 2400.
 But later in the following results predator demise age has been increased to 5000 iterations.
@@
 At around the same time different other species of prey population gets to be born with mutated CA patterns.
-Over time the population of CA Rule 110 dominates the population as most predators recognizes it as unpalatable.
-And similarly a population of CA Rule 110 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 30 (Time: 5000 approx.) which was initially considered as a set of palatable species.
+Over time the population of CA Rule 30 dominates the population as most predators recognizes it as unpalatable.
+And similarly a population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 5000 approx.) which was initially considered as a set of palatable species.
 
@@
 
-As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations.
+As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 26 rings at the end of 10000 iterations.
 We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.

### 2010-12-05 report/ringSizePlot.m

@@ -5,7 +5,8 @@ T = rings(:, 1);
 R = rings(:, 2);
 %Plot ring size
 plot(T, R, '-k');
+%axis([0 T(size(T, 1)) -1 25 ]);
 axis([0 T(size(T, 1)) 0 R(size(R, 1))+2 ]);
-xlabel('Simulation Time');
-ylabel('Number of Rings');
-title('Mimicry number of ring variation');
+xlabel('Simulation Time','fontsize',14);
+ylabel('Number of Rings','fontsize',14);
+title('Mimicry number of ring variation','fontsize',14);

### 2010-12-05 src/Mimicry/System.cpp
New image update.

@@ -102,7 +102,7 @@ const int System::NUMBER_OF_RINGS_TO_REPORT = 8;
 /**
  * Minimum number of patterns that need to be stored in Predator memory before starting recognition.
  */
-int System::MIN_MEMORY_SIZE = 4;
+int System::MIN_MEMORY_SIZE = 2;
 
 /**
  * Maximum number of patterns stored in Hopfield Memory
@@ -128,7 +128,7 @@ int System::PREDATOR_ATTACK_INTERVAL = 100;
  * Probability of the number of new born \a Predator species with a 
  * mutating genome.
  */
-float System::PREDATOR_GENOME_MUTATION_RATE = (float)0.3;
+float System::PREDATOR_GENOME_MUTATION_RATE = (float)0.03;
 
 /**
  * Mimminum age for \a Predator species to start reproduction.
@@ -138,12 +138,12 @@ int System::PREDATOR_REPRODUCTION_AGE_LIMIT = 500;
 /**
  * Time interval to wait before a \a Predators start reproducing again.
  */
-int System::PREDATOR_REPRODUCTION_INTERVAL = 2000;
+int System::PREDATOR_REPRODUCTION_INTERVAL = 1000;
 
 /**
  * Maximum age upto which \a Predator species will survive in the environment.
  */
-int System::PREDATOR_DEMISE_AGE = 5000;
+int System::PREDATOR_DEMISE_AGE = 2400;
 
 /**
  * Display outline in the model window when non-zero.

### 2010-12-05 docs/tex/result.tex
Two prey species figure update.

--- 2010-11-29 docs/tex/result.tex
@@
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1200} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
@@
 Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500.
-But later in the following results predator demise age has been increased to 5000 iterations.
+But in the later experiments predator demise age has been increased to 5000 iterations.
 Predators in this simulation generates selection pressure for the evolution of mimicry.
@@
 	\centering
-	\includegraphics[scale=0.50]{images/simTime10k-2Prey}
-	\caption[Population distribution of mimicry rings (2 prey species)]{Population distribution of mimicry rings, initialized with 2 prey species.}
+	\includegraphics[scale=0.40]{images/simTime10k-2Prey}
+	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
 	\label{fig:plot-2-prey}
@@
 
-The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for over 10000 iterations.
+The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations.
 With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
@@
 
-By closely observing the graph we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species.
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime5k-2Prey}
+	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
+	\label{fig:plot-2-prey-5k}
+\end{figure}
+
+Figure \ref{fig:plot-2-prey-5k} is the same experiment as of Figure \ref{fig:plot-2-prey}, but only up to 5000 iterations.
+By closely observing the graph of Figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species.
 At around time 1000 the prey population starts reproducing as the population increases.
 At around the same time different other species of prey population gets to be born with mutated CA patterns.
-Over time the population of CA Rule 110 dominates the population as most predators recognizes it as unpalatable.
-And similarly a population of CA Rule 110 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 30 (Time: 5000 approx.) which was initially considered as a set of palatable species.
+Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognizes it as unpalatable.
+And similarly a population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.) which was initially considered as a set of palatable species.
 
@@
 
-As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations.
+As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
 We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
@@
 Only the 8 most populous rings have presented in the graph above with population verses simulation time.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
+	\caption[Population distribution of generated mimicry rings (initialized with 2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
+	\label{fig:plot-2-prey-generated-prey}
+\end{figure}
+
+Figure \ref{fig:plot-2-prey-generated-prey} is the same experimental data of Figure \ref{fig:plot-2-prey} but with only the generated ring of prey species.
+The initialized dominant population of CA rule 110 and 30, both palatable and unpalatable has been eliminated from this graph to observe the newly created rings.
+In this graph we can observe that among the population of new patterns the unpalatable ones dominate (CA Rule 14, 26, 94).
+Also the palatable counterpart of the unpalatable population is increasing their number.
+Species with un-mimicked palatable pattern is very few in number.
 
@@
   						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1400} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline

### 2010-12-06 docs/tex/result.tex
New Graphs added...

@@
 Also the palatable prey species with similar patterns to CA rule 55 and 110 are taking full advantage of their deceiving pattern and increasing their population (represented with line curve).
-The two unpalatable set of patterns CA Rule 90 and 130 are unable to dominate the population.
-Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in Figure \ref{fig:ringSize10k-4Prey}, the total number of rings reached somewhere near 33 while each of them has comparatively low representative population.
+The two palatable set of patterns CA Rule 190 and 30 are unable to dominate the population.
+Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in Figure \ref{fig:ringSize10k-4Prey}.
+The total number of rings reached somewhere near 37 while each of them has comparatively low representative population.
 Batesian mimicry is in full effect in this simulated environment.
@@
   						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime9K-4MorePrey}
+	\includegraphics[scale=0.45]{images/simTime10K-4MorePrey}
 	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
@@
   						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
   Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-6Prey}
+	\includegraphics[scale=0.45]{images/simTime10k-6Prey}
 	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
@@
   \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{30}} \\ \cline{2-4}
+  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
   					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-unp}
+	\includegraphics[scale=0.45]{images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 The results according to Figure \ref{fig:plot-4-prey-unp} are expected as it can be observed the population of unpalatable species has prevailed.
-After nearly 9000 iterations we can see unpalatable species CA rule 55 has prevailed with the most population.
+After nearly 8000 iterations we can see unpalatable species CA rule 55 has prevailed with the most population.
 Its palatable counter part is following this population.
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize9k-4Prey-unp}
+	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-unp}
 	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}

### 2010-12-06 report/ringsAllData.m

@@ -12,20 +12,20 @@ legends = {};
 %markers = {'<k';'>k';'^k';'vk';'dk';'sk';'*k';'ok';'+k'};
 markers = {'<';'>';'^';'v';'d';'s';'*';'o'};
 grey = [0.5 0.5 0.5];
-pink = [0.5 0 0];
-markerFaceCol = {'y';'m';'c';pink;'g';'b';'w';grey};
+brown = [0.5 0 0];
+markerFaceCol = {'y';'m';'c';brown;'g';'b';'w';grey};
 
 %Plot predator population
-plot(T, logs(:, 2), '-k');
-p0 = plot(T(1:35:timeSize), logs(1:35:timeSize, 2), 'h', 'MarkerEdgeColor','k','MarkerFaceColor','r');
+plot(T, logs(:, 2), '-k', 'LineWidth',1.0);
+p0 = plot(T(1:35:timeSize), logs(1:35:timeSize, 2), 'h', 'MarkerEdgeColor','k','MarkerFaceColor','r', 'MarkerSize',8);
 
 %Plot all the 8 rings of prey population both palatable and unpalatable.
 for c = 3:3:size(logs, 2)
-    p1 = plot(T, logs(:, c + 1), '-k');
-    p2 = plot(T(1:50:timeSize), logs(1:50:timeSize, c + 1), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i});
+    p1 = plot(T, logs(:, c + 1), '-k', 'LineWidth',1.0);
+    p2 = plot(T(1:50:timeSize), logs(1:50:timeSize, c + 1), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i}, 'MarkerSize',8);
 %    p2 = plot(T(1:c*3:timeSize), logs(1:c*3:timeSize, c + 1), markers{i});
-    p3 = plot(T, logs(:, c + 2), ':k');
-    plot(T(1:75:timeSize), logs(1:75:timeSize, c + 2), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i});
+    p3 = plot(T, logs(:, c + 2), ':k', 'LineWidth',1.0);
+    plot(T(1:75:timeSize), logs(1:75:timeSize, c + 2), markers{i},'MarkerEdgeColor','k','MarkerFaceColor',markerFaceCol{i}, 'MarkerSize',8);
[…]

### 2010-12-06 src/Mimicry/System.cpp
All results updated...

@@ -128,7 +128,7 @@ int System::PREDATOR_ATTACK_INTERVAL = 100;
  * Probability of the number of new born \a Predator species with a 
  * mutating genome.
  */
-float System::PREDATOR_GENOME_MUTATION_RATE = (float)0.03;
+float System::PREDATOR_GENOME_MUTATION_RATE = (float)0.3;
 
 /**
  * Mimminum age for \a Predator species to start reproduction.
@@ -138,12 +138,12 @@ int System::PREDATOR_REPRODUCTION_AGE_LIMIT = 500;
 /**
  * Time interval to wait before a \a Predators start reproducing again.
  */
-int System::PREDATOR_REPRODUCTION_INTERVAL = 1000;
+int System::PREDATOR_REPRODUCTION_INTERVAL = 2500;
 
 /**
  * Maximum age upto which \a Predator species will survive in the environment.
  */
-int System::PREDATOR_DEMISE_AGE = 2400;
+int System::PREDATOR_DEMISE_AGE = 7000;
 
 /**
  * Display outline in the model window when non-zero.

### 2010-12-06 docs/tex/result.tex
All results updated...

@@
 	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
-	\caption[Population distribution of generated mimicry rings (initialized with 2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
+	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
 	\label{fig:plot-2-prey-generated-prey}
@@
   						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
@@
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{30}} \\ \cline{2-4}
+  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
   					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
+	\includegraphics[scale=0.40]{images/simTime10k-4Prey-p}
 	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
+	\includegraphics[scale=0.50]{images/ringSize10k-4Prey-p}
 	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
+	\includegraphics[scale=0.40]{images/simTime8k-1Prey-unp}
 	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime9k-1-p}
+	\includegraphics[scale=0.40]{images/simTime10k-1Prey-p}
 	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
+	\includegraphics[scale=0.50]{images/ringSize10k-1Prey-p}
 	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}

### 2010-12-07 src/Mimicry/Mimicry.cpp
Results chapter completed...

@@ -523,7 +523,7 @@ int main(int argc, char** argv)
 		&System::MIN_MEMORY_SIZE,
         MIN_MEMORY_SIZE,
         control);
-    predatorMinMemorySize->set_int_limits(2, 20);
+    predatorMinMemorySize->set_int_limits(1, 20);
 
     GLUI_Spinner *predatorMaxMemorySize = glui->add_spinner_to_panel(
         hopfieldNetworkConfg,

### 2010-12-07 docs/tex/result.tex
Results chapter completed...

@@
 \section{Initial configuration with two prey species}
+\label{sec:init-conf-2prey}
 % Put the table here
@@
 Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation.
-The Genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents.
+The genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents.
 As mentioned earlier the genome mutation rate has been separated from the pattern mutation rate to bring more control to the number of mimicry rings generated.
@@
 With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
-Two prey species are in a ring if their CA pattern have a hamming distance within 10 bits, parameter mentioned in Table \ref{tab:ring-report-control-parameters}.
+Two prey species are considered to be in a ring if their CA pattern have a hamming distance within 10 bits.
+This parameter is mentioned in Table \ref{tab:ring-report-control-parameters}.
 Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve.
@@
 
-Figure \ref{fig:plot-2-prey-5k} is the same experiment as of Figure \ref{fig:plot-2-prey}, but only up to 5000 iterations.
-By closely observing the graph of Figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species.
-At around time 1000 the prey population starts reproducing as the population increases.
-At around the same time different other species of prey population gets to be born with mutated CA patterns.
-Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognizes it as unpalatable.
-And similarly a population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.) which was initially considered as a set of palatable species.
+The plot of figure \ref{fig:plot-2-prey-5k} is from the same experiment as of figure \ref{fig:plot-2-prey}, but only up to 5000 iterations.
+By closely observing the graph of figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches the maturity for consuming prey species (effect of the parameter `Minimum Attack Age' from table \ref{tab:config-table-2-prey}).
+At around time 1000 the prey population starts reproducing as the population increases (controlled by `Reproduction Age Limit' from table \ref{tab:config-table-2-prey}).
+At the same time different other species of prey gets to be born with mutated CA patterns.
+There is a straight drop of prey population at time 2000, when all the prey species with which the simulation was initialized come to its demise age (controlled by `Prey Demise Age' at table \ref{tab:config-table-2-prey}).
+Over time the population of CA Rule 30 dominates the population (figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
+Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.).
+CA Rule 110 was initialized as a set of palatable species.
 
-We can observe from the above results that the evolution of mimicry has taken effect.
-A population of mimics were successfully able to exceed the population of other prey species the reason being avoidance by predators of prey pattern similar to unpalatable ones.
+We can observe from the above result that the evolution of mimicry has taken effect.
+A population of mimics were successfully able to exceed the population of other prey species, and the reason being avoidance by predators of prey pattern similar to unpalatable ones.
 We can conclude that Batesian mimicry has taken effect in the simulation.
 
-The above configuration in Table \ref{tab:config-table-2-prey} is also the most appropriate condition for Mullerian Mimicry.
+The configuration in table \ref{tab:config-table-2-prey} is also the most appropriate condition for Mullerian Mimicry.
 We can observe that a single pattern of unpalatable species dominate the entire population.
-These effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviors of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.
+The effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviors of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.
 
@@
 
-As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
-We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
-For example if we observe the set of pattern genotype with very different phenotype in Table \ref{tab:diff-in-pattern}.
+Observing from figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
+A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
+For example if we take a look at the set of pattern genotype with very different phenotype in table \ref{tab:diff-in-pattern}.
 
@@
 
-All the patterns in Table \ref{tab:diff-in-pattern} have a genetic bit difference of 1.
+All the patterns in table \ref{tab:diff-in-pattern} have a genetic bit difference of 1.
 So by a single mutation there can be three different set of phenotype for a child organism from its parent.
-This is largely the reason for the increased number of Rings created in the simulation.
-Only the 8 most populous rings have presented in the graph above with population verses simulation time.
+This is largely the reason for the increased number of mimicry rings created in the simulation.
+Only the 8 most populous rings are presented in the graphs with population verses simulation time.
 
@@
 
-Figure \ref{fig:plot-2-prey-generated-prey} is the same experimental data of Figure \ref{fig:plot-2-prey} but with only the generated ring of prey species.
+Figure \ref{fig:plot-2-prey-generated-prey} is the same experimental data of figure \ref{fig:plot-2-prey} but with only the newly generated ring of prey species.
 The initialized dominant population of CA rule 110 and 30, both palatable and unpalatable has been eliminated from this graph to observe the newly created rings.
-In this graph we can observe that among the population of new patterns the unpalatable ones dominate (CA Rule 14, 26, 94).
+In this plot, among the population of new patterns the unpalatable ones dominate (CA Rule 14, 26, 94).
 Also the palatable counterpart of the unpalatable population is increasing their number.
-Species with un-mimicked palatable pattern is very few in number.
+Species with \textsl{un-mimicked} palatable pattern is very few in number.
+
+The screen shot in Figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
+The red agents are predators while the black agents with different textured patterns are the prey species.
+According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.
 
@@
 \end{figure}
-
-The screen shot in Figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
-The red agents are predators while the black agents with different textured patterns are the prey species.
-According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.
 
@@
 The predator reproduction interval has been increased to 1400, while the minimum memory size has been increased to 4 instead of 2 as the predator is expected to memorize four different species of prey before starting to make intelligent decision about consuming them.
+The rest of the parameters remain the same as from the experiment in section \ref{sec:init-conf-2prey}.
 
@@
 
-By observing the graph in Figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species which was put at the initial sate of the simulation has dominated after 10000 iterations.
+By observing the graph in Figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial sate of the simulation has dominated after 10000 iterations.
 CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve).
@@
 The two palatable set of patterns CA Rule 190 and 30 are unable to dominate the population.
-Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in Figure \ref{fig:ringSize10k-4Prey}.
-The total number of rings reached somewhere near 37 while each of them has comparatively low representative population.
+Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in figure \ref{fig:ringSize10k-4Prey}.
+The total number of rings reached somewhere near 37 while most of them have comparatively low representative population.
 Batesian mimicry is in full effect in this simulated environment.
@@
 In this run of the simulation some significant parameters have been updated.
-One is the initial population of prey species.
+First one is the initial population of prey species.
 It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600.
@@
 
-Some very interesting diversity of rings can be observed in the simulation for updating these parameters.
-The unpalatable rings and their deceptive counterparts(palatable prey with similar pattern) still have their dominance.
-We can observe CA Rule 55 and 190 are the highest number of population.
-Interestingly enough CA Rule 110 which started as a palatable prey species has also taken dominance in the population which is the second highest.
-Both palatable and unpalatable version of CA Rule 110 are present with equal population density.
+Some very interesting diversity of mimicry rings can be observed in the simulation for updating these parameters.
+The unpalatable rings and their deceptive counterparts (palatable prey with similar pattern) still have their dominance.
+We can observe CA Rule 55 and 190 are the highest in number of population.
+Interestingly enough CA Rule 30 and 110 which started as palatable prey species has also taken dominance in the simulation, following 55 and 190.
+The unpalatable counter part of CA Rule 30 and 110 are also following the palatable population.
+
+The total number of rings have increased much in this run compared to the previous one.
+To summarize the results of this experiment, we can observe, increased diversity of prey population and much more interaction between predator and prey.
 
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-4MorePrey}
+	\includegraphics[scale=0.40]{images/ringSize10k-4MorePrey}
 	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
@@
 
-The total number of rings had much increment in this run compared to the previous one.
-To summarize we can observe increased diversity of prey population and much more interaction between predators and prey.
-
 \section{Initial population with six prey species}
+\label{sec:init-conf-6-prey}
 \begin{table}[H]
@@
 To evaluate the simulation at a more complex level we increase the prey population to 900, consisting of 6 different species with very different pattern configuration.
-Similarly to increase predator-prey interaction we also increase the number of predator population to 30.
+To boost predator-prey interaction we also increase the number of predator population to 30.
 Predator reproduction interval has been set comparatively lower in this simulation to 2000 iteration similar to the demise age which is set to 5000.
@@
 For memory configuration, the minimum number is set to 6, meaning the predator will have to store 6 different prey pattern configuration before starting to make intelligent decision about consuming them.
-As previously mention this number is always set in accordance with the initial number of different prey configuration.
+As previously mentioned this number is always set in accordance with the initial number of different prey configuration.
 
@@
 
-With the above set of parameters we can receive the plot of Figure \ref{fig:plot-6-prey}.
+With the above set of parameters we receive the plot of Figure \ref{fig:plot-6-prey}.
+An enormous diversity of species can be observed from this experiment.
+In addition to the six prey species with which the simulation starts, the total number of mimicry rings reach nearly 50.
+Observing the top 8 as presented in the plot of figure \ref{fig:plot-6-prey}, effects of Batesian mimicry is obvious.
+Unpalatable CA Rule 190 and 30 dominates the population.
+Similarly unpalatable CA Rule 105 is also dominant.
+But after 10000 iterations CA Rule 55 seems to have higher population than 105 even though 55 is a \textsl{palatable} set of species.
+This anomaly could be the reason for storing large number of patterns in the predator Hopfiled memory.
+As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate.
+In this simulation memory size is controlled by the 'Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}.
+Also it seems from this experiment that the 'Minimum Memory Configuration' being 6 is rather a large number.
+So there could be possibility of wrong recognition by Hopfield memory.
+Then again this phenomenon is common if we consider behavior of predators in nature.
+It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{sec:mullerian-mimicry}.
 
@@
 
-To further observe the effects of mimicry ring we initialize the simulation with four unpalatable population of prey species.
-As explained earlier the minimum memory configuration is set to 4 as the initial population of prey has four different species.
+To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species.
+After finding different anomalous behavior of predator recognition capability in section \ref{sec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
+As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species.
+Rest of the parameters remain quite unchanged.
 
@@
 
-The results according to Figure \ref{fig:plot-4-prey-unp} are expected as it can be observed the population of unpalatable species has prevailed.
-After nearly 8000 iterations we can see unpalatable species CA rule 55 has prevailed with the most population.
-Its palatable counter part is following this population.
-Unpalatable CA Rule 110 and its palatable counter part are also following the above.
-Similarly the other two species are increasing its population with dominance where the palatable population of deceivers are following them.
+The results according to figure \ref{fig:plot-4-prey-unp} are much expected.
+The population of unpalatable species have prevailed.
+After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed with the most population.
+All of their palatable counter parts are also increasing their population deceiving the predators.
+We observe the effect of the simulation up to 8000 iterations instead of 10000 as the total number of prey species increases at an enormous rate in this simulation within very short period of time.
+As most of the species are unpalatable, predators most do not get the opportunity to consume, causing a much lower prey death rate.
 
@@
 \end{figure}
+
+This experiment is an ideal scenario for observing Mullerian mimicry.
+As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
+From the second work of Frank and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
+But is this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
+By setting this property to one and also increasing `Predator Demise Age' to 7000 while decreasing `Predator Age Interval' to 1500, we get the following plot.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.45]{images/simTime6k-4Prey-unp-1-mem}
+	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.
+Minimum Memory size reduced to one.}
+	\label{fig:plot-4-prey-unp-1-mem}
+\end{figure}
+
+After running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring.
+As it can be observed in figure \ref{fig:plot-4-prey-unp-1-mem} all four unpalatable prey population have a very dominant presence in the simulation.
+Even though predator minimum memory has been reduced to only one pattern, different population of predators become familiar with different prey patterns, which results in the existence of multiple Mullerian mimicry ring instead of a single one.
 
@@
 
+The results for the configuration in table \ref{tab:config-table-4-prey-palatable} can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
+By analyzing details we can see, around simulation time 500 all population of species come to a steady downfall as at this point initial predator species reach its' age for consumption.
+Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction.
+At iteration time 2000 a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
+By this time the population of unpalatable species mutated from the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey come to its demise.
+Predator population, from the beginning of the simulation has taken a very dominant effect.
+As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keep increasing in a geometric rate.
+
 \begin{figure}[H]
@@
 \end{figure}
-
-The results for the configuration in Table \ref{tab:config-table-4-prey-palatable} can be observed in Figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
-By analyzing details we can see, around simulation time 500 all population of species comes to a steady downfall as at this point initial predator species reaches its age for consumption.
-Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction.
-At iteration time 2000 a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
-By this time the population of unpalatable species deceiving the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey comes to its demise.
-Predator population, from the beginning of the simulation has taken a very dominant effect.
-As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keeps increasing in a geometric rate.
 
@@
 Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-p}.
-The number of rings keep increasing but comes to a sudden drop around simulation time 7000 it goes to zero.
+The number of rings keep increasing but comes to a sudden drop around simulation time 7000 and goes to zero.
 
@@
 Until now all experiments have been initialized with multiple prey species.
-The following set of experiments have been done with only a single prey species, for both cases of palatable and unpalatable.
+The following set of experiments have been initialized with only a single prey species, for both cases of unpalatable and palatable.
 
@@
 
-From Figure \ref{fig:plot-1-prey-unp}, it can be observed, the initial set of unpalatable species is dominant as expected.
-And the palatable population mimicking that set is following it.
-Also a bunch of other rings with majority of unpalatable species have been created.
-Mainly because the initial population started with a bunch of unpalatable species, so their evolving generations have similar behavior as well.
+From figure \ref{fig:plot-1-prey-unp}, it can be observed, the initial set of unpalatable species is dominant as expected.
+The palatable population mimicking that set is following it.
+A bunch of other rings with majority of unpalatable species have been reproduced through mutation.
+Mainly because the initial population started with a bunch of unpalatable species, so their reproduced generation have similar behavior as well.
 
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-1Prey-p}
+	\includegraphics[scale=0.45]{images/simTime10k-1Prey-p}
 	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
@@
 Major difference from Section \ref{subsec:single-prey-unpalatable} is the total number of prey population created.
-For the unpalatable species section, total population reaches above 12 thousand.
-But for palatable species total population reaches nearly above 5000 prey species.
+For the unpalatable species in section \ref{subsec:single-prey-unpalatable}, total prey population reach above 12 thousand.
+But for palatable species total population reach nearly above 5000 prey species, as when the preys are palatable there is more consumption from predators.
 
@@
 Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}.
-In this experiment we initialize the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations we can observe that all of the initial unpalatable rings have survived with dominance.
-So we can be conclude that our results match with the one from Frank and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
+For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
+The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four.
+So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern.
+But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
+It can be concluded that our results match with the one from Frank and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
 

### 2010-12-08 docs/tex/review.tex
New image update.
Some minor changes...

@@
 Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts.
-The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment." - Christopher G.
-Langton}
+The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."}
 \end{quote}
+
+The field of Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}.
+While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.
+
+%Describe Wetware, Software and Hardware systems of artificial life.
 
@@
 
-The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}.
-While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.
-
-%Describe Wetware, Software and Hardware systems of artificial life.
-
 \subsection{Complex Adaptive System}
@@
 \subsubsection{Criteria}
-Echo has been constructed on a certain set of criteria. The following is a short summary on it extracted from \cite{holland1996}.
+Echo has been constructed on a certain set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
 
@@
 So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation.
-5
 	\item 
@@
 
-\paragraph{Criteria}
-
 \section{Cellular Automata}

### 2010-12-08 src/Mimicry/System.cpp

@@ -102,7 +102,7 @@ const int System::NUMBER_OF_RINGS_TO_REPORT = 8;
 /**
  * Minimum number of patterns that need to be stored in Predator memory before starting recognition.
  */
-int System::MIN_MEMORY_SIZE = 2;
+int System::MIN_MEMORY_SIZE = 1;
 
 /**
  * Maximum number of patterns stored in Hopfield Memory
@@ -138,7 +138,7 @@ int System::PREDATOR_REPRODUCTION_AGE_LIMIT = 500;
 /**
  * Time interval to wait before a \a Predators start reproducing again.
  */
-int System::PREDATOR_REPRODUCTION_INTERVAL = 2500;
+int System::PREDATOR_REPRODUCTION_INTERVAL = 1500;
 
 /**
  * Maximum age upto which \a Predator species will survive in the environment.

### 2010-12-08 docs/tex/conclusion.tex
A conclusion.. will revise later.

%Concluding chapter
\chapter{Conclusion}
If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature. If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry. But considering Artificial Life as a subject where we essentially learn from nature, its behavior, and use that knowledge to find better solution to existing problems in the field of computer science then this thesis has not been completely successful. We have not been able to find the appropriate problem solving scenario for which the natural process of mimicry can be applied.

Humans came to understand the concept of biological evolution and its significance when it was first proposed by Charles Darwin in 1859 in his book \textsl{On the Origin of Species} \cite{darwin1859}. Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsec:evo-comp-history}). Eventually in 1975 John Holland was able to make the most applicable use of the process to evolution to solve problems in computer science by his invention of Genetic Algorithms. The time for this invention was appropriate as the field of computer science was in its burgeoning state. Over the next couple of decades computers became one of most useful and important machinery in human history. Genetic Algorithms became popular as well because of increased capability of computers in term of speed and complexity.

Even though we do not have any problem solving application for the evolutionary process of mimicry at this point, it does not imply that this study will not be useful in the future to give us solution to an important problem in computer science or any other field for that matter. The simulation presented in this thesis, itself, consists of building blocks of knowledge such as Hopfield Network and Cellular Automata. Maybe to apply mimicry to a problem solving scenario other diverse building blocks are necessary which has not yet been invented.

The objective of any research is to look for \textsl{unexplored} territory to find new \textsl{knowledge}, \textsl{understanding} or \textsl{explanation}. From the research presented in this thesis we certainly get new \textsl{understanding} of the capability of computer science to emulate natures behavior. We also get to \textsl{explore} a new model for the evolutionary process of  mimicry. This model provides us with additional \textsl{explanation} and \textsl{understanding}, while enforcing some existing \textsl{knowledge} with greater support.

### 2010-12-08 docs/tex/conclusion.tex
Conclusion.. more content.

@@
 If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
+As mentioned in section \ref{sec:result-conclusion} this model give us proof of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
+Also it enforces findings of the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
+
 If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry.
-But considering Artificial Life as a subject where we essentially learn from nature, its behavior, and use that knowledge to find better solution to existing problems in the field of computer science then this thesis has not been completely successful.
+From the sections of \ref{sec:result-batesian-mimicry} and \ref{sec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
+
+But considering Artificial Life as a subject where we essentially learn from nature, its behaviors, and use that knowledge to find better solution to existing problems in the field of computer science then this thesis has not been completely successful.
 We have not been able to find the appropriate problem solving scenario for which the natural process of mimicry can be applied.
@@
 The simulation presented in this thesis, itself, consists of building blocks of knowledge such as Hopfield Network and Cellular Automata.
-Maybe to apply mimicry to a problem solving scenario other diverse building blocks are necessary which has not yet been invented.
+Maybe to use mimicry to solve a problem, other diverse building blocks are necessary which has not yet been invented.
 
@@
 We also get to \textsl{explore} a new model for the evolutionary process of  mimicry.
-This model provides us with additional \textsl{explanation} and \textsl{understanding}, while enforcing some existing \textsl{knowledge} with greater support.
+In addition to that, the model provides us with better \textsl{explanation} and \textsl{understanding} of nature, while enforcing some existing \textsl{knowledge} with greater support (section \ref{sec:result-mullerian-mimicry}).

### 2010-12-08 docs/tex/result.tex
Conclusion.. more content.

@@
 \section{Analysis of Batesian Mimicry}
+\label{sec:result-batesian-mimicry}
 For all possible initial conditions, Batesian mimicry has taken effect.
@@
 \section{Analysis of Mullerian Mimicry}
+\label{sec:result-mullerian-mimicry}
 Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}.
@@
 \section{Conclusion}
+\label{sec:result-conclusion}
 Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.

### 2010-12-08 docs/tex/abstract.tex
abstract.tex file

\begin{abstract}
A novel agent based, artificial life model, for the evolution of mimicry is presented. This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network. A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of all behavior and reproduction capability to evolve new behaviors in successive generations. These agents are classified into categories of predator and prey species. Genes of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented. Through evolution, successive generations of prey species have new pattern to represent them visually and to the predators. Predators on the other hand have Hopfiled Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability. Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved. Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied. 
\end{abstract}

### 2010-12-09 docs/tex/acknowledgment.tex
The acknowledgment page

\begin{center}
\begin{large}
\textbf{Acknowledgement}
\end{large}
\end{center}
I really acknowledge..

### 2010-12-09 docs/tex/abstract.tex
The acknowledgment page

@@
 This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network.
-A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of all behavior and reproduction capability to evolve new behaviors in successive generations.
+A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
 These agents are classified into categories of predator and prey species.
 Genes of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented.
-Through evolution, successive generations of prey species have new pattern to represent them visually and to the predators.
-Predators on the other hand have Hopfiled Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
+Through evolution, successive generations of prey species have new pattern to represent them both visually and to the predators.
+Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry.
+They are equipped with Hopfiled Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
 Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved.
 Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
+\setcounter{page}{3}
 \end{abstract}

### 2010-12-09 docs/tex/acknowledgment.tex
Page number issues for abstract and acknowledgment is fixed.

@@
+\newpage
+\phantomsection \label{acknowledgements}
+\addcontentsline{toc}{chapter}{\numberline{}Acknowledgment}
+
 \begin{center}
 \begin{large}
-\textbf{Acknowledgement}
+\textbf{Acknowledgements}
 \end{large}
 \end{center}
-I really acknowledge..
+My first appreciation goes to my supervisor Dr.
+Peter Grogono.
+It is not only a privilege to work with him, but also the inspiration and encouragement that I have received from him during the period of this work, made it possible.
+
+My second appreciation goes to my parents. Their hard work and sacrifice in life made it possible for me to be able to come all this way.
+
+My third appreciation is to my sister, who also made it easier for me, to be able to give all the time that I required to complete my thesis.

### 2010-12-09 docs/tex/abstract.tex
Page number issues for abstract and acknowledgment is fixed.
Improved abstract formatting.

@@
-\begin{abstract}
+\begin{center}
+
+\begin{Large}
+\textbf{Abstract}\\[0.5cm]
+\end{Large}
+
+\begin{large}
+\textbf{Modeling the Evolution of Mimicry}\\
+\end{large}
+
+\begin{small}
+\textbf{Mohiul Islam}\\
+\end{small}
+
+\end{center}
+
 A novel agent based, artificial life model, for the evolution of mimicry is presented.
@@
 These agents are classified into categories of predator and prey species.
-Genes of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented.
+Genome of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented.
 Through evolution, successive generations of prey species have new pattern to represent them both visually and to the predators.
@@
 Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
+
 \setcounter{page}{3}
-\end{abstract}

### 2010-12-09 docs/tex/signature.tex
Title and Signature pages complete.

%\newpage
\begin{titlepage}
\begin{center}
\Large \textbf{CONCORDIA UNIVERSITY}\\
\Large \textbf{School of Graduate Studies}\\[2cm]
\end{center}
This is to certify that the thesis prepared\\
\makebox[1.6in][l]{By:} Mohiul Islam\\
\makebox[1.6in][l]{Entitled:}  Modeling the Evolution of Mimicry\\
and submitted in partial fulfillment of the requirements for the degree of
\begin{center}
\small \textbf{Master of Computer Science}\\
\end{center}
complies with the regulations of the University and meets the accepted standards with respect to originality and quality.\\[1cm]
Signed by the final examining committee:\\

\begin{flushright}
\begin{minipage}{8cm}
\rule{5cm}{0.1mm} Chair\\[0.4cm]
\rule{5cm}{0.1mm} Examiner\\[0.4cm]
\rule{5cm}{0.1mm} Examiner\\[0.4cm]
\rule{5cm}{0.1mm} Supervisor\\[0.8cm]
\end{minipage}
\end{flushright}
\makebox[4cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
\makebox[4cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
\makebox[4cm][l]{\rule{2cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
\makebox[4cm][l]{} Dean of Faculty

\end{titlepage}

### 2010-12-09 docs/tex/title.tex
Title and Signature pages complete.

\begin{titlepage}
\begin{center}

\Large Modeling the Evolution of Mimicry\\[1.5cm]
\large Mohiul Islam\\[2.5cm]
\large A Thesis\\ in\\ The Department\\ of\\ Computer Science\\ and Software Engineering\\[2.5cm]
\large Presented in Partial Fulfillment of the Requirements\\ for the Degree of Master of Computer Science at\\ Concordia University\\ Montreal, Quebec, Canada\\[1.5cm]
\large December 2010\\[2cm]

\vfill

\large \copyright Mohiul Islam, 2010
\end{center}
\end{titlepage}

### 2010-12-09 docs/tex/signature.tex
Title date time updated

@@
 \begin{flushright}
-\begin{minipage}{8cm}
-\rule{5cm}{0.1mm} Chair\\[0.4cm]
-\rule{5cm}{0.1mm} Examiner\\[0.4cm]
-\rule{5cm}{0.1mm} Examiner\\[0.4cm]
-\rule{5cm}{0.1mm} Supervisor\\[0.8cm]
+\begin{minipage}{10cm}
+\rule{7cm}{0.1mm} Chair\\[0.4cm]
+\rule{7cm}{0.1mm} Examiner\\[0.4cm]
+\rule{7cm}{0.1mm} Examiner\\[0.4cm]
+\rule{7cm}{0.1mm} Supervisor\\[0.8cm]
 \end{minipage}
 \end{flushright}
-\makebox[4cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
-\makebox[4cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
-\makebox[4cm][l]{\rule{2cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
-\makebox[4cm][l]{} Dean of Faculty
+\makebox[5cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
+\makebox[5cm][l]{\rule{3cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Dean of Faculty
 

### 2010-12-11 docs/tex/review.tex
A conclusion.. will revise later.
Echo criterion have been added.

@@
 \subsection{History}
+\label{subsec:evo-comp-history}
 
@@
 Instead of being a constant value it should evolve along with the system.
-	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}.
+	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}".
 Interpretation of results from the Echo model should be direct and ready-made.
@@
 So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation.
-	\item 
-	\item 
+Another advantage is with the help of interpretations, selected mechanisms can be shown to be sufficient to generate the phenomenon of interest.
+Even though simulation cannot establish that a given mechanism is actually present, but it can establish its sufficiency or plausibility.
+	\item The architecture of the Echo model should be flexible enough so that other well-studied mathematical models of particular \textsl{CAS} can be incorporated whenever required.
+Among other models the significant ones include, Dawkins' \textsl{biological arms race} \cite{dawkins1990} and Brower's \textsl{survival of mimics} \cite{brower1988} from ecology; Wicksell's \textsl{Triangle} \cite{marimon1989} and \textsl{overlapping generation models} \cite{anderson1989} in economics; the \textsl{prisoner's dilemma game} \cite{axelrod1984} in political science; Holland's \textsl{two-Armed bandits} \cite{holland1975} in operational research and Perelson's \textsl{antigen-body matching} \cite{perelson1999} in immunology.
+	\item As mathematical analysis provides the surest route to arrive at a valid generalization point, most aspects of the Echo model should be amenable to mathematical analysis. 
 \end{itemize}
+
+In developing Echo using the above set of criterion, a step by step approach has been taken.
+Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997} is discussed in the following.
 
@@
 
-\subsubsection{Agents}
+\paragraph{Resources and Sites}
+
+\paragraph{Agents}
 Individual agents in echo
 
-\subsubsection{Replication}
-
-\subsubsection{Interactions}
+\paragraph{Replication}
+\paragraph{Interactions}
 \paragraph{Combat}

### 2010-12-12 docs/tex/review.tex
Echo section is fairly complete.

@@
 In developing Echo using the above set of criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997} is discussed in the following.
+Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997}, which is more from an ecological perspective is discussed in the following.
 
 \subsubsection{Organization}
+As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resource.
+Agents in Echo have freedom and flexibility to move around this environment.
+These agents are capable of replicating themselves, while also having the capability of making complex interactions.
+Interactions include combat, trading and mating.
 
 \paragraph{Resources and Sites}
+Resource in a site of Echo is its very foundation.
+They are represented by letters [a,b,c,d].
+Everything is Echo is constructed by combining these letters as strings.
+These resources are treated much like an `atom' and by combining them as a molecular string agents are constructed.
+Geographically, Echo is a collection of interconnected sites.
+Each site contains a fountain which is the source of resource for the agents in Echo.
+The amount of resource available in each site varies in time.
+A site with no resource can be compared to a `desert' while another site with increased availability of letters can be water spring or a pond.
 
 \paragraph{Agents}
-Individual agents in echo
+`Agents have a genome that is roughly analogous to a single chromosome in an haploid species'.
+An agents \textsl{tag} is an external phenotype of its respective genotype (such as color).
+Agents have internal conditions or rules of interaction with which are genetically represented and they encode the agents internal preferences, behavioral rules and so forth.
+So interactions between multiple agents occur based on their conditions (rules for interactions) and tags (appearance), which results in sophisticated interactions between agents such as deception (mimicry, bluffing) and in-transitivities.
+`The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition'.
+These genes are used to determine what sort of interaction between agents are will take place and also the outcome of their interaction.
+
+Agents have two ways of reproduction, one being self replication, while the other is by interaction between a pair of agents.
 
 \paragraph{Replication}
+The replication process for agents is an asexual reproduction.
+An agent needs to collect sufficient resource to start the self-replication process.
+After replication, the newly created agent receives a fraction of its parent's resource.
+Spontaneous mutation is applied to the gene for a replication process, where different mutation rate is applied to different parts of the gene.
+
 \paragraph{Interactions}
+Their are diverse interactions between agents consisting of combat, trading and mating.
+Agents need to be in the same location in site for any interaction to take place.
+Testing for which interaction to take place is always conducted in the order of combat, trade and mating.
+
 \paragraph{Combat}
+The interaction of combat is analogous to real world antagonistic behavior, where one agent is killed resulting in the survivor agent to receive all its resource.
+Depending on each agent's offense and defense tag and the tag prefixes, the winner is decided.
+A \textsl{combat matrix} is also calculated with the genome of individual agents, which helps in calculating the winner.
+
 \paragraph{Trading}
+When two agents are chosen to interact and they do not engage in combat, they are given the opportunity to trade and mate.
+Trading and mating are very much a mutual agreement between agents compared to combat, which is more of a destructive process.
+``Agents A and B will trade if A's trading condition is a prefix of B's offense tag and vice versa".
+Trading takes place for excess resources between agents, where excess is defined as the amount which the agent possess above the amount required for a replication process, plus some reserves.
+The value of the reserve is controlled with the help of a simulation parameter.
+A deceptive process is introduced here while trading takes place, when an agent might not have excess resource but will still be engaged in trade, as it is not possible for the other agent to know the resource of its opposite interactor.
+
 \paragraph{Mating}
-\subsubsection{Results}
+Only if two agents find each other suitable, they will engage in the mating process.
+Suitability is decided on certain conditions based on the mating tag of individual agents.
+A form of two point crossover takes place to perform the mating action and produce diverse new agents.
+
+\subsubsection{Discussion of Results}
+The Echo model has good resemblance with natural ecosystem.
+It has stable patterns of interactions among genetic variants, or tropic networks.
+I consists different levels of resources along with relative species abundance.
+Even different cataclysmic events such as meteors, droughts and so fourth are introduced.
+Also several isolation effects are observed where a number of sites are allowed to evolve independently.
+In addition to that Echo contains interesting flow of resources.
+
+Two separate experiments are done with the above simulation to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
+To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems.
+The objective is to compare ecosystems - the Preston  curve and the species-area scaling relation.
+This allowed them to compare Echo diversity patterns with empirical patterns of species abundance.
+
+Preston's canonical log normal distribution is the most widely accepted formalization of the relative commonness and rarity of species.
+The species-area scaling relation is also an important ecological pattern.
+The theory of island biography is predicted on species-are relations.
+In conservation biology, this relation has been used to predict the effects of different reserve sized on species diversity.
+Although the species-area relation can be derived from Preston's canonical log-normal distribution, a satisfactory explanation of the processes that regulate this relation has not been advanced.
+
+Now the question is, does Echo exhibit the robust ecological phenomenon of Preston curve and species area scaling relation?.
+For Preston's curve plot, the data show that qualitatively the pattern of genome abundances in Echo populations resembles the general patterns found in biological systems, although some differences are observed.
+But for species area curve some discrepancy was observed between the expected result and the observed values.
+Several factors were raised for this discrepancy.
+One was the choice of the simulation parameters.
+Second being the definition of different species Echo.
+Agents having different genome is considered as from different species.
+Another factor being the balance between rates of speciation and extinction of population.
+
+Finally to answer the above question, it has been concluded that, Echo showed good quantitative agreement with naturally occurring species abundance distributions and species area scaling relations.
 

### 2010-12-12 docs/tex/review.tex
Initiating CAS...
More on Echo

@@
 \subsection{Echo}
-Echo is a gedanken experiment rather than a precise simulation.
+Echo is simulation of a Complex Adaptive System. It is more of a gedanken experiment rather than a precise simulation.
 
 \subsubsection{Criteria}
-Echo has been constructed on a certain set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
+Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
 
@@
 Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model.
-	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting, while mobility is also part of a wide range of geographical setting.
-Input to the environment which are considered as stimuli or resource can also be diversified.
-	\item Fitness of each of the agents is an evolving criteria.
+	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting.
+Their mobility is also part of a wide range of geographical setting.
+Input to the environment which is considered as a stimuli or resource, can also be diversified.
+	\item Fitness of each of agent, is an evolving criteria.
 Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents.
-Instead of being a constant value it should evolve along with the system.
+The fitness value, instead of being a constant should evolve along with the system.
 	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}".
@@
 In developing Echo using the above set of criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997}, which is more from an ecological perspective is discussed in the following.
+Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997} is more from an ecological perspective and has been discussed in the following.
 
@@
 Resource in a site of Echo is its very foundation.
-They are represented by letters [a,b,c,d].
-Everything is Echo is constructed by combining these letters as strings.
-These resources are treated much like an `atom' and by combining them as a molecular string agents are constructed.
+They are represented by letters (a,b,c,d).
+Everything in Echo is constructed by combining these letters as strings.
+These resources are treated much like an `atom' and by combining them as a molecular string, agents are constructed.
 Geographically, Echo is a collection of interconnected sites.
@@
 The amount of resource available in each site varies in time.
-A site with no resource can be compared to a `desert' while another site with increased availability of letters can be water spring or a pond.
+A site with no resource can be compared to a `desert' while another site with increased availability of letters can be a water spring or a pond.
 
@@
 An agents \textsl{tag} is an external phenotype of its respective genotype (such as color).
-Agents have internal conditions or rules of interaction with which are genetically represented and they encode the agents internal preferences, behavioral rules and so forth.
-So interactions between multiple agents occur based on their conditions (rules for interactions) and tags (appearance), which results in sophisticated interactions between agents such as deception (mimicry, bluffing) and in-transitivities.
+Agents have internal conditions or rules of interaction, which are genetically represented and they encode the agents internal preferences, behavioral rules and so forth.
+So interactions between multiple agents occur based on their conditions (rules for interactions) and tags (appearance).
+This results in sophisticated interaction between agents such as deception (mimicry, bluffing) and in-transitivities.
 `The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition'.
@@
 After replication, the newly created agent receives a fraction of its parent's resource.
-Spontaneous mutation is applied to the gene for a replication process, where different mutation rate is applied to different parts of the gene.
+Spontaneous mutation is applied to the gene for this process, where different mutation rate is applied to different parts of the gene.
 
@@
 Only if two agents find each other suitable, they will engage in the mating process.
-Suitability is decided on certain conditions based on the mating tag of individual agents.
+Suitability for mating is decided on certain conditions based on the mating tag of individual agents.
 A form of two point crossover takes place to perform the mating action and produce diverse new agents.
@@
 It has stable patterns of interactions among genetic variants, or tropic networks.
-I consists different levels of resources along with relative species abundance.
-Even different cataclysmic events such as meteors, droughts and so fourth are introduced.
+It consists of different levels of resources along with relative species abundance.
+Even different cataclysmic events such as meteor, drought and so fourth are introduced.
 Also several isolation effects are observed where a number of sites are allowed to evolve independently.
@@
 Two separate experiments are done with the above simulation to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
-To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems.
-The objective is to compare ecosystems - the Preston  curve and the species-area scaling relation.
-This allowed them to compare Echo diversity patterns with empirical patterns of species abundance.
+To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature.
+The objective is to compare these naturally occurring ecosystems with Echo.
+The ecological patterns are the Preston  curve and the species-area scaling relation.
+This allowed comparison of Echo diversity patterns with empirical patterns of species abundance.
 
@@
 The species-area scaling relation is also an important ecological pattern.
-The theory of island biography is predicted on species-are relations.
-In conservation biology, this relation has been used to predict the effects of different reserve sized on species diversity.
+The theory of island biography is predicted on species-area relations.
+In conservation biology, this relation has been used to predict the effects of different reserve size, with species diversity.
 Although the species-area relation can be derived from Preston's canonical log-normal distribution, a satisfactory explanation of the processes that regulate this relation has not been advanced.
 
-Now the question is, does Echo exhibit the robust ecological phenomenon of Preston curve and species area scaling relation?.
-For Preston's curve plot, the data show that qualitatively the pattern of genome abundances in Echo populations resembles the general patterns found in biological systems, although some differences are observed.
+Now the question is, does Echo exhibit the robust ecological phenomenon of Preston curve and species area scaling relation?
+For Preston's curve plot, the data show, qualitatively the pattern of genome abundances in Echo population resembles the general patterns found in biological systems, although some differences are observed.
 But for species area curve some discrepancy was observed between the expected result and the observed values.
 Several factors were raised for this discrepancy.
-One was the choice of the simulation parameters.
-Second being the definition of different species Echo.
-Agents having different genome is considered as from different species.
+One was the choice of the simulation parameter.
+Second being the definition of different species in Echo as agents having different genome is considered from different species.
 Another factor being the balance between rates of speciation and extinction of population.
 
-Finally to answer the above question, it has been concluded that, Echo showed good quantitative agreement with naturally occurring species abundance distributions and species area scaling relations.
+Finally to answer the above question, it has been concluded that, Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.
 

### 2010-12-12 docs/tex/intro.tex
An incomplete introduction.

@@
 \chapter{Introduction}
-Throughout history mankind has learned from nature. Human aspiration to fly in the sky comes from observing birds in the sky. Aspiration leads to inspiration, and airplanes are invented.
+
+%A few paragraphs are required to bring an appropriate introduction.
+%Throughout history mankind has learned from nature. Human aspiration to fly in the sky comes from observing birds in the sky. Aspiration leads to inspiration, and airplanes are invented.
+
+%Individual chapter descriptions begins from chapter 2
+Chapter 2 is intended to provide background knowledge upon which this thesis is based.
+It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
+It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models with computer science to emulate nature.
+
+Chapter 3 discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis.
+Mimicry is an evolutionary process which not only provides us with insight into the process of evolution as it happens in nature but also it is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
+In addition, this chapter discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us to explain each of these cases.
+
+Chapter 4 contains description of an agent based artificial life model, which is the primary purpose of this thesis.
+Inspired by the evolutionary mimetic process as it happens in nature we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
+This model is based on a FormAL (Form Artifical Life) framework which is similar to Holland's Echo model but with a slightly different approach.
+
+Chapter 5 deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry as it happens in nature.
+The results are extracted by applying different initial conditions to the model.
+As this work is with complex adaptive system, the data that we extract from such system is also expected to be convoluted.
+But our effort in this section is to come up with simplified analysis of the data to be able to comprehend complex activities in the model.
+
+Chapter 6 tries to provide direction for possible future work.
+Our goal for this thesis was not only to come up with a model and emulate natures mimetic process but also to apply this method to solve problems in the field of computer science.
+This approach is similar to the way evolutionary algorithms and genetic programming help us in optimizing solutions of complicated problems.
+
+Chapter 7 is an effort to bring a conclusion to justify the work done on this thesis.

### 2010-12-12 docs/tex/review.tex
An incomplete introduction.

@@
 As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
-In contrast to that in Artificial Life scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.
+In contrast to that, in Artificial Life, scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.
 
 Christopher G.
-Langton is considered as one of the founders of the filed of Artificial Life.
-He invented the term in the late 1980's when he organized the first ``International Conference on the Synthesis and Simulation of Living Systems" at the Los Alamos National Laboratory in 1987.
+Langton is considered as one of the founders of the field of Artificial Life.
+He invented the term in the late 1980's while organizing the first `\textsl{International Conference on the Synthesis and Simulation of Living Systems'} at the Los Alamos National Laboratory in 1987.
 
@@
 \subsection{Complex Adaptive System}
+The following definition of Complex Adaptive System is the most comprehensive.
+
+\begin{quote}
+\textsl{``A Complex Adaptive System (CAS) is a dynamic network of many agents (which may represent cells, species, individuals, firms, nations) acting in parallel, constantly acting and reacting to what the other agents are doing.
+The control of a CAS tends to be highly dispersed and decentralized.
+If there is to be any coherent behavior in the system, it has to arise from competition and cooperation among the agents themselves.
+The overall behavior of the system is the result of a huge number of decisions made every moment by many individual agents." - John H.
+Holland}
+\end{quote}
 

### 2010-12-12 docs/tex/review.tex
`complex adaptive system' more or less complete

@@
 \subsection{Complex Adaptive System}
-The following definition of Complex Adaptive System is the most comprehensive.
+\label{subsec:complex-adaptive-system}
+Complex adaptive systems (CAS) are special cases of complex systems.
+They are complex as they are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.
+Examples of complex adaptive systems include the stock market, social insect and ant colonies, the biosphere and the ecosystem, the brain and the immune system, the cell and the developing embryo, manufacturing businesses and any human social group-based endeavor in a cultural and social system such as political parties or communities.
+This includes some large-scale online systems, such as collaborative tagging or social bookmarking systems.
+
+The following definition of Complex Adaptive System is comprehensive.
 
@@
 
+Holland also provides some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:
+
+\begin{enumerate}
+	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."}
+	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
+	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
+	\item \textsl{``Complex adaptive systems anticipate."}
+\end{enumerate}
+
 \subsection{Echo}
-Echo is simulation of a Complex Adaptive System. It is more of a gedanken experiment rather than a precise simulation.
+Echo is a class of simulation model of a complex adaptive system, designed primarily for gedanken experiments rather than a precise simulation.
+Echo provides, for the study of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
+Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.
 

### 2010-12-13 docs/tex/review.tex
Some more changes...

@@
 As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
-In contrast to that, in Artificial Life, scientist take concepts from Biology, specially Evolutionary Biology and genetics and implement into computer science.
+In contrast to that, in Artificial Life, scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.
 
@@
 \begin{enumerate}
-	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."}
+	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems.
+As because different interactions between agents are simultaneous, parallel computing is helpful in term of simulating and analyzing these systems.
 	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
@@
 \subsubsection{Criteria}
-Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's, \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
+Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
 
@@
 
-\section{Cellular Automata}
-
 \section{Conclusion}
+This chapter discusses the field of science that takes concepts from evolutionary biology to solve and optimize problems in compute science.
+It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze these science.
+The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core discussion of this thesis.

### 2010-12-13 docs/tex/intro.tex
Some more changes...

@@
 It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
-It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models with computer science to emulate nature.
+It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models to emulate nature.
 
 Chapter 3 discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis.
-Mimicry is an evolutionary process which not only provides us with insight into the process of evolution as it happens in nature but also it is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
-In addition, this chapter discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us to explain each of these cases.
+Mimicry is an evolutionary process, which not only provides us with insight into the process of evolution as it happens in nature but also is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
+In addition, this chapter discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us explain each of these cases.
 

### 2010-12-13 docs/tex/intro.tex
Chapter labels added...

@@
 \chapter{Introduction}
+\label{chapter:introduction}
+\pagenumbering{arabic}
 
@@
 %Individual chapter descriptions begins from chapter 2
-Chapter 2 is intended to provide background knowledge upon which this thesis is based.
+Chapter \ref{chapter:review} is intended to provide background knowledge upon which this thesis is based.
 It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
@@
 
-Chapter 3 discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis.
+Chapter \ref{chapter:mimicry} discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis.
 Mimicry is an evolutionary process, which not only provides us with insight into the process of evolution as it happens in nature but also is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
@@
 
-Chapter 4 contains description of an agent based artificial life model, which is the primary purpose of this thesis.
+Chapter \ref{chapter:model} contains description of an agent based artificial life model, which is the primary purpose of this thesis.
 Inspired by the evolutionary mimetic process as it happens in nature we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
-This model is based on a FormAL (Form Artifical Life) framework which is similar to Holland's Echo model but with a slightly different approach.
+This model is based on a FormAL (Form Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.
 
-Chapter 5 deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry as it happens in nature.
+Chapter \ref{chapter:results} deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry as it happens in nature.
 The results are extracted by applying different initial conditions to the model.
@@
 
-Chapter 6 tries to provide direction for possible future work.
-Our goal for this thesis was not only to come up with a model and emulate natures mimetic process but also to apply this method to solve problems in the field of computer science.
+Chapter \ref{chapter:application} tries to provide direction for possible future work.
+The goal of this thesis was not only to come up with a model that emulate natures mimetic process but also to apply this method to solve problems in the field of computer science.
 This approach is similar to the way evolutionary algorithms and genetic programming help us in optimizing solutions of complicated problems.
 
-Chapter 7 is an effort to bring a conclusion to justify the work done on this thesis.
+Chapter \ref{chapter:conclusion} is an effort to bring a conclusion to justify the work done on this thesis.

### 2010-12-13 docs/tex/review.tex
Chapter labels added...

@@
 \chapter{Review}
-
+\label{chapter:review}
 \begin{quote}
@@
 \section{Introduction}
+The intention of this chapter is to discuss the field of Evolutionary Computing and Artificial Life.
+Both of these field of computer science are inspired by the process of evolution as it happens in nature.
+The model presented in this thesis is also based on an evolutionary process existing in nature.
+This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems.
+In addition to the model presented in chapter \ref{chapter:model}, this thesis put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
+Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.
 
 \section{Evolutionary Computation}
-
-\textsl{``The fundamental metaphor of evolutionary computing relates this powerful natural evolution to a particular style of problem solving - that of trial and error" - Eiben \cite{eiben2003}}
+The field of evolutionary computing is the collective name for a range of problem-solving techniques based on principles of biological evolution, such as natural selection and genetic inheritance.
 
@@
 So given a problem the algorithm initializes the environment with a random set of population or solutions.
-Then it uses the fitness function to select a better set of solutions from the existing once.
-After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set born from the existing ones.
+Then it uses the fitness function to select a better set of solutions from the existing ones.
+After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set, born from the existing ones.
 Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.
@@
 \section{Artificial Life}
-As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
+Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
 In contrast to that, in Artificial Life, scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.
@@
 Langton is considered as one of the founders of the field of Artificial Life.
-He invented the term in the late 1980's while organizing the first `\textsl{International Conference on the Synthesis and Simulation of Living Systems'} at the Los Alamos National Laboratory in 1987.
+He invented the term while organizing the first `\textsl{International Conference on the Synthesis and Simulation of Living Systems'} at the Los Alamos National Laboratory in 1987.
 
@@
 
-The field of Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}.
+Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}.
 While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.
+
+\paragraph{Wetware systems}
+Wetware artificial life systems are the most similar to natural life and indeed are actually derived from natural life.
+
+\paragraph{Software systems}
+
+\paragraph{Hardware systems}
 
@@
 \begin{enumerate}
-	\item \textsl{``All complex adaptive system involves large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems.
+	\item \textsl{``All complex adaptive system involve large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems.
 As because different interactions between agents are simultaneous, parallel computing is helpful in term of simulating and analyzing these systems.
-	\item \textsl{``The impact of these systems in human affairs centers on the aggregate behavior, the behavior of the whole."}
+	\item \textsl{``The impact of these systems in human affairs center on the aggregate behavior, the behavior of the whole."}
 	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}

### 2010-12-13 docs/tex/review.tex
Some changes in review

@@
 \section{Introduction}
-The intention of this chapter is to discuss the field of Evolutionary Computing and Artificial Life.
+This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life.
 Both of these field of computer science are inspired by the process of evolution as it happens in nature.
@@
 This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems.
-In addition to the model presented in chapter \ref{chapter:model}, this thesis put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
+In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
 Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.

### 2010-12-13 docs/tex/mimicry.tex
Results chapter completed...
Chapter labels added...
Revision updates...

@@
 \chapter{The Inspiration: Mimicry}
-
+\label{chapter:mimicry}
 \begin{quote}
@@
 Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces.
-When the deceptive animal possesses an innate reaction to the model the number of mimics can be virtually unlimited.
+When the deceptive animal possesses an innate reaction to the model, the number of mimics can be virtually unlimited.
 	\item \textsl{``that the imitators differ from the bulk of their allies".} The most remarkable cases of mimicry are those where close relatives form divergent models.
@@
 \section{Mullerian Mimicry}
+\label{sec:mullerian-mimicry}
 Bates was not able to explain some phenomena of mimicry.
@@
 
-\textsl{``According to punctuated equilibrium, therefore, evolution is not more of less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories.
+\textsl{``According to punctuated equilibrium, therefore, evolution is not more or less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories.
 Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
@@
  \item But mutations of color patterns are occurring all the time.
-Suppose that species B happens to produce a mutation whole pattern falls within the envelop of protection afforded to species A.
+Suppose that species B happens to produce a mutation whose pattern falls within the envelop of protection afforded to species A.
 The mimicry need not be perfect, but if it is good enough, the mutation will have an advantage and will spread.

### 2010-12-13 docs/tex/result.tex
Chapter labels added...
Revision updates...

@@
 \chapter{The Results}
-
+\label{chapter:results}
 \begin{quote}
@@
 The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations.
-With the initial configuration in the above table we can observe that multiple rings of prey population has been created.
+With the initial configuration in the above table we can observe that multiple rings of prey population have been created.
 Two prey species are considered to be in a ring if their CA pattern have a hamming distance within 10 bits.
@@
 We can observe from the above result that the evolution of mimicry has taken effect.
-A population of mimics were successfully able to exceed the population of other prey species, and the reason being avoidance by predators of prey pattern similar to unpalatable ones.
+A population of mimics were successfully able to exceed the population of other prey species, and the reason being, avoidance by predators of prey pattern similar to unpalatable ones.
 We can conclude that Batesian mimicry has taken effect in the simulation.
@@
 As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate.
-In this simulation memory size is controlled by the 'Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}.
-Also it seems from this experiment that the 'Minimum Memory Configuration' being 6 is rather a large number.
+In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}.
+Also it seems from this experiment that the `Minimum Memory Configuration' being 6 is rather a large number.
 So there could be possibility of wrong recognition by Hopfield memory.
@@
 We observe the effect of the simulation up to 8000 iterations instead of 10000 as the total number of prey species increases at an enormous rate in this simulation within very short period of time.
-As most of the species are unpalatable, predators most do not get the opportunity to consume, causing a much lower prey death rate.
+As most of the species are unpalatable, predators mostly do not get the opportunity to consume, causing a much lower prey death rate.
 
@@
 From the second work of Frank and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
-But is this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
-By setting this property to one and also increasing `Predator Demise Age' to 7000 while decreasing `Predator Age Interval' to 1500, we get the following plot.
+But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
+By setting this property to one and also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.
 

### 2010-12-13 docs/tex/model.tex
Results chapter completed...
Chapter labels added...
Revision updates...

@@
 \chapter{The Model: Evolution of Mimicry}
+\label{chapter:model}
 
@@
 %Explain more about the first model by Frank and Noble
-The \textbf{first} model by Frank and Noble \cite{franks2002} is where ``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed." Each individual had a single gene: a value representing their external appearance or phenotype.
+The \textbf{first} model by Frank and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
+Each individual had a single gene: a value representing their external appearance or phenotype.
 The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors).
@@
 
-\paragraph{}
 The \textbf{second} model by Frank and Noble \cite{franks2003} is based on two working hypothesis:
@@
 There was existence of multiple mimicry rings of very different frequency (population).
-Second experiment was carried out with some palatable species along with the unpalatable once which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out.
+Second experiment was carried out with some palatable species along with the unpalatable ones which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out.
 It can be observed that,
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in Table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (Table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in \cite{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in section \ref{subsec:echo} \cite{hraber1997}.
 
@@
 The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry.
-As it can observed new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
+As it can be observed new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
 Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation.
@@
 As it can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
-This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increase predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
+This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
 
@@
 There are two control parameters that effect the reproduction of predator species.
-The first is \textsl{"Reproduction Age Limit"}.
+The first is \textsl{``Reproduction Age Limit"}.
 This is the minimum age a predator has to reach before starting to involve itself for reproduction.
 This parameter has been set to 500 iterations during the result and analysis section of the thesis.
-The second parameter is \textsl{"Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
+The second parameter is \textsl{``Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
 This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment.
@@
 If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species in born which also resides on the same cell and initializes with zero memory configuration.
-Similarly when the new born predator reaches its maturity of reproductive age and if its capable to reproduce then the process iterates itself.
+Similarly when the new born predator reaches its maturity of reproductive age and if it is capable of reproduction then the process iterates itself.
 

### 2010-12-13 docs/tex/review.tex
Revision updates...

@@
 
-Holland also provides some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:
+Holland also provided some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:
 
@@
 \subsection{Echo}
-Echo is a class of simulation model of a complex adaptive system, designed primarily for gedanken experiments rather than a precise simulation.
-Echo provides, for the study of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+\label{subsec:echo}
+Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
+Echo provides, a of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
@@
 `The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition'.
-These genes are used to determine what sort of interaction between agents are will take place and also the outcome of their interaction.
+These genes are used to determine what sort of interaction between agents will take place and also the outcome of their interaction.
 
@@
 Agents need to be in the same location in site for any interaction to take place.
-Testing for which interaction to take place is always conducted in the order of combat, trade and mating.
+Testing for which selection of interaction to take place, is always conducted in the order of combat, trade and mating.
 

### 2010-12-14 docs/tex/intro.tex
Description of Alife

@@
 It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
-It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models to emulate nature.
+It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models and to emulate nature.
 

### 2010-12-14 docs/tex/review.tex
Description of Alife

@@
 Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}.
-While providing a brief survey over different AL models he talks about \textbf{Wetware systems} which work at the molecular level, the \textbf{Software systems} which work at the cellular level and the \textbf{Hardware systems} which works at the organism level.
-
-\paragraph{Wetware systems}
-Wetware artificial life systems are the most similar to natural life and indeed are actually derived from natural life.
-
-\paragraph{Software systems}
-
-\paragraph{Hardware systems}
-
-%Describe Wetware, Software and Hardware systems of artificial life.
-
-%\section{History}
-
-%\paragraph{Jon Von Neumann}
-
-%\paragraph{Tierra}
-
-%\paragraph{Avida}
+While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
+\textsl{Wetware} artificial life systems are the most similar to natural life and indeed are actually derived from natural life.
+Most of the experiments are attempts to direct an artificial evolutionary process toward the production of ribonucleic acid (RNA) molecules with specific catalytic properties.
+The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \cite{neumann1966}.
+He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties.
+\textsl{Hardware systems} at the organism level can deal with an organism's sensory and nervous system, its body and its environment.
+Even though an organism's nervous system is usually considered as fantastically complex, the other interesting complex components can be its geometric, mechanical, dynamical or thermal properties.
 
@@
 \section{Conclusion}
-This chapter discusses the field of science that takes concepts from evolutionary biology to solve and optimize problems in compute science.
-It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze these science.
+This chapter discusses evolutionary computation, the field that takes concepts from evolutionary biology to solve and optimize problems in compute science.
+It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze life as it is in nature.
 The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core discussion of this thesis.

### 2010-12-14 docs/tex/intro.tex
Predator image update

--- 2010-12-13 docs/tex/intro.tex
@@
 It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
-It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models to emulate nature.
+It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models to emulate nature and its life like behavior.
 
@@
 Chapter \ref{chapter:model} contains description of an agent based artificial life model, which is the primary purpose of this thesis.
-Inspired by the evolutionary mimetic process as it happens in nature we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
+Inspired by the evolutionary mimetic process we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
 This model is based on a FormAL (Form Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.
 
-Chapter \ref{chapter:results} deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry as it happens in nature.
+Chapter \ref{chapter:results} deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry.
 The results are extracted by applying different initial conditions to the model.

### 2010-12-14 docs/tex/result.tex
Predator image update

@@
 As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
-Parameters are mentioned in Table \ref{tab:ring-report-control-parameters}.
+Parameters are mentioned in table \ref{tab:ring-report-control-parameters}.
 
@@
 
-The set of parameters in Table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
+The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
 This test has been done with two sets of prey species with very different CA pattern and with opposite palatability and equal population.
@@
 Otherwise evolution of mimicry is not observed.
-As mentioned in Table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
+As mentioned in table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
 After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment.
@@
 Two prey species are considered to be in a ring if their CA pattern have a hamming distance within 10 bits.
-This parameter is mentioned in Table \ref{tab:ring-report-control-parameters}.
+This parameter is mentioned in table \ref{tab:ring-report-control-parameters}.
 Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve.
@@
 
-The parameters for this simulation has been set exactly the same as in Table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
+The parameters for this simulation has been set exactly the same as in table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
 All predator configuration has also been set to exactly same as before.
@@
 
-This configuration is set exactly as according to Section \ref{subsec:single-prey-unpalatable} but with a single set of palatable species.
-The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of Section \ref{sec:init-only-palatable-species}.
+This configuration is set exactly as according to section \ref{subsec:single-prey-unpalatable} but with a single set of palatable species.
+The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of section \ref{sec:init-only-palatable-species}.
 
@@
 From the initial palatable population we see a bunch of palatable rings created.
-Major difference from Section \ref{subsec:single-prey-unpalatable} is the total number of prey population created.
+Major difference from section \ref{subsec:single-prey-unpalatable} is the total number of prey population created.
 For the unpalatable species in section \ref{subsec:single-prey-unpalatable}, total prey population reach above 12 thousand.

### 2010-12-14 docs/tex/model.tex
Predator image update

@@
 The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
-\(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in Table \ref{tab:environment-control-parameters}).
+\(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in table \ref{tab:environment-control-parameters}).
 
@@
 A cell is a three dimensional cubical section of the hyperspace.
-Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
+Accordingly in table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
 The size of a cell is evaluated from the entire world size.
@@
 
-Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while Table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.
+Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.
 
@@
 So that is why we have two separate mutation rate while reproducing prey species.
-One being the ``Pattern Mutation Rate" (default values are mentioned in Table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (Table \ref{tab:prey-genome}).
+One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
 Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in section \ref{subsec:echo} \cite{hraber1997}.
@@
 \subsection{Genome}
-The Genome of the prey species consists of 17 bits as presented in Table \ref{tab:prey-genome}.
+The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}.
 The first eight bits is the rule, which is used to generate Cellular Automata pattern.
-The next two bits are used to represent palatability of the organism explained detail in Section \ref{sec:genetic-palatability-representation}.
+The next two bits are used to represent palatability of the organism explained detail in section \ref{sec:genetic-palatability-representation}.
 The next six bits is the magnitude of the force with which mobility of the organism is calculated.
@@
 
-This representation in Table \ref{tab:genetic-representation-palatability} is unlike Frank and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+This representation in table \ref{tab:genetic-representation-palatability} is unlike Frank and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
 
@@
 A new genome is created from the existing genome of the two prey by applying single point crossover operation.
-Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in Table \ref{tab:prey-control-parameters}.
+Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in table \ref{tab:prey-control-parameters}.
 So there is two point mutation for the genome.
@@
 A set of parameters are defined to control predators' population and learning ability in the environment.
-Details of these parameters are given in Table \ref{tab:predator-control-parameters}.
+Details of these parameters are given in table \ref{tab:predator-control-parameters}.
 
@@
 Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive.
-The ``Hopfield Minimum Memory Size" (default value in Table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
+The ``Hopfield Minimum Memory Size" (default value in table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
 After a predator is born, it start attacking prey without any caution.
@@
 \subsection{Genome}
-Each predator has a 5 bit genome as explained in Table \ref{tab:predator-genome}.
+Each predator has a 5 bit genome as explained in table \ref{tab:predator-genome}.
 The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment.

### 2010-12-14 docs/tex/review.tex
Predator image update

@@
 It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze life as it is in nature.
-The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core discussion of this thesis.
+The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core idea of this thesis.

### 2010-12-14 docs/tex/acknowledgment.tex
Improved abstract formatting.
Title and Signature pages complete.
Chapter labels added...
Revision updates

--- 2010-12-09 docs/tex/acknowledgment.tex
@@
+\newpage
+\phantomsection
+\label{acknowledgments}
 \begin{center}
-\begin{large}
-\textbf{Acknowledgement}
-\end{large}
+\Large \textbf{Acknowledgments}\\[0.5cm]
 \end{center}
-I really acknowledge..
+
+My first appreciation goes to my supervisor Dr.
+Peter Grogono.
+It is not only a privilege to work with him, but also the inspiration and encouragement that I have received from him during the period of this work, made it possible.
+
+My second appreciation goes to my parents Mobinul Islam and Latifa Mobin. Their hard work and sacrifice in life made it possible for me to be able to come all this way.
+
+My third appreciation is to my sister Shagufta Islam, who also made it easier for me to be able to give all the time that I required to complete my thesis.

### 2010-12-14 docs/tex/result.tex
Revision updates

@@
 \section{Mimicry Ring Reports}
-The mimicry ring reports consists entirely of the population of prey species categorized according to patterns and palatability.
+The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability.
 Data is stored at every instance of time of the simulation keeping an interval of 10 iterations.
@@
 But in the later experiments predator demise age has been increased to 5000 iterations.
-Predators in this simulation generates selection pressure for the evolution of mimicry.
+Predators in this simulation generate selection pressure for the evolution of mimicry.
 So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid.
@@
 
-The configuration in table \ref{tab:config-table-2-prey} is also the most appropriate condition for Mullerian Mimicry.
-We can observe that a single pattern of unpalatable species dominate the entire population.
-The effects can be observed in this configuration where we can see the continuous increment of prey and predator population and eventually behaviors of Mullerian mimicry, where all prey species converge to a single ring of CA pattern.
-
 %Put the number of rings picture:
@@
 
-The screen shot in Figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
+The screen shot in figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
 The red agents are predators while the black agents with different textured patterns are the prey species.
@@
 
-By observing the graph in Figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial sate of the simulation has dominated after 10000 iterations.
+By observing the graph in figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial sate of the simulation has dominated after 10000 iterations.
 CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve).
@@
 Secondly the number of predator population has been increased from 20 to 30.
-Thirdly, Predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
+Thirdly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
 Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.
@@
 
-With the above set of parameters we receive the plot of Figure \ref{fig:plot-6-prey}.
+With the above set of parameters we receive the plot of figure \ref{fig:plot-6-prey}.
 An enormous diversity of species can be observed from this experiment.
@@
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
-By setting this property to one and also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.
+By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.
 
@@
 
-After running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring.
+Running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring.
 As it can be observed in figure \ref{fig:plot-4-prey-unp-1-mem} all four unpalatable prey population have a very dominant presence in the simulation.
@@
 Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction.
-At iteration time 2000 a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
+At iteration time 2000 there is a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
 By this time the population of unpalatable species mutated from the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey come to its demise.
@@
 
-Observation of mimicry rings also tell us about the results we have seen in the plot of Figure \ref{fig:plot-4-prey-p}.
+Observation of mimicry rings also tell us about the results we have seen in the plot of figure \ref{fig:plot-4-prey-p}.
 The number of rings keep increasing but comes to a sudden drop around simulation time 7000 and goes to zero.
@@
 This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
-So from the analysis it can be concluded that the model under discussion has successfully simulated the evolution of Batesian mimicry.
+So from this analysis it can be concluded that the model under discussion has successfully simulated the evolution of Batesian mimicry.
 

### 2010-12-14 docs/tex/review.tex
Revision updates

@@
 
-Using GA for a binary representation mutation can be single point or multiple point, where a random location is selected from the binary genome and the bit is flipped.
+Using GA for a binary representation, mutation can be single point or multiple point, where a random location is selected from the binary genome and the bit is flipped.
 For integer representation random resetting is used instead of bit flipping.
@@
 Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination.
-Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome but instead their genomes are derived from their parent using an arithmetic formula.
+Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome, but instead, their genomes are derived from their parent using an arithmetic formula.
 Permutation representation has many interesting recombination operators, out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems.
@@
 Premature convergence being one where individuals that are a lot better than the rest take over the entire population.
-Also when fitness values are all very close there is almost no selection pressure in evolution of the fittest.
+Also when fitness values are all very close, there is almost no selection pressure in evolution of the fittest.
 Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection.
@@
 Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
-In contrast to that, in Artificial Life, scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.
+In contrast to that, in Artificial Life scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.
 
@@
 
-In defining Artificial Life Christopher G. Langton states the following,
+In defining Artificial Life Langton states the following,
 
@@
 
-Artificial Life (AL) has been described by Taylor also as a tool for biological inquiry \cite{taylor1993}.
+Artificial Life (AL) has been described by Taylor, also as a tool for biological inquiry \cite{taylor1993}.
 While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
@@
 The fitness value, instead of being a constant should evolve along with the system.
-	\item ``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}".
+	\item \textsl{``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}"}.
 Interpretation of results from the Echo model should be direct and ready-made.
@@
 \paragraph{Agents}
-`Agents have a genome that is roughly analogous to a single chromosome in an haploid species'.
+\textsl{``Agents have a genome that is roughly analogous to a single chromosome in an haploid species"}.
 An agents \textsl{tag} is an external phenotype of its respective genotype (such as color).
@@
 This results in sophisticated interaction between agents such as deception (mimicry, bluffing) and in-transitivities.
-`The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition'.
+\textsl{``The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition"}.
 These genes are used to determine what sort of interaction between agents will take place and also the outcome of their interaction.
@@
 Trading and mating are very much a mutual agreement between agents compared to combat, which is more of a destructive process.
-``Agents A and B will trade if A's trading condition is a prefix of B's offense tag and vice versa".
+\textsl{``Agents A and B will trade if A's trading condition is a prefix of B's offense tag and vice versa"}.
 Trading takes place for excess resources between agents, where excess is defined as the amount which the agent possess above the amount required for a replication process, plus some reserves.

### 2010-12-14 docs/tex/conclusion.tex
An incomplete introduction.
Revision updates

@@
 \chapter{Conclusion}
+\label{chapter:conclusion}
 If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
 As mentioned in section \ref{sec:result-conclusion} this model give us proof of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
-Also it enforces findings of the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
+Also it enforces findings from the work of Frank and Noble that multiple Mullerian mimics do not converge into one large ring.
 

### 2010-12-14 docs/tex/model.tex
Revision updates

@@
 \subsection{Mobility}
-An agents position is calculated once during each step of update in time.
+An agent's position is calculated once during each step of update in time.
 The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
@@
 
-In generating the pattern of Figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the 'New state of center cell'.
-As Figure \ref{fig:cellular-automata-rule-30} is a rule 30 cellular automata, the eight bit binary representation of 30 would be the genetic representation for this pattern.
+In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
+As figure \ref{fig:cellular-automata-rule-30} is a rule 30 cellular automata, the eight bit binary representation of 30 would be the genetic representation for this pattern.
 Generation of automata pattern from this binary string can be considered analogous to the complex pathway between the genotype and the phenotype that exists in all living organism.
@@
 \subsection{Species diversity}
-Franks and Noble have used different models to diversify species.
+Frank and Noble have used different models to diversify species.
 In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing ``Echo" as mentioned in section \ref{subsec:echo} \cite{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsec:echo} \cite{hraber1997}.
 
@@
 The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry.
-As it can be observed new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
+As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
 Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation.
@@
 \subsubsection{Input to memory}
-Each prey contains an evolving cellular automata which is represented by a binary gene.
+Each prey contains an evolving cellular automata which is represented by a binary genome.
 This two dimensional pattern is serialized to be available as a one dimensional binary array, which is taken as input for any predator organism trying to interact with the prey.
 This binary representation of the pattern gets converted to a bipolar representation.
-Each input pattern will consist of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
+Each input pattern consists of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
 The \textit{m} by \textit{n} pattern configuration will be serialized by putting all row vectors in one single row sequentially.
@@
 				\IF {$currentMemorySize < MinimumMemorySize$}
-					\STATE $attemptToKill(preyToAttack);$ \COMMENT {Function defined in Algorithm \ref{algo:algorithm-attemptToKill}}
+					\STATE $attemptToKill(preyToAttack);$ \COMMENT {Function defined in algorithm \ref{algo:algorithm-attemptToKill}}
 				\ELSE
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
@@
 
-The screen shot in Figure \ref{fig:predators-40} is from the simulation with only 40 predator species.
-It is presented to show the behavior of predator species in the simulation in absence of any prey species.
-As it can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on which ever contains the least number of predator and also most number of prey species.
+The screen shot in figure \ref{fig:predators-40} is from the simulation with only 40 predator species.
+It is presented to show the behavior of predator species in the simulation, in absence of any prey species.
+As it can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
 This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
@@
 
-\begin{table}[H]
+\begin{table}[h!]
 \centering
@@
 Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
-This model can also be considered as a complex adaptive system similar to Hollands work on ``Echo" \cite{holland1996}.
+This model can also be considered as a complex adaptive system similar to Hollands work on Echo \cite{holland1996}.
 The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks are present in this model.

### 2010-12-14 docs/tex/intro.tex
Introduction

@@
 %A few paragraphs are required to bring an appropriate introduction.
-%Throughout history mankind has learned from nature. Human aspiration to fly in the sky comes from observing birds in the sky. Aspiration leads to inspiration, and airplanes are invented.
+Mimicry is a process of deception.
+It is an evolutionary process with the help of which organisms survive by deceiving its predator.
+But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable.
+Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.
+
+Artificial Life is an interdisciplinary study of life and life-like processes that uses synthetic methodology.
+This thesis consists of such a work which concentrates specifically on the life-like process of the evolution of mimicry.
+The synthetic tools used for this simulation is a three dimensional graphical environment, Cellular Automata and Neural Network.
 

### 2010-12-14 docs/tex/model.tex
Frank has been changed to Franks

@@
 
-The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Frank and Noble.
+The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble.
 Their initial work \cite{franks2002} seems of focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
 
-On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Frank and Noble.
+On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble.
 Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics.
@@
 
-Frank and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}.
+Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}.
 Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
@@
 
-\subsection{Models by Frank and Noble}
+\subsection{Models by Franks and Noble}
 \label{subsec:models-by-frank-and-noble}
-%Explain more about the first model by Frank and Noble
-The \textbf{first} model by Frank and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
+%Explain more about the first model by Franks and Noble
+The \textbf{first} model by Franks and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
 Each individual had a single gene: a value representing their external appearance or phenotype.
@@
 
-The \textbf{second} model by Frank and Noble \cite{franks2003} is based on two working hypothesis:
+The \textbf{second} model by Franks and Noble \cite{franks2003} is based on two working hypothesis:
 
@@
 
-%Explain the results for the second model by Frank and Noble
+%Explain the results for the second model by Franks and Noble
 \paragraph{Results}
@@
 \subsection{Species diversity}
-Frank and Noble have used different models to diversify species.
+Franks and Noble have used different models to diversify species.
 In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
@@
 
-This representation in table \ref{tab:genetic-representation-palatability} is unlike Frank and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
 

### 2010-12-14 docs/tex/result.tex
Frank has been changed to Franks

@@
 As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
-From the second work of Frank and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
+From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
@@
 But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
-It can be concluded that our results match with the one from Frank and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
+It can be concluded that our results match with the one from Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
 

### 2010-12-19 docs/tex/review.tex
Simple update
Thesis slides first commit

@@
 In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
-Similar to evolutionary computation, we intend to apply the deceptive process of mimicry to solve a problem in computer science.
+Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.
 
@@
 Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
-Echo provides, a of populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+Echo provides, a populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.

### 2010-12-22 docs/tex/signature.tex
Updates to the signature page.

@@
 \Large \textbf{CONCORDIA UNIVERSITY}\\
-\Large \textbf{School of Graduate Studies}\\[2cm]
+\Large \textbf{School of Graduate Studies}\\[1cm]
 \end{center}
@@
 \end{center}
-complies with the regulations of the University and meets the accepted standards with respect to originality and quality.\\[1cm]
-Signed by the final examining committee:\\
-
-\begin{flushright}
-\begin{minipage}{10cm}
-\rule{7cm}{0.1mm} Chair\\[0.4cm]
-\rule{7cm}{0.1mm} Examiner\\[0.4cm]
-\rule{7cm}{0.1mm} Examiner\\[0.4cm]
-\rule{7cm}{0.1mm} Supervisor\\[0.8cm]
-\end{minipage}
-\end{flushright}
+complies with the regulations of the University and meets the accepted standards with respect to originality and quality.\\[0.4cm]
+Signed by the final examining committee:\\[0.6cm]
+\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Chair\\[0.6cm]
+\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Dr. Thiruvengadam Radhakrishnan, Examiner\\[0.6cm]
+\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Dr. Nawwaf Kharma, Examiner\\[0.6cm]
+\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Dr. Peter Grogono, Supervisor\\[0.6cm]
 \makebox[5cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
-\makebox[5cm][l]{\rule{3cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Dean of Faculty
+\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[0.6cm]
+\makebox[5cm][l]{\rule{4cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Dr. Robin A. L. Drew, Dean \\
+\makebox[5cm][l]{} Faculty of Engineering and Computer Science
 

### 2010-12-22 docs/tex/signature.tex
Signature page updates.

@@
 complies with the regulations of the University and meets the accepted standards with respect to originality and quality.\\[0.4cm]
-Signed by the final examining committee:\\[0.6cm]
-\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Chair\\[0.6cm]
-\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Dr. Thiruvengadam Radhakrishnan, Examiner\\[0.6cm]
-\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Dr. Nawwaf Kharma, Examiner\\[0.6cm]
-\makebox[5cm][l]{} \rule{8cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Dr. Peter Grogono, Supervisor\\[0.6cm]
+Signed by the final examining committee:\\[0.5cm]
+\makebox[5cm][l]{} \rule{7cm}{0.1mm} Chair\\ 
+\makebox[5cm][l]{} Dr. Eusebius J. Doedel\\[0.5cm]
+\makebox[5cm][l]{} \rule{7cm}{0.1mm} Examiner\\ 
+\makebox[5cm][l]{} Dr. Thiruvengadam Radhakrishnan\\[0.5cm]
+\makebox[5cm][l]{} \rule{7cm}{0.1mm} Examiner\\ 
+\makebox[5cm][l]{} Dr. Nawwaf Kharma\\[0.5cm]
+\makebox[5cm][l]{} \rule{7cm}{0.1mm} Supervisor\\ 
+\makebox[5cm][l]{} Dr. Peter Grogono\\[0.5cm]
 \makebox[5cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[0.6cm]
-\makebox[5cm][l]{\rule{4cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
+\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[0.5cm]
+\makebox[5cm][l]{} \rule{10cm}{0.1mm}\\ 
 \makebox[5cm][l]{} Dr. Robin A. L. Drew, Dean \\
-\makebox[5cm][l]{} Faculty of Engineering and Computer Science
+\makebox[5cm][l]{} Faculty of Engineering and Computer Science\\[0.5cm]
+\makebox[5cm][l]{Date} \rule{7cm}{0.1mm}
 

### 2010-12-22 docs/tex/signature.tex
First name initials for sign page
Avoiding paragraph spacing and line space for professor names.

@@
 complies with the regulations of the University and meets the accepted standards with respect to originality and quality.\\[0.4cm]
-Signed by the final examining committee:\\[0.5cm]
+\begin{spacing}{1}
+\noindent
+Signed by the final examining committee:\\[0.8cm]
 \makebox[5cm][l]{} \rule{7cm}{0.1mm} Chair\\ 
-\makebox[5cm][l]{} Dr. Eusebius J. Doedel\\[0.5cm]
+\makebox[5cm][l]{} Dr. E. J. Doedel\\[0.8cm]
 \makebox[5cm][l]{} \rule{7cm}{0.1mm} Examiner\\ 
-\makebox[5cm][l]{} Dr. Thiruvengadam Radhakrishnan\\[0.5cm]
+\makebox[5cm][l]{} Dr. T. Radhakrishnan\\[0.8cm]
 \makebox[5cm][l]{} \rule{7cm}{0.1mm} Examiner\\ 
-\makebox[5cm][l]{} Dr. Nawwaf Kharma\\[0.5cm]
+\makebox[5cm][l]{} Dr. N. Kharma\\[0.8cm]
 \makebox[5cm][l]{} \rule{7cm}{0.1mm} Supervisor\\ 
-\makebox[5cm][l]{} Dr. Peter Grogono\\[0.5cm]
+\makebox[5cm][l]{} Dr. P. Grogono\\[0.8cm]
 \makebox[5cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
-\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[0.5cm]
+\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[0.8cm]
 \makebox[5cm][l]{} \rule{10cm}{0.1mm}\\ 
 \makebox[5cm][l]{} Dr. Robin A. L. Drew, Dean \\
-\makebox[5cm][l]{} Faculty of Engineering and Computer Science\\[0.5cm]
+\makebox[5cm][l]{} Faculty of Engineering and Computer Science\\[0.8cm]
 \makebox[5cm][l]{Date} \rule{7cm}{0.1mm}
-
+\end{spacing}
 \end{titlepage}

### 2010-12-25 docs/tex/model.tex
Thesis slides first commit
fixed minor grammatical mistakes.

@@
 The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble.
-Their initial work \cite{franks2002} seems of focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
+Their initial work \cite{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
 
@@
 In addition to it, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
-Their mobility and reproduction capability is controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
+Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
 So every new predator species gets to born with zero memory and with no inheritance from parents.
@@
 \subsection{Genome}
-Each predator has a 5 bit genome as explained in table \ref{tab:predator-genome}.
+Each predator has a 5 bits genome as explained in table \ref{tab:predator-genome}.
 The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment.

### 2010-12-25 docs/tex/result.tex
fixed minor grammatical mistakes.

@@
 Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
-So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern previously captured and the patterns stored in memory.
+So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern currently captured and the patterns stored in memory.
 
@@
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
-By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing `Predator Age Interval' to 1500, we get the following plot.
+By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we get the following plot.
 

### 2010-12-26 docs/slides/application.tex
New Theme added.

\section{Application}

\frame
{
	\frametitle{Application}
}

### 2010-12-26 docs/slides/conclusion.tex
New Theme added.

\section{Conclusion}

\frame
{
	\frametitle{Conclusion}
}

### 2010-12-26 docs/slides/model.tex
New Theme added.

\section{The Model}

\frame
{
	\frametitle{The Model}
}

### 2010-12-26 docs/slides/review.tex
New Theme added.

\section{Review}

\frame
{
	\frametitle{Review}
}

### 2010-12-26 docs/slides/mimicry.tex
New Theme added.

\section{Mimicry}

\frame
{
	\frametitle{Mimicry}
}

### 2010-12-26 docs/slides/result.tex
New Theme added.

\section{Results}

\frame
{
	\frametitle{Results}
}

### 2010-12-27 docs/slides/result.tex
Result added

@@
 }
+
+\subsection{Experiments}
+
+%-----------------------------
+%----- Two Prey Species ------
+%-----------------------------
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & 108 
+	  														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
+	  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  & 108 
+	  					 									& \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1200} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 2 prey species}
+	\label{tab:config-table-2-prey}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-2Prey}
+		\caption{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
+		\label{fig:plot-2-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Population vs. Time (5k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime5k-2Prey}
+		\caption{Population distribution of mimicry rings (2 prey species, 5k iterations)}
+		\label{fig:plot-2-prey-5k}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-2Prey}
+		\caption{Number of mimicry rings, initialized with 2 prey species.}
+		\label{fig:ringSize10k-2Prey}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{Prey Pattern}
+	\framesubtitle{Genotype vs. Phenotype}
+
+	\begin{table}
+	\centering
+	\begin{scriptsize}
+	\begin{tabular}{|l|c|c|c|}
+	  \hline
+	  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
+	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule60}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule61}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule62}}\\
+	  \hline
+	\end{tabular}
+	\end{scriptsize}
+	\caption{Difference in prey pattern genotype and phenotype}
+	\label{tab:diff-in-pattern}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Generated Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-2Prey-generated-prey}
+		\caption{Population distribution of generated mimicry rings (2 prey species)}
+		\label{fig:plot-2-prey-generated-prey}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Four Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																										& 50 & \multicolumn{2}{|c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
+	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}
+	  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}
+	  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}
+	  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1400} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species}
+	\label{tab:config-table-4-prey}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey}
+		\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
+		\label{fig:plot-4-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4Prey}
+		\caption{Number of mimicry rings, initialized with 4 prey species.}
+		\label{fig:ringSize10k-4Prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Simulation Time: 11k}
+
+	\begin{figure}[H]
+		\centering
+		\label{fig:screenshot-simTime11K-4Prey}
+		\includegraphics[scale=0.4]{../tex/images/simTime11K-4Prey}
+		\caption{Graphical representation of the model (simulation time: 11200)}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Four Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}	
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150} & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150} & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150} & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150} & \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}	
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species with increased population}
+	\label{tab:config-table-4-more-prey}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population\\ Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10K-4MorePrey}
+		\caption{Population distribution of mimicry rings (4 prey species, increased population)}
+		\label{fig:plot-4-more-prey}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population\\ Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4MorePrey}
+		\caption{Number of mimicry rings (4 prey species, increased population)}
+	\end{figure}	
+}
+
+%-----------------------------
+%----- Six Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{|c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
+	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}} 
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule57}}    
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule105}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 6 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 6 prey species.}
+	\label{tab:config-table-6-prey}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-6Prey}
+		\caption{Population distribution of mimicry rings (6 prey species)}
+		\label{fig:plot-6-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-6Prey}
+		\caption{Number of mimicry rings (6 prey species)}
+		\label{fig:ringSize10k-6-Prey}
+	\end{figure}	
+}
+
+%-----------------------------
+%----- Unpalatable Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species all unpalatable.}
+	\label{tab:config-table-4-prey-unpalatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime8k-4Prey-unp}
+		\caption{Population distribution of mimicry rings(4 prey species all unpalatable)}
+		\label{fig:plot-4-prey-unp}
+	\end{figure}
+
+}
+
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Reduced Predator Memory\\ Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime6k-4Prey-unp-1-mem}
+		\caption{Population distribution of mimicry rings. 4 prey, all unpalatable but reduced predator memory}
+		\label{fig:plot-4-prey-unp-1-mem}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Palatable Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{spacing}{1.5}
+	\begin{tiny}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{tiny}
+	\end{spacing}
+	\caption{Agent configuration of 4 prey species all palatable.}
+	\label{tab:config-table-4-prey-palatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Population vs. Time (7k)}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey-p}
+	\caption{Population distribution of mimicry rings (4 prey species all palatable)}
+	\label{fig:plot-4-prey-p}
+\end{figure}
+}
+
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.3]{../tex/images/ringSize10k-4Prey-p}
+		\caption{Number of mimicry rings (4 prey species all palatable)}
+		\label{fig:ringSize8k-4-Prey-p}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Single Unpalatable ----
+%-----------------------------
+\frame
+{
+	\frametitle{Single Unpalatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
+	  																									& 216 & \multicolumn{2}{|c|}{10} \\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 1 prey species unpalatable.}
+	\label{tab:config-table-1-prey-unpalatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Single Unpalatable Species}
+	\framesubtitle{Population vs. Time (8k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime8k-1Prey-unp}
+		\caption{Population distribution of mimicry rings (1 prey species unpalatable)}
+		\label{fig:plot-1-prey-unp}
+	\end{figure}
+
+}
+
+%-----------------------------
+%----- Single Palatable ----
+%-----------------------------
+\frame
+{
+	\frametitle{Single Palatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{|c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+	  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
+	  																									& 216 & \multicolumn{2}{|c|}{8} \\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 1 prey species palatable.}
+	\label{tab:config-table-1-prey-palatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Single Palatable Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-1Prey-p}
+		\caption{Population distribution of mimicry rings (1 prey species palatable)}
+		\label{fig:plot-1-prey-p}
+	\end{figure}
+}
+
+\subsection{Analysis}

### 2010-12-28 docs/slides/result.tex
An update on table structures.

--- 2010-12-26 docs/slides/result.tex
@@
 	\frametitle{Results}
+
+	\begin{itemize}
+	  \item \textbf{Objective}: Evaluate evolution of mimicry.
+	  \item \textbf{Evaluation process}:
+			\begin{itemize}
+			  \item Calculate number mimicry rings.
+			  \item Calculate size of mimicry rings:
+					\begin{itemize}
+					  \item Population of \textit{palatable} species.
+					  \item Population of \textit{unpalatable} species.
+					\end{itemize}			  
+			\end{itemize}
+		\item \textbf{Report parameters}:
+			\begin{table}
+			\centering
+			\begin{scriptsize}
+			\begin{spacing}{1.5}
+			\begin{tabular}{| l | c |}
+				\hline
+					\textbf{Parameter} & \textbf{Value} \\ \hline
+					Mimicry Ring hamming distance & 10 \% of the Pattern Size \\ \hline
+					Number of Rings to report & 8 \\
+				\hline
+			\end{tabular}
+			\end{spacing}
+			\end{scriptsize}
+			\caption{Parameters to mimicry ring report.}
+			\label{tab:ring-report-control-parameters}
+			\end{table}		
+	\end{itemize}
 }
+
+\subsection{Experiments}
+
+%-----------------------------
+%----- Two Prey Species ------
+%-----------------------------
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & 108 
+	  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
+	  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  & 108 
+	  					 									& \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 2 prey species}
+	\label{tab:config-table-2-prey}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-2Prey}
+		\caption{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
+		\label{fig:plot-2-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Population vs. Time (5k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime5k-2Prey}
+		\caption{Population distribution of mimicry rings (2 prey species, 5k iterations)}
+		\label{fig:plot-2-prey-5k}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Two Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-2Prey}
+		\caption{Number of mimicry rings, initialized with 2 prey species.}
+		\label{fig:ringSize10k-2Prey}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{Prey Pattern}
+	\framesubtitle{Genotype vs. Phenotype}
+
+	\begin{table}
+	\centering
+	\begin{scriptsize}
+	\begin{tabular}{|l|c|c|c|}
+	  \hline
+	  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
+	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule60}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule61}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule62}}\\
+	  \hline
+	\end{tabular}
+	\end{scriptsize}
+	\caption{Difference in prey pattern genotype and phenotype}
+	\label{tab:diff-in-pattern}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Generated Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-2Prey-generated-prey}
+		\caption{Population distribution of generated mimicry rings (2 prey species)}
+		\label{fig:plot-2-prey-generated-prey}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Four Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
+	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}
+	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}
+	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}
+	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species}
+	\label{tab:config-table-4-prey}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey}
+		\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
+		\label{fig:plot-4-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4Prey}
+		\caption{Number of mimicry rings, initialized with 4 prey species.}
+		\label{fig:ringSize10k-4Prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Simulation Time: 11k}
+
+	\begin{figure}[H]
+		\centering
+		\label{fig:screenshot-simTime11K-4Prey}
+		\includegraphics[scale=0.4]{../tex/images/simTime11K-4Prey}
+		\caption{Graphical representation of the model (simulation time: 11200)}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Four Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}	
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150} & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150} & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150} & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150} & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}	
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species with increased population}
+	\label{tab:config-table-4-more-prey}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population\\ Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10K-4MorePrey}
+		\caption{Population distribution of mimicry rings (4 prey species, increased population)}
+		\label{fig:plot-4-more-prey}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{Four Prey Species}
+	\framesubtitle{Increased Population\\ Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4MorePrey}
+		\caption{Number of mimicry rings (4 prey species, increased population)}
+	\end{figure}	
+}
+
+%-----------------------------
+%----- Six Prey Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
+	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}} 
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule57}}    
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 6 prey species.}
+	\label{tab:config-table-6-prey}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-6Prey}
+		\caption{Population distribution of mimicry rings (6 prey species)}
+		\label{fig:plot-6-prey}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Six Prey Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.30]{../tex/images/ringSize10k-6Prey}
+		\caption{Number of mimicry rings (6 prey species)}
+		\label{fig:ringSize10k-6-Prey}
+	\end{figure}	
+}
+
+%-----------------------------
+%----- Unpalatable Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 4 prey species all unpalatable.}
+	\label{tab:config-table-4-prey-unpalatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime8k-4Prey-unp}
+		\caption{Population distribution of mimicry rings(4 prey species all unpalatable)}
+		\label{fig:plot-4-prey-unp}
+	\end{figure}
+
+}
+
+\frame
+{
+	\frametitle{Only Unpalatable Species}
+	\framesubtitle{Reduced Predator Memory\\ Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime6k-4Prey-unp-1-mem}
+		\caption{Population distribution of mimicry rings. 4 prey, all unpalatable but reduced predator memory}
+		\label{fig:plot-4-prey-unp-1-mem}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Palatable Species ------
+%-----------------------------
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{spacing}{1.5}
+	\begin{tiny}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
+	  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
+	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{tiny}
+	\end{spacing}
+	\caption{Agent configuration of 4 prey species all palatable.}
+	\label{tab:config-table-4-prey-palatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Population vs. Time (7k)}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey-p}
+	\caption{Population distribution of mimicry rings (4 prey species all palatable)}
+	\label{fig:plot-4-prey-p}
+\end{figure}
+}
+
+\frame
+{
+	\frametitle{Only Palatable Species}
+	\framesubtitle{Number of Mimicry Rings}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.3]{../tex/images/ringSize10k-4Prey-p}
+		\caption{Number of mimicry rings (4 prey species all palatable)}
+		\label{fig:ringSize8k-4-Prey-p}
+	\end{figure}
+}
+
+%-----------------------------
+%----- Single Unpalatable ----
+%-----------------------------
+\frame
+{
+	\frametitle{Single Unpalatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
+	  																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 1 prey species unpalatable.}
+	\label{tab:config-table-1-prey-unpalatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Single Unpalatable Species}
+	\framesubtitle{Population vs. Time (8k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime8k-1Prey-unp}
+		\caption{Population distribution of mimicry rings (1 prey species unpalatable)}
+		\label{fig:plot-1-prey-unp}
+	\end{figure}
+
+}
+
+%-----------------------------
+%----- Single Palatable ----
+%-----------------------------
+\frame
+{
+	\frametitle{Single Palatable Species}
+	\framesubtitle{Initial Configuration}
+
+	\begin{table}[H]
+	\centering
+	\begin{tiny}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|l|l|c|c|l|c|}
+	  \hline
+	   														&\multicolumn{3}{c|}{Prey configuration} 																	
+	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+	  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
+	  																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
+	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
+	\end{tabular}
+	\end{spacing}
+	\end{tiny}
+	\caption{Agent configuration of 1 prey species palatable.}
+	\label{tab:config-table-1-prey-palatable}
+	\end{table}
+
+}
+
+\frame
+{
+	\frametitle{Single Palatable Species}
+	\framesubtitle{Population vs. Time (10k)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.25]{../tex/images/simTime10k-1Prey-p}
+		\caption{Population distribution of mimicry rings (1 prey species palatable)}
+		\label{fig:plot-1-prey-p}
+	\end{figure}
+}
+
+\subsection{Analysis}

### 2010-12-28 docs/tex/result.tex
An update on table structures.

@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
-  														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
+  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
   					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
-  					 									& \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1200} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  					 									& \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																										& 50 & \multicolumn{2}{|c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
+  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
   					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}
-  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}
-  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}
-  					 																					& 50 & \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1400} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  	 & 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
-  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}  & 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																									& 150 & \multicolumn{2}{|c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
+  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
   					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}} 
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule57}}    
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
-  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule105}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 6 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
   					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
-  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
   					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
   					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
-  																									& 216 & \multicolumn{2}{|c|}{10} \\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}
@@
   \hline
-   														&\multicolumn{3}{|c|}{Prey configuration} 																	
-   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
+   														&\multicolumn{3}{c|}{Prey configuration} 																	
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
   Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
-  																									& 216 & \multicolumn{2}{|c|}{8} \\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
+  																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
+  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
+  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
+  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
 \end{tabular}

### 2010-12-28 docs/slides/result.tex
Updates to result parameters.

@@
 	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05}& \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
 	  						 									 & Genome    & \multicolumn{2}{c|}{0.5} & \multicolumn{2}{c|}{} \\ \hline
@@
 
+	\begin{itemize}
+		\item Genetic bit difference of one.
+		\item Vastly different phenotype.
+	\end{itemize}
+
 	\begin{table}
@@
 	  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule60}} 
-	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule61}} 
-	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule62}}\\
+	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule60}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule61}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule62}}\\
 	  \hline
@@
 	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{1400\(\uparrow\)}} \\ \hline
 	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
@@
 	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{4\(\uparrow\)} \\ \cline{5-6}
 	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150} & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150} & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150} & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150} & \multicolumn{2}{c|}{}\\ \hline
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
+	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \hline
 	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
 	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
 	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{\textbf{7000 \(\uparrow\)}} \\ \hline
 	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
@@
 	  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
-	  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
+	  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{\textbf{30\(\uparrow\)}}} \\ \cline{2-4}
 	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
@@
 	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{6 \(\uparrow\)} \\ \cline{5-6}
 	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
-	  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{\textbf{20 \(\downarrow\)}}} \\ \cline{2-4}
 	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
@@
 	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
+	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{\textbf{5000 \(\downarrow\)}} \\ \hline
 	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{4 \(\downarrow\)} \\ \cline{5-6}
 	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
-	  																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
+	  																									& 216 & \multicolumn{2}{c|}{\textbf{10 \(\downarrow\)}} \\ \hline
 	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
+	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
 	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
@@
 	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{2 \(\downarrow\)} \\ \cline{5-6}
 	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
-	  																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
+	  																									& 216 & \multicolumn{2}{c|}{\textbf{8 \(\downarrow\)}} \\ \hline
 	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}

### 2010-12-28 docs/tex/result.tex
Updates to result parameters.

@@
 It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600.
-Secondly the number of predator population has been increased from 20 to 30.
-Thirdly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
+Secondly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
 Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.
@@
 To boost predator-prey interaction we also increase the number of predator population to 30.
-Predator reproduction interval has been set comparatively lower in this simulation to 2000 iteration similar to the demise age which is set to 5000.
+Predator reproduction interval has been set comparatively lower in this simulation to 2000 iterations.
 As the initial population of prey species is very high, over time we are expecting even larger number of prey species.

### 2010-12-29 docs/slides/result.tex
Analysis and application updated.

@@
 \subsection{Analysis}
+
+\frame
+{
+	\frametitle{Analysis}
+	\framesubtitle{Batesian Mimicry}
+
+	\begin{itemize}
+		\item Batesian Mimicry has taken effect, for all possible initial conditions.
+			\begin{itemize}
+				\item Every ring of unpalatable species there is a palatable ring.
+			\end{itemize}
+	\end{itemize}
+
+	\begin{itemize}
+		\item Start with palatable population, prey reaches extinction.\\
+		\textbf{Reason:} No models to mimic for palatable species.
+	\end{itemize}
+
+	\begin{itemize}
+		\item \textbf{Conclusion:} This model can simulate evolution of Batesian Mimicry.
+	\end{itemize}
+
+}
+
+\frame
+{
+	\frametitle{Analysis}
+	\framesubtitle{Mullerian Mimicry}
+
+	\begin{quote}
+		``Mullerian mimics converge into one large ring."
+	\end{quote}
+
+	\begin{itemize}
+		\item Initialize simulation with 4 unpalatable species. No palatable ones.
+		\item After 10k iteration all unpalatable species survive with dominance.
+		\item \textbf{Reason:} Predator minimum memory configuration set to 4.
+	\end{itemize}
+
+	\begin{itemize}
+		\item \textbf{New experiment:} reduce predator memory to 1.\\
+		\item \textbf{Observation:} The phenomenon of single large ring do not occur. 
+		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
+		Multiple Mullerian mimics do not converge into one large ring.
+	\end{itemize}	
+}
+
+\frame
+{
+	\frametitle{Analysis}
+	\framesubtitle{Conclusion}
+
+	\begin{itemize}
+		\item Successful simulation of evolution of mimicry.
+		\item Accurate simulation of mimicry ring.\\
+		Diverse new rings and shift in their population.
+		\item Proof of the theory of Turner: evolution of mimicry with punctuated equilibrium.
+	\end{itemize}
+}

### 2010-12-29 docs/slides/application.tex
Analysis and application updated.

@@
 {
-	\frametitle{Application}
+	\frametitle{Future Work:}
+	\framesubtitle{Application}
+
+	\begin{itemize}
+		\item \textbf{Goal:} Apply evolution of mimicry to solve a problem in Computer Science.
+		\item Challenges for applying to optimization problem:
+			\begin{itemize}
+				\item Associating palatability with CA pattern.
+				\item Solution set: 2D CA pattern among which the prey species vary.
+				\item Palatability is equivalent to evaluation/fitness function.
+				\item Then why have mimics in the solution set, when mimics will have the same pattern as the model.
+			\end{itemize}
+		\item Conclusion: solving optimization problem is futile.
+		\item Apply evolution of mimicry to a problem where \textit{deception} is useful.
+	\end{itemize}
 }
+
+\frame
+{
+	\frametitle{Deception}
+	\framesubtitle{Anti-Virus vs. Virus scenario}
+
+	\begin{itemize}
+		\item Anti-Virus \(\leftrightarrow\) Predator
+		\item Program (virus free) \(\leftrightarrow\) Prey (model, unpalatable)
+		\item Virus \(\leftrightarrow\) Prey (mimic, palatable)
+	\end{itemize}
+
+	\begin{itemize}
+		\item Objective of a virus is to \textit{mimic} a normal program to get pass an anti-virus software.
+		\item Objective is \textbf{malicious}.
+	\end{itemize}
+}

### 2010-12-29 docs/tex/result.tex
Some slides added.

@@
 It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600.
-Secondly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
+Secondly, predator population has been increased from 10 to 20.
+Thirdly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
 Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.

### 2010-12-29 docs/slides/result.tex
Some slides added.

@@
 	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{\textbf{20 \(\uparrow\)}}} \\ \cline{2-4}
 	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}

### 2011-01-02 docs/slides/mimicry.tex
Result added
Some slides added.
Batesian and Mullerian mimicry slides.

@@
-\section{Mimicry}
+\section{The Inspiration: Mimicry}
 
@@
 {
-	\frametitle{Mimicry}
+	\begin{center}
+		\LARGE The Inspiration: Mimicry
+	\end{center}
 }
+
+\frame
+{
+	\frametitle{The Inspiration: Mimicry}
+	\framesubtitle{History}
+
+	\begin{itemize}
+		\item Henry W. Bates first published in 1862.
+		\item \textbf{Content:} Similarity and dissimilarity between Heliconiinae and Ithomiinae butterflies. 
+		\item Bates collected 94 species of butterfly.
+		\item They were grouped according to their similar appearance.
+		\item \textbf{Discovery:} Similar appearing butterfly with morphological feature pointing to different species.
+		\item 67 of the 94 are classified as Ithomiinae.
+		\item 27 are Heliconiinae.
+	\end{itemize}
+}
+
+\subsection{Batesian Mimicry}
+
+\frame
+{
+	\frametitle{The Inspiration: Mimicry}
+	\framesubtitle{Batesian Mimicry}
+
+	\begin{itemize}
+		\item Heliconiids are,
+			\begin{itemize}
+				\item conspicuously colored
+				\item extremely abundant 
+				\item slow in mobility.
+			\end{itemize}
+		\item Predators, such as insectivorous birds do not prey on them.
+			\begin{itemize}
+				\item \textbf{Reason:} Heliconiids are inedible and unpalatable.
+			\end{itemize}
+		\item Heliconiids are easily recalled by predators. 
+			\begin{itemize}
+				\item Reason: Conspicuously coloration
+				\item This color acts as warning to predators.
+			\end{itemize}
+		\item Ithomiinae and Pieridae are,
+			\begin{itemize}
+				\item edible 
+				\item palatable
+				\item and they want to pretend like Heliconiids to enjoy protection.
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{The Inspiration: Mimicry}
+	\framesubtitle{Batesian Mimicry}
+
+	\begin{itemize}
+		\item According to Wilcker: \\
+			\textsl{``An actor is a mime, so representation of a false warning pattern in called Mimicry. Bates was the first to point out this phenomenon, so its Batesian mimicry in his name."}
+		\item \textbf{Model:} The animal which is avoided by predator for unpalatable behavior.
+		\item \textbf{Mimic:} The imitating animal.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Batesian Mimicry}
+	\framesubtitle{Plate from Bates (1862)}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.6]{../tex/images/Batesplate_ArM}
+		\caption{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).}
+		\label{fig:batesian-butterfly}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Definition of Mimicry}
+	\framesubtitle{by Bates and Zoological Congress}
+
+	\begin{itemize}
+		\item Bates: \textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
+		\item International Zoological Congress in Washington, 1963: \textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Definition of Mimicry}
+	\framesubtitle{by Wallace}
+
+	Definition by Wallace and listed in Poulton's \textit{``The color of animals, their meaning and use"}.
+		\begin{itemize}
+			\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
+			\item \textsl{``that the imitators are always,"}
+				\begin{itemize}
+					\item \textsl{``the more defenseless"}
+					\item \textsl{``less numerous in individuals"}
+					\item \textsl{``differ from the bulk of their allies"}
+				\end{itemize}
+			\item \textsl{``that the imitation, however minute"}
+				\begin{itemize}
+					\item \textsl{``is external and visible only"}
+					\item \textsl{``never extending to internal characters or to such as do not affect the external appearance."}
+				\end{itemize}
+		\end{itemize}
+}
+
+\subsection{Mullerian Mimicry}
+
+\frame
+{
+	\frametitle{Mullerian Mimicry}
+
+	\begin{itemize}
+		\item Two inedible unrelated butterfly species have similar appearance. Bates was unable to explain this.
+		\item Explanation came from Fitz Muller in 1878.
+		\item Muller's research was in Brazil.
+	\end{itemize}
+
+\textbf{Explanation:}
+	\begin{itemize}
+		\item Predator's limited memory.
+		\item Different species loose their number even being inedible.
+		\item To save this loss and also for survival of species, inedible ones from different family evolve to have similar appearance.
+		\item Phenomenon is referred as Mullerian mimicry, named after Fritz Muller.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Mullerian Mimicry}
+	\framesubtitle{Huheey's explanation}
+
+	\begin{itemize}
+		\item Reduced predation lead.
+		\item Contribution from naive young predators.
+		\item Mutual advertising.
+		\item Opportunity from mutation.
+		\item Predator's generalization.
+	\end{itemize}
+
+	\begin{itemize}
+		\item Mullerian mimicry is not deception.
+		\item Predator's advantage to know all noxious species and deterrent species.
+		\item Prey species creating the most traumatic stimuli to a predator have more possibility of the being the model.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Mullerian Mimicry}
+	\framesubtitle{Viceroy and Monarch}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.5]{../tex/images/BatesMimButter}
+		\caption{A very well-known example of mimicry. Viceroy (top). Unpalatable Monarch (bottom). Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
+		\label{fig:mullerian-butterfly}
+	\end{figure}
+
+}
+
+\subsection{Evolutionary Dynamics}
+
+\frame
+{
+	\frametitle{Evolutionary Dynamics}
+}
+
+\subsubsection{Mimicry Rings}
+
+\frame
+{
+	\frametitle{Mimicry Rings}
+}

### 2011-01-02 docs/slides/mimicry.tex
Evolutionary Dynamics section added to slides.

@@
-\section{The Inspiration: Mimicry}
+\section{The Inspiration}
 
@@
 	\frametitle{Evolutionary Dynamics}
+	\framesubtitle{Punctuated Equilibrium}
+
+	Explanation for evolutionary dynamics of mimicry is from Turner. Most sexually reproducing species will remain:
+	\begin{itemize}
+		\item in extended state of \textit{stasis}.
+		\item Little evolutionary change in most of their geological history.
+	\end{itemize}
+
+	Cladogenesis:
+	\begin{itemize}
+		\item Process of speciation.
+		\item One species split into two distinct species.
+		\item It is a discontinuous change, rather than a gradual transformation in a geological time.
+	\end{itemize}
 }
-
-\subsubsection{Mimicry Rings}
 
@@
 {
-	\frametitle{Mimicry Rings}
+	\frametitle{Evolutionary Dynamics}
+	\framesubtitle{Phyletic Gradualism}
+
+	\begin{itemize}
+		\item Species continue to adapt to new environmental and biological selection pressure.
+		\item Gradually becomes a new species.
+	\end{itemize}
+
+	Phyletic gradualism holds that,
+	\begin{itemize}
+		\item Species population changes gradually.
+		\item There is no clear demarcation between an ancestral species and a descendant species.
+		\item Gradually changing lineage is divided arbitrarily.
+		\item Evolution is 
+			\begin{itemize}
+				\item smooth
+				\item steady
+				\item incremental
+				\item but not necessary constant and slow rate in geological time scale.
+			\end{itemize}
+	\end{itemize}
 }
+
+\frame
+{
+	\frametitle{Evolutionary Dynamics}
+	\framesubtitle{Punctuated Equilibrium vs. Phyletic Gradualism}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.3]{../tex/images/Punctuated-equilibrium}
+		\caption{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
+Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
+		\label{fig:punctuated-equilibrium}
+	\end{figure}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Dynamics}
+	\framesubtitle{Turner's Two Stage Model}
+
+	\begin{itemize}
+		\item Turner came up with a synthetic theory.
+		\item Theory originated from Poulton and Nicholson.
+		\item Mimicry arises in two steps:
+			\begin{enumerate}
+				\item A comparatively large mutation achieves a good approximate resemblance.
+				\item A gradual evolutionary change refines the resemblance to a higher degree of perfection.
+			\end{enumerate}
+		\item This theory has also been applied to Mullerian Mimicry.
+	\end{itemize}
+}
+
+\subsubsection{Mimicry Ring}
+
+\frame
+{
+	\frametitle{Mimicry Ring}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}	
+}
+
+\frame
+{
+	\frametitle{Mimicry Ring}
+	\framesubtitle{Formation}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}
+}

### 2011-01-02 docs/slides/model.tex
Result added
Some slides added.
Batesian and Mullerian mimicry slides.
Additional slides.

@@
 {
+	\begin{center}
+		\LARGE The Model: Evolution of Mimicry
+	\end{center}
+}
+
+\frame
+{
 	\frametitle{The Model}
+	\framesubtitle{Evolution of Mimicry}
+
+	\begin{itemize}
+		\item \textbf{Objective:} Build an \textit{agent based} Artificial Life model for simulating the evolution of mimicry.	
+		\item Two species of agents:
+			\begin{enumerate}
+				\item Prey
+					\begin{itemize}
+						\item Model
+						\item Mimic
+					\end{itemize}
+				\item Predator
+			\end{enumerate}
+		\item Prey pattern representation: Cellular Automata.
+		\item Predator pattern recognition: Hopfield Network.
+		\item Environment: Visual representation, 3D, toroidal.
+	\end{itemize}	
 }
+
+\subsection{Past Work}
+
+\frame
+{
+	\frametitle{The Model}
+	\framesubtitle{Past Work}
+
+	\begin{itemize}
+		\item Turner and Huheey:
+			\begin{itemize}
+				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
+				\item Predators use simple Monte Carlo learning or mathematical approach.
+			\end{itemize}
+		\item Sherratt:
+			\begin{itemize}
+				\item Co-evolving predator and prey population.
+				\item Predators are deterministic, cannot learn from experience.
+				\item Predators attack policy is fixed, either attack or avoid.
+			\end{itemize}
+	\end{itemize}
+}
+
+\subsection{FormAL}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+}
+
+\subsection{Prey}
+
+\frame
+{
+	\frametitle{Prey}
+}
+
+\subsection{Predator}
+
+\frame
+{
+	\frametitle{Predator}
+}

### 2011-01-02 docs/slides/mimicry.tex
Additional slides.

@@
 	\begin{itemize}
-		\item 
+		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
+		\item Each cluster of species, all sharing a common pattern is termed as Mullerina mimicry ring.
+		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.
 	\end{itemize}	
@@
 
+	Turner's theory of Mimicry Ring Formation, takes into account
 	\begin{itemize}
-		\item 
+		\item the level of protection of different rings
+		\item their difference in phenotypic warning patterns.
+	\end{itemize}
+
+}
+
+\frame
+{
+	\frametitle{Mimicry Ring}
+	\framesubtitle{Formation}
+
+	Varying these two parameters give different formation of mimicry rings:
+	\begin{itemize}
+		\item Similar pattern in one habitat:
+			\begin{itemize}
+				\item Similar enough that the envelop of protection in one provides protection to the other.
+				\item \textbf{Result:} Natural protection of mutual convergence.
+			\end{itemize}
+		\item Very dissimilar patterns:
+			\begin{itemize}
+				\item Envelop of protection do not overlap. Predator consuming one will not mistake of the other pattern.
+				\item \textbf{Result:} No convergence, two patterns will remain distinct.
+			\end{itemize}
+		\item Mutation:
+			\begin{itemize}
+				\item Mutation can lead one species into the envelop of protection of another species. 
+				\item \textbf{Result:} Gradual convergence of one pattern with another.
+			\end{itemize}
 	\end{itemize}

### 2011-01-03 docs/slides/model.tex
Updates to the model description.

@@
 	\begin{itemize}
-		\item Turner and Huheey:
+		\item Turner(1996) and Huheey(1988):
 			\begin{itemize}
@@
 			\end{itemize}
-		\item Sherratt:
+		\item Sherratt(2002):
 			\begin{itemize}
@@
 
+%-------------------------------
+%More slides on Franks and Noble
+%-------------------------------
+
+\frame
+{
+	\frametitle{Past Work}
+	\framesubtitle{Franks and Noble}
+
+	\begin{itemize}
+		\item First Model(2002):
+			\begin{itemize}
+				\item \textbf{Focus:} 
+				\item Predators use simple Monte Carlo learning or mathematical approach.
+			\end{itemize}
+		\item Second Model(2004):
+			\begin{itemize}
+				\item Co-evolving predator and prey population.
+				\item Predators are deterministic, cannot learn from experience.
+				\item Predators attack policy is fixed, either attack or avoid.
+			\end{itemize}
+	\end{itemize}
+}
+
+%-------------------------------
+%More slides on Franks and Noble
+%-------------------------------
+
 \subsection{FormAL}
@@
 	\frametitle{FormAL Framework}
+
+	\begin{itemize}
+		\item Ideas from Peter Grogono's Formal Artificial Life (FormAL) project.
+		\item \textbf{Goal:}		
+			\begin{itemize}
+				\item To study the emergence of complexity.
+				\item No variable unless genetically controlled or influenced. \textit{Principal not followed for Hopfield Network.}
+			\end{itemize}
+		\item \textbf{Agents:}
+			\begin{itemize}
+				\item Simulated organism.
+				\item Able to reproduce itself using genetic information.
+				\item Capable of modifying structures of genome between generations.
+				\item Able to interact with other agents.
+				\item Survive and reproduce in a challenging environment.
+			\end{itemize}
+	\end{itemize}
+
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Environment}
+
+	Environment is 3D, where agents get complete freedom of movement defined from genetic representation.
+	\begin{itemize}
+		\item \textbf{Space:}
+			\begin{itemize}
+				\item 
+			\end{itemize}
+		\item \textbf{Time:}
+			\begin{itemize}
+				\item 
+			\end{itemize}
+		\item \textbf{Cell:}
+			\begin{itemize}
+				\item 
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Environment Parameters}
+
+	\begin{table}[H]
+	\centering
+	\begin{spacing}{1.5}
+	\begin{scriptsize}
+%	\begin{tabular}{| p{2.2cm} | >{\centering} p{3cm} | p{7.5cm} |}
+	\begin{tabular}{| p{1.5cm} | >{\centering} p{2cm} | p{4cm} |}
+		\hline
+			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+			ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
+			World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
+			Cell Size & \( World Size / ISize \) & Size of each cell\\ \hline
+			Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
+		\hline
+	\end{tabular}
+	\end{scriptsize}
+	\end{spacing}
+	\caption{Parameters to control the environment.}
+	\label{tab:environment-control-parameters}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Environment - Visual representation - Front}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.40]{../tex/images/cells-front}
+		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
+	\label{tab:3-d-environment-images-1}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Environment - Visual representation - Top}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.40]{../tex/images/cells-top}
+		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
+	\label{tab:3-d-environment-images-2}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Environment - Visual representation - Side}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=0.40]{../tex/images/cells-side}
+		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
+	\label{tab:3-d-environment-images-3}
+	\end{figure}	
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Agent Mobility}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}
+
+}
+
+\frame
+{
+	\frametitle{FormAL Framework}
+	\framesubtitle{Mobility Parameters}
+
+	\begin{table}
+	\centering
+	\begin{scriptsize}
+	\begin{spacing}{1.5}
+	\begin{tabular}{| p{1.3cm} | >{\centering} p{1cm} | p{5cm} |}
+		\hline
+			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+			Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
+			Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
+			Friction & 5 & The friction constant used for motion calculations.\\ \hline
+			Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
+		\hline
+	\end{tabular}
+	\end{spacing}
+	\end{scriptsize}
+	\caption{Parameters to control mobility of agents.}
+	\label{tab:mobility-control-parameters}
+	\end{table}
+
 }
@@
 {
-	\frametitle{Prey}
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Pattern Representation}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Species Diversity}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Genome}
+
+	\begin{table}[H]
+	\centering
+	\begin{scriptsize}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+			\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
+			10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
+	\end{tabular}
+	\end{spacing}
+	\end{scriptsize}
+	\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
+	\label{tab:prey-genome}
+	\end{table}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Punctuated Equilibrium}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Palatability: Genomic Representation }
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Interaction: other prey}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Interaction: predators}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Mobility}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Reproduction}
+}
+
+\frame
+{
+	\frametitle{The Prey: Mimics and Models}
+	\framesubtitle{Configuration Parameters}
+
+	\begin{table}[H]
+	\centering
+	\begin{scriptsize}
+	\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{4cm} |}
+		\hline
+			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+			Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
+			Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
+			Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
+			Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
+			Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
+			Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
+		\hline
+	\end{tabular}
+	\end{scriptsize}
+	\caption{Parameters to control prey population and visibility.}
+	\label{tab:prey-control-parameters}
+	\end{table}
 }
@@
 {
-	\frametitle{Predator}
+	\frametitle{The Predator}
 }

### 2011-01-03 docs/slides/model.tex
More slides...

@@
 			\begin{itemize}
-				\item 
+				\item 3D Lattice of discreet points.
+				\item \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
+				\item \(S\) is a universal constant, small positive number. Value is 20, \(World Size\) parameter. 
 			\end{itemize}
@@
 			\begin{itemize}
-				\item 
+				\item Integer value, increases in discreet steps. 
+				\item Each agent updates itself in each time step.
 			\end{itemize}
@@
 			\begin{itemize}
-				\item 
+				\item Entire environment is divided into multiple cells.
+				\item A 3D cubical section of the hyperspace.
+				\item \(ISize\) parameter kept at 6. Total \(ISize^3 = 216\) cells.
 			\end{itemize}
@@
 	\begin{itemize}
-		\item 
+		\item Position is calculated in each step in time.
+		\item \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
+		\item \(force\) is calculated from the mobility genes.
+		\item Newton's law of motion is used to calculate \(acceleration\) when \(force\) is not zero.
+		\item \(acceleration\) is integrated to obtain velocity and new position.
 	\end{itemize}
@@
 	\begin{spacing}{1.5}
-	\begin{tabular}{| p{1.3cm} | >{\centering} p{1cm} | p{5cm} |}
+	\begin{tabular}{| p{1.7cm} | >{\centering} p{0.6cm} | p{5cm} |}
 		\hline
@@
 	\framesubtitle{Pattern Representation}
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[scale=3]{../tex/images/CA_rule30s}
+		\caption{Cellular Automata Rule 30.
+		Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
+		\label{fig:cellular-automata-rule-30}
+	\end{figure}
+
+	\begin{table}
+		\centering
+		\begin{scriptsize}
+		\begin{tabular}{| p{2cm} | c | c | c | c | c | c | c | c |}
+		  \hline
+		  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
+		  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
+		  \hline
+		\end{tabular}
+		\end{scriptsize}		
+		\caption{Cellular Automata rule}
+		\label{tab:cellular-automata-rule}
+	\end{table}
 }
@@
 	\framesubtitle{Species Diversity}
+
+	\begin{itemize}
+		\item Agent's pattern genome is 8 bit binary value.
+		\item Decimal range 0 to 255.
+		\item 256 unique CA pattern associated.
+		\item The linear representation of this pattern is stored in Hopfield Network.
+		\item Hamming distance between a pattern's linear representation is used to consider similarity.
+		\item Group of prey with a specific pattern is considered in a single species.
+		\item Inter species reproduction is restricted to control diversity of patterns.
+		\item Using ``Pattern Mutation Rate" we control diversity of new species.
+	\end{itemize}
 }
@@
 	\framesubtitle{Genome}
+
+	\begin{itemize}
+		\item 17 bit prey Genome
+	\end{itemize}
 
@@
 	\framesubtitle{Punctuated Equilibrium}
-}
 
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Palatability: Genomic Representation }
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Interaction: other prey}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Interaction: predators}
+	\begin{itemize}
+		\item Punctuated Equilibrium:
+			\begin{itemize}
+				\item inclined to cladogenesis instead of gradualism.
+				\item Turner emphasizes on punctuated equilibrium to explain evolution of mimicry.
+				\item CA pattern evolution is in a single mutation in the pattern genome.
+				\item Change of pattern is not a gradual process but rather an arbitrary discontinuous one.
+			\end{itemize}
+	\end{itemize}
 }
@@
 	\framesubtitle{Mobility}
+
+	\begin{itemize}
+		\item Six bit of the mobility gene is used to calculate the magnitude of force for mobility.
+		\item Direction is decided based on 
+			\begin{itemize}
+				\item Towards collection of maximum prey species in a cell.
+				\item Away from concentration of predators.
+				\item Move towards the selected cell with the magnitude of force calculated.
+			\end{itemize}
+	\end{itemize}
 }
@@
 	\framesubtitle{Reproduction}
+
+	\begin{itemize}
+		\item Reproduction begins at ``Reproductive Age"
+		\item Reproduction capability is decided on 17th bit gene.
+		\item Mate selection is random, but within same cell.
+		\item Mate needs to be
+			\begin{itemize}
+				\item similar species
+				\item genetically capable to reproduce
+				\item reached maturity 
+			\end{itemize}
+		\item Reproduction process:
+			\begin{itemize}
+				\item Single point crossover.
+				\item Two point mutation is applied based different rates.
+					\begin{itemize}
+						\item \textit{Pattern Mutation Rate}
+						\item \textit{Genome Mutation Rate}
+					\end{itemize}
+			\end{itemize}
+	\end{itemize}
 }
@@
 	\frametitle{The Predator}
+
+	\begin{itemize}
+		\item Agent in the FormAL environment.
+		\item Provide selection pressure for the evolution of mimicry.
+		\item Each agent equipped with Hopfield Network Memory.
+		\item Mobility and reproduction capability controlled genetically.
+		\item Unable to represent pattern recognition capability with genome.
+		\item New predators are born with zero memory, as memory is not inherited.
+	\end{itemize}
 }
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Learning}
+
+	\begin{itemize}
+		\item Predator's interaction objective with prey is consumption.
+		\item Consumption is based on palatability.
+		\item If unable to consume prey is thrown back into environment.
+		\item At this event prey pattern is stored into predators memory with the associated palatability.
+		\item New pattern learned with Hebbian Learning.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Hebbian Learning}
+
+	\begin{itemize}
+		\item Initially all weights are set to zero.
+		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
+		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
+	\end{itemize}
+
+Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
+\begin{equation}
+w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
+%\label{eq:}
+\end{equation}
+\[
+w_{ij} = 0, i = j
+\]
+where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
+
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Design of Memory}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Attack Algorithm}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Genome}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Mobility}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Reproduction process}
+}
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Configuration Parameters}
+
+	\begin{table}
+	\centering
+	\begin{tiny}
+	\begin{tabular}{| p{1.3cm} | >{\centering} p{0.8cm} | p{5cm} |}
+		\hline
+			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
+			Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
+			Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
+			Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
+Usually the network reaches a steady state before that.
+But this restriction is to avoid infinite loop in case the network never reaches a steady state.
+\\ \hline
+			Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
+			Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
+			Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
+			Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
+			Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
+			Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
+		\hline
+	\end{tabular}
+	\end{tiny}
+	\caption{Parameters to control predator population and pattern recognition capability.}
+	\label{tab:predator-control-parameters}
+	\end{table}
+}

### 2011-01-03 docs/slides/model.tex
Predator section complete.

@@
 	\framesubtitle{Design of Memory}
+
+	\begin{itemize}
+		\item Input to Memory:
+			\begin{itemize}
+				\item Each prey has an evolving CA represented by a binary Genome.
+				\item This 2D pattern is serialized to a 1D binary array.
+				\item Binary representation is converted to bipolar representation.
+			\end{itemize}
+		\item Pattern Recognition with Hopfield Network:
+			\begin{itemize}
+				\item Learning: Apply Hebbian learning to calculate weights.
+				\item Initialization: Input to the network is initialized with value of the input vector.
+				\item Iterate Until Convergence: Each neuron is updated asynchronously with the input of its previous state until convergence.
+				\item Output: Finally a pattern is set as output when the network reaches convergence.
+			\end{itemize}
+	\end{itemize}
 }
@@
 	\framesubtitle{Attack Algorithm}
+
+	\begin{itemize}
+		\item When agent reaches `Minimum Attack Age' it starts hunting.
+		\item Select a random prey within vicinity (same cell).
+		\item Attack process involves recognition of prey pattern.
+		\item Two parameters to limit pattern memorization and recognition process as both are computationally expensive.
+			\begin{itemize}
+				\item Hopfield Minimum Memory Size (value 2 to 6)
+				\item Hopfield Maximum Memory Size (value 10)
+			\end{itemize}
+		\item New predator attacks without caution. 
+		\item Attacks everyone and in the process store pattern and palatability.
+		\item When memory reaches `Hopfield Minimum Memory Size': intelligent selection.
+	\end{itemize}
 }
@@
 	\framesubtitle{Genome}
+
+	\begin{table}
+	\centering
+	\begin{scriptsize}
+	\begin{spacing}{1.5}
+	\begin{tabular}{|c|c|}
+		\hline
+			\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
+					 1101					   &					1						 		\\ \hline
+	\end{tabular}
+	\end{spacing}
+	\end{scriptsize}
+	\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
+	\label{tab:predator-genome}
+	\end{table}
 }
@@
 	\framesubtitle{Mobility}
+
+	\begin{itemize}
+		\item First 4 bits of the genome calculated to evaluate the magnitude of force of movement.
+		\item Direction is decided based on the number of prey species present in a neighboring cell.
+		\item Move towards the cell with least number of predator and most number of prey.
+		\item This is such that predators are distributed all over the environment.
+		\item Increases agent's predatory behavior.
+	\end{itemize}
 }
@@
 	\framesubtitle{Reproduction process}
+
+	\begin{itemize}
+		\item Agent reaches reproduction age.
+		\item Agent exceeds reproduction age interval, which is difference in time between two reproduction activity.
+		\item Agent is capable of reproduction depending on 5th gene.
+		\item Select another predator from same cell which satisfy above conditions.
+		\item Perform crossover and mutation to create another predator.
+		\item Predator is initialized with zero memory.
+	\end{itemize}
 }

### 2011-01-03 docs/slides/model.tex
Past work section complete.

@@
 	\begin{itemize}
-		\item Turner(1996) and Huheey(1988):
+		\item Turner (1996) and Huheey (1988):
 			\begin{itemize}
@@
 			\end{itemize}
-		\item Sherratt(2002):
+		\item Sherratt (2002):
 			\begin{itemize}
@@
 
-%-------------------------------
-%More slides on Franks and Noble
-%-------------------------------
+\frame
+{
+	\frametitle{Past Work}
+	\framesubtitle{First Model by Franks and Noble}
+
+	\begin{itemize}
+		\item Multiple species are preyed upon by a single abstract predator.
+		\item Appearance of the prey can evolve.
+		\item Palatability is fixed.
+		\item Each individual has a single gene, value representing external appearance.
+		\item Phenotypes are a ring of value from 1-20 (20 and 1 are neighbors).
+		\item Distance represents similarity.
+		\item Predator uses simple reinforcement learning system.
+		\item Three experiments carried out varying palatability of prey.
+		\item Batesian mimicry was established.
+	\end{itemize}
+}
 
@@
 {
-	\frametitle{Past Work}
-	\framesubtitle{Franks and Noble}
+	\frametitle{Franks and Noble}
+	\framesubtitle{Second Model: Working hypothesis}
+
+	\begin{enumerate}
+		\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
+		\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
+	\end{enumerate}
+}
+
+\frame
+{
+	\frametitle{Franks and Noble}
+	\framesubtitle{Second Model: Prey}
 
 	\begin{itemize}
-		\item First Model(2002):
+		\item Prey population has appearance and palatability.
+		\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
+		\item Two genes representing external appearance, using values between 1 to 200.
+		\item Euclidean distance between values represents similarity.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Franks and Noble}
+	\framesubtitle{Second Model: Predator}
+
 	\begin{itemize}
-				\item \textbf{Focus:} 
-				\item Predators use simple Monte Carlo learning or mathematical approach.
+		\item Monte Carlo reinforcement learning system.
+		\item Predators use generation on the basis of experience.
+		\item Set of probability formula was used to make decision for consumption of prey, depending on phenotype.
 	\end{itemize}
-		\item Second Model(2004):
+}
+
+\frame
+{
+	\frametitle{Franks and Noble}
+	\framesubtitle{Second Model: Result}
+
 	\begin{itemize}
-				\item Co-evolving predator and prey population.
-				\item Predators are deterministic, cannot learn from experience.
-				\item Predators attack policy is fixed, either attack or avoid.
+		\item First Experiment:
+			\begin{itemize}
+				\item 20 unpalatable prey species.
+				\item Hypothesis 1 of a single large ring did was not established.
+				\item Multiple mimicry rings exist with different frequency.
+			\end{itemize}
+		\item Second Experiment:
+			\begin{itemize}
+				\item Some palatable and some unpalatable species.
+				\item Reaches condition of Batesian mimicry. Hypothesis 2 is established.
+				\item \textbf{Observation:}
+					\begin{itemize}
+						\item Batesian mimics provide pressure on mutants.
+						\item Batesian pressure on mimicry rings push one into the range of another.
+					\end{itemize}
 			\end{itemize}
@@
 }
-
-%-------------------------------
-%More slides on Franks and Noble
-%-------------------------------
 

### 2011-01-08 docs/slides/review.tex
Result added
Batesian and Mullerian mimicry slides.
Past work section complete.
More slides added.
Review updates.

@@
 \section{Review}
+
+\frame
+{
+	\begin{center}
+		\LARGE A Review
+	\end{center}
+}
 
@@
 }
+
+\subsection{Evolutionary Computation}
+
+\frame
+{
+	\frametitle{Evolutionary Computation}
+	\framesubtitle{History}
+
+	\begin{itemize}
+		\item Turing (1948): ``Intelligent Machinery", expression ``genetical or evolutionary search"
+		\item Bremermann (1962): Solve optimization problems. Minimize a real-valued function.
+		\item Rechenberg (1964): Evolutionary strategies. Aerodynamic wing design.
+		\item L. Fogel, Owens and Walsh (1965): Merged evolutionary computation and computational intelligence.
+		\item Holland (1975): Genetic Algorithms, Schema theorem.
+		\item Koza (1992): Genetic Programming. Automated method for creating computer program.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Algorithm}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Strategy: survival of the fittest.
+		\item Optimize mathematical expressions or fitness function.
+		\item Apply mutation and recombination.
+		\item ``Variation operators creates the necessary diversity and there by facilitates novelty."
+		\item ``Selection acts as a force pushing quality."
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Genetic Algorithm}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Strategies}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Self adaptation of strategy parameters.
+		\item Real-valued vectors
+		\item Recombination process is discrete or intermediary.
+		\item Mutation process uses Gaussian perturbation.
+		\item Fast and good optimizer for real-valued optimization.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Programming}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Generate Artificial Intelligence by simulating evolution as a learning process.
+		\item Intelligence: System should adapt its behavior to meet specified goal in the environment.
+		\item Representation: real-valued vectors.
+		\item Parent selection: Deterministic.
+		\item Off springs are created via mutation.
+		\item No recombination operator for evolutionary programming.
+		\item Mutation is applied with Gaussian perturbation.
+		\item Survivor selection is probabilistic.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Genetic Programming}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Applied to machine learning tasks such as prediction and classification.
+		\item Attribute feature: Behaves similar to Neural Network.
+		\item Algorithm itself is a very slow process.
+		\item Non-linear chromosomes such as trees and graphs.
+		\item Mutation is mostly avoided.
+		\item Recombination operator work by exchanging trees.
+		\item Parent selection: Fitness proportional.
+		\item Survivor selection: Replacement of generations.
+		\item Difference from genetic algorithm: the chromosomes are trees.
+	\end{itemize}
+}
+
+\subsection{Artificial Life}
+
+\frame
+{
+	\frametitle{Artificial Life}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Introduced by Christopher G. Langton.
+		\item Organized at `International Conference on the Synthesis and Simulation of Living Systems', Los Alamos National laboratory 1987.
+		\item Described by Taylor as a tool for biological inquiry.
+		\item Wetware system:
+			\begin{itemize}
+				\item Similar to natural life. Indeed actually derived from natural life.
+				\item Direct an artificial evolutionary process toward the production of RNA molecules.
+			\end{itemize}
+		\item Software system:
+			\begin{itemize}
+				\item Initial contribution from John von Neumann.
+				\item Self reproducing, computation universal cellular automata.
+			\end{itemize}
+		\item Hardware system:
+			\begin{itemize}
+				\item Organism level.
+				\item Can deal with organism's sensory and nervous system, its body and its environment.
+				\item Geometric, mechanical, dynamical, thermal properties.
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Complex Adaptive System}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Special cases of complex systems.
+		\item Diverse and made up of multiple interconnected elements.
+		\item Adaptive as they have the capacity to change and learn from experience.
+		\item Examples:
+		\begin{itemize}
+			\item Stock market, social insect and ant colonies.
+			\item Biosphere and the ecosystem.
+			\item Brain and the immune system.
+			\item Cell and the developing embryo.
+			\item Manufacturing businesses.
+			\item Human social group-based endeavor in a cultural and social system.
+			\item Large-scale online systems, collaborative tagging or social bookmarking systems.
+		\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Complex Adaptive Systems}
+	\framesubtitle{Criteria}
+
+	\begin{itemize}
+		\item ``All complex adaptive system involve large number of parts undergoing a kaleidoscopic
+array of simultaneous non linear interactions."
+		\item ``The impact of these systems in human affairs center on the aggregate behavior, the
+behavior of the whole."
+		\item ``The interactions evolve over time, as the parts adapt in an attempt to survive in the
+environment provided by the other parts."
+		\item ``Complex adaptive systems anticipate."
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Echo}
+	\framesubtitle{Criteria}
+
+	\begin{itemize}
+		\item Simplicity, thought experiment, primitive internal model.
+		\item
+		\item Fitness is an evolving criteria. It is provided by the site and other agents.
+		\item ``The primitive mechanisms in Echo should have ready counter parts in all CAS".
+		\item Flexible architecture to incorporate well studied mathematical models.
+		\begin{itemize}
+			\item Dawkins' biological arms race.
+			\item Brower's survival of mimics.
+			\item Wicksell's Triangle and overlapping generation models in economics.
+			\item Prisoner's dilemma game in political science.
+			\item Holland's two-armed bandits in operational research.
+			\item Perelson's antigen-body matching in immunology.
+		\end{itemize}
+		\item Echo model should be amenable to mathematical analysis.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Ecology of Echo}
+	\framesubtitle{Organization}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Ecology of Echo}
+	\framesubtitle{Resources and Sites}
+
+	\begin{itemize}
+		\item 
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Ecology of Echo}
+	\framesubtitle{Agents}
+
+	\begin{itemize}
+		\item Replication
+		\begin{itemize}
+			\item
+		\end{itemize}
+		\item Interactions
+		\begin{itemize}
+			\item
+		\end{itemize}
+		\item Combat
+		\begin{itemize}
+			\item
+		\end{itemize}
+		\item Trading
+		\begin{itemize}
+			\item
+		\end{itemize}
+		\item Mating
+		\begin{itemize}
+			\item
+		\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Ecology of Echo}
+	\framesubtitle{Results}
+
+	\begin{itemize}
+		\item Preston's Curve
+		\begin{itemize}
+			\item
+		\end{itemize}
+		\item Species-area scaling relation
+		\begin{itemize}
+			\item
+		\end{itemize}
+	\end{itemize}
+}

### 2011-01-08 docs/slides/mimicry.tex
More slides added.
Some updates...

@@
 	\begin{itemize}
-		\item Reduced predation lead.
+		\item Reduced predation load.
 		\item Contribution from naive young predators.
@@
 		\item Predator's advantage to know all noxious species and deterrent species.
-		\item Prey species creating the most traumatic stimuli to a predator have more possibility of the being the model.
+		\item Prey creating most traumatic stimuli to a predator is the model.
 	\end{itemize}
@@
 		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
-		\item Each cluster of species, all sharing a common pattern is termed as Mullerina mimicry ring.
+		\item Each cluster of species, all sharing a common pattern is termed as Mullerian mimicry ring.
 		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.

### 2011-01-10 docs/slides/review.tex
Some updates...
Updates to the review slides.

--- 2010-12-26 docs/slides/review.tex
@@
 {
+	\begin{center}
+		\LARGE A Review
+	\end{center}
+}
+
+\frame
+{
 	\frametitle{Review}
+
+	\begin{itemize}
+		\item Evolutionary Computation
+			\begin{itemize}
+				\item Genetic Algorithms
+				\item Evolutionary Strategies
+				\item Evolutionary Programming
+				\item Genetic Programming
+			\end{itemize}
+		\item Artificial Life
+			\begin{itemize}
+				\item Complex Adaptive System
+				\item Echo
+			\end{itemize}
+	\end{itemize}
 }
+
+\subsection{Evolutionary Computation}
+
+\frame
+{
+	\frametitle{Evolutionary Computation}
+	\framesubtitle{History}
+
+%	\begin{itemize}
+%		\item Turing (1948): ``Intelligent Machinery", expression ``genetical or evolutionary search"
+%		\item Bremermann (1962): Solve optimization problems. Minimize a real-valued function.
+%		\item Rechenberg (1964): Evolutionary strategies. Aerodynamic wing design.
+%		\item L. Fogel, Owens and Walsh (1965): Merged evolutionary computation and computational intelligence.
+%		\item Holland (1975): Genetic Algorithms, Schema theorem.
+%		\item Koza (1992): Genetic Programming. Automated method for creating computer program.
+%	\end{itemize}
+
+	\begin{itemize}
+		\item Turing (1948):
+			\begin{itemize}
+				\item ``Intelligent Machinery"
+				\item expression ``genetical or evolutionary search"
+			\end{itemize}
+		\item Bremermann (1962):
+			\begin{itemize}
+				\item Solve optimization problems.
+				\item Minimize a real-valued function.
+			\end{itemize}
+		\item Rechenberg (1964):
+			\begin{itemize}
+				\item Evolutionary strategies.
+				\item Aerodynamic wing design.
+			\end{itemize}
+		\item L. Fogel, Owens and Walsh (1965):
+			\begin{itemize}
+				\item Merged evolutionary computation and computational intelligence.
+			\end{itemize}
+	\end{itemize}	
+}
+
+\frame
+{
+	\frametitle{Evolutionary Computation}
+	\framesubtitle{History}
+
+	\begin{itemize}
+		\item Holland (1975):
+			\begin{itemize}
+				\item Genetic Algorithms
+				\item Schema theorem.
+			\end{itemize}
+		\item Koza (1992):
+			\begin{itemize}
+				\item Genetic Programming.
+				\item Automated method for creating computer program.
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Algorithm}
+
+	\begin{itemize}
+		\item Strategy: survival of the fittest.
+		\item Fitness function
+		\item Variation operators:
+			\begin{itemize}
+				\item Mutation
+				\item Recombination
+			\end{itemize}
+		\item Fundamental forces:
+			\begin{itemize}
+					\item ``Variation operators create diversity; facilitates novelty."
+					\item ``Selection acts as a force pushing quality."
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Genetic Algorithm}
+
+	\begin{itemize}
+		\item Wide set of applications.
+		\item Holland's ``Adaptation in natural and artificial systems"
+		\item Effective to solve optimization problems.
+		\item Ineffective: solution set does not have gnomic representation.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Strategies}
+
+	\begin{itemize}
+		\item Self adaptation of strategy parameters.
+		\item Real-valued vectors
+		\item Recombination: discrete or intermediary.
+		\item Mutation: Gaussian perturbation.
+		\item Fast and good optimizer for real-valued optimization.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Evolutionary Programming}
+
+	\begin{itemize}
+		\item Generate Artificial Intelligence by simulating evolution as a learning process.
+		\item Intelligence: System should adapt its behavior to meet specified goal in the environment.
+		\item Representation: real-valued vectors.
+		\item Parent selection: Deterministic.
+		\item Off springs are created via mutation.
+		\item No recombination operator.
+		\item Mutation: Gaussian perturbation.
+		\item Survivor selection: probabilistic.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Genetic Programming}
+
+	\begin{itemize}
+		\item Applied to machine learning: prediction and classification.
+		\item Behavior: similar to Neural Network.
+		\item Very slow process.
+		\item Non-linear chromosomes such as trees and graphs.
+		\item Mutation is mostly avoided.
+		\item Recombination operator work by exchanging trees.
+		\item Parent selection: Fitness proportional.
+		\item Survivor selection: Replacement of generations.
+		\item Difference from genetic algorithm: the chromosomes are trees.
+	\end{itemize}
+}
+
+\subsection{Artificial Life}
+
+\frame
+{
+	\frametitle{Artificial Life}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Introduced by Christopher G. Langton.
+		\item At `International Conference on the Synthesis and Simulation of Living Systems', Los Alamos National laboratory 1987.
+		\item Described by Taylor as a tool for biological inquiry.
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Artificial Life}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Wetware system (Molecular level):
+			\begin{itemize}
+				\item Natural life or derived from it.
+				\item Artificial evolutionary process toward the production of RNA molecules.
+			\end{itemize}
+		\item Software system (Cellular level):
+			\begin{itemize}
+				\item Initial contribution: John von Neumann.
+				\item Self reproducing, computation universal Cellular Automata.
+			\end{itemize}
+		\item Hardware system (Organism level):
+			\begin{itemize}
+				\item Organism's sensory and nervous system: body and environment.
+				\item Geometric, mechanical, dynamical, thermal properties.
+			\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Complex Adaptive System}
+	\framesubtitle{}
+
+	\begin{itemize}
+		\item Special cases of complex systems.
+		\item Diverse and made up of multiple interconnected elements.
+		\item Adaptive: capacity to change and learn from experience.
+		\item Examples:
+		\begin{itemize}
+			\item Stock market.
+			\item Social insect and ant colonies.
+			\item Biosphere and the ecosystem.
+			\item Brain and the immune system.
+			\item Cell and the developing embryo.
+			\item Manufacturing businesses.
+			\item Human social group-based endeavor in a cultural and social system.
+			\item Large-scale online systems, collaborative tagging or social bookmarking systems.
+		\end{itemize}
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Complex Adaptive Systems}
+	\framesubtitle{Criteria}
+
+	\begin{itemize}
+		\item ``Large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."
+		\item ``Impact in human affairs: aggregate behavior; behavior of the whole."
+		\item ``Interactions evolve over time: parts adapt to survive in the environment"
+		\item ``Complex adaptive systems anticipate."
+	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Echo}
+	\framesubtitle{Criteria}
+
+	\begin{itemize}
+		\item Simplicity, thought experiment, primitive internal model.
+		\item Fitness: an evolving criteria.
+		\item ``The primitive mechanisms in Echo should have ready counter parts in all CAS".
+		\item Flexible architecture: incorporate well studied mathematical models.
+		\begin{itemize}
+			\item Dawkins' biological arms race.
+			\item Brower's survival of mimics.
+			\item Wicksell's Triangle and overlapping generation models in economics.
+			\item Prisoner's dilemma game in political science.
+			\item Holland's two-armed bandits in operational research.
+			\item Perelson's antigen-body matching in immunology.
+		\end{itemize}
+		\item Amenable to mathematical analysis.
+	\end{itemize}
+}

### 2011-01-10 docs/tex/conclusion.tex
Frank has been changed to Franks
Updates to the review slides.

@@
 As mentioned in section \ref{sec:result-conclusion} this model give us proof of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
-Also it enforces findings from the work of Frank and Noble that multiple Mullerian mimics do not converge into one large ring.
+Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
 
@@
 Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsec:evo-comp-history}).
-Eventually in 1975 John Holland was able to make the most applicable use of the process to evolution to solve problems in computer science by his invention of Genetic Algorithms.
+Eventually in 1975 John Holland was able to make the most applicable use of the process of evolution to solve problems in computer science by his invention of Genetic Algorithms.
 The time for this invention was appropriate as the field of computer science was in its burgeoning state.

### 2011-01-10 docs/slides/mimicry.tex
Mimicry slides update.

@@
 		\item Henry W. Bates first published in 1862.
+			\begin{itemize}
 				\item \textbf{Content:} Similarity and dissimilarity between Heliconiinae and Ithomiinae butterflies. 
+			\end{itemize}
 		\item Bates collected 94 species of butterfly.
-		\item They were grouped according to their similar appearance.
-		\item \textbf{Discovery:} Similar appearing butterfly with morphological feature pointing to different species.
-		\item 67 of the 94 are classified as Ithomiinae.
-		\item 27 are Heliconiinae.
+		\item Grouped according to similar appearance.
+		\item \textbf{Discovery:} Appearance: similar, Morphological feature: different species.
+		\item 67 of 94: Ithomiinae.
+		\item 27 of 94: Heliconiinae.
 	\end{itemize}
@@
 			\end{itemize}
-		\item Predators, such as insectivorous birds do not prey on them.
+		\item Predators, insectivorous birds do not prey on Heliconiids.
 			\begin{itemize}
-				\item \textbf{Reason:} Heliconiids are inedible and unpalatable.
+				\item \textbf{Reason:} Inediblity and unpalatability.
 			\end{itemize}
@@
 			\begin{itemize}
-				\item Reason: Conspicuously coloration
-				\item This color acts as warning to predators.
+				\item Reason: Conspicuous coloration.
+				\item Color acts as warning.
 			\end{itemize}
@@
 				\item palatable
-				\item and they want to pretend like Heliconiids to enjoy protection.
+				\item pretend like Heliconiids, enjoy protection.
 			\end{itemize}
@@
 	\begin{itemize}
-		\item According to Wilcker: \\
-			\textsl{``An actor is a mime, so representation of a false warning pattern in called Mimicry. Bates was the first to point out this phenomenon, so its Batesian mimicry in his name."}
-		\item \textbf{Model:} The animal which is avoided by predator for unpalatable behavior.
-		\item \textbf{Mimic:} The imitating animal.
+		\item According to Wilcker:
+			\begin{itemize}
+				\item Actor is a mime.
+				\item False representation of warning pattern: Mimicry.
+				\item Bates: First to point out, so Batesian Mimicry.
+			\end{itemize}
+		\item \textbf{Model:} Animal avoided by predator for unpalatable behavior.
+		\item \textbf{Mimic:} Imitating animal.
 	\end{itemize}
@@
 
-\frame
-{
-	\frametitle{Definition of Mimicry}
-	\framesubtitle{by Bates and Zoological Congress}
+%\frame
+%{
+%	\frametitle{Definition of Mimicry}
+%	\framesubtitle{by Bates and Zoological Congress}
+%	
+%	\begin{itemize}
+%		\item Bates: \textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
+%		\item International Zoological Congress in Washington, 1963: \textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
+%	\end{itemize}
+%}
 
-	\begin{itemize}
-		\item Bates: \textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
-		\item International Zoological Congress in Washington, 1963: \textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{Definition of Mimicry}
-	\framesubtitle{by Wallace}
-
-	Definition by Wallace and listed in Poulton's \textit{``The color of animals, their meaning and use"}.
-		\begin{itemize}
-			\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
-			\item \textsl{``that the imitators are always,"}
-				\begin{itemize}
-					\item \textsl{``the more defenseless"}
-					\item \textsl{``less numerous in individuals"}
-					\item \textsl{``differ from the bulk of their allies"}
-				\end{itemize}
-			\item \textsl{``that the imitation, however minute"}
-				\begin{itemize}
-					\item \textsl{``is external and visible only"}
-					\item \textsl{``never extending to internal characters or to such as do not affect the external appearance."}
-				\end{itemize}
-		\end{itemize}
-}
+%\frame
+%{
+%	\frametitle{Definition of Mimicry}
+%	\framesubtitle{by Wallace}
+%	
+%	Definition by Wallace and listed in Poulton's \textit{``The color of animals, their meaning and use"}.
+%		\begin{itemize}
+%			\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
+%			\item \textsl{``that the imitators are always,"}
+%				\begin{itemize}
+%					\item \textsl{``the more defenseless"}
+%					\item \textsl{``less numerous in individuals"}
+%					\item \textsl{``differ from the bulk of their allies"}
+%				\end{itemize}
+%			\item \textsl{``that the imitation, however minute"}
+%				\begin{itemize}
+%					\item \textsl{``is external and visible only"}
+%					\item \textsl{``never extending to internal characters or to such as do not affect the external appearance."}
+%				\end{itemize}
+%		\end{itemize}
+%}
 
@@
 	\begin{itemize}
-		\item Two inedible unrelated butterfly species have similar appearance. Bates was unable to explain this.
-		\item Explanation came from Fitz Muller in 1878.
-		\item Muller's research was in Brazil.
+		\item Two inedible unrelated butterfly species have similar appearance. 
+		\item Bates: Unable to explain.
+		\item Explanation: from Fitz Muller in 1878.
+		\item Muller's research was also in Brazil.
 	\end{itemize}
@@
 		\item Predator's limited memory.
-		\item Different species loose their number even being inedible.
-		\item To save this loss and also for survival of species, inedible ones from different family evolve to have similar appearance.
-		\item Phenomenon is referred as Mullerian mimicry, named after Fritz Muller.
+		\item Inedible species loose number.
+		\item Save loss and survival of species:
+			\begin{itemize}
+				\item inedible, different family 
+				\item evolve to have similar appearance.
+			\end{itemize}
+		\item Phenomenon: Mullerian mimicry, named after Fritz Muller.
 	\end{itemize}
@@
 	\begin{itemize}
+		\item Predator:
+			\begin{itemize}
 				\item Reduced predation load.
 				\item Contribution from naive young predators.
+				\item Predator's generalization.
+			\end{itemize}
+		\item Prey:
+			\begin{itemize}
 				\item Mutual advertising.
 				\item Opportunity from mutation.
-		\item Predator's generalization.
+			\end{itemize}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Mullerian mimicry is not deception.
+		\item Not deception.
 		\item Predator's advantage to know all noxious species and deterrent species.
@@
 
-	Explanation for evolutionary dynamics of mimicry is from Turner. Most sexually reproducing species will remain:
+	Most sexually reproducing species remain:
 	\begin{itemize}
-		\item in extended state of \textit{stasis}.
-		\item Little evolutionary change in most of their geological history.
+		\item extended state of \textit{stasis}.
+		\item Little evolutionary change in most geological history.
 	\end{itemize}
@@
 		\item Process of speciation.
-		\item One species split into two distinct species.
-		\item It is a discontinuous change, rather than a gradual transformation in a geological time.
+		\item One split into two distinct species.
+		\item In geological time:
+			\begin{itemize}
+				\item Discontinuous change
+				\item Not gradual transformation
+			\end{itemize}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Species continue to adapt to new environmental and biological selection pressure.
-		\item Gradually becomes a new species.
+		\item Continued adaptation to new environmental and biological selection pressure.
+		\item Gradually becoming new species.
 	\end{itemize}
 
-	Phyletic gradualism holds that,
+	Phyletic gradualism holds,
 	\begin{itemize}
 		\item Species population changes gradually.
-		\item There is no clear demarcation between an ancestral species and a descendant species.
+		\item No clear demarcation between ancestral and descendant species.
 		\item Gradually changing lineage is divided arbitrarily.
@@
 	\begin{itemize}
-		\item Turner came up with a synthetic theory.
-		\item Theory originated from Poulton and Nicholson.
+		\item Turner: Synthetic theory.
+		\item Originated from Poulton and Nicholson.
 		\item Mimicry arises in two steps:
@@
 			\end{enumerate}
-		\item This theory has also been applied to Mullerian Mimicry.
+		\item Theory also applied to Mullerian Mimicry.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Examine the local butterfly fauna in any area of the world to find, between all the aposomatic species, only a limited number of different patterns, normally far smaller than the number of species.
-		\item Each cluster of species, all sharing a common pattern is termed as Mullerian mimicry ring.
-		\item Consider all the rain forest in South and Central America, most of the long winged butterflies (ithomiids, danaids and heliconids) belong to one of only five different rings.
+		\item Examine the local butterfly fauna in any area of the world
+		\begin{itemize}
+			\item all the aposomatic species
+			\item limited number of different patterns
+			\item normally far smaller than the number of species.
+		\end{itemize}
+		\item Mullerian mimicry ring: 
+			\begin{itemize}
+				\item Each cluster of species
+				\item all sharing a common pattern
+			\end{itemize}		
+		\item All the rain forest in South and Central America,
+		\begin{itemize}
+			\item most of the long winged butterflies (ithomiids, danaids and heliconids) 
+			\item belong to one of only five different rings.
+		\end{itemize}
 	\end{itemize}	
@@
 			\begin{itemize}
-				\item Similar enough that the envelop of protection in one provides protection to the other.
+				\item Similar enough the envelop of protection in one provides protection to the other.
 				\item \textbf{Result:} Natural protection of mutual convergence.
@@
 			\begin{itemize}
-				\item Envelop of protection do not overlap. Predator consuming one will not mistake of the other pattern.
+				\item Envelop of protection do not overlap. 
+				\item Predator consuming one will not mistake of the other pattern.
 				\item \textbf{Result:} No convergence, two patterns will remain distinct.
@@
 			\begin{itemize}
-				\item Mutation can lead one species into the envelop of protection of another species. 
+				\item Mutation can lead one species into the envelop of protection of another. 
 				\item \textbf{Result:} Gradual convergence of one pattern with another.

### 2011-01-10 docs/slides/conclusion.tex
Analysis and application updated.
Batesian and Mullerian mimicry slides.
Slide updates before submission.

@@
 {
+	\begin{center}
+		\LARGE Conclusion
+	\end{center}
+}
+
+\frame
+{
 	\frametitle{Conclusion}
+
+	Artificial Life:
+	\begin{itemize}
+		\item Tool for Biological inquiry
+			\begin{itemize}
+				\item Success: Proof of Turner's punctuated equilibrium
+				\item Proof of Franks and Noble's converge of one large ring.
+			\end{itemize}
+		\item Nature inspired computer science
+			\begin{itemize}
+				\item Success: Appropriate emulation of Batesian and Mullerian mimicry.
+			\end{itemize}
+		\item Solve problem in Computer Science
+			\begin{itemize}
+				\item Not successful: unable to find the appropriate problem solving scenario.
+			\end{itemize}
+	\end{itemize}
 }
+
+\frame
+{
+	\frametitle{Conclusion}
+	\framesubtitle{Objective of Research}
+
+	\begin{itemize}
+		\item Objective of any research:
+			\begin{itemize}
+				\item Unexplored Territory: find new knowledge, understanding, explanation.
+			\end{itemize}
+		\item This research:
+			\begin{itemize}
+				\item New Understanding: Can emulate natures behavior.
+				\item Explore a new model.
+				\item Better explanation and understanding of nature.
+			\end{itemize}
+	\end{itemize}
+}

### 2011-01-10 docs/slides/model.tex
Some updates...
Slide updates before submission.

@@
 				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
-				\item Predators use simple Monte Carlo learning or mathematical approach.
+				\item Predator: Simple Monte Carlo learning or mathematical approach.
 			\end{itemize}
@@
 				\item Co-evolving predator and prey population.
-				\item Predators are deterministic, cannot learn from experience.
-				\item Predators attack policy is fixed, either attack or avoid.
+				\item Predators:
+				\begin{itemize}
+					\item deterministic
+					\item cannot learn from experience.
+					\item attack policy is fixed, either attack or avoid.
+				\end{itemize}
 			\end{itemize}
@@
 	\begin{itemize}
-		\item Multiple species are preyed upon by a single abstract predator.
-		\item Appearance of the prey can evolve.
+	\item Prey
+		\begin{itemize}
+			\item Appearance can evolve.
 			\item Palatability is fixed.
-		\item Each individual has a single gene, value representing external appearance.
-		\item Phenotypes are a ring of value from 1-20 (20 and 1 are neighbors).
+			\item Single gene: value representing external appearance.
+			\item Phenotype: a ring of value from 1-20 (20 and 1 are neighbors).
 			\item Distance represents similarity.
-		\item Predator uses simple reinforcement learning system.
-		\item Three experiments carried out varying palatability of prey.
+		\end{itemize}
+	\item Predator
+		\begin{itemize}
+			\item Single abstract predator.
+			\item Simple reinforcement learning system.
+		\end{itemize}
+
+		\item Three experiments, varying palatability of prey.
 		\item Batesian mimicry was established.
@@
 	\begin{itemize}
-		\item Prey population has appearance and palatability.
+		\item Prey: appearance and palatability.
 		\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
@@
 		\item Predators use generation on the basis of experience.
-		\item Set of probability formula was used to make decision for consumption of prey, depending on phenotype.
+		\item Decision for consumption of prey:
+		\begin{itemize}
+			\item Use: set of probability formula.
+			\item Dependence on phenotype.
+		\end{itemize}
 	\end{itemize}
@@
 				\item Some palatable and some unpalatable species.
-				\item Reaches condition of Batesian mimicry. Hypothesis 2 is established.
+				\item Reaches condition of Batesian mimicry. 
+				\item Hypothesis 2 is established.
 				\item \textbf{Observation:}
@@
 			\begin{itemize}
-				\item To study the emergence of complexity.
+				\item Study the emergence of complexity.
 				\item No variable unless genetically controlled or influenced. \textit{Principal not followed for Hopfield Network.}
@@
 				\item Simulated organism.
-				\item Able to reproduce itself using genetic information.
+				\item Reproduce itself using genetic information.
 				\item Capable of modifying structures of genome between generations.
-				\item Able to interact with other agents.
+				\item Interaction with other agents.
 				\item Survive and reproduce in a challenging environment.
@@
 
-	Environment is 3D, where agents get complete freedom of movement defined from genetic representation.
+	Environment is 3D, complete freedom of movement defined from genetic representation.
 	\begin{itemize}
@@
 		\item Position is calculated in each step in time.
-		\item \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
+		\item Vector components: \(position\), \(force\), \(acceleration\) and \(velocity\).
 		\item \(force\) is calculated from the mobility genes.
-		\item Newton's law of motion is used to calculate \(acceleration\) when \(force\) is not zero.
-		\item \(acceleration\) is integrated to obtain velocity and new position.
+		\item Newton's law of motion, used to calculate \(acceleration\) when \(force\) is not zero.
+		\item \(acceleration\) is integrated to obtain \(velocity\) and new \(position\).
 	\end{itemize}
@@
 \subsection{Prey}
+
+\frame
+{
+	\frametitle{The Prey}
+	\framesubtitle{Mimics and Models}
+
+	\begin{itemize}
+		\item Agent in the FormAL environment.
+		\item Genetic representation of pattern with Cellular Automata.
+		\item Creates diversity of species.
+		\item Pattern evolution is in the process of punctuated equilibrium.
+		\item Mobility and reproduction capability controlled genetically.
+	\end{itemize}
+}
 
@@
 	\begin{itemize}
-		\item Agent's pattern genome is 8 bit binary value.
-		\item Decimal range 0 to 255.
-		\item 256 unique CA pattern associated.
-		\item The linear representation of this pattern is stored in Hopfield Network.
-		\item Hamming distance between a pattern's linear representation is used to consider similarity.
-		\item Group of prey with a specific pattern is considered in a single species.
-		\item Inter species reproduction is restricted to control diversity of patterns.
-		\item Using ``Pattern Mutation Rate" we control diversity of new species.
+		\item Pattern genome is 8 bit binary. Decimal range 0 to 255.
+		\item 256 unique CA pattern.
+		\item Linear representation of pattern stored in Hopfield Network.
+		\item Pattern similarity: Hamming distance between linear representation.
+		\item Single species: group of prey with a specific pattern.
+		\item Inter species reproduction: restricted to control diversity of patterns.
+		\item ``Pattern Mutation Rate": control diversity of new species.
 	\end{itemize}
@@
 				\item inclined to cladogenesis instead of gradualism.
-				\item Turner emphasizes on punctuated equilibrium to explain evolution of mimicry.
-				\item CA pattern evolution is in a single mutation in the pattern genome.
-				\item Change of pattern is not a gradual process but rather an arbitrary discontinuous one.
+				\item Turner's emphasis on punctuated equilibrium to explain evolution of mimicry.
+				\item CA pattern evolution: single mutation in the pattern genome.
+				\item Change of pattern: 
+					\begin{itemize}
+						\item not gradual
+						\item arbitrary discontinuous
+					\end{itemize}
 			\end{itemize}
@@
 	\begin{itemize}
-		\item Six bit of the mobility gene is used to calculate the magnitude of force for mobility.
-		\item Direction is decided based on 
+		\item Mobility gene: 6 bits. 
+		\item Use: calculate the magnitude of force for mobility.
+		\item Direction:
 			\begin{itemize}
@@
 	\begin{itemize}
-		\item Reproduction begins at ``Reproductive Age"
-		\item Reproduction capability is decided on 17th bit gene.
+		\item Begins at ``Reproductive Age"
+		\item Capability is decided on 17th bit gene.
 		\item Mate selection is random, but within same cell.
@@
 				\item Single point crossover.
-				\item Two point mutation is applied based different rates.
+				\item Two point mutation: different rates
 					\begin{itemize}
@@
 		\item Provide selection pressure for the evolution of mimicry.
-		\item Each agent equipped with Hopfield Network Memory.
+		\item Equipped with Hopfield Network Memory.
 		\item Mobility and reproduction capability controlled genetically.
@@
 		\item If unable to consume prey is thrown back into environment.
-		\item At this event prey pattern is stored into predators memory with the associated palatability.
+		\item Store prey pattern into memory with the associated palatability.
 		\item New pattern learned with Hebbian Learning.
@@
 				\item Each prey has an evolving CA represented by a binary Genome.
-				\item This 2D pattern is serialized to a 1D binary array.
-				\item Binary representation is converted to bipolar representation.
+				\item 2D pattern is serialized to a 1D binary array.
+				\item Binary representation converted to bipolar representation.
 			\end{itemize}
@@
 				\item Learning: Apply Hebbian learning to calculate weights.
-				\item Initialization: Input to the network is initialized with value of the input vector.
-				\item Iterate Until Convergence: Each neuron is updated asynchronously with the input of its previous state until convergence.
+				\item Initialization: Input to network initialized with input vector.
+				\item Iterate Until Convergence: Asynchronous update of each neuron. Input: previous state.
 				\item Output: Finally a pattern is set as output when the network reaches convergence.
@@
 	\begin{itemize}
-		\item When agent reaches `Minimum Attack Age' it starts hunting.
+		\item Agent reaches `Minimum Attack Age' it starts hunting.
 		\item Select a random prey within vicinity (same cell).
-		\item Attack process involves recognition of prey pattern.
-		\item Two parameters to limit pattern memorization and recognition process as both are computationally expensive.
+		\item Involves recognition of prey pattern.
+		\item Pattern memorization and recognition process: computationally expensive.
+		\item Two parameters to limit 
 			\begin{itemize}
@@
 	\begin{itemize}
-		\item First 4 bits of the genome calculated to evaluate the magnitude of force of movement.
-		\item Direction is decided based on the number of prey species present in a neighboring cell.
+		\item Magnitude of force of movement: 4 bits of genome.
+		\item Direction: number of prey species present in a neighboring cell.
 		\item Move towards the cell with least number of predator and most number of prey.
-		\item This is such that predators are distributed all over the environment.
+		\item Result: Predators are distributed all over the environment.
 		\item Increases agent's predatory behavior.
@@
 	\begin{itemize}
-		\item Agent reaches reproduction age.
-		\item Agent exceeds reproduction age interval, which is difference in time between two reproduction activity.
-		\item Agent is capable of reproduction depending on 5th gene.
-		\item Select another predator from same cell which satisfy above conditions.
-		\item Perform crossover and mutation to create another predator.
-		\item Predator is initialized with zero memory.
+		\item Reproduction age: begins.
+		\item Reproduction age interval: which is difference in time between two reproduction activity.
+		\item Capability: 5th gene.
+		\item Selection: another predator from same cell which satisfy above conditions.
+		\item Perform genome crossover and mutation: create new predator.
+		\item New predator initialized with zero memory.
 	\end{itemize}

### 2011-01-10 docs/slides/result.tex
Batesian and Mullerian mimicry slides.
Slide updates before submission.

@@
 \section{Results}
+
+\frame
+{
+	\begin{center}
+		\LARGE The Results
+	\end{center}
+}
 
@@
 			\begin{itemize}
-			  \item Calculate number mimicry rings.
+			  \item Calculate number of mimicry rings.
 			  \item Calculate size of mimicry rings:
@@
 
+	\textbf{New experiment:}
 	\begin{itemize}
-		\item \textbf{New experiment:} reduce predator memory to 1.\\
-		\item \textbf{Observation:} The phenomenon of single large ring do not occur. 
+		\item Reduce predator memory to 1.\\
+		\item \textbf{Observation:} Single large ring do not occur. 
 		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
+	\end{itemize}	
 	Multiple Mullerian mimics do not converge into one large ring.
-	\end{itemize}	
+
 }

### 2011-01-14 docs/slides_shortened/application.tex
Thesis shortened.

--- 2010-12-29 docs/slides/application.tex
@@
 \section{Application}
+
+\frame
+{
+	\begin{center}
+		\LARGE Future work: Application
+	\end{center}
+}
 
@@
 				\item Palatability is equivalent to evaluation/fitness function.
-				\item Then why have mimics in the solution set, when mimics will have the same pattern as the model.
+				\item Why have mimics in the solution set, when mimics will have the same pattern as the model.
 			\end{itemize}
 		\item Conclusion: solving optimization problem is futile.
-		\item Apply evolution of mimicry to a problem where \textit{deception} is useful.
+		\item Apply to a problem where \textit{deception} is useful.
 	\end{itemize}

### 2011-01-14 docs/slides_shortened/introduction.tex
Thesis shortened.

\section{Introduction}

\frame
{
	\begin{center}
		\LARGE Introduction
	\end{center}
}

\frame
{
	\frametitle{Introduction}

	\begin{itemize}
		\item Mimicry:
			\begin{itemize}
				\item Process of deception.
				\item Evolutionary process.
				\item Organisms survive by deceiving its predators.
				\item Occurs in existence of similar appearing noxious organisms.
				\item Palatable mimics unpalatable for \textit{survival of species}.
			\end{itemize}
		\item Artificial Life:
			\begin{itemize}
				\item Interdisciplinary study of life and \textit{life-like process} using \textit{synthetic method}.
				\item Life-like process: Evolution of mimicry.
				\item Synthetic tools:
					\begin{enumerate}
						\item 3D Visual Environment.
						\item Cellular Automata.
						\item Neural Network.
					\end{enumerate}
			\end{itemize}
	\end{itemize}
}

### 2011-01-14 docs/slides_shortened/mimicry.tex
Thesis shortened.

--- 2011-01-10 docs/slides/mimicry.tex
@@
 
-%\frame
-%{
-%	\frametitle{Definition of Mimicry}
-%	\framesubtitle{by Bates and Zoological Congress}
-%	
-%	\begin{itemize}
-%		\item Bates: \textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
-%		\item International Zoological Congress in Washington, 1963: \textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
-%	\end{itemize}
-%}
-
-%\frame
-%{
-%	\frametitle{Definition of Mimicry}
-%	\framesubtitle{by Wallace}
-%	
-%	Definition by Wallace and listed in Poulton's \textit{``The color of animals, their meaning and use"}.
-%		\begin{itemize}
-%			\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
-%			\item \textsl{``that the imitators are always,"}
-%				\begin{itemize}
-%					\item \textsl{``the more defenseless"}
-%					\item \textsl{``less numerous in individuals"}
-%					\item \textsl{``differ from the bulk of their allies"}
-%				\end{itemize}
-%			\item \textsl{``that the imitation, however minute"}
-%				\begin{itemize}
-%					\item \textsl{``is external and visible only"}
-%					\item \textsl{``never extending to internal characters or to such as do not affect the external appearance."}
-%				\end{itemize}
-%		\end{itemize}
-%}
-
 \subsection{Mullerian Mimicry}
@@
 		\item Phenomenon: Mullerian mimicry, named after Fritz Muller.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{Mullerian Mimicry}
-	\framesubtitle{Huheey's explanation}
-
-	\begin{itemize}
-		\item Predator:
-			\begin{itemize}
-				\item Reduced predation load.
-				\item Contribution from naive young predators.
-				\item Predator's generalization.
-			\end{itemize}
-		\item Prey:
-			\begin{itemize}
-				\item Mutual advertising.
-				\item Opportunity from mutation.
-			\end{itemize}
-	\end{itemize}
-
-	\begin{itemize}
-		\item Not deception.
-		\item Predator's advantage to know all noxious species and deterrent species.
-		\item Prey creating most traumatic stimuli to a predator is the model.
 	\end{itemize}
@@
 		\includegraphics[scale=0.3]{../tex/images/Punctuated-equilibrium}
-		\caption{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
-Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
+		\caption{Punctuated equilibrium (bottom), phyletic gradualism (top). Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
 		\label{fig:punctuated-equilibrium}
@@
 }
-
-\frame
-{
-	\frametitle{Mimicry Ring}
-	\framesubtitle{Formation}
-
-	Turner's theory of Mimicry Ring Formation, takes into account
-	\begin{itemize}
-		\item the level of protection of different rings
-		\item their difference in phenotypic warning patterns.
-	\end{itemize}
-
-}
-
-\frame
-{
-	\frametitle{Mimicry Ring}
-	\framesubtitle{Formation}
-
-	Varying these two parameters give different formation of mimicry rings:
-	\begin{itemize}
-		\item Similar pattern in one habitat:
-			\begin{itemize}
-				\item Similar enough the envelop of protection in one provides protection to the other.
-				\item \textbf{Result:} Natural protection of mutual convergence.
-			\end{itemize}
-		\item Very dissimilar patterns:
-			\begin{itemize}
-				\item Envelop of protection do not overlap. 
-				\item Predator consuming one will not mistake of the other pattern.
-				\item \textbf{Result:} No convergence, two patterns will remain distinct.
-			\end{itemize}
-		\item Mutation:
-			\begin{itemize}
-				\item Mutation can lead one species into the envelop of protection of another. 
-				\item \textbf{Result:} Gradual convergence of one pattern with another.
-			\end{itemize}
-	\end{itemize}
-}

### 2011-01-14 docs/slides_shortened/model.tex
Thesis shortened.

--- 2011-01-10 docs/slides/model.tex
@@
 {
-	\frametitle{Past Work}
-	\framesubtitle{First Model by Franks and Noble}
-
-	\begin{itemize}
-	\item Prey
-		\begin{itemize}
-			\item Appearance can evolve.
-			\item Palatability is fixed.
-			\item Single gene: value representing external appearance.
-			\item Phenotype: a ring of value from 1-20 (20 and 1 are neighbors).
-			\item Distance represents similarity.
-		\end{itemize}
-	\item Predator
-		\begin{itemize}
-			\item Single abstract predator.
-			\item Simple reinforcement learning system.
-		\end{itemize}
-
-		\item Three experiments, varying palatability of prey.
-		\item Batesian mimicry was established.
-	\end{itemize}
-}
-
-\frame
-{
 	\frametitle{Franks and Noble}
-	\framesubtitle{Second Model: Working hypothesis}
+	\framesubtitle{Working hypothesis}
 
@@
 	\frametitle{Franks and Noble}
-	\framesubtitle{Second Model: Prey}
+	\framesubtitle{Prey}
 
@@
 	\frametitle{Franks and Noble}
-	\framesubtitle{Second Model: Predator}
+	\framesubtitle{Predator}
 
@@
 	\frametitle{Franks and Noble}
-	\framesubtitle{Second Model: Result}
+	\framesubtitle{Result}
 
@@
 	\frametitle{FormAL Framework}
-	\framesubtitle{Environment Parameters}
-
-	\begin{table}[H]
-	\centering
-	\begin{spacing}{1.5}
-	\begin{scriptsize}
-%	\begin{tabular}{| p{2.2cm} | >{\centering} p{3cm} | p{7.5cm} |}
-	\begin{tabular}{| p{1.5cm} | >{\centering} p{2cm} | p{4cm} |}
-		\hline
-			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-			ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
-			World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
-			Cell Size & \( World Size / ISize \) & Size of each cell\\ \hline
-			Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
-		\hline
-	\end{tabular}
-	\end{scriptsize}
-	\end{spacing}
-	\caption{Parameters to control the environment.}
-	\label{tab:environment-control-parameters}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
 	\framesubtitle{Environment - Visual representation - Front}
@@
 	\label{tab:3-d-environment-images-1}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Environment - Visual representation - Top}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.40]{../tex/images/cells-top}
-		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images-2}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Environment - Visual representation - Side}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.40]{../tex/images/cells-side}
-		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images-3}
 	\end{figure}	
@@
 	\end{itemize}
-
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Mobility Parameters}
-
-	\begin{table}
-	\centering
-	\begin{scriptsize}
-	\begin{spacing}{1.5}
-	\begin{tabular}{| p{1.7cm} | >{\centering} p{0.6cm} | p{5cm} |}
-		\hline
-			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-			Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
-			Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
-			Friction & 5 & The friction constant used for motion calculations.\\ \hline
-			Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
-		\hline
-	\end{tabular}
-	\end{spacing}
-	\end{scriptsize}
-	\caption{Parameters to control mobility of agents.}
-	\label{tab:mobility-control-parameters}
-	\end{table}
 
@@
 	\end{itemize}
+}
+
+\frame
+{
+	\frametitle{Prey Pattern}
+	\framesubtitle{Genotype vs. Phenotype}
+
+	\begin{itemize}
+		\item Genetic bit difference of one.
+		\item Vastly different phenotype.
+	\end{itemize}
+
+	\begin{table}
+	\centering
+	\begin{scriptsize}
+	\begin{tabular}{|l|c|c|c|}
+	  \hline
+	  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
+	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule60}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule61}} 
+	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule62}}\\
+	  \hline
+	\end{tabular}
+	\end{scriptsize}
+	\caption{Difference in prey pattern genotype and phenotype}
+	\label{tab:diff-in-pattern}
+	\end{table}
 }
@@
 	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Configuration Parameters}
-
-	\begin{table}[H]
-	\centering
-	\begin{scriptsize}
-	\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{4cm} |}
-		\hline
-			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-			Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
-			Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
-			Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
-			Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
-			Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
-			Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
-		\hline
-	\end{tabular}
-	\end{scriptsize}
-	\caption{Parameters to control prey population and visibility.}
-	\label{tab:prey-control-parameters}
-	\end{table}
 }
@@
 }
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Configuration Parameters}
-
-	\begin{table}
-	\centering
-	\begin{tiny}
-	\begin{tabular}{| p{1.3cm} | >{\centering} p{0.8cm} | p{5cm} |}
-		\hline
-			\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-			Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
-			Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
-			Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
-Usually the network reaches a steady state before that.
-But this restriction is to avoid infinite loop in case the network never reaches a steady state.
-\\ \hline
-			Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
-			Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
-			Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
-			Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
-			Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
-			Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
-		\hline
-	\end{tabular}
-	\end{tiny}
-	\caption{Parameters to control predator population and pattern recognition capability.}
-	\label{tab:predator-control-parameters}
-	\end{table}
-}

### 2011-01-14 docs/slides_shortened/parameter.tex
Thesis shortened.

--- 2011-01-03 docs/slides/model.tex
@@
-\section{The Model}
+\section{Appendix: Simulation Parameters}
 
@@
 	\begin{center}
-		\LARGE The Model: Evolution of Mimicry
+		\LARGE Appendix: Simulation Parameters
 	\end{center}
-}
-
-\frame
-{
-	\frametitle{The Model}
-	\framesubtitle{Evolution of Mimicry}
-
-	\begin{itemize}
-		\item \textbf{Objective:} Build an \textit{agent based} Artificial Life model for simulating the evolution of mimicry.	
-		\item Two species of agents:
-			\begin{enumerate}
-				\item Prey
-					\begin{itemize}
-						\item Model
-						\item Mimic
-					\end{itemize}
-				\item Predator
-			\end{enumerate}
-		\item Prey pattern representation: Cellular Automata.
-		\item Predator pattern recognition: Hopfield Network.
-		\item Environment: Visual representation, 3D, toroidal.
-	\end{itemize}	
-}
-
-\subsection{Past Work}
-
-\frame
-{
-	\frametitle{The Model}
-	\framesubtitle{Past Work}
-
-	\begin{itemize}
-		\item Turner(1996) and Huheey(1988):
-			\begin{itemize}
-				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
-				\item Predators use simple Monte Carlo learning or mathematical approach.
-			\end{itemize}
-		\item Sherratt(2002):
-			\begin{itemize}
-				\item Co-evolving predator and prey population.
-				\item Predators are deterministic, cannot learn from experience.
-				\item Predators attack policy is fixed, either attack or avoid.
-			\end{itemize}
-	\end{itemize}
-}
-
-%-------------------------------
-%More slides on Franks and Noble
-%-------------------------------
-
-\frame
-{
-	\frametitle{Past Work}
-	\framesubtitle{Franks and Noble}
-
-	\begin{itemize}
-		\item First Model(2002):
-			\begin{itemize}
-				\item \textbf{Focus:} 
-				\item Predators use simple Monte Carlo learning or mathematical approach.
-			\end{itemize}
-		\item Second Model(2004):
-			\begin{itemize}
-				\item Co-evolving predator and prey population.
-				\item Predators are deterministic, cannot learn from experience.
-				\item Predators attack policy is fixed, either attack or avoid.
-			\end{itemize}
-	\end{itemize}
-}
-
-%-------------------------------
-%More slides on Franks and Noble
-%-------------------------------
-
-\subsection{FormAL}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-
-	\begin{itemize}
-		\item Ideas from Peter Grogono's Formal Artificial Life (FormAL) project.
-		\item \textbf{Goal:}		
-			\begin{itemize}
-				\item To study the emergence of complexity.
-				\item No variable unless genetically controlled or influenced. \textit{Principal not followed for Hopfield Network.}
-			\end{itemize}
-		\item \textbf{Agents:}
-			\begin{itemize}
-				\item Simulated organism.
-				\item Able to reproduce itself using genetic information.
-				\item Capable of modifying structures of genome between generations.
-				\item Able to interact with other agents.
-				\item Survive and reproduce in a challenging environment.
-			\end{itemize}
-	\end{itemize}
-
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Environment}
-
-	Environment is 3D, where agents get complete freedom of movement defined from genetic representation.
-	\begin{itemize}
-		\item \textbf{Space:}
-			\begin{itemize}
-				\item 3D Lattice of discreet points.
-				\item \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
-				\item \(S\) is a universal constant, small positive number. Value is 20, \(World Size\) parameter. 
-			\end{itemize}
-		\item \textbf{Time:}
-			\begin{itemize}
-				\item Integer value, increases in discreet steps. 
-				\item Each agent updates itself in each time step.
-			\end{itemize}
-		\item \textbf{Cell:}
-			\begin{itemize}
-				\item Entire environment is divided into multiple cells.
-				\item A 3D cubical section of the hyperspace.
-				\item \(ISize\) parameter kept at 6. Total \(ISize^3 = 216\) cells.
-			\end{itemize}
-	\end{itemize}
 }
@@
 	\frametitle{FormAL Framework}
-	\framesubtitle{Environment - Visual representation - Front}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.40]{../tex/images/cells-front}
-		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images-1}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Environment - Visual representation - Top}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.40]{../tex/images/cells-top}
-		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images-2}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Environment - Visual representation - Side}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.40]{../tex/images/cells-side}
-		\caption{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images-3}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Agent Mobility}
-
-	\begin{itemize}
-		\item Position is calculated in each step in time.
-		\item \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
-		\item \(force\) is calculated from the mobility genes.
-		\item Newton's law of motion is used to calculate \(acceleration\) when \(force\) is not zero.
-		\item \(acceleration\) is integrated to obtain velocity and new position.
-	\end{itemize}
-
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
 	\framesubtitle{Mobility Parameters}
@@
 
-}
-
-\subsection{Prey}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Pattern Representation}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=3]{../tex/images/CA_rule30s}
-		\caption{Cellular Automata Rule 30.
-		Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
-		\label{fig:cellular-automata-rule-30}
-	\end{figure}
-
-	\begin{table}
-		\centering
-		\begin{scriptsize}
-		\begin{tabular}{| p{2cm} | c | c | c | c | c | c | c | c |}
-		  \hline
-		  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
-		  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
-		  \hline
-		\end{tabular}
-		\end{scriptsize}		
-		\caption{Cellular Automata rule}
-		\label{tab:cellular-automata-rule}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Species Diversity}
-
-	\begin{itemize}
-		\item Agent's pattern genome is 8 bit binary value.
-		\item Decimal range 0 to 255.
-		\item 256 unique CA pattern associated.
-		\item The linear representation of this pattern is stored in Hopfield Network.
-		\item Hamming distance between a pattern's linear representation is used to consider similarity.
-		\item Group of prey with a specific pattern is considered in a single species.
-		\item Inter species reproduction is restricted to control diversity of patterns.
-		\item Using ``Pattern Mutation Rate" we control diversity of new species.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Genome}
-
-	\begin{itemize}
-		\item 17 bit prey Genome
-	\end{itemize}
-
-	\begin{table}[H]
-	\centering
-	\begin{scriptsize}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|c|c|c|c|}
-		\hline
-			\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
-			10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
-	\end{tabular}
-	\end{spacing}
-	\end{scriptsize}
-	\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
-	\label{tab:prey-genome}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Punctuated Equilibrium}
-
-	\begin{itemize}
-		\item Punctuated Equilibrium:
-			\begin{itemize}
-				\item inclined to cladogenesis instead of gradualism.
-				\item Turner emphasizes on punctuated equilibrium to explain evolution of mimicry.
-				\item CA pattern evolution is in a single mutation in the pattern genome.
-				\item Change of pattern is not a gradual process but rather an arbitrary discontinuous one.
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Mobility}
-
-	\begin{itemize}
-		\item Six bit of the mobility gene is used to calculate the magnitude of force for mobility.
-		\item Direction is decided based on 
-			\begin{itemize}
-				\item Towards collection of maximum prey species in a cell.
-				\item Away from concentration of predators.
-				\item Move towards the selected cell with the magnitude of force calculated.
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Reproduction}
-
-	\begin{itemize}
-		\item Reproduction begins at ``Reproductive Age"
-		\item Reproduction capability is decided on 17th bit gene.
-		\item Mate selection is random, but within same cell.
-		\item Mate needs to be
-			\begin{itemize}
-				\item similar species
-				\item genetically capable to reproduce
-				\item reached maturity 
-			\end{itemize}
-		\item Reproduction process:
-			\begin{itemize}
-				\item Single point crossover.
-				\item Two point mutation is applied based different rates.
-					\begin{itemize}
-						\item \textit{Pattern Mutation Rate}
-						\item \textit{Genome Mutation Rate}
-					\end{itemize}
-			\end{itemize}
-	\end{itemize}
 }
@@
 	\end{table}
-}
-
-\subsection{Predator}
-
-\frame
-{
-	\frametitle{The Predator}
-
-	\begin{itemize}
-		\item Agent in the FormAL environment.
-		\item Provide selection pressure for the evolution of mimicry.
-		\item Each agent equipped with Hopfield Network Memory.
-		\item Mobility and reproduction capability controlled genetically.
-		\item Unable to represent pattern recognition capability with genome.
-		\item New predators are born with zero memory, as memory is not inherited.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Learning}
-
-	\begin{itemize}
-		\item Predator's interaction objective with prey is consumption.
-		\item Consumption is based on palatability.
-		\item If unable to consume prey is thrown back into environment.
-		\item At this event prey pattern is stored into predators memory with the associated palatability.
-		\item New pattern learned with Hebbian Learning.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Hebbian Learning}
-
-	\begin{itemize}
-		\item Initially all weights are set to zero.
-		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
-		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
-	\end{itemize}
-
-Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
-\begin{equation}
-w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
-%\label{eq:}
-\end{equation}
-\[
-w_{ij} = 0, i = j
-\]
-where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
-
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Design of Memory}
-
-	\begin{itemize}
-		\item Input to Memory:
-			\begin{itemize}
-				\item Each prey has an evolving CA represented by a binary Genome.
-				\item This 2D pattern is serialized to a 1D binary array.
-				\item Binary representation is converted to bipolar representation.
-			\end{itemize}
-		\item Pattern Recognition with Hopfield Network:
-			\begin{itemize}
-				\item Learning: Apply Hebbian learning to calculate weights.
-				\item Initialization: Input to the network is initialized with value of the input vector.
-				\item Iterate Until Convergence: Each neuron is updated asynchronously with the input of its previous state until convergence.
-				\item Output: Finally a pattern is set as output when the network reaches convergence.
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Attack Algorithm}
-
-	\begin{itemize}
-		\item When agent reaches `Minimum Attack Age' it starts hunting.
-		\item Select a random prey within vicinity (same cell).
-		\item Attack process involves recognition of prey pattern.
-		\item Two parameters to limit pattern memorization and recognition process as both are computationally expensive.
-			\begin{itemize}
-				\item Hopfield Minimum Memory Size (value 2 to 6)
-				\item Hopfield Maximum Memory Size (value 10)
-			\end{itemize}
-		\item New predator attacks without caution. 
-		\item Attacks everyone and in the process store pattern and palatability.
-		\item When memory reaches `Hopfield Minimum Memory Size': intelligent selection.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Genome}
-
-	\begin{table}
-	\centering
-	\begin{scriptsize}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|c|c|}
-		\hline
-			\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
-					 1101					   &					1						 		\\ \hline
-	\end{tabular}
-	\end{spacing}
-	\end{scriptsize}
-	\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
-	\label{tab:predator-genome}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Mobility}
-
-	\begin{itemize}
-		\item First 4 bits of the genome calculated to evaluate the magnitude of force of movement.
-		\item Direction is decided based on the number of prey species present in a neighboring cell.
-		\item Move towards the cell with least number of predator and most number of prey.
-		\item This is such that predators are distributed all over the environment.
-		\item Increases agent's predatory behavior.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Reproduction process}
-
-	\begin{itemize}
-		\item Agent reaches reproduction age.
-		\item Agent exceeds reproduction age interval, which is difference in time between two reproduction activity.
-		\item Agent is capable of reproduction depending on 5th gene.
-		\item Select another predator from same cell which satisfy above conditions.
-		\item Perform crossover and mutation to create another predator.
-		\item Predator is initialized with zero memory.
-	\end{itemize}
 }

### 2011-01-14 docs/slides_shortened/result.tex
Thesis shortened.

--- 2011-01-10 docs/slides/result.tex
@@
 {
-	\frametitle{Prey Pattern}
-	\framesubtitle{Genotype vs. Phenotype}
-
-	\begin{itemize}
-		\item Genetic bit difference of one.
-		\item Vastly different phenotype.
-	\end{itemize}
-
-	\begin{table}
-	\centering
-	\begin{scriptsize}
-	\begin{tabular}{|l|c|c|c|}
-	  \hline
-	  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-	  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule60}} 
-	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule61}} 
-	  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule62}}\\
-	  \hline
-	\end{tabular}
-	\end{scriptsize}
-	\caption{Difference in prey pattern genotype and phenotype}
-	\label{tab:diff-in-pattern}
-	\end{table}
-}
-
-\frame
-{
 	\frametitle{Generated Prey Species}
@@
 		\label{fig:plot-2-prey-generated-prey}
-	\end{figure}
-}
-
-%-----------------------------
-%----- Four Prey Species ------
-%-----------------------------
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Initial Configuration}
-
-	\begin{table}
-	\centering
-	\begin{tiny}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
-	  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
-	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}
-	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}
-	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}
-	  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{1400\(\uparrow\)}} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{4\(\uparrow\)} \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{spacing}
-	\end{tiny}
-	\caption{Agent configuration of 4 prey species}
-	\label{tab:config-table-4-prey}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Population vs. Time (10k)}
-
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey}
-		\caption{Population distribution of mimicry rings, initialized with 4 prey species.}
-		\label{fig:plot-4-prey}
-	\end{figure}
-}
-
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Number of Mimicry Rings}
-
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4Prey}
-		\caption{Number of mimicry rings, initialized with 4 prey species.}
-		\label{fig:ringSize10k-4Prey}
-	\end{figure}
-}
-
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Simulation Time: 11k}
-
-	\begin{figure}[H]
-		\centering
-		\label{fig:screenshot-simTime11K-4Prey}
-		\includegraphics[scale=0.4]{../tex/images/simTime11K-4Prey}
-		\caption{Graphical representation of the model (simulation time: 11200)}
 	\end{figure}
@@
 		\label{fig:plot-4-more-prey}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Increased Population\\ Number of Mimicry Rings}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.30]{../tex/images/ringSize10k-4MorePrey}
-		\caption{Number of mimicry rings (4 prey species, increased population)}
 	\end{figure}	
@@
 		\label{fig:plot-6-prey}
-	\end{figure}
-}
-
-\frame
-{
-	\frametitle{Six Prey Species}
-	\framesubtitle{Number of Mimicry Rings}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.30]{../tex/images/ringSize10k-6Prey}
-		\caption{Number of mimicry rings (6 prey species)}
-		\label{fig:ringSize10k-6-Prey}
 	\end{figure}
@@
 
-%-----------------------------
-%----- Single Unpalatable ----
-%-----------------------------
-\frame
-{
-	\frametitle{Single Unpalatable Species}
-	\framesubtitle{Initial Configuration}
-
-	\begin{table}[H]
-	\centering
-	\begin{tiny}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
-	  																									& 216 & \multicolumn{2}{c|}{\textbf{10 \(\downarrow\)}} \\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{2 \(\downarrow\)} \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{spacing}
-	\end{tiny}
-	\caption{Agent configuration of 1 prey species unpalatable.}
-	\label{tab:config-table-1-prey-unpalatable}
-	\end{table}
-
-}
-
-\frame
-{
-	\frametitle{Single Unpalatable Species}
-	\framesubtitle{Population vs. Time (8k)}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime8k-1Prey-unp}
-		\caption{Population distribution of mimicry rings (1 prey species unpalatable)}
-		\label{fig:plot-1-prey-unp}
-	\end{figure}
-
-}
-
-%-----------------------------
-%----- Single Palatable ----
-%-----------------------------
-\frame
-{
-	\frametitle{Single Palatable Species}
-	\framesubtitle{Initial Configuration}
-
-	\begin{table}[H]
-	\centering
-	\begin{tiny}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}} 
-	  																									& 216 & \multicolumn{2}{c|}{\textbf{8 \(\downarrow\)}} \\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{spacing}
-	\end{tiny}
-	\caption{Agent configuration of 1 prey species palatable.}
-	\label{tab:config-table-1-prey-palatable}
-	\end{table}
-
-}
-
-\frame
-{
-	\frametitle{Single Palatable Species}
-	\framesubtitle{Population vs. Time (10k)}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime10k-1Prey-p}
-		\caption{Population distribution of mimicry rings (1 prey species palatable)}
-		\label{fig:plot-1-prey-p}
-	\end{figure}
-}
-
 \subsection{Analysis}
@@
 		\item \textbf{Conclusion:} Similar to Franks and Noble.\\
+		Multiple Mullerian mimics do not converge into one large ring.
 	\end{itemize}
-	Multiple Mullerian mimics do not converge into one large ring.
 

### 2011-01-14 docs/slides_shortened/result.tex
Slides reduced.

@@
 		\label{fig:plot-4-more-prey}
-	\end{figure}	
-}
-
-%-----------------------------
-%----- Six Prey Species ------
-%-----------------------------
-\frame
-{
-	\frametitle{Six Prey Species}
-	\framesubtitle{Initial Configuration}
-
-	\begin{table}
-	\centering
-	\begin{tiny}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
-	  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{\textbf{30\(\uparrow\)}}} \\ \cline{2-4}
-	  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}} 
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule57}}    
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & \textbf{6 \(\uparrow\)} \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{spacing}
-	\end{tiny}
-	\caption{Agent configuration of 6 prey species.}
-	\label{tab:config-table-6-prey}
-	\end{table}
-
-}
-
-\frame
-{
-	\frametitle{Six Prey Species}
-	\framesubtitle{Population vs. Time (10k)}
-
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime10k-6Prey}
-		\caption{Population distribution of mimicry rings (6 prey species)}
-		\label{fig:plot-6-prey}
 	\end{figure}	

### 2011-01-14 docs/slides_shortened/model.tex
Slides reduced.
Thesis further shortened..

@@
 	\frametitle{Franks and Noble}
-	\framesubtitle{Prey}
+	\framesubtitle{Prey and Predator}
 
 \begin{itemize}
-		\item Prey: appearance and palatability.
+	\item Prey:
+		\begin{itemize}
+			\item Appearance and palatability.
 			\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
@@
 		\end{itemize}	
-}
-
-\frame
-{
-	\frametitle{Franks and Noble}
-	\framesubtitle{Predator}
-
+	\item Predator:
 		\begin{itemize}
 			\item Monte Carlo reinforcement learning system.
-		\item Predators use generation on the basis of experience.
 			\item Decision for consumption of prey:
@@
 		\end{itemize}
+\end{itemize}
+
 }
@@
 	\begin{itemize}
-		\item First Experiment:
-			\begin{itemize}
-				\item 20 unpalatable prey species.
 		\item Hypothesis 1 of a single large ring did was not established.
-				\item Multiple mimicry rings exist with different frequency.
-			\end{itemize}
-		\item Second Experiment:
-			\begin{itemize}
-				\item Some palatable and some unpalatable species.
-				\item Reaches condition of Batesian mimicry. 
 		\item Hypothesis 2 is established.
@@
 				\item Batesian pressure on mimicry rings push one into the range of another.
-					\end{itemize}
 			\end{itemize}
@@
 	\frametitle{The Predator}
-	\framesubtitle{Hebbian Learning}
-
-	\begin{itemize}
-		\item Initially all weights are set to zero.
-		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
-		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
-	\end{itemize}
-
-Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
-\begin{equation}
-w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
-%\label{eq:}
-\end{equation}
-\[
-w_{ij} = 0, i = j
-\]
-where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
-
-}
-
-\frame
-{
-	\frametitle{The Predator}
 	\framesubtitle{Design of Memory}

### 2011-01-14 docs/slides_shortened/parameter.tex
Slides reduced.
Thesis further shortened..

@@
-\section{Appendix: Simulation Parameters}
+\section{Appendix}
 
@@
 }
+
+\frame
+{
+	\frametitle{The Predator}
+	\framesubtitle{Hebbian Learning}
+
+	\begin{itemize}
+		\item Initially all weights are set to zero.
+		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
+		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
+	\end{itemize}
+
+Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
+\begin{equation}
+w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
+%\label{eq:}
+\end{equation}
+\[
+w_{ij} = 0, i = j
+\]
+where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
+
+}

### 2011-01-16 docs/tex/model.tex
Updates to the review slides.
Dr. Grogono's updates.

@@
 The choice of Hopfield Network memory for a predator can be considered appropriate as the number of patterns which can be recognized by this network is inversely proportional to the accuracy of recall.
-As more patterns are memorized, Hopfiled network tends to make more errors.
+As more patterns are memorized, Hopfield network tends to make more errors.
 This behavior will be appropriate for the simulation of Mullerian mimicry.
@@
 Palatable species have values greater than 0.5, and unpalatable species have values lower than 0.5.
-Each prey species has used two genes with values compositely representing their external appearance or phenotype.
+Each prey species have used two genes with values compositely representing their external appearance or phenotype.
 Both of these genes were constrained to values from 1 - 200.
@@
 The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}.
-The first eight bits is the rule, which is used to generate Cellular Automata pattern.
+The first eight bits represent the rule, which is used to generate Cellular Automata pattern.
 The next two bits are used to represent palatability of the organism explained detail in section \ref{sec:genetic-palatability-representation}.
@@
 It is presented to show the behavior of predator species in the simulation, in absence of any prey species.
-As it can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
+It can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
 This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
@@
 Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
-This model can also be considered as a complex adaptive system similar to Hollands work on Echo \cite{holland1996}.
-The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks are present in this model.
+This model can also be considered as a complex adaptive system similar to Holland's work on Echo \cite{holland1996}.
+The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model.

### 2011-01-16 docs/tex/abstract.tex
Title and Signature pages complete.
Chapter labels added...
Dr. Grogono's updates.

@@
+\newpage
+\phantomsection
+\label{abstract}
 \begin{center}
 
-\begin{Large}
-\textbf{Abstract}\\[0.5cm]
-\end{Large}
-
-\begin{large}
-\textbf{Modeling the Evolution of Mimicry}\\
-\end{large}
-
-\begin{small}
-\textbf{Mohiul Islam}\\
-\end{small}
+\Large \textbf{Abstract}\\[0.5cm]
+\large \textbf{Modeling the Evolution of Mimicry}\\
+\small \textbf{Mohiul Islam}\\
 
@@
 Genome of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented.
-Through evolution, successive generations of prey species have new pattern to represent them both visually and to the predators.
+Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators.
 Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry.
-They are equipped with Hopfiled Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
+They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
 Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved.

### 2011-01-16 docs/tex/result.tex
Updates to the review slides.
Dr. Grogono's updates.

@@
 With the initial configuration in the above table we can observe that multiple rings of prey population have been created.
-Two prey species are considered to be in a ring if their CA pattern have a hamming distance within 10 bits.
+Two prey species are considered to be in a ring if their CA pattern have a Hamming distance within 10 bits.
 This parameter is mentioned in table \ref{tab:ring-report-control-parameters}.
@@
 In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}.
-Also it seems from this experiment that the `Minimum Memory Configuration' being 6 is rather a large number.
+In this experiment, the value of `Minimum Memory Configuration' is 6, which is rather a large number.
 So there could be possibility of wrong recognition by Hopfield memory.
@@
 This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
-So from this analysis it can be concluded that the model under discussion has successfully simulated the evolution of Batesian mimicry.
+So from this analysis it can be concluded that the model under discussion have successfully simulated the evolution of Batesian mimicry.
 
@@
 But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
-It can be concluded that our results match with the one from Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
+It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
 
@@
 Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
-This model also proves the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.
+This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.

### 2011-01-16 docs/tex/review.tex
Dr. Grogono's updates.

@@
 \paragraph{Rechenberg(1964)}
-Rechenberg's contribution is considered mostly in providing Evolutionary Strategies.
+Rechenberg's contribution is notable mainly for providing Evolutionary Strategies.
 He invented a highly influential set of optimization method which were successfully applied to challenging problems such as aerodynamic wing design.
@@
 There are many different forms of evolutionary algorithm.
-All of which can be generalized to follow their pattern from natural selection.
+All of them can be generalized to follow their pattern from natural selection.
 The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space.
@@
 The population is the solution set of the problem over which EA will be applied.
-It is literally analogous to the same meaning in biology.
+It is used with the same meaning as in biology.
 The diversity of the population is very important.
@@
 Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
-Echo provides, a populations of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+Echo provides a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
@@
 \begin{itemize}
-	\item Simplicity is considered as the first and foremost criteria.
+	\item Simplicity is considered as the first and foremost criterion.
 Instead of emulating a real system Echo is more of a thought experiment.
@@
 Input to the environment which is considered as a stimuli or resource, can also be diversified.
-	\item Fitness of each of agent, is an evolving criteria.
+	\item Fitness of each agent, is an evolving criterion.
 Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents.
@@
 \subsubsection{Organization}
-As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resource.
+As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resources.
 Agents in Echo have freedom and flexibility to move around this environment.
@@
 \paragraph{Resources and Sites}
-Resource in a site of Echo is its very foundation.
+Resource in a site of Echo form its very foundation.
 They are represented by letters (a,b,c,d).
@@
 \paragraph{Replication}
-The replication process for agents is an asexual reproduction.
+The replication process for agents is asexual reproduction.
 An agent needs to collect sufficient resource to start the self-replication process.
@@
 The Echo model has good resemblance with natural ecosystem.
-It has stable patterns of interactions among genetic variants, or tropic networks.
+It has stable patterns of interactions among genetic variants, or trophic networks.
 It consists of different levels of resources along with relative species abundance.

### 2011-01-16 docs/tex/conclusion.tex
Updates from Radhakrisna.

@@
 If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
-As mentioned in section \ref{sec:result-conclusion} this model give us proof of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
+As mentioned in section \ref{sec:result-conclusion} this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
 Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.

### 2011-01-16 docs/tex/result.tex
Updates from Radhakrisna.

@@
 This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
-Also it can be established whether Batesian Mimicry and Mullerian Mimicry has taken effect by analyzing the data set of these populations.
+Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.
 
@@
 The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
-This test has been done with two sets of prey species with very different CA pattern and with opposite palatability and equal population.
+This test has been done with two sets of prey species with very different Cellular Automata pattern and with opposite palatability and equal population.
 To control reproduction of the prey species their age limit has been set to 100 iterations into the time the species were alive.

### 2011-01-16 docs/tex/review.tex
Updates from Radhakrisna.

@@
 The model presented in this thesis is also based on an evolutionary process existing in nature.
-This thesis is part of the field of Artificial Life, motivated by the work of Echo and other such simulated Complex Adaptive Systems.
+This thesis is part of the field of Artificial Life, motivated by the work of Echo \ref{holland1996} and other such simulated Complex Adaptive Systems.
 In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
@@
 Rechenberg's contribution is notable mainly for providing Evolutionary Strategies.
-He invented a highly influential set of optimization method which were successfully applied to challenging problems such as aerodynamic wing design.
+He invented a highly influential set of optimization methods which were successfully applied to challenging problems such as aerodynamic wing design.
 \cite{rechenberg1973}
@@
 These two operators work by dividing the parent genome at one or multiple random points and combining them to create an offspring.
-Uniform-crossover \cite{sywerda1989} is another method which works by treating each gene independently and making a random choice at to which parent it should inherit from.
+Uniform-crossover \cite{sywerda1989} is another method which works by treating each gene independently and making a random choice to which parent it should inherit from.
 Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination.
@@
 Both of the above mentioned selection procedures requires knowledge of the entire population.
-But when the population size is very large Tournament selection is an effective process.
+But when the population size is very large Tournament selection is an effective process \cite{eiben2003}.
 In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.
@@
 The algorithm itself is a very slow process.
-These sets of algorithms use non-linear chromosomes such as trees and graphs.
+These sets of algorithms use non-linear chromosomes such as trees and graphs (data structures).
 Mutation is mostly avoided for genetic programming.
@@
 \subsubsection{Criteria}
-Echo has been constructed on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
+Echo has been constructed based on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
 
@@
 As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resources.
-Agents in Echo have freedom and flexibility to move around this environment.
+Agents in Echo have freedom and flexibility to move around in this environment.
 These agents are capable of replicating themselves, while also having the capability of making complex interactions.
@@
 \paragraph{Interactions}
-Their are diverse interactions between agents consisting of combat, trading and mating.
+There are diverse interactions between agents consisting of combat, trading and mating.
 Agents need to be in the same location in site for any interaction to take place.

### 2011-01-16 docs/tex/application.tex
All results updated...
Chapter labels added...
Updates from Radhakrisna.

--- 2010-08-04 docs/tex/application.tex
@@
-\chapter{Application}
+\chapter{Future Work: Application}
+\label{chapter:application}
 
-Part of this thesis was to think about whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions.
+The goal of this thesis is to investigate whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions.
 Predator-prey co-evolution has also been used for solving interesting problems \cite{hillis1990}, giving better result than conventional methodologies.

### 2011-01-16 docs/tex/intro.tex
Thesis slides first commit
Updates from Radhakrisna.

@@
 It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
-It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts of biology, economics and physics to build complex and adaptive models to emulate nature and its life like behavior.
+It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts from biology, economics and physics to build complex and adaptive models to emulate nature and its life like behavior.
 
@@
 Inspired by the evolutionary mimetic process we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
-This model is based on a FormAL (Form Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.
+This model is based on a FormAL (Formal Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.
 

### 2011-01-16 docs/tex/model.tex
Updates from Radhakrisna.

@@
 Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string.
-The predator will be equipped with a Hopfield network, to be able to have pattern recognition capability.
+The predator will be equipped with a Hopfield network \cite{hopfield1982}, to be able to have pattern recognition capability.
 The process of evolution will of course be running at the genetic level.
@@
 \end{equation}
+Here, \(\textbf{o}\) is the output vector.
 The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning.
@@
 When the above two conditions are met, meaning the predator reaches its age for reproduction and also crosses its age interval, it randomly select another predator residing in the same cell.
-If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species in born which also resides on the same cell and initializes with zero memory configuration.
+If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species is born which also resides on the same cell and initializes with zero memory configuration.
 Similarly when the new born predator reaches its maturity of reproductive age and if it is capable of reproduction then the process iterates itself.

### 2011-01-16 docs/tex/model.tex
Acronyms

@@
 These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry.
-We represent evolution of pattern for the model and the mimic with the help of Cellular Automata(CA).
+We represent evolution of pattern for the model and the mimic with the help of \gls{ca}.
 Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string.
@@
 \section{FormAL Framework}
-The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's FormAL(Formal Artificial Life) project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
 The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}".

### 2011-01-16 docs/tex/review.tex
Acronyms

@@
 
-Contemporary terminology denotes the fields of \textbf{Evolutionary Strategy}, \textbf{Evolutionary Programming}, \textbf{Genetic Algorithm} and \textbf{Genetic Programming} to be under one umbrella termed as \textbf{Evolutionary Computation} while the algorithms are called \textbf{Evolutionary Algorithms}.
+Contemporary terminology denotes the fields of \textbf{\gls{es}}, \textbf{\gls{ep}}, \textbf{\gls{ga}} and \textbf{\gls{gp}} to be under one umbrella termed as \textbf{\gls{ec}} while the algorithms are called \textbf{\gls{ea}}.
 
@@
 
-Artificial Life (AL) has been described by Taylor, also as a tool for biological inquiry \cite{taylor1993}.
+\gls{al} has been described by Taylor, also as a tool for biological inquiry \cite{taylor1993}.
 While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
 \textsl{Wetware} artificial life systems are the most similar to natural life and indeed are actually derived from natural life.
-Most of the experiments are attempts to direct an artificial evolutionary process toward the production of ribonucleic acid (RNA) molecules with specific catalytic properties.
+Most of the experiments are attempts to direct an artificial evolutionary process toward the production of \gls{rna} molecules with specific catalytic properties.
 The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \cite{neumann1966}.
@@
 \label{subsec:complex-adaptive-system}
-Complex adaptive systems (CAS) are special cases of complex systems.
+\gls{cas} are special cases of complex systems.
 They are complex as they are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.

### 2011-01-16 docs/tex/application.tex
Some additions in application and model design.

@@
 We should be looking for a problem where the idea of deception can be useful in term of solving it.
-Unfortunately during the time of this research we were unable to find such a problem.
+An interesting analogy is with anti-virus and virus software.
+If we consider anti-virus to be predator and virus (mimic) to be prey species, then the objective of a virus would be to look like a regular virus free program (model) to get pass an anti-virus software.
+In this way if a virus can mimic a regular program then it will be able to get pass any anti-virus software available in the market.
+To successfully implement this software we need to create a virus program which can evolve itself to pretend like a regular program (virus free).
+The environment will be the operating system itself where all the programs reside.
+It is worth noting the fact that this objective is malicious for the computer industry, which makes it less significant to pursue.

### 2011-01-16 docs/tex/model.tex
Some additions in application and model design.

@@
 \subsection{Species diversity}
+\label{subsec:species-diversity}
 Franks and Noble have used different models to diversify species.
@@
 The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model.
+Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}.
+Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them.
+We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome.
+The model has its \textit{flow} as it progresses in time.
+Also there is \textit{diversity} of prey species in the environment (\ref{subsec:species-diversity}).
+
+To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \cite{holland1996}.
+He choose to use the term `Internal Model' to refer to the mechanism for anticipation.
+Predators in this model anticipate the bitter taste of prey, by making intelligent decisions for consuming them.
+This mechanism for anticipation can be considered as the property of \textit{internal model} for this specific study.

### 2011-01-16 docs/tex/result.tex
some more changes

@@
 
-By observing the graph in figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial sate of the simulation has dominated after 10000 iterations.
+By observing the graph in figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial state of the simulation has dominated after 10000 iterations.
 CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve).

### 2011-01-16 docs/tex/review.tex
some more changes

@@
 The model presented in this thesis is also based on an evolutionary process existing in nature.
-This thesis is part of the field of Artificial Life, motivated by the work of Echo \ref{holland1996} and other such simulated Complex Adaptive Systems.
+This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems.
 In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
@@
 \subsection{Evolutionary Algorithms}
-Algorithms which are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generation, can be defined as evolutionary algorithms.
+Evolutionary algorithms are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generations.
 There are many different forms of evolutionary algorithm.
@@
 Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection.
-This procedure preserves a constant selection pressure by sorting the population on the basis on fitness, and then allocating selection probabilities to individuals according to their rank.
+This procedure preserves a constant selection pressure by sorting the population on the basis of fitness, and then allocating selection probabilities to individuals according to their rank.
 Both of the above mentioned selection procedures requires knowledge of the entire population.

### 2016-02-24 docs/paper/Paper.tex
The Paper - Initial commit

\documentclass[letterpaper]{article}
\usepackage{natbib,alifeconf}
\usepackage{hyperref}
%Graphics package
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.jpg,.pdf}
%For multirow feature to draw tables
\usepackage{multirow}
%Middle allignment in tables.
\usepackage{array}
%For Mathematics
\usepackage{amsmath}
\numberwithin{equation}{section}
%Float package used to specify positioning
\usepackage{float}
%Depth of upto four in sections.
%\setcounter{secnumdepth}{3}
\usepackage{algorithmic}
\usepackage{algorithm}

\title{Modeling the Evolution of Mimicry}
\author{Mohiul Islam$^{1}$ \and Peter Grogono$^{1}$ \\
\mbox{}\\
$^1$Concordia University  \\
moh\_i@encs.concordia.ca \\
grogono@cse.concordia.ca}

\begin{document}
\maketitle

\begin{abstract}
A novel agent based, artificial life model, for the evolution of mimicry is presented. This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network. A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations. These agents are classified into categories of predator and prey species. Genome of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented. Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators. Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry. They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability. Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved. Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
\end{abstract}

%Introductory Section
\section{Introduction}
\label{section:introduction}

%A few paragraphs are required to bring an appropriate introduction.
Mimicry is a process of deception. It is an evolutionary process with the help of which organisms survive by deceiving its predator. But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable. Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.

Artificial Life is an interdisciplinary study of life and life-like processes that uses synthetic methodology. This thesis consists of such a work which concentrates specifically on the life-like process of the evolution of mimicry. The synthetic tools used for this simulation is a three dimensional graphical environment, Cellular Automata and Neural Network.

%Individual chapter descriptions begins from chapter 2
Section \ref{section:review} is intended to provide background knowledge upon which this thesis is based. It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods. It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts from biology, economics and physics to build complex and adaptive models to emulate nature and its life like behavior.

Section \ref{section:mimicry} discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis. Mimicry is an evolutionary process, which not only provides us with insight into the process of evolution as it happens in nature but also is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species. In addition, this chapter discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us explain each of these cases.

Section \ref{section:model} contains description of an agent based artificial life model, which is the primary purpose of this thesis. Inspired by the evolutionary mimetic process we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring. This model is based on a FormAL (Formal Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.

Section \ref{section:results} deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry. The results are extracted by applying different initial conditions to the model. As this work is with complex adaptive system, the data that we extract from such system is also expected to be convoluted. But our effort in this section is to come up with simplified analysis of the data to be able to comprehend complex activities in the model.

Section \ref{section:application} tries to provide direction for possible future work. The goal of this thesis was not only to come up with a model that emulate natures mimetic process but also to apply this method to solve problems in the field of computer science. This approach is similar to the way evolutionary algorithms and genetic programming help us in optimizing solutions of complicated problems.

Section \ref{section:conclusion} is an effort to bring a conclusion to justify the work done on this thesis.

\section{Review}
\label{section:review}
\subsection{Introduction}

This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life. Both of these field of computer science are inspired by the process of evolution as it happens in nature. The model presented in this thesis is also based on an evolutionary process existing in nature. This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems. In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}). Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.

\subsection{Evolutionary Computation}
The field of evolutionary computing is the collective name for a range of problem-solving techniques based on principles of biological evolution, such as natural selection and genetic inheritance.

\subsubsection{History}
\label{subsubsec:evo-comp-history}

\paragraph{Turing(1948)}
Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled \textsl{``Intelligent Machinery"} where the expression of \textsl{``genetical or evolutionary search"}  was used \cite{turing1948}. He suggested a range of ideas for systems which could be said to modify their own programs.

\paragraph{Bremermann(1962)}
Bremermann was the first to apply the concept of biological evolution to execute computer experiments for solving optimization problems \cite{bremermann1962}. He was the first to consider the problem of minimizing a real-valued fitness function. He selected very simple functions to optimize in order to provide a more tractable analysis of the evolutionary process.

\paragraph{Rechenberg(1964)}
Rechenberg's contribution is notable mainly for providing Evolutionary Strategies. He invented a highly influential set of optimization methods which were successfully applied to challenging problems such as aerodynamic wing design. \cite{rechenberg1973}

\paragraph{L. Fogel, Owens and Walsh (1965)}
A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in \textsl{``Artificial Intelligence through a simulation of evolution"} \cite{fogel1966}. In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series. Evolutionary prediction of such kind was motivated by the concept that prediction is a keystone to intelligent behavior (defined in terms of adaptive behavior, in that the intelligent organism must anticipate events in order to adapt behavior in light of a goal).

\paragraph{Holland(1975)}
Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H. Holland. His ground breaking book \textsl{``Adaptation in natural and artificial systems"} \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.

\paragraph{Koza(1992)}
Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem. Starting from a high-level statement of \textsl{``what needs to be done"} it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.

Contemporary terminology denotes the fields of \textbf{\gls{es}}, \textbf{\gls{ep}}, \textbf{\gls{ga}} and \textbf{\gls{gp}} to be under one umbrella termed as \textbf{\gls{ec}} while the algorithms are called \textbf{\gls{ea}}.

\subsubsection{Evolutionary Algorithms}
Evolutionary algorithms are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generations. There are many different forms of evolutionary algorithm. All of them can be generalized to follow their pattern from natural selection. The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space. An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment. So given a problem the algorithm initializes the environment with a random set of population or solutions. Then it uses the fitness function to select a better set of solutions from the existing ones. After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set, born from the existing ones. Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.

According to Eiben \cite{eiben2003} this process has two fundamental forces that form the basis of evolutionary systems:

\begin{itemize}
	\item \textsl{``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."}
	\item \textsl{``Selection acts as a force pushing quality."}
\end{itemize}

Important components of evolutionary algorithms are

\paragraph{Representation (Individuals or Solution Space)}
Evolutionary Algorithms(EA) are considered as robust problem solvers as it provides evenly good performance over a wide range of problems. To apply evolutionary algorithm to this wide range the most important part is representation of the solution space. In EA representation is analogous to the complex pathway that exits between \textbf{genotype} and \textbf{phenotype} of a biological organism.

\paragraph{Evaluation Function (Fitness Function)}
This is the function with which the solution is evaluated. The outcome of applying evolutionary algorithm to the problem depends on this function. It is defined to evaluate each of the solutions of the problem. In biology evaluation function is analogous to the decision of survival of any species in an environment.

\paragraph{Population}
The population is the solution set of the problem over which EA will be applied. It is used with the same meaning as in biology. The diversity of the population is very important. If the initial random population of solutions are diverse then there is more possibility of reaching an optimal solution space very quickly, and it also avoids reaching local optimum instead of the global optimum.

\paragraph{Variation operators, recombination and mutation}
Considering arity (number of object as input) variation operators are divided into two kinds. The mutation operator accepts only one operand. The process of mutation is similar to the way it happens in biology. It is a stochastic process, meaning, its output the child depends on the outcomes of a series of random choices. The operator is responsible for causing a random unbiased change. Mutation has very different roles in different fields of EC, for example in Genetic Programming it is not used at all, while in genetic algorithms it is a very pivotal process as it provides fresh blood to the existing set of solutions. Getting a new mutated child is like stepping into a new solution space outside of the ones which already exist in the parent pool. A recombination operator is responsible for merging two parent genotypes into one or two offspring genotypes. It is also a stochastic process depending on the choice of the parts of the parent individuals. Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent. According to Eiben \cite{eiben2003} \textsl{``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features."} It is important that variation operators are defined based on the representation of the problem under consideration.

\subsubsection{Genetic Algorithm}
Genetic Algorithms(GA) have the most wide set of applications. It was first conceived by John H. Holland for studying adaptive behavior as in \textit{Adaptation in natural and artificial systems} \cite{holland1975}. They are mainly considered as function optimizers. In general GA have many diverse representation schemes considering the solution set of the problem. Depending on the problem scenario an appropriate representation could be Binary, Grey Code, Integer, Real-Valued, Floating-point or Permutation based.

Using GA for a binary representation, mutation can be single point or multiple point, where a random location is selected from the binary genome and the bit is flipped. For integer representation random resetting is used instead of bit flipping. Creep mutation is another scheme which was designed for ordinal attributes and works by adding a small (positive or negative) value to each gene with a random probability. For a real-valued or floating-point mutation none of the above strategy is applicable. As for this case mutation is applied to a random gene maintaining a certain range of value within an upper and a lower bound and using a standard for randomization, such as Uniform, Gaussian or Cauchy distribution. For permutation representation, swap mutation is a strategy used by simply swapping the location of two randomly selected genes. Insert mutation is another strategy where a random gene is selected and inserted to a random location in the genome, causing the other genes to move a single space. In scramble mutation, location of a collection of randomly selected genes are scrambled, while in inversion mutation serialized location of a set of genes are inverted.

GA also have many different recombination operators for each representation. For binary and integer representation one-point crossover and \textit{N}-point-crossover are the most frequently used. These two operators work by dividing the parent genome at one or multiple random points and combining them to create an offspring. Uniform-crossover \cite{sywerda1989} is another method which works by treating each gene independently and making a random choice to which parent it should inherit from. Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination. Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome, but instead, their genomes are derived from their parent using an arithmetic formula. Permutation representation has many interesting recombination operators, out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems. Other useful operators for permutation representation are Edge crossover, Order crossover and Cycle crossover, where their name provides more or less an appropriate description of their operation.

In regards to parent selection the most commonly used process by GA is fitness proportion selection, where the selection probability of a parent depends on the absolute fitness value of the individual compared to the absolute fitness values of the rest of the population. A fitness value is evaluated from the evaluation or the fitness function. Introduced by Holland \cite{holland1975} this procedure has a few problems. Premature convergence being one where individuals that are a lot better than the rest take over the entire population. Also when fitness values are all very close, there is almost no selection pressure in evolution of the fittest. Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection. This procedure preserves a constant selection pressure by sorting the population on the basis of fitness, and then allocating selection probabilities to individuals according to their rank. Both of the above mentioned selection procedures requires knowledge of the entire population. But when the population size is very large Tournament selection is an effective process \cite{eiben2003}. In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.

Genetic Algorithms are one of the most effective strategy used in the field of evolutionary computation to solve optimization problems. Then again there are limitations. When the solution set of a problem do not have a gnomic representation, genetic algorithms cannot play any role in improving it. So the set of optimization problems to which GA can be applied is not universal.

\subsubsection{Evolutionary Strategies}
The key important property of the set of algorithms termed as ``Evolutionary Strategy" is \textbf{self-adaptation} of strategy parameters. The  parameters of Evolutionary Algorithm are included in the chromosomes and they co-evolve with the solution set while running the algorithm. To summarize these set of algorithms, they usually have real-valued vectors, their recombination process is discrete or intermediary, their mutation process uses Gaussian perturbation while parent selection is uniform random. In terms of their attribute feature they are fast and good optimizer for real-valued optimization.

\subsubsection{Evolutionary Programming}
The primary objective of evolutionary programming was to generate artificial intelligence by simulating evolution as a learning process \cite{fogel1966}. Capability of a system to adapt its behavior to meet some specified goal in the environment was considered as intelligence. Fogel used finite state machines as predictors and evolved them. Usually representation for evolutionary programming is with real-valued vectors. Its parent selection is deterministic, where each parent creates one offspring via mutation. There is no recombination operator for evolutionary programming. Mutation is applied with Gaussian perturbation. While survivor selection is probabilistic.

\subsubsection{Genetic Programming}
Genetic programming is typically applied to machine learning tasks such as prediction and classification. Its attribute feature behaves similar to neural network and usually has huge populations of solution combination. The algorithm itself is a very slow process. These sets of algorithms use non-linear chromosomes such as trees and graphs (data structures). Mutation is mostly avoided for genetic programming. Recombination operators work by exchanging subtrees. Mutation if applied will be a random changing process in the tree. Parent selection process is usually fitness proportional while the survivor selection process is usually replacement of generations. From a technical point of view, genetic programming is simply a variant of genetic algorithm working with a different data structure: the chromosomes are trees.

\subsection{Artificial Life}
Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that, in Artificial Life scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.

Christopher G. Langton is considered as one of the founders of the field of Artificial Life. He invented the term while organizing the first `\textsl{International Conference on the Synthesis and Simulation of Living Systems'} at the Los Alamos National Laboratory in 1987.

In defining Artificial Life Langton states the following,

\begin{quote}
\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."}
\end{quote}

\gls{al} has been described by Taylor, also as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level. \textsl{Wetware} artificial life systems are the most similar to natural life and indeed are actually derived from natural life. Most of the experiments are attempts to direct an artificial evolutionary process toward the production of \gls{rna} molecules with specific catalytic properties. The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \cite{neumann1966}. He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties. \textsl{Hardware systems} at the organism level can deal with an organism's sensory and nervous system, its body and its environment. Even though an organism's nervous system is usually considered as fantastically complex, the other interesting complex components can be its geometric, mechanical, dynamical or thermal properties.

\subsubsection{Complex Adaptive System}
\label{subsec:complex-adaptive-system}
\gls{cas} are special cases of complex systems. They are complex as they are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience. Examples of complex adaptive systems include the stock market, social insect and ant colonies, the biosphere and the ecosystem, the brain and the immune system, the cell and the developing embryo, manufacturing businesses and any human social group-based endeavor in a cultural and social system such as political parties or communities. This includes some large-scale online systems, such as collaborative tagging or social bookmarking systems.

The following definition of Complex Adaptive System is comprehensive.

\begin{quote}
\textsl{``A Complex Adaptive System (CAS) is a dynamic network of many agents (which may represent cells, species, individuals, firms, nations) acting in parallel, constantly acting and reacting to what the other agents are doing. The control of a CAS tends to be highly dispersed and decentralized. If there is to be any coherent behavior in the system, it has to arise from competition and cooperation among the agents themselves. The overall behavior of the system is the result of a huge number of decisions made every moment by many individual agents." - John H. Holland}
\end{quote}

Holland also provided some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:

\begin{enumerate}
	\item \textsl{``All complex adaptive system involve large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems. As because different interactions between agents are simultaneous, parallel computing is helpful in term of simulating and analyzing these systems. 
	\item \textsl{``The impact of these systems in human affairs center on the aggregate behavior, the behavior of the whole."}
	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
	\item \textsl{``Complex adaptive systems anticipate."}
\end{enumerate}

\subsubsection{Echo}
\label{subsec:echo}
Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations. Echo provides a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites. Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes. Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.

\paragraph{Criteria}
Echo has been constructed based on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.

\begin{itemize}
	\item Simplicity is considered as the first and foremost criterion. Instead of emulating a real system Echo is more of a thought experiment. Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model. 
	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting. Their mobility is also part of a wide range of geographical setting. Input to the environment which is considered as a stimuli or resource, can also be diversified.
	\item Fitness of each agent, is an evolving criterion. Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents. The fitness value, instead of being a constant should evolve along with the system. 
	\item \textsl{``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}"}. Interpretation of results from the Echo model should be direct and ready-made. As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point. So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation. Another advantage is with the help of interpretations, selected mechanisms can be shown to be sufficient to generate the phenomenon of interest. Even though simulation cannot establish that a given mechanism is actually present, but it can establish its sufficiency or plausibility.
	\item The architecture of the Echo model should be flexible enough so that other well-studied mathematical models of particular \textsl{CAS} can be incorporated whenever required. Among other models the significant ones include, Dawkins' \textsl{biological arms race} \cite{dawkins1990} and Brower's \textsl{survival of mimics} \cite{brower1988} from ecology; Wicksell's \textsl{Triangle} \cite{marimon1989} and \textsl{overlapping generation models} \cite{anderson1989} in economics; the \textsl{prisoner's dilemma game} \cite{axelrod1984} in political science; Holland's \textsl{two-Armed bandits} \cite{holland1975} in operational research and Perelson's \textsl{antigen-body matching} \cite{perelson1999} in immunology. 
	\item As mathematical analysis provides the surest route to arrive at a valid generalization point, most aspects of the Echo model should be amenable to mathematical analysis. 
\end{itemize}

In developing Echo using the above set of criterion, a step by step approach has been taken. Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997} is more from an ecological perspective and has been discussed in the following.

\paragraph{Organization}
As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resources. Agents in Echo have freedom and flexibility to move around in this environment. These agents are capable of replicating themselves, while also having the capability of making complex interactions. Interactions include combat, trading and mating.

\subparagraph{Resources and Sites}
Resource in a site of Echo form its very foundation. They are represented by letters (a,b,c,d). Everything in Echo is constructed by combining these letters as strings. These resources are treated much like an `atom' and by combining them as a molecular string, agents are constructed. Geographically, Echo is a collection of interconnected sites. Each site contains a fountain which is the source of resource for the agents in Echo. The amount of resource available in each site varies in time. A site with no resource can be compared to a `desert' while another site with increased availability of letters can be a water spring or a pond.

\subparagraph{Agents}
\textsl{``Agents have a genome that is roughly analogous to a single chromosome in an haploid species"}. An agents \textsl{tag} is an external phenotype of its respective genotype (such as color). Agents have internal conditions or rules of interaction, which are genetically represented and they encode the agents internal preferences, behavioral rules and so forth. So interactions between multiple agents occur based on their conditions (rules for interactions) and tags (appearance). This results in sophisticated interaction between agents such as deception (mimicry, bluffing) and in-transitivities. \textsl{``The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition"}. These genes are used to determine what sort of interaction between agents will take place and also the outcome of their interaction.

Agents have two ways of reproduction, one being self replication, while the other is by interaction between a pair of agents.

\subparagraph{Replication}
The replication process for agents is asexual reproduction. An agent needs to collect sufficient resource to start the self-replication process. After replication, the newly created agent receives a fraction of its parent's resource. Spontaneous mutation is applied to the gene for this process, where different mutation rate is applied to different parts of the gene.

\subparagraph{Interactions}
There are diverse interactions between agents consisting of combat, trading and mating. Agents need to be in the same location in site for any interaction to take place. Testing for which selection of interaction to take place, is always conducted in the order of combat, trade and mating.

\subparagraph{Combat}
The interaction of combat is analogous to real world antagonistic behavior, where one agent is killed resulting in the survivor agent to receive all its resource. Depending on each agent's offense and defense tag and the tag prefixes, the winner is decided. A \textsl{combat matrix} is also calculated with the genome of individual agents, which helps in calculating the winner.

\subparagraph{Trading}
When two agents are chosen to interact and they do not engage in combat, they are given the opportunity to trade and mate. Trading and mating are very much a mutual agreement between agents compared to combat, which is more of a destructive process. \textsl{``Agents A and B will trade if A's trading condition is a prefix of B's offense tag and vice versa"}. Trading takes place for excess resources between agents, where excess is defined as the amount which the agent possess above the amount required for a replication process, plus some reserves. The value of the reserve is controlled with the help of a simulation parameter. A deceptive process is introduced here while trading takes place, when an agent might not have excess resource but will still be engaged in trade, as it is not possible for the other agent to know the resource of its opposite interactor.

\subparagraph{Mating}
Only if two agents find each other suitable, they will engage in the mating process. Suitability for mating is decided on certain conditions based on the mating tag of individual agents. A form of two point crossover takes place to perform the mating action and produce diverse new agents.

\paragraph{Discussion of Results}
The Echo model has good resemblance with natural ecosystem. It has stable patterns of interactions among genetic variants, or trophic networks. It consists of different levels of resources along with relative species abundance. Even different cataclysmic events such as meteor, drought and so fourth are introduced. Also several isolation effects are observed where a number of sites are allowed to evolve independently. In addition to that Echo contains interesting flow of resources.

Two separate experiments are done with the above simulation to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo. To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature. The objective is to compare these naturally occurring ecosystems with Echo. The ecological patterns are the Preston  curve and the species-area scaling relation. This allowed comparison of Echo diversity patterns with empirical patterns of species abundance.

Preston's canonical log normal distribution is the most widely accepted formalization of the relative commonness and rarity of species. The species-area scaling relation is also an important ecological pattern. The theory of island biography is predicted on species-area relations. In conservation biology, this relation has been used to predict the effects of different reserve size, with species diversity. Although the species-area relation can be derived from Preston's canonical log-normal distribution, a satisfactory explanation of the processes that regulate this relation has not been advanced.

Now the question is, does Echo exhibit the robust ecological phenomenon of Preston curve and species area scaling relation? For Preston's curve plot, the data show, qualitatively the pattern of genome abundances in Echo population resembles the general patterns found in biological systems, although some differences are observed. But for species area curve some discrepancy was observed between the expected result and the observed values. Several factors were raised for this discrepancy. One was the choice of the simulation parameter. Second being the definition of different species in Echo as agents having different genome is considered from different species. Another factor being the balance between rates of speciation and extinction of population.

Finally to answer the above question, it has been concluded that, Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.

\subsection{Conclusion}
This chapter discusses evolutionary computation, the field that takes concepts from evolutionary biology to solve and optimize problems in compute science. It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze life as it is in nature. The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core idea of this thesis.

\section{The Inspiration: Mimicry}
\label{section:mimicry}

\subsection{History}
Henry W. Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies, after 10 years of research in the Brazilian rain forest. For the next hundred years, it simulated heated discussion among all groups of people, scientists, philosophers, theologians, teachers and amateur naturalists. Bates collected ninety-four pieces of butterfly. He grouped them according to their similar appearance. He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families. Out of the ninety four species, sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.

\subsection{Batesian Mimicry}
Even though Heliconiids are conspicuously colored, they are extremely abundant. They are also slow in mobility. Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature. Also because of this phenomenon other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.

Repulsive animals, such as heliconiids are very conspicuously colored. Having this noticeable property, they are easily recalled by predators. Their wing pattern works as a warning to predators. Once a predator has the knowledge of their inedible and unpalatable property, they would probably never attempt to try it again. As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators. Wickler \cite{wickler1986} expresses,
\begin{quote}
\textsl{``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they `act a part'. An actor is a mime, and so the representation of a false warning pattern was called \textit{mimicry}. Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."}
\end{quote}
In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.

\begin{figure}[H]
	\centering
	\includegraphics[scale=1]{images/Batesplate_ArM}
	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
	\label{fig:batesian-butterfly}
\end{figure}

\subsubsection{Definitions of Mimicry}
The following account on the definition of Mimicry is mostly extracted from Wickler's \textit{Mimicry in plants and animals} \cite{wickler1986}.

According to Wickler the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following

\begin{quote}
\textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
\end{quote}

The following more sophisticated definition was provided at the international Zoological Congress in Washington, 1963,

\begin{quote}
\textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
\end{quote}

The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}. The clauses are presented in the following:

\begin{itemize}
	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".} This increases the probability that a predator will affect both parties concerned. Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
	\item \textsl{``that the imitators are always the more defenseless".} On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
	\item \textsl{``that the imitators are always less numerous in individuals".} What is meant here is that the deceived animal should encounter the mimic less often than the model. This is true when the deceived animal must learn to recognize model and mimic and when positive and negative experiences carry equal weight. But it is known from various learning experiments that when an animal has learned about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences. Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces. When the deceptive animal possesses an innate reaction to the model, the number of mimics can be virtually unlimited. 
	\item \textsl{``that the imitators differ from the bulk of their allies".} The most remarkable cases of mimicry are those where close relatives form divergent models. It is nevertheless highly possible that groups of closely related species may be similar mimics of the same model. Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry. 
	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} This criteria, like the previous one is aimed at defining mimicry as a special adaptation. But if one of two closely related species both of which are poisonous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
\end{itemize}

According to Wickler \cite{wickler1986}, these five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed. But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.

\subsection{Mullerian Mimicry}
\label{subsec:mullerian-mimicry}
Bates was not able to explain some phenomena of mimicry. Occasionally two inedible unrelated butterfly species are amazingly similar in appearance. An explanation for this was provided by Fritz Muller in 1878. Like Bates, Muller observed and caught butterflies in Brazil. When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid. Because of predator's limited memory, all these species still lose their number even after being inedible. So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different family also tend to evolve to have similar appearance. This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.

According to Huheey \cite{huheey1988} \textsl{``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution" \cite{muller1879}.} In Muller's view, predation load on each species are reduced when their warning signals are shared or converged. Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species. For cases like these, all unpalatable species should benefit from mutual advertising. If mutation gives opportunity for a single unpalatable prey to resemble a warningly colored species, it is expected to be more likely to survive predation than if the change was in opposite direction. Predators surviving on warningly colored species need to generalize; meaning if similar patterns signal unpalatability, predators recognition rate becomes much higher. Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance provides some protection.

It is worth observing the fact that Mullerian mimicry is not deception, as it is to the predator's advantage to be able to recognize all deterrent and noxious species. Preys resemblance does not have to be close enough to cause misidentification on the part of the predator, but merely similar enough to remind it of a bitter past experience with similar prey. As Huheey continues \textsl{``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise. Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian."}

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.75]{images/BatesMimButter}
	\caption[A very well-known example of mimicry, the viceroy butterfly]{A very well-known example of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom). It was considered for a long time that this is an ideal example of Batesian mimicry. But recently Brower discovered that the viceroy is actually just as noxious as the monarch, making this a case of Mullerian mimicry. \cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
	\label{fig:mullerian-butterfly}
\end{figure}

\subsection{Evolutionary Dynamics of Mimicry}
\label{sec:evolutionary-dynamics-of-mimicry}
The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.

\paragraph{Punctuated Equilibrium}
In evolutionary biology, punctuated equilibrium is the theory which proposes that most sexually reproducing species will remain in an extended state called \textit{stasis} while experiencing little evolutionary change for most of their geological history. When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis. Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another. Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}}.

\paragraph{Phyletic Gradualism}
In contrast to punctuated equilibrium, phyletic gradualism states that species continue to adapt to new environmental and biological selection pressures over the course of their history, gradually becoming new species. Phyletic gradualism holds that a species population changes gradually; that is there is no clear line of demarcation between an ancestral species and a descendant species unless a splitting (cladogenetic) event occurs or the gradually-changing lineage is divided arbitrarily. During this process, evolution occurs at a smooth, steady and incremental (but not necessarily constant and slow) rate on a geological time scale.

On this issue Turner states,

\textsl{``According to punctuated equilibrium, therefore, evolution is not more or less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories. Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}. The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}}

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{images/Punctuated-equilibrium}
	\caption[Punctuated equilibrium vs. phyletic gradualism]{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism. Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
	\label{fig:punctuated-equilibrium}
\end{figure}

To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \cite{turner1988}, which was originated by Poulton \cite{poulton1912} and Nicholson \cite{nicholson1927}, termed as the \textbf{two stage model}. This theory states that mimicry normally arises in two steps. A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \cite{sheppard1972} \cite{ford1964}. This two-stage theory has been applied for the explanation of Mullerian mimicry as well.

\subsubsection{Mimicry Ring}
Any theory of Mullerian mimicry has to take into account the phenomenon of the coexistence of multiple mimicry rings. If we examine the local butterfly fauna in any area of the world, we will find that between all the aposomatic (warningly colored and defended) species present there are normally only a limited number of different patterns, normally far smaller than the number of species. Each cluster of species, all sharing a common pattern, is termed as Mullerian mimicry ring. Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.

\paragraph{Formation of Mimicry Rings}
In regards to the formation of mimicry ring Turner \cite{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns. Different level of variation of these two parameter can give us very different formation of mimicry ring evolution. The cases are considered below.

\begin{itemize}
	\item If we imagine two different rings of similar warning patterns in one single habitat, similar enough that the envelop of protection afforded to one gives some protection to the more extreme variant of the other (in a simplified language, suppose that predators that have sampled species A sometimes avoid the more extreme members of species B because they mistake them as A), then these two species are subject to natural protection for mutual convergence of their patterns. Eventually they will form a rather accurate Mullerian mimicry ring.
	\item By contrast, if the two species have patterns so dissimilar that predators encountering one never imagine that it might be the other (the envelop of protection do not overlap the other species' phenotype distribution), then there is no selection whatever for convergence, and the two patterns will remain distinct indefinitely.
 \item But mutations of color patterns are occurring all the time. Suppose that species B happens to produce a mutation whose pattern falls within the envelop of protection afforded to species A. The mimicry need not be perfect, but if it is good enough, the mutation will have an advantage and will spread. In this way species B may, by a single mutation, become a Mullerian mimic of species A; in other word species B may switch from one Mullerian mimicry ring to another. Clearly, if the mimicry is not perfect, the two patterns will then gradually converge, making the resemblance ever closer. 
\end{itemize}

Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage. It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.

\subsection{Conclusion}
Mimicry is one of the most fascinating cases of evolutionary biology. This phenomenon has been studied extensively as infinite number of evidence exists in nature. One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it. And this figure is more than 40 years old as it has been taken from Wilcker \cite{wickler1986}, published in 1968. It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless. Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \cite{cott1957}.

%Chapter describing the model
\section{The Model: Evolution of Mimicry}
\label{section:model}

\begin{quote}
\textsl{``Modeling, it should be clear is an art form. It depends on the experience and taste of the modeler. In this it is much like cartooning. The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" - John H. Holland \cite{holland1996}.}
\end{quote}

\subsection{Introduction}
%Entire section until past work needs to be revised when the model has been fully described.
The objective of this thesis is to design an agent based artificial life model for simulating the natural process of the evolution of mimicry.

There are mainly two species of agents. These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry. We represent evolution of pattern for the model and the mimic with the help of \gls{ca}. Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string. The predator will be equipped with a Hopfield network \cite{hopfield1982}, to be able to have pattern recognition capability. The process of evolution will of course be running at the genetic level.

The choice of Hopfield Network memory for a predator can be considered appropriate as the number of patterns which can be recognized by this network is inversely proportional to the accuracy of recall. As more patterns are memorized, Hopfield network tends to make more errors. This behavior will be appropriate for the simulation of Mullerian mimicry. Mullerian mimicry happens because of limited memory of the predators. Because of this limited memory, multiple inedible butterflies seems to converge to a single ring.

The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \cite{grogono2003}.

\subsection{Past Work}
Various models of mimicry has been simulated and explored. The model by Turner \cite{turner1996} and the mathematical model of Huheey \cite{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.

Sherratt \cite{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations. The model's predators are deterministic, in that they have a fixed behavioral strategy over their lifetime, and cannot learn from experience. For both cryptic and conspicuous prey, each predator has fixed policy of either attacking or avoiding.

The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble. Their initial work \cite{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.

On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble. Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics. So an evolutionary simulation to observe the above mentioned phenomenon has been presented in this piece of work.

Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}. Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded. In this model prey colorations are free to evolve. This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.

\subsubsection{Models by Franks and Noble}
\label{subsec:models-by-frank-and-noble}
%Explain more about the first model by Franks and Noble
The \textbf{first} model by Franks and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}. Each individual had a single gene: a value representing their external appearance or phenotype. The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors). The distance of one phenotype from another represents their levels of similarity.

A single abstract predator was modeled with a simple reinforcement learning system. The predator's experience of each phenotype was represented by a score, which would be maintained by probability to consume the next prey species depending on similarity or difference in phenotype.

The existence of mimetic effect were measured with the initial and final distances between prey species' phenotypes. Three experiments were noted. Firstly, with one palatable and one unpalatable species. For this Batesian mimicry was evolved. For the second experiment, with two unpalatable species, Mullerian mimicry was evolved if the two prey species have some initial resemblance. Experiment 3 was carried out with two unpalatable and one palatable species, where the phenotype of the palatable species moved towards that of one of the unpalatable species, which is in other words Batesian Mimicry.

The \textbf{second} model by Franks and Noble \cite{franks2003} is based on two working hypothesis:

\begin{enumerate}
	\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
	\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
\end{enumerate}

Although there are many mathematical and stochastic models of mimicry in the biological literature, this model gives attention to the evolution of mimicry ring phenomenon from an artificial life perspective.

%\subsubsection{Model Description}
\paragraph{Prey}
Similar to the first model this also contains a population of prey species each having an appearance and palatability level. Different species of prey were each assigned a fixed palatability level on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable. Palatable species have values greater than 0.5, and unpalatable species have values lower than 0.5. Each prey species have used two genes with values compositely representing their external appearance or phenotype. Both of these genes were constrained to values from 1 - 200. The Euclidean distance of one phenotype from another represented their level of similarity.

\paragraph{Predator}
Similar to Turner's stochastic model \cite{turner_et_al1984},  predators were modeled with a Monte Carlo reinforcement learning system. The predator's experience of each phenotype was represented by an attack probability, which was initialized to ambivalence at 0.5. After eating prey of a particular phenotype, the predator would make a post-attack update of the relevant probability according to the palatability of the prey consumed. The predator would use its experience of different prey appearances to help it decide on whether or not to attack at the next opportunity.

In contrary to the stochastic model \cite{turner_et_al1984},  predators would generalize on the basis of experience. A set of probability formula was used to come up with the current probability to consume a prey species based on its palatability and the previous probability of consumption based on experience using generalization rate and the Euclidean distance between the experienced phenotype and the consumed prey phenotype.

%Explain the results for the second model by Franks and Noble
\paragraph{Results}
According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established. There was existence of multiple mimicry rings of very different frequency (population). Second experiment was carried out with some palatable species along with the unpalatable ones which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out. It can be observed that,

\begin{quote}
\textsl{``The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species. Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them." \cite{franks2003}}
\end{quote}

\subsection{FormAL Framework}
The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry. The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}". While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}". We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.

\subsubsection{Agents}
In FormAL, an \textbf{Agent} is a simulated organism. It is designed simply, but with the following qualities:

\begin{itemize}
	\item It has behaviors to be able to reproduce itself using genetic information.
	\item Capable of modifying the structure of genome between generations.
	\item Able to interact with other agents.
	\item And also to survive and reproduce in a challenging environment.
\end{itemize}

\subsubsection{Spatial representation of the environment}
The framework consists of a three dimensional visual environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.

\paragraph{Space}
The space of the environment is a three-dimensional lattice of discrete points. The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\). \(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in table \ref{tab:environment-control-parameters}).

\paragraph{Time}
Time, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.

\paragraph{Cell}
The entire three dimensional toroidal environment is divided in multiple cells. A cell is a three dimensional cubical section of the hyperspace. Accordingly in table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment. The size of a cell is evaluated from the entire world size. And the total number of cell is calculated as \(ISize^3 = 216\).

\begin{table}[H]
\centering
\begin{tabular}{| p{2.2cm} | >{\centering} p{3cm} | p{7.5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
		World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
		Cell Size & \( World Size / ISize \) & Size of each cell\\ \hline
		Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
	\hline
\end{tabular}
\caption{Parameters to control the environment.}
\label{tab:environment-control-parameters}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{cc}
		\multicolumn{2}{c}{ \includegraphics[scale=0.60]{images/cells-front} } \\
		\includegraphics[scale=0.50]{images/cells-top} & \includegraphics[scale=0.50]{images/cells-side} \\
\end{tabular}
\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
\label{tab:3-d-environment-images}
\end{table}

\subsubsection{Mobility}
An agent's position is calculated once during each step of update in time. The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components. The \(force\) component is calculated from agent's mobility gene. And it is used to compute agent's \(acceleration\). If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion. Otherwise, Newton's law is used to obtain the \(acceleration\), which is integrated to obtain the new \(velocity\) and new \(position\).

\begin{algorithm}
	\caption{Algorithm for updating movement of the Agents}
	\label{algo:algorithm-movement-agents}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $accelaration \gets ForceFactor * force - Friction * velocity$
			\STATE $velocity \gets DT*accelaration$ \COMMENT{DT is considered as Differential Time Set}
			\STATE $deltaPos \gets DT*velocity$
			\STATE $position \gets position + deltaPos$
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{table}[H]
\centering
\begin{tabular}{| p{2.2cm} | >{\centering} p{1.3cm} | p{9cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
		Friction & 5 & The friction constant used for motion calculations.\\ \hline
		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
	\hline
\end{tabular}
\caption{Parameters to control mobility of agents.}
\label{tab:mobility-control-parameters}
\end{table}

Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.

\subsection{The Prey: Mimics and Models}

\subsubsection{Pattern representation by Cellular Automata}
Only the significant characteristics which are required for a successful model of mimicry is implemented. As for this simulation we are considering heliconius butterfly, the representation of their wing pattern is with the help of cellular automata. So basically every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.

%More content needs to be added for cellular automata.
\paragraph{Cellular Automata}

Cellular automata are computer generated patterns applying very simple rules. First invented by Jon von Neuman and later extended by Stephen Wolfram, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules. We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.

\begin{figure}[H]
	\centering
	\includegraphics[scale=5]{images/CA_rule30s}
	\caption[Cellular Automata]{Cellular Automata Rule 30.
	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
	\label{fig:cellular-automata-rule-30}
\end{figure}

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
	  \hline
	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
	  \hline
	\end{tabular}
	\caption{Cellular Automata rule}
	\label{tab:cellular-automata-rule}
\end{table}

In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'. As figure \ref{fig:cellular-automata-rule-30} is a rule 30 cellular automata, the eight bit binary representation of 30 would be the genetic representation for this pattern. Generation of automata pattern from this binary string can be considered analogous to the complex pathway between the genotype and the phenotype that exists in all living organism.

\subsubsection{Species diversity}
\label{subsec:species-diversity}
Franks and Noble have used different models to diversify species. In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

To use CA as prey pattern, an agent's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255. Each of this 256 values have a unique CA pattern associated with it. When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.

With CA based pattern representation, population of prey species with a specific CA pattern can be grouped as one single species. And by restricting inter species reproduction we can control the diversity of patterns. But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species. So that is why we have two separate mutation rate while reproducing prey species. One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}). Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsec:echo} \cite{hraber1997}.

\subsubsection{Genome}
The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}. The first eight bits represent the rule, which is used to generate Cellular Automata pattern. The next two bits are used to represent palatability of the organism explained detail in section \ref{sec:genetic-palatability-representation}. The next six bits is the magnitude of the force with which mobility of the organism is calculated. The 17th bit is used to evaluate reproduction capability of the organism, depending on which the prey species is either capable or not capable to participate in reproduction.

\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
	\hline
		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
\label{tab:prey-genome}
\end{table}

\subsubsection{Reflection of punctuated equilibrium}
\label{subsec:reflection-of-punctuated-equilibrium}
Punctuated equilibrium has been defined in section \ref{sec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism. Also Turner \cite{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism. The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry. As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene. Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation. The mutations that are favored, helps the mimics to survive while the unfavored ones fail to persist. It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene.

\subsubsection{Genetic representation of palatability}
\label{sec:genetic-palatability-representation}
The palatability of each prey species is fixed and has been represented with 2 bits of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|}
		\hline
			\textbf{Gene (Index 8 to 9)} &	\textbf{Palatable} \\ \hline
			00									& True 			\\ \hline
			01									& True 			\\ \hline
			10									& False 		\\ \hline
			11									& False 		\\
		\hline
	\end{tabular}
	\caption{Genetic representation of palatability}
	\label{tab:genetic-representation-palatability}
\end{table}

This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.

\subsubsection{Interaction between other Prey and Predators}
The prey have been defined to have many conglomerate behavior in the environment. Prey interaction with other prey species and with predators make the evolution of mimicry possible. Mobility of prey species and their reproduction capability are two important behaviors which result from interaction.

\paragraph{Mobility}
The mobility genes of the prey consist of 6 bits. These six bits are used to calculate the force with which each prey try to move towards any neighborhood cell. The algorithm sorts all neighboring cell descending to the number of prey species. Then it selects the cell which contains the highest number of prey with zero predator. If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least. Algorithm \ref{algo:algorithm-movement-prey} explains in detail.

\begin{algorithm}[H]
	\caption{Algorithm for updating position of the Prey species}
	\label{algo:algorithm-movement-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
			\STATE Get list of neighborhood cells, sorted by population of prey species.
			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\paragraph{Reproduction}
Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}. If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it. Now the other prey also needs to be genetically capable of reproduction and needs to reach its age limit. A new genome is created from the existing genome of the two prey by applying single point crossover operation. Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in table \ref{tab:prey-control-parameters}. So there is two point mutation for the genome.

\begin{algorithm}[H]
	\caption{Algorithm for reproduction of the Prey species}
	\label{algo:algorithm-reproduction-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $capableToReproduce \gets$ true or false depending on the 17th bit of the genome, and maturity on reproduction age.
			\IF {$capableToReproduce == true$ and $currentCellPopulation > 1$ } 
				\STATE $anotherPrey \gets$ Select random prey from same cell.
				\IF {$anotherPrey$ is alive and $capableToReproduce$ and of similar $pattern$ and $palatability$}
					\STATE Perform genetic cross over and mutation to create new genome.
					\STATE Create new prey with new genome, and release into environment.
					\STATE Record reproduction time for both prey.
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{table}[H]
\centering
\begin{tabular}{| p{2.2cm} | >{\centering} p{1.5cm} | p{9cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
	\hline
\end{tabular}
\caption{Parameters to control prey population and visibility.}
\label{tab:prey-control-parameters}
\end{table}

\subsection{Predator}

Predators in the system are designed to provide selection pressure to \textit{models} and \textit{mimics} for the evolution of mimicry. Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction. In addition to it, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species. Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network. So every new predator species gets to born with zero memory and with no inheritance from parents. A set of parameters are defined to control predators' population and learning ability in the environment. Details of these parameters are given in table \ref{tab:predator-control-parameters}.

\subsubsection{Learning}
The objective of a predator's interaction with prey is always to consume it. But based on the prey's pattern and palatability, the predator will either be able to consume it or throw it back to the environment. At this event the predator needs to learn the pattern with which the prey has been represented. The pattern represents palatability of the prey species, at least to the predator. To store this new pattern into memory, each predator is equipped with a Hopfield Network Memory. Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one. The learning procedure used for this memory is Hebbian Learning.

\paragraph{Hebbian Learning}
\textit{Hebb's postulate of learning} is the oldest and most famous of all learning rules; it is named in honor of the neuropsychologist Donald Hebb(1949). Hebb's book \textit{The Organization of Behavior} \cite{hebb1949} states the following:

\begin{quote}
\textsl{``When an axon of cell A is near enough to excite a cell B and repeatedly or persistently takes part in firing it, some growth process or metabolic changes take place in one or both cells such that A's efficiency as one of the cells firing B is increased."}
\end{quote}

The following \textit{general learning rule} is adopted in neural network studies: \textit{The weight vector} \( \textbf{w}_i = [w_{i1} \> w_{i2} \> ... \> w_{in}]^t \) \textit{increases in proportion to the product of input} \textbf{x} \textit{and learning signal r}. The learning signal r is in general a function of \(\textbf{w}_i,\textbf{x}\), and sometimes of the teacher's signal \(d_i\). Thus we have, 
\begin{equation}
	r = r(\textbf{w}_i,\textbf{x},d_i)
%\label{eq:}
\end{equation}
The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
\begin{equation}
	\Delta\textbf{w}_i(t)=cr[\textbf{w}_i(t),\textbf{x}(t),d_i(t)]\textbf{x}(t)
%\label{eq:}
\end{equation}
when c is a positive number called the \textit{learning constant} that determines the rate of learning.

For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
\begin{equation}
	r \overset{\Delta}{=} f(\textbf{w}_i^t \textbf{x})
%\label{eq:}
\end{equation}
The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
\begin{equation}
	\Delta\textbf{w}_i = cf(\textbf{w}_i^t \textbf{x})\textbf{x}
%\label{eq:}
\end{equation}
The single weight \( w_{ij} \) is adapted using the following increment:
\begin{equation}
	\Delta\textit{w}_{ij} = cf(\textbf{w}_i^t \textbf{x})x_j
%\label{eq:}
\end{equation}
This can be written briefly as 
\begin{equation}
	\Delta\textit{w}_{ij} = c o_i x_j, \> \text{for} \> j = 1, 2, ..., n
%\label{eq:}
\end{equation}
Here, \(\textbf{o}\) is the output vector. The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning. The Hebbian learning rule represents a purely feed-forward, unsupervised learning. The rule implements the interpretation of the classic \textit{Hebb's postulate of learning} stated above.

The rule states that if the cross product of output and input, or correlation term \(o_ix_j\) is positive, this results in an increase of weight \(w_{ij}\); otherwise the weight decreases. It can be seen that the output is strengthened in turn for each input presented. Therefore, frequent input patterns will have most influence at the neuron's weight vector and will eventually produce the largest output.

Training for Hopfield Network used for predator's memory is done by Hebbian Learning. Initially the weights are all set to zero. Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern. As Hopfield is a feedback network, the output of the network is also the input. The outer vector matrix of all the patterns are summed to come up with the final weight matrix. Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
\begin{equation}
w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
%\label{eq:}
\end{equation}
\[
w_{ij} = 0, i = j
\]
where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.

\subsubsection{Design of Memory with Hopfield Network}

\paragraph{Hopfield Network}

Algorithm for the Hopfield model is described in the following:

\begin{enumerate}
	\item \textit{Learning.} Let \( \boldsymbol{\xi}_1, \boldsymbol{\xi}_2, ..., \boldsymbol{\xi}_{\mu} \) denote a known set of N-dimensional fundamental memories. Use the outer-product rule (i.e. Hebb's postulate of learning) to compute the synaptic weights of the network as 
	\begin{equation}
		w_{ji} =
			\begin{cases}
				\frac{1}{N} \sum_{\mu=1}^{M}\xi_{\mu,j}\xi_{\mu,i}	& j \neq i \\
				0																										& j = i 
			\end{cases}
	%\label{eq:}
	\end{equation}
	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\). The elements of the vector \( \boldsymbol{\xi}_\mu \) equal \(\pm 1\) (bipolar). Once they are computed, the synaptic weights are kept fixed.

	\item \textit{Initialization.} Let \( \boldsymbol{\xi}_{probe} \) denote an unknown N-dimensional input vector (probe) presented to the network. The algorithm is initialized by setting
	\begin{equation}
		x_j(0) = \xi_{j,probe}, \> j = 1,...,N
	%\label{eq:}
	\end{equation}
	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).

	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
	\begin{equation}
		x_j(n+1)=sgn \Bigg(\sum_{i=1}^{N} w_{ji}x_i(n) \Bigg), \> j = 1,2, ..., N
	%\label{eq:}
	\end{equation}
	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.

	\item \textit{Outputting.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
	\begin{equation}
		\boldsymbol{y} = \boldsymbol{x}_{fixed}
	\label{eq:}
	\end{equation}
	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
\end{enumerate}

%This section needs to use similar variables as mentioned in the above section on Hopfield Network.
\paragraph{Input to memory}
Each prey contains an evolving cellular automata which is represented by a binary genome. This two dimensional pattern is serialized to be available as a one dimensional binary array, which is taken as input for any predator organism trying to interact with the prey. This binary representation of the pattern gets converted to a bipolar representation. Each input pattern consists of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension). The \textit{m} by \textit{n} pattern configuration will be serialized by putting all row vectors in one single row sequentially.

\paragraph{Predator attack algorithm}
As soon as a predator reaches its attack age it selects random prey species around its vicinity and starts attacking them. This attack process also involves recognition of prey pattern, which is at the heart of mimicry simulation for this research. Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive. The ``Hopfield Minimum Memory Size" (default value in table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species. After a predator is born, it start attacking prey without any caution. But after every attack the predator will store its pattern and palatability level inside its memory. As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next species. It will try to recognize the pattern and if found palatable, prey will be consumed. Otherwise prey will be thrown back into the environment. If the pattern is not recognized predator will try to consume it and in the process will store its palatability and pattern into memory.

In this way the predator memory is limited to \textsl{``Hopfield Maximum Memory Size"}. After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored. Algorithm \ref{algo:algorithm-attack-prey} and \ref{algo:algorithm-attemptToKill} explains the process in every detail.

\begin{algorithm}
	\caption{Algorithm for attacking Prey species}
	\label{algo:algorithm-attack-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\IF {Predator has reached Minimum attack age}
				\STATE $preyToAttack \gets$ select random prey species from the same cell.
				\IF {$currentMemorySize < MinimumMemorySize$}
					\STATE $attemptToKill(preyToAttack);$ \COMMENT {Function defined in algorithm \ref{algo:algorithm-attemptToKill}}
				\ELSE
					\STATE recognize $preyToAttack$ pattern from memory.
					\IF {prey is not recognized or prey is palatable}
						\STATE $attemptToKill(preyToAttack)$
					\ELSE 
						\STATE Prey is recognized as unpalatable, so release it back into environment.
					\ENDIF
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{algorithm}
	\caption{$attemptToKill(preyToAttack)$}
	\label{algo:algorithm-attemptToKill}
	\begin{algorithmic}
		\STATE Kill $preyToAttack$.
		\IF {Memory size $< MaxMemorySize$}
			\STATE Associate $preyToAttack$ pattern and palatability and store into memory.
			\STATE Recalculate Hopfield Memory Weights using Hebbian Learning outer product rule.
		\ENDIF
	\end{algorithmic}	
\end{algorithm}

\subsubsection{Genome}
Each predator has a 5 bits genome as explained in table \ref{tab:predator-genome}. The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment. The last bit controls reproduction capability of each species.

\begin{table}[H]
\centering
\begin{tabular}{|c|c|}
	\hline
		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
				 1101					   &					1						 		\\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
\label{tab:predator-genome}
\end{table}

\subsubsection{Mobility and reproduction capability}
Movement behavior of a predator is calculated from its genome. The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of prey present within its neighborhood. So magnitude of movement of a predator varies within a range of 0-15 units. If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells. A predator chooses the neighborhood cell which contains the least number of predators. When the neighborhood contains zero predators, it would select any one of them randomly and move towards that cell.

\begin{algorithm}[h]
	\caption{Algorithm for updating position of the Predator species}
	\label{algo:algorithm-movement-predator}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $forceMagnitude \gets convertToDecimal(genome[0-3])$
			\STATE Get list of sorted neighborhood cells. Sorted by population of prey species.
			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.60]{images/predators-40}
	\caption[A population of predators]{A population of 40 predators distributed over the environment.}
	\label{fig:predators-40}
\end{figure}

The screen shot in figure \ref{fig:predators-40} is from the simulation with only 40 predator species. It is presented to show the behavior of predator species in the simulation, in absence of any prey species. It can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species. This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.

\subsubsection{Reproduction process}
The  fifth gene of the predator is used to represent their capability of reproduction.  Depending on its binary value a predator in the simulation will or will not be able to reproduce. The reproduction process for predators is similar to prey species. As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability takes effect in the reproductive process from one generation to another.

There are two control parameters that effect the reproduction of predator species. The first is \textsl{``Reproduction Age Limit"}. This is the minimum age a predator has to reach before starting to involve itself for reproduction. This parameter has been set to 500 iterations during the result and analysis section of the thesis. The second parameter is \textsl{``Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species. This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment. Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.

\begin{algorithm}[H]
	\caption{Algorithm for reproduction of the Predator species}
	\label{algo:algorithm-reproduction-predator}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $capableToReproduce \gets$ true or false depending on the 5th bit of the genome, and maturity on reproduction age.
			\IF {$capableToReproduce == true$ and $currentCellPopulationOfPredators > 1$ } 
				\STATE $anotherPredator \gets$ Select random predator from same cell.
				\IF {$anotherPredator$ is alive and $capableToReproduce$ and also reached reproduction maturity age}
					\STATE Perform genetic cross over and mutation to create new genome.
					\STATE Create new predator with new genome and zero memory, and release into environment.
					\STATE Record reproduction time for both predators.
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

When the above two conditions are met, meaning the predator reaches its age for reproduction and also crosses its age interval, it randomly select another predator residing in the same cell. If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species is born which also resides on the same cell and initializes with zero memory configuration. Similarly when the new born predator reaches its maturity of reproductive age and if it is capable of reproduction then the process iterates itself.

\begin{table}[h!]
\centering
\begin{tabular}{| p{2.2cm} | >{\centering} p{2.2cm} | p{8cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern. Usually the network reaches a steady state before that. But this restriction is to avoid infinite loop in case the network never reaches a steady state. \\ \hline
		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
	\hline
\end{tabular}
\caption{Parameters to control predator population and pattern recognition capability.}
\label{tab:predator-control-parameters}
\end{table}

\subsection{Conclusion}
This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \cite{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model. Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}. Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them. We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome. The model has its \textit{flow} as it progresses in time. Also there is \textit{diversity} of prey species in the environment (\ref{subsec:species-diversity}).

To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \cite{holland1996}. He choose to use the term `Internal Model' to refer to the mechanism for anticipation. Predators in this model anticipate the bitter taste of prey, by making intelligent decisions for consuming them. This mechanism for anticipation can be considered as the property of \textit{internal model} for this specific study.

\section{The Results}
\label{section:results}

\subsection{Introduction}
It is always a challenge to extract and analyze data from an Artificial Life simulation. Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place. This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species. Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.

\subsection{Mimicry Ring Reports}
The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability. Data is stored at every instance of time of the simulation keeping an interval of 10 iterations. As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot. Parameters are mentioned in table \ref{tab:ring-report-control-parameters}.

\begin{table}[H]
\centering
\begin{tabular}{| p{2cm} | >{\centering} p{2.2cm} | p{8cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
	\hline
\end{tabular}
\caption{Parameters to mimicry ring report.}
\label{tab:ring-report-control-parameters}
\end{table}

\subsection{Initial configuration with two prey species}
\label{sec:init-conf-2prey}
% Put the table here
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
  					 									& \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation. This test has been done with two sets of prey species with very different Cellular Automata pattern and with opposite palatability and equal population. To control reproduction of the prey species their age limit has been set to 100 iterations into the time the species were alive. And the reproduction interval was set to 1000 iterations.

Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation. The genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents. As mentioned earlier the genome mutation rate has been separated from the pattern mutation rate to bring more control to the number of mimicry rings generated.

Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500. But in the later experiments predator demise age has been increased to 5000 iterations. Predators in this simulation generate selection pressure for the evolution of mimicry. So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid. But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.

Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation. The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die accept their natural cause of death, that is to reach their demise age. So predator population can explode very easily. That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.

The memory configuration size for predators is a very interesting parameter. The minimum memory size is directly associated with the number of prey species with which we initiate the simulation. Otherwise evolution of mimicry is not observed. As mentioned in table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species. After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment. At this point its memory size is zero. As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank. No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species. When catching a prey if its memory tells that it is palatable, it will consume that prey. Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.

Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory. So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern currently captured and the patterns stored in memory.

% Put the image
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure}

The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations. With the initial configuration in the above table we can observe that multiple rings of prey population have been created. Two prey species are considered to be in a ring if their CA pattern have a Hamming distance within 10 bits. This parameter is mentioned in table \ref{tab:ring-report-control-parameters}. Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve. Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population. The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime5k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
	\label{fig:plot-2-prey-5k}
\end{figure}

The plot of figure \ref{fig:plot-2-prey-5k} is from the same experiment as of figure \ref{fig:plot-2-prey}, but only up to 5000 iterations. By closely observing the graph of figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches the maturity for consuming prey species (effect of the parameter `Minimum Attack Age' from table \ref{tab:config-table-2-prey}). At around time 1000 the prey population starts reproducing as the population increases (controlled by `Reproduction Age Limit' from table \ref{tab:config-table-2-prey}). At the same time different other species of prey gets to be born with mutated CA patterns. There is a straight drop of prey population at time 2000, when all the prey species with which the simulation was initialized come to its demise age (controlled by `Prey Demise Age' at table \ref{tab:config-table-2-prey}). Over time the population of CA Rule 30 dominates the population (figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable. Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.). CA Rule 110 was initialized as a set of palatable species.

We can observe from the above result that the evolution of mimicry has taken effect. A population of mimics were successfully able to exceed the population of other prey species, and the reason being, avoidance by predators of prey pattern similar to unpalatable ones. We can conclude that Batesian mimicry has taken effect in the simulation.

%Put the number of rings picture:
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

Observing from figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations. A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented. For example if we take a look at the set of pattern genotype with very different phenotype in table \ref{tab:diff-in-pattern}.

%CARule table
\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|}
  \hline
  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule60}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule61}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule62}}\\
  \hline
\end{tabular}
\caption{Difference in prey pattern genotype and phenotype}
\label{tab:diff-in-pattern}
\end{table}

All the patterns in table \ref{tab:diff-in-pattern} have a genetic bit difference of 1. So by a single mutation there can be three different set of phenotype for a child organism from its parent. This is largely the reason for the increased number of mimicry rings created in the simulation. Only the 8 most populous rings are presented in the graphs with population verses simulation time.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey-generated-prey}
\end{figure}

Figure \ref{fig:plot-2-prey-generated-prey} is the same experimental data of figure \ref{fig:plot-2-prey} but with only the newly generated ring of prey species. The initialized dominant population of CA rule 110 and 30, both palatable and unpalatable has been eliminated from this graph to observe the newly created rings. In this plot, among the population of new patterns the unpalatable ones dominate (CA Rule 14, 26, 94). Also the palatable counterpart of the unpalatable population is increasing their number. Species with \textsl{un-mimicked} palatable pattern is very few in number.

The screen shot in figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation. The red agents are predators while the black agents with different textured patterns are the prey species. According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.

%Screenshot of the simulation
\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime7600-2-prey}
	\includegraphics[scale=0.55]{images/simTime7600}
	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
\end{figure}

\subsection{Initial configuration with four prey species}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species}
\label{tab:config-table-4-prey}
\end{table}

This run of the simulation has been initialized with four prey species with very different CA pattern configuration. The predator reproduction interval has been increased to 1400, while the minimum memory size has been increased to 4 instead of 2 as the predator is expected to memorize four different species of prey before starting to make intelligent decision about consuming them. The rest of the parameters remain the same as from the experiment in section \ref{sec:init-conf-2prey}.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
	\label{fig:plot-4-prey}
\end{figure}

By observing the graph in figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial state of the simulation has dominated after 10000 iterations. CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve). Also the palatable prey species with similar patterns to CA rule 55 and 110 are taking full advantage of their deceiving pattern and increasing their population (represented with line curve). The two palatable set of patterns CA Rule 190 and 30 are unable to dominate the population. Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in figure \ref{fig:ringSize10k-4Prey}. The total number of rings reached somewhere near 37 while most of them have comparatively low representative population. Batesian mimicry is in full effect in this simulated environment.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
	\label{fig:ringSize10k-4Prey}
\end{figure}

\begin{figure}[H]
	\centering
	\label{fig:screenshot-simTime11K-4Prey}
	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
	\caption[Graphical representation of the model (simulation time: 11200)]{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
\end{figure}

\subsection{Increased initial population with four prey species}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species with increased population}
\label{tab:config-table-4-more-prey}
\end{table}

In this run of the simulation some significant parameters have been updated. First one is the initial population of prey species. It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600. Secondly, predator population has been increased from 10 to 20. Thirdly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500. Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45]{images/simTime10K-4MorePrey}
	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:plot-4-more-prey}
\end{figure}

Some very interesting diversity of mimicry rings can be observed in the simulation for updating these parameters. The unpalatable rings and their deceptive counterparts (palatable prey with similar pattern) still have their dominance. We can observe CA Rule 55 and 190 are the highest in number of population. Interestingly enough CA Rule 30 and 110 which started as palatable prey species has also taken dominance in the simulation, following 55 and 190. The unpalatable counter part of CA Rule 30 and 110 are also following the palatable population.

The total number of rings have increased much in this run compared to the previous one. To summarize the results of this experiment, we can observe, increased diversity of prey population and much more interaction between predator and prey.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/ringSize10k-4MorePrey}
	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:ringSize10k-4MorePrey}
\end{figure}

\subsection{Initial population with six prey species}
\label{sec:init-conf-6-prey}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}} 
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule57}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 6 prey species.}
\label{tab:config-table-6-prey}
\end{table}

To evaluate the simulation at a more complex level we increase the prey population to 900, consisting of 6 different species with very different pattern configuration. To boost predator-prey interaction we also increase the number of predator population to 30. Predator reproduction interval has been set comparatively lower in this simulation to 2000 iterations. As the initial population of prey species is very high, over time we are expecting even larger number of prey species. If predator population does not increase at similar rate there might be a prey population explosion were predator will have no effect on providing selection pressure for the evolution of mimicry. So that is why predator population control parameter has been set to this level. For memory configuration, the minimum number is set to 6, meaning the predator will have to store 6 different prey pattern configuration before starting to make intelligent decision about consuming them. As previously mentioned this number is always set in accordance with the initial number of different prey configuration.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45]{images/simTime10k-6Prey}
	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
	\label{fig:plot-6-prey}
\end{figure}

With the above set of parameters we receive the plot of figure \ref{fig:plot-6-prey}. An enormous diversity of species can be observed from this experiment. In addition to the six prey species with which the simulation starts, the total number of mimicry rings reach nearly 50. Observing the top 8 as presented in the plot of figure \ref{fig:plot-6-prey}, effects of Batesian mimicry is obvious. Unpalatable CA Rule 190 and 30 dominates the population. Similarly unpalatable CA Rule 105 is also dominant. But after 10000 iterations CA Rule 55 seems to have higher population than 105 even though 55 is a \textsl{palatable} set of species. This anomaly could be the reason for storing large number of patterns in the predator Hopfiled memory. As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate. In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}. In this experiment, the value of `Minimum Memory Configuration' is 6, which is rather a large number. So there could be possibility of wrong recognition by Hopfield memory. Then again this phenomenon is common if we consider behavior of predators in nature. It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{sec:mullerian-mimicry}.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
	\label{fig:ringSize10k-6-Prey}
\end{figure}

\subsection{Initial configuration with only unpalatable species}
\label{sec:init-conf-only-unp}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all unpalatable.}
\label{tab:config-table-4-prey-unpalatable}
\end{table}

To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species. After finding different anomalous behavior of predator recognition capability in section \ref{sec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four. As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species. Rest of the parameters remain quite unchanged.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45]{images/simTime8k-4Prey-unp}
	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure}

The results according to figure \ref{fig:plot-4-prey-unp} are much expected. The population of unpalatable species have prevailed. After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed with the most population. All of their palatable counter parts are also increasing their population deceiving the predators. We observe the effect of the simulation up to 8000 iterations instead of 10000 as the total number of prey species increases at an enormous rate in this simulation within very short period of time. As most of the species are unpalatable, predators mostly do not get the opportunity to consume, causing a much lower prey death rate.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-unp}
	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:ringSize10k-4-Prey-unp}
\end{figure}

This experiment is an ideal scenario for observing Mullerian mimicry. As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population. From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium. But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them. By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we get the following plot.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45]{images/simTime6k-4Prey-unp-1-mem}
	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable. Minimum Memory size reduced to one.}
	\label{fig:plot-4-prey-unp-1-mem}
\end{figure}

Running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring. As it can be observed in figure \ref{fig:plot-4-prey-unp-1-mem} all four unpalatable prey population have a very dominant presence in the simulation. Even though predator minimum memory has been reduced to only one pattern, different population of predators become familiar with different prey patterns, which results in the existence of multiple Mullerian mimicry ring instead of a single one.

\subsection{Initial configuration with only palatable species}
\label{sec:init-only-palatable-species}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all palatable.}
\label{tab:config-table-4-prey-palatable}
\end{table}

The parameters for this simulation has been set exactly the same as in table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point. All predator configuration has also been set to exactly same as before.

The results for the configuration in table \ref{tab:config-table-4-prey-palatable} can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations. By analyzing details we can see, around simulation time 500 all population of species come to a steady downfall as at this point initial predator species reach its' age for consumption. Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction. At iteration time 2000 there is a sudden drop of prey population because the initial population of prey have reached its demise age at this point. By this time the population of unpalatable species mutated from the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey come to its demise. Predator population, from the beginning of the simulation has taken a very dominant effect. As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keep increasing in a geometric rate.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-4Prey-p}
	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4Prey-p}
	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

Observation of mimicry rings also tell us about the results we have seen in the plot of figure \ref{fig:plot-4-prey-p}. The number of rings keep increasing but comes to a sudden drop around simulation time 7000 and goes to zero.

\subsection{Initial configuration with single prey species}
Until now all experiments have been initialized with multiple prey species. The following set of experiments have been initialized with only a single prey species, for both cases of unpalatable and palatable.

\subsubsection{Unpalatable}
\label{subsec:single-prey-unpalatable}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species unpalatable.}
\label{tab:config-table-1-prey-unpalatable}
\end{table}

This configuration has only one unpalatable species, one in each of the 216 cells, equally distributed all over the environment. Also have a set of 10 predators. Their minimum memory configuration has been set to 2 as any value below 2 will not help the Hopfield Network Memory to differentiate between two patterns.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime8k-1Prey-unp}
	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:plot-1-prey-unp}
\end{figure}

From figure \ref{fig:plot-1-prey-unp}, it can be observed, the initial set of unpalatable species is dominant as expected. The palatable population mimicking that set is following it. A bunch of other rings with majority of unpalatable species have been reproduced through mutation. Mainly because the initial population started with a bunch of unpalatable species, so their reproduced generation have similar behavior as well.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:ringSize8k-1-Prey-unp}
\end{figure}

\subsubsection{Palatable}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species palatable.}
\label{tab:config-table-1-prey-palatable}
\end{table}

This configuration is set exactly as according to section \ref{subsec:single-prey-unpalatable} but with a single set of palatable species. The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of section \ref{sec:init-only-palatable-species}.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.45]{images/simTime10k-1Prey-p}
	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
	\label{fig:plot-1-prey-p}
\end{figure}

From the initial palatable population we see a bunch of palatable rings created. Major difference from section \ref{subsec:single-prey-unpalatable} is the total number of prey population created. For the unpalatable species in section \ref{subsec:single-prey-unpalatable}, total prey population reach above 12 thousand. But for palatable species total population reach nearly above 5000 prey species, as when the preys are palatable there is more consumption from predators.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-1Prey-p}
	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
	\label{fig:ringSize8k-1-Prey-p}
\end{figure}

\subsection{Analysis of Batesian Mimicry}
\label{sec:result-batesian-mimicry}
For all possible initial conditions, Batesian mimicry has taken effect. It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart. Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{sec:init-only-palatable-species}). This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction. So from this analysis it can be concluded that the model under discussion have successfully simulated the evolution of Batesian mimicry.

\subsection{Analysis of Mullerian Mimicry}
\label{sec:result-mullerian-mimicry}
Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}. For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance. The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four. So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern. But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings. It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.

\subsection{Conclusion}
\label{sec:result-conclusion}
Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry. In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings. Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population. This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.

\section{Future Work: Application}
\label{section:application}

The goal of this thesis is to investigate whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions. Predator-prey co-evolution has also been used for solving interesting problems \cite{hillis1990}, giving better result than conventional methodologies.

The biggest challenge faced while searching for the appropriate problem to be optimized is the idea of associating palatability with CA pattern with which the prey species has been represented. If we consider the CA pattern to be a certain solution to a problem then the set of 2D CA pattern among which the prey species vary could be considered as the solution set of the problem. And if we consider that the predator species are responsible for selecting the appropriate pattern based on their palatability, then we can consider palatability as the criteria for selection of the pattern (or the evaluation/fitness function for the case of Evolutionary Programming/Genetic Algorithm). If the predator associates the CA pattern with palatability then it does not make any sense of having a mimic in the solution space as mimics will have the same pattern with opposite palatability. So using the evolution of mimicry to solve an optimization problem is futile if we try conventional problems which already can be solved with the help of evolutionary programming or genetic algorithm.

So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods. We should be looking for a problem where the idea of deception can be useful in term of solving it. An interesting analogy is with anti-virus and virus software. If we consider anti-virus to be predator and virus (mimic) to be prey species, then the objective of a virus would be to look like a regular virus free program (model) to get pass an anti-virus software. In this way by mimicking a regular program a virus can get pass any anti-virus software available in the market. To successfully implement this software we need to create a virus program which can evolve itself to pretend like a regular program (virus free). The environment will be the operating system itself where all the programs reside. It is worth noting the fact that this objective is malicious for the computer industry, which makes it less significant to pursue.

\section{Conclusion}
\label{section:conclusion}
If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature. As mentioned in section \ref{sec:result-conclusion} this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium. Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.

If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry. From the sections of \ref{sec:result-batesian-mimicry} and \ref{sec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.

But considering Artificial Life as a subject where we essentially learn from nature, its behaviors, and use that knowledge to find better solution to existing problems in the field of computer science then this thesis has not been completely successful. We have not been able to find the appropriate problem solving scenario for which the natural process of mimicry can be applied.

Humans came to understand the concept of biological evolution and its significance when it was first proposed by Charles Darwin in 1859 in his book \textsl{On the Origin of Species} \cite{darwin1859}. Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsec:evo-comp-history}). Eventually in 1975 John Holland was able to make the most applicable use of the process of evolution to solve problems in computer science by his invention of Genetic Algorithms. The time for this invention was appropriate as the field of computer science was in its burgeoning state. Over the next couple of decades computers became one of most useful and important machinery in human history. Genetic Algorithms became popular as well because of increased capability of computers in term of speed and complexity.

Even though we do not have any problem solving application for the evolutionary process of mimicry at this point, it does not imply that this study will not be useful in the future to give us solution to an important problem in computer science or any other field for that matter. The simulation presented in this thesis, itself, consists of building blocks of knowledge such as Hopfield Network and Cellular Automata. Maybe to use mimicry to solve a problem, other diverse building blocks are necessary which has not yet been invented.

The objective of any research is to look for \textsl{unexplored} territory to find new \textsl{knowledge}, \textsl{understanding} or \textsl{explanation}. From the research presented in this thesis we certainly get new \textsl{understanding} of the capability of computer science to emulate natures behavior. We also get to \textsl{explore} a new model for the evolutionary process of  mimicry. In addition to that, the model provides us with better \textsl{explanation} and \textsl{understanding} of nature, while enforcing some existing \textsl{knowledge} with greater support (section \ref{sec:result-mullerian-mimicry}).

\bibliographystyle{apalike}
\bibliography{references}

\end{document}

### 2016-02-24 docs/paper/Paper.tex
Refactored image references

@@
 \usepackage{natbib,alifeconf}
-\usepackage{hyperref}
 %Graphics package
@@
 
+%Reformat current date and time
+\usepackage{datetime}
+
+%For hyper referencing
+\usepackage[pdfborder={text},colorlinks={true},linkcolor={black},citecolor={black},urlcolor={black}]{hyperref}
+%In case you use the package hyperref to create a PDF, the links to tables or figures will point to the caption of the table or figure, which is always below the table or figure itself.
+Therefore the table or figure will not be visible, if it is above the pointer and one has to scroll up in order to see it.
+If you want the link point to the top of the image you can use the package hypcap with:
+\usepackage[all]{hypcap}
+
+\usepackage[acronym]{glossaries}
+\makeglossaries
+\input{acronym}
+
 \title{Modeling the Evolution of Mimicry}
@@
 This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems.
-In addition to the model discussed in chapter \ref{chapter:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{chapter:application}).
+In addition to the model discussed in chapter \ref{section:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{section:application}).
 Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.
@@
 	\centering
-	\includegraphics[scale=1]{images/Batesplate_ArM}
+	\includegraphics[scale=1]{../tex/images/Batesplate_ArM}
 	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
@@
 	\centering
-	\includegraphics[scale=0.75]{images/BatesMimButter}
+	\includegraphics[scale=0.75]{../tex/images/BatesMimButter}
 	\caption[A very well-known example of mimicry, the viceroy butterfly]{A very well-known example of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom).
@@
 	\centering
-	\includegraphics[scale=0.5]{images/Punctuated-equilibrium}
+	\includegraphics[scale=0.5]{../tex/images/Punctuated-equilibrium}
 	\caption[Punctuated equilibrium vs.
@@
 \begin{tabular}{cc}
-		\multicolumn{2}{c}{ \includegraphics[scale=0.60]{images/cells-front} } \\
-		\includegraphics[scale=0.50]{images/cells-top} & \includegraphics[scale=0.50]{images/cells-side} \\
+		\multicolumn{2}{c}{ \includegraphics[scale=0.60]{../tex/images/cells-front} } \\
+		\includegraphics[scale=0.50]{../tex/images/cells-top} & \includegraphics[scale=0.50]{../tex/images/cells-side} \\
 \end{tabular}
@@
 	\centering
-	\includegraphics[scale=5]{images/CA_rule30s}
+	\includegraphics[scale=5]{../tex/images/CA_rule30s}
 	\caption[Cellular Automata]{Cellular Automata Rule 30.
@@
 	\centering
-	\includegraphics[scale=0.60]{images/predators-40}
+	\includegraphics[scale=0.60]{../tex/images/predators-40}
 	\caption[A population of predators]{A population of 40 predators distributed over the environment.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
   														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
+  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
   					 									& \multicolumn{2}{c|}{}\\ \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-2Prey}
+	\includegraphics[scale=0.40]{../tex/images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime5k-2Prey}
+	\includegraphics[scale=0.40]{../tex/images/simTime5k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-2Prey}
+	\includegraphics[scale=0.50]{../tex/images/ringSize10k-2Prey}
 	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule60}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule61}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule62}}\\
+  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
   \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
+	\includegraphics[scale=0.40]{../tex/images/simTime10k-2Prey-generated-prey}
 	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
@@
 	\label{fig:screenshot-simTime7600-2-prey}
-	\includegraphics[scale=0.55]{images/simTime7600}
+	\includegraphics[scale=0.55]{../tex/images/simTime7600}
 	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
   																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}
+  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}
   					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}
+  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}
   					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}
+  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}
   					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-4Prey}
+	\includegraphics[scale=0.40]{../tex/images/simTime10k-4Prey}
 	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-4Prey}
+	\includegraphics[scale=0.50]{../tex/images/ringSize10k-4Prey}
 	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
@@
 	\label{fig:screenshot-simTime11K-4Prey}
-	\includegraphics[scale=0.55]{images/simTime11K-4Prey}
+	\includegraphics[scale=0.55]{../tex/images/simTime11K-4Prey}
 	\caption[Graphical representation of the model (simulation time: 11200)]{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
+  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
 	\centering
-	\includegraphics[scale=0.45]{images/simTime10K-4MorePrey}
+	\includegraphics[scale=0.45]{../tex/images/simTime10K-4MorePrey}
 	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
@@
 	\centering
-	\includegraphics[scale=0.40]{images/ringSize10k-4MorePrey}
+	\includegraphics[scale=0.40]{../tex/images/ringSize10k-4MorePrey}
 	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}} 
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}} 
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule57}}    
+  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule57}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
 	\centering
-	\includegraphics[scale=0.45]{images/simTime10k-6Prey}
+	\includegraphics[scale=0.45]{../tex/images/simTime10k-6Prey}
 	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-6Prey}
+	\includegraphics[scale=0.50]{../tex/images/ringSize10k-6Prey}
 	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
 	\centering
-	\includegraphics[scale=0.45]{images/simTime8k-4Prey-unp}
+	\includegraphics[scale=0.45]{../tex/images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-unp}
+	\includegraphics[scale=0.50]{../tex/images/ringSize8k-4Prey-unp}
 	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.45]{images/simTime6k-4Prey-unp-1-mem}
+	\includegraphics[scale=0.45]{../tex/images/simTime6k-4Prey-unp-1-mem}
 	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
+  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
+  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime10k-4Prey-p}
+	\includegraphics[scale=0.40]{../tex/images/simTime10k-4Prey-p}
 	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-4Prey-p}
+	\includegraphics[scale=0.50]{../tex/images/ringSize10k-4Prey-p}
 	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
+  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
   																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{images/simTime8k-1Prey-unp}
+	\includegraphics[scale=0.40]{../tex/images/simTime8k-1Prey-unp}
 	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-unp}
+	\includegraphics[scale=0.50]{../tex/images/ringSize8k-1Prey-unp}
 	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
@@
    														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
+  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
   																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
@@
 	\centering
-	\includegraphics[scale=0.45]{images/simTime10k-1Prey-p}
+	\includegraphics[scale=0.45]{../tex/images/simTime10k-1Prey-p}
 	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{images/ringSize10k-1Prey-p}
+	\includegraphics[scale=0.50]{../tex/images/ringSize10k-1Prey-p}
 	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
@@
 
+\printglossaries
+\phantomsection \label{acronyms}
+
 \end{document}

### 2016-02-24 docs/paper/Paper.tex
Revert "More formtting"
This reverts commit a11fb7808ed8b619a9306377c9ad2917659f5e55.

@@
 
-%Reformat current date and time
-\usepackage{datetime}
-
 %For hyper referencing
-\usepackage[pdfborder={text},colorlinks={true},linkcolor={black},citecolor={black},urlcolor={black}]{hyperref}
+\usepackage[colorlinks={true},linkcolor={black},citecolor={black},urlcolor={black}]{hyperref}
 %In case you use the package hyperref to create a PDF, the links to tables or figures will point to the caption of the table or figure, which is always below the table or figure itself.
@@
 Mimicry is an evolutionary process, which not only provides us with insight into the process of evolution as it happens in nature but also is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
-In addition, this chapter discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us explain each of these cases.
+In addition, this section discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us explain each of these cases.
 
@@
 
-This chapter contains a discussion on the field of Evolutionary Computing and Artificial Life.
+This section contains a discussion on the field of Evolutionary Computing and Artificial Life.
 Both of these field of computer science are inspired by the process of evolution as it happens in nature.
@@
 This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems.
-In addition to the model discussed in chapter \ref{section:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (chapter \ref{section:application}).
+In addition to the model discussed in section \ref{section:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (section \ref{section:application}).
 Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.
@@
 \subsubsection{Complex Adaptive System}
-\label{subsec:complex-adaptive-system}
+\label{subsubsec:complex-adaptive-system}
 \gls{cas} are special cases of complex systems.
@@
 \subsubsection{Echo}
-\label{subsec:echo}
+\label{subsubsec:echo}
 Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
@@
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
-Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsec:complex-adaptive-system}.
+Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsubsec:complex-adaptive-system}.
 
@@
 \subsection{Conclusion}
-This chapter discusses evolutionary computation, the field that takes concepts from evolutionary biology to solve and optimize problems in compute science.
+This section discusses evolutionary computation, the field that takes concepts from evolutionary biology to solve and optimize problems in compute science.
 It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze life as it is in nature.
-The discussion of this chapter is expected to provide a base upon which the following chapters will begin construction of the core idea of this thesis.
+The discussion of this section is expected to provide a base upon which the following sections will begin construction of the core idea of this thesis.
 
@@
 	\centering
-	\includegraphics[scale=1]{../tex/images/Batesplate_ArM}
+	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
 	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
@@
 \subsection{Evolutionary Dynamics of Mimicry}
-\label{sec:evolutionary-dynamics-of-mimicry}
+\label{subsec:evolutionary-dynamics-of-mimicry}
 The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
@@
 \subsubsection{Models by Franks and Noble}
-\label{subsec:models-by-frank-and-noble}
+\label{subsubsec:models-by-frank-and-noble}
 %Explain more about the first model by Franks and Noble
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{3cm} | p{7.5cm} |}
+\begin{table}[h]
+\centering
+\begin{tabular}{| p{1.5cm} | >{\centering} p{1.6cm} | p{4cm} |}
 	\hline
@@
 		World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
-		Cell Size & \( World Size / ISize \) & Size of each cell\\ \hline
+		Cell Size & \( World Size\) / \(ISize \) & Size of each cell\\ \hline
 		Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{cc}
-		\multicolumn{2}{c}{ \includegraphics[scale=0.60]{../tex/images/cells-front} } \\
-		\includegraphics[scale=0.50]{../tex/images/cells-top} & \includegraphics[scale=0.50]{../tex/images/cells-side} \\
-\end{tabular}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../tex/images/cells-front}
 	\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
 	\label{tab:3-d-environment-images}
-\end{table}
+\end{figure}
 
@@
 \centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{1.3cm} | p{9cm} |}
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
 	\hline
@@
 	\centering
-	\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
+	\setlength\tabcolsep{2pt}
+	\begin{tabular}{| p{2.2cm} | c | c | c | c | c | c | c | c |}
 	  \hline
@@
 \subsubsection{Species diversity}
-\label{subsec:species-diversity}
+\label{subsubsec:species-diversity}
 Franks and Noble have used different models to diversify species.
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsec:echo} \cite{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsubsec:echo} \cite{hraber1997}.
 
@@
 The first eight bits represent the rule, which is used to generate Cellular Automata pattern.
-The next two bits are used to represent palatability of the organism explained detail in section \ref{sec:genetic-palatability-representation}.
+The next two bits are used to represent palatability of the organism explained detail in section \ref{subsubsec:genetic-palatability-representation}.
 The next six bits is the magnitude of the force with which mobility of the organism is calculated.
@@
 \centering
+\setlength\tabcolsep{2pt}
 \begin{tabular}{|c|c|c|c|}
@@
 \subsubsection{Reflection of punctuated equilibrium}
-\label{subsec:reflection-of-punctuated-equilibrium}
-Punctuated equilibrium has been defined in section \ref{sec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism.
+\label{subsubsec:reflection-of-punctuated-equilibrium}
+Punctuated equilibrium has been defined in section \ref{subsec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism.
 Also Turner \cite{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
@@
 \subsubsection{Genetic representation of palatability}
-\label{sec:genetic-palatability-representation}
+\label{subsubsec:genetic-palatability-representation}
 The palatability of each prey species is fixed and has been represented with 2 bits of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
 
-\begin{table}[H]
+\begin{table}[h]
 	\centering
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[h]
 	\caption{Algorithm for reproduction of the Prey species}
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{1.5cm} | p{9cm} |}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1cm} | p{5cm} |}
 	\hline
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
 	\caption{Algorithm for attacking Prey species}
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
 	\caption{$attemptToKill(preyToAttack)$}
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \centering
@@
 \centering
-\begin{tabular}{| p{2.2cm} | >{\centering} p{2.2cm} | p{8cm} |}
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
 	\hline
@@
 The model has its \textit{flow} as it progresses in time.
-Also there is \textit{diversity} of prey species in the environment (\ref{subsec:species-diversity}).
+Also there is \textit{diversity} of prey species in the environment (\ref{subsubsec:species-diversity}).
 
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{| p{2cm} | >{\centering} p{2.2cm} | p{8cm} |}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
 	\hline
@@
 \subsection{Initial configuration with two prey species}
-\label{sec:init-conf-2prey}
+\label{subsec:init-conf-2prey}
 % Put the table here
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime10k-2Prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime5k-2Prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
@@
 	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize10k-2Prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
 	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
@@
 %CARule table
-\begin{table}[H]
+\begin{table}[h]
 \centering
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime10k-2Prey-generated-prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey-generated-prey}
 	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
@@
 %Screenshot of the simulation
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
 	\label{fig:screenshot-simTime7600-2-prey}
-	\includegraphics[scale=0.55]{../tex/images/simTime7600}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime7600}
 	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
@@
 \subsection{Initial configuration with four prey species}
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 The predator reproduction interval has been increased to 1400, while the minimum memory size has been increased to 4 instead of 2 as the predator is expected to memorize four different species of prey before starting to make intelligent decision about consuming them.
-The rest of the parameters remain the same as from the experiment in section \ref{sec:init-conf-2prey}.
+The rest of the parameters remain the same as from the experiment in section \ref{subsec:init-conf-2prey}.
 
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime10k-4Prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey}
 	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize10k-4Prey}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey}
 	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
@@
 
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
 	\centering
-	\includegraphics[scale=0.45]{../tex/images/simTime10K-4MorePrey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10K-4MorePrey}
 	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/ringSize10k-4MorePrey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4MorePrey}
 	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
@@
 \subsection{Initial population with six prey species}
-\label{sec:init-conf-6-prey}
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\label{subsec:init-conf-6-prey}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
+  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	\centering
-	\includegraphics[scale=0.45]{../tex/images/simTime10k-6Prey}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-6Prey}
 	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
@@
 Then again this phenomenon is common if we consider behavior of predators in nature.
-It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{sec:mullerian-mimicry}.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize10k-6Prey}
+It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{subsec:mullerian-mimicry}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-6Prey}
 	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
@@
 \subsection{Initial configuration with only unpalatable species}
-\label{sec:init-conf-only-unp}
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\label{subsec:init-conf-only-unp}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
 To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species.
-After finding different anomalous behavior of predator recognition capability in section \ref{sec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
+After finding different anomalous behavior of predator recognition capability in section \ref{subsec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
 As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species.
@@
 	\centering
-	\includegraphics[scale=0.45]{../tex/images/simTime8k-4Prey-unp}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize8k-4Prey-unp}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-4Prey-unp}
 	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 This experiment is an ideal scenario for observing Mullerian mimicry.
-As mentioned in section \ref{sec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
-From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
+As mentioned in section \ref{subsec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
+From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
@@
 	\centering
-	\includegraphics[scale=0.45]{../tex/images/simTime6k-4Prey-unp-1-mem}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime6k-4Prey-unp-1-mem}
 	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.
@@
 \subsection{Initial configuration with only palatable species}
-\label{sec:init-only-palatable-species}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\label{subsec:init-only-palatable-species}
+
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime10k-4Prey-p}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey-p}
 	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize10k-4Prey-p}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey-p}
 	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
@@
 \subsubsection{Unpalatable}
-\label{subsec:single-prey-unpalatable}
-
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\label{subsubsec:single-prey-unpalatable}
+
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
 	\centering
-	\includegraphics[scale=0.40]{../tex/images/simTime8k-1Prey-unp}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-1Prey-unp}
 	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
@@
 	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize8k-1Prey-unp}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-1Prey-unp}
 	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
@@
 \subsubsection{Palatable}
-\begin{table}[H]
-\centering
-\begin{tabular}{|l|l|c|c|l|c|}
+\begin{table}[h]
+\centering
+\setlength\tabcolsep{2pt}
+\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
 
-This configuration is set exactly as according to section \ref{subsec:single-prey-unpalatable} but with a single set of palatable species.
-The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of section \ref{sec:init-only-palatable-species}.
+This configuration is set exactly as according to section \ref{subsubsec:single-prey-unpalatable} but with a single set of palatable species.
+The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of section \ref{subsec:init-only-palatable-species}.
 
@@
 	\centering
-	\includegraphics[scale=0.45]{../tex/images/simTime10k-1Prey-p}
+	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-1Prey-p}
 	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
@@
 From the initial palatable population we see a bunch of palatable rings created.
-Major difference from section \ref{subsec:single-prey-unpalatable} is the total number of prey population created.
-For the unpalatable species in section \ref{subsec:single-prey-unpalatable}, total prey population reach above 12 thousand.
+Major difference from section \ref{subsubsec:single-prey-unpalatable} is the total number of prey population created.
+For the unpalatable species in section \ref{subsubsec:single-prey-unpalatable}, total prey population reach above 12 thousand.
 But for palatable species total population reach nearly above 5000 prey species, as when the preys are palatable there is more consumption from predators.
@@
 	\centering
-	\includegraphics[scale=0.50]{../tex/images/ringSize10k-1Prey-p}
+	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-1Prey-p}
 	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
@@
 \subsection{Analysis of Batesian Mimicry}
-\label{sec:result-batesian-mimicry}
+\label{subsec:result-batesian-mimicry}
 For all possible initial conditions, Batesian mimicry has taken effect.
 It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
-Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{sec:init-only-palatable-species}).
+Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{subsec:init-only-palatable-species}).
 This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
@@
 \subsection{Analysis of Mullerian Mimicry}
-\label{sec:result-mullerian-mimicry}
-Effects of Mullerian mimicry can be observed best for the experiment in section \ref{sec:init-conf-only-unp}.
+\label{subsec:result-mullerian-mimicry}
+Effects of Mullerian mimicry can be observed best for the experiment in section \ref{subsec:init-conf-only-unp}.
 For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
@@
 But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
-It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
+It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsubsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
 
 \subsection{Conclusion}
-\label{sec:result-conclusion}
+\label{subsec:result-conclusion}
 Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
@@
 Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
-This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.
+This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsubsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.
 
@@
 If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
-As mentioned in section \ref{sec:result-conclusion} this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
+As mentioned in section \ref{subsec:result-conclusion} this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
 Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
@@
 If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry.
-From the sections of \ref{sec:result-batesian-mimicry} and \ref{sec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
+From the sections of \ref{subsec:result-batesian-mimicry} and \ref{subsec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
 
@@
 Humans came to understand the concept of biological evolution and its significance when it was first proposed by Charles Darwin in 1859 in his book \textsl{On the Origin of Species} \cite{darwin1859}.
-Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsec:evo-comp-history}).
+Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsubsec:evo-comp-history}).
 Eventually in 1975 John Holland was able to make the most applicable use of the process of evolution to solve problems in computer science by his invention of Genetic Algorithms.
@@
 We also get to \textsl{explore} a new model for the evolutionary process of  mimicry.
-In addition to that, the model provides us with better \textsl{explanation} and \textsl{understanding} of nature, while enforcing some existing \textsl{knowledge} with greater support (section \ref{sec:result-mullerian-mimicry}).
+In addition to that, the model provides us with better \textsl{explanation} and \textsl{understanding} of nature, while enforcing some existing \textsl{knowledge} with greater support (section \ref{subsec:result-mullerian-mimicry}).
 

### 2016-02-24 docs/paper/Paper.tex
Revert "Revert "More formtting""
This reverts commit 2cc5e3dd1f6627b38d8fa264cd300954f0530773.

@@
 
-\begin{table}[H]
+\begin{table}[h]
 	\centering
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[h]
 	\caption{Algorithm for updating position of the Prey species}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[h]
 	\caption{Algorithm for reproduction of the Predator species}
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
@@
 % Put the image
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
@@
 %Put the number of rings picture:
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
@@
 \centering
+\setlength\tabcolsep{2pt}
 \begin{tabular}{|l|c|c|c|}
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
   Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 

### 2016-02-24 docs/paper/Paper.tex
Formatting update

@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
+   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
   Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 

### 2016-02-25 docs/paper/Paper.tex
Removing unnecessaries

@@
 
-Artificial Life is an interdisciplinary study of life and life-like processes that uses synthetic methodology.
-This thesis consists of such a work which concentrates specifically on the life-like process of the evolution of mimicry.
-The synthetic tools used for this simulation is a three dimensional graphical environment, Cellular Automata and Neural Network.
-
-%Individual chapter descriptions begins from chapter 2
-Section \ref{section:review} is intended to provide background knowledge upon which this thesis is based.
-It reviews different fields of science where the concept of evolution has been applied to solve complex computer science problems, and achieved better result than other conventional methods.
-It also discusses the field of Artificial Life which is an inter disciplinary field of science where scientist take concepts from biology, economics and physics to build complex and adaptive models to emulate nature and its life like behavior.
-
-Section \ref{section:mimicry} discusses an inspiration from the field of evolutionary biology which is the primary purpose of building the model of this thesis.
-Mimicry is an evolutionary process, which not only provides us with insight into the process of evolution as it happens in nature but also is fascinating to study and learn how nature adapts itself in complicated situation for the survival of its species.
-In addition, this section discusses the different kinds of mimicry such as Batesian and Mullerian, while including how the concept of mimicry ring helps us explain each of these cases.
-
-Section \ref{section:model} contains description of an agent based artificial life model, which is the primary purpose of this thesis.
-Inspired by the evolutionary mimetic process we present a model whose purpose is not only to emulate the evolution of mimicry but also to come up with complicated scenario of Batesian and Mullerian mimicry with the help of mimicry ring.
-This model is based on a FormAL (Formal Artificial Life) framework which is similar to Holland's Echo model but with a slightly different approach.
-
-Section \ref{section:results} deals with the results extracted from the model and its analysis to evaluate successful emulation of mimicry.
-The results are extracted by applying different initial conditions to the model.
-As this work is with complex adaptive system, the data that we extract from such system is also expected to be convoluted.
-But our effort in this section is to come up with simplified analysis of the data to be able to comprehend complex activities in the model.
-
-Section \ref{section:application} tries to provide direction for possible future work.
-The goal of this thesis was not only to come up with a model that emulate natures mimetic process but also to apply this method to solve problems in the field of computer science.
-This approach is similar to the way evolutionary algorithms and genetic programming help us in optimizing solutions of complicated problems.
-
-Section \ref{section:conclusion} is an effort to bring a conclusion to justify the work done on this thesis.
-
-\section{Review}
-\label{section:review}
-\subsection{Introduction}
-
-This section contains a discussion on the field of Evolutionary Computing and Artificial Life.
-Both of these field of computer science are inspired by the process of evolution as it happens in nature.
-The model presented in this thesis is also based on an evolutionary process existing in nature.
-This thesis is part of the field of Artificial Life, motivated by the work of Echo \cite{holland1996} and other such simulated Complex Adaptive Systems.
-In addition to the model discussed in section \ref{section:model}, this thesis also put some effort in finding application for the evolutionary process of mimicry (section \ref{section:application}).
-Similar to evolutionary computation, we intend to apply the deceptive process to solve a problem in computer science.
-
-\subsection{Evolutionary Computation}
-The field of evolutionary computing is the collective name for a range of problem-solving techniques based on principles of biological evolution, such as natural selection and genetic inheritance.
-
-\subsubsection{History}
-\label{subsubsec:evo-comp-history}
-
-\paragraph{Turing(1948)}
-Ideas for evolutionary computation initiated from Alan Turing from his 1948 report titled \textsl{``Intelligent Machinery"} where the expression of \textsl{``genetical or evolutionary search"}  was used \cite{turing1948}.
-He suggested a range of ideas for systems which could be said to modify their own programs.
-
-\paragraph{Bremermann(1962)}
-Bremermann was the first to apply the concept of biological evolution to execute computer experiments for solving optimization problems \cite{bremermann1962}.
-He was the first to consider the problem of minimizing a real-valued fitness function.
-He selected very simple functions to optimize in order to provide a more tractable analysis of the evolutionary process.
-
-\paragraph{Rechenberg(1964)}
-Rechenberg's contribution is notable mainly for providing Evolutionary Strategies.
-He invented a highly influential set of optimization methods which were successfully applied to challenging problems such as aerodynamic wing design.
-\cite{rechenberg1973}
-
-\paragraph{L. Fogel, Owens and Walsh (1965)}
-A seminal work that merged the fields of evolutionary computation and computational intelligence was by Fogel, Owens and Walsh in \textsl{``Artificial Intelligence through a simulation of evolution"} \cite{fogel1966}.
-In this book, evolutionary process was applied to finite state automata to predict symbol strings generated from Markov processes and non-stationary time series.
-Evolutionary prediction of such kind was motivated by the concept that prediction is a keystone to intelligent behavior (defined in terms of adaptive behavior, in that the intelligent organism must anticipate events in order to adapt behavior in light of a goal).
-
-\paragraph{Holland(1975)}
-Perhaps the most significant work in terms of applications in the field of evolutionary computation comes from the inventor of genetic algorithms, John H.
-Holland.
-His ground breaking book \textsl{``Adaptation in natural and artificial systems"} \cite{holland1975} is where he developed \textit{The Schema Theorem} which is the foundation for explanation of the power of Genetic Algorithms.
-
-\paragraph{Koza(1992)}
-Koza's invention is the idea of Genetic Programming, which is an automated method for creating a working computer program from a high level statement of a problem.
-Starting from a high-level statement of \textsl{``what needs to be done"} it searches through all possible permutation of steps and finds the optimum solution through evolutionary methods \cite{koza1992}.
-
-Contemporary terminology denotes the fields of \textbf{\gls{es}}, \textbf{\gls{ep}}, \textbf{\gls{ga}} and \textbf{\gls{gp}} to be under one umbrella termed as \textbf{\gls{ec}} while the algorithms are called \textbf{\gls{ea}}.
-
-\subsubsection{Evolutionary Algorithms}
-Evolutionary algorithms are inspired by the strategy of \textit{survival of the fittest} from evolutionary biology, and uses different methods to optimize mathematical expressions which are used to evaluate a pool of population of solutions over generations.
-There are many different forms of evolutionary algorithm.
-All of them can be generalized to follow their pattern from natural selection.
-The mathematical expression, also termed as \textbf{fitness function} is used to evaluate the fitness of each individual from the set of existing solution space.
-An individual or a solution which provides higher output from the fitness function is considered as more fit to survive in the environment.
-So given a problem the algorithm initializes the environment with a random set of population or solutions.
-Then it uses the fitness function to select a better set of solutions from the existing ones.
-After that different operators of \textbf{mutation} and \textbf{recombination} are applied to the selected set of solution to come up with a new generation of solution set, born from the existing ones.
-Again the fitness function is applied to the current set of population to come up with a better set and this process iterates until the evaluation from the fitness function is satisfactory to give the best set of solutions.
-
-According to Eiben \cite{eiben2003} this process has two fundamental forces that form the basis of evolutionary systems:
-
-\begin{itemize}
-	\item \textsl{``Variation operators (recombination and mutation) creates the necessary diversity and thereby facilitate novelty."}
-	\item \textsl{``Selection acts as a force pushing quality."}
-\end{itemize}
-
-Important components of evolutionary algorithms are
-
-\paragraph{Representation (Individuals or Solution Space)}
-Evolutionary Algorithms(EA) are considered as robust problem solvers as it provides evenly good performance over a wide range of problems.
-To apply evolutionary algorithm to this wide range the most important part is representation of the solution space.
-In EA representation is analogous to the complex pathway that exits between \textbf{genotype} and \textbf{phenotype} of a biological organism.
-
-\paragraph{Evaluation Function (Fitness Function)}
-This is the function with which the solution is evaluated.
-The outcome of applying evolutionary algorithm to the problem depends on this function.
-It is defined to evaluate each of the solutions of the problem.
-In biology evaluation function is analogous to the decision of survival of any species in an environment.
-
-\paragraph{Population}
-The population is the solution set of the problem over which EA will be applied.
-It is used with the same meaning as in biology.
-The diversity of the population is very important.
-If the initial random population of solutions are diverse then there is more possibility of reaching an optimal solution space very quickly, and it also avoids reaching local optimum instead of the global optimum.
-
-\paragraph{Variation operators, recombination and mutation}
-Considering arity (number of object as input) variation operators are divided into two kinds.
-The mutation operator accepts only one operand.
-The process of mutation is similar to the way it happens in biology.
-It is a stochastic process, meaning, its output the child depends on the outcomes of a series of random choices.
-The operator is responsible for causing a random unbiased change.
-Mutation has very different roles in different fields of EC, for example in Genetic Programming it is not used at all, while in genetic algorithms it is a very pivotal process as it provides fresh blood to the existing set of solutions.
-Getting a new mutated child is like stepping into a new solution space outside of the ones which already exist in the parent pool.
-A recombination operator is responsible for merging two parent genotypes into one or two offspring genotypes.
-It is also a stochastic process depending on the choice of the parts of the parent individuals.
-Recombination operators with high arity (using more than two parent) are mathematically possible and easy to implement but does not have any biological equivalent.
-According to Eiben \cite{eiben2003} \textsl{``the principle behind recombination is simple - by mating two individuals with different but desirable features, we can produce an offspring that combines both of those features."} It is important that variation operators are defined based on the representation of the problem under consideration.
-
-\subsubsection{Genetic Algorithm}
-Genetic Algorithms(GA) have the most wide set of applications.
-It was first conceived by John H.
-Holland for studying adaptive behavior as in \textit{Adaptation in natural and artificial systems} \cite{holland1975}.
-They are mainly considered as function optimizers.
-In general GA have many diverse representation schemes considering the solution set of the problem.
-Depending on the problem scenario an appropriate representation could be Binary, Grey Code, Integer, Real-Valued, Floating-point or Permutation based.
-
-Using GA for a binary representation, mutation can be single point or multiple point, where a random location is selected from the binary genome and the bit is flipped.
-For integer representation random resetting is used instead of bit flipping.
-Creep mutation is another scheme which was designed for ordinal attributes and works by adding a small (positive or negative) value to each gene with a random probability.
-For a real-valued or floating-point mutation none of the above strategy is applicable.
-As for this case mutation is applied to a random gene maintaining a certain range of value within an upper and a lower bound and using a standard for randomization, such as Uniform, Gaussian or Cauchy distribution.
-For permutation representation, swap mutation is a strategy used by simply swapping the location of two randomly selected genes.
-Insert mutation is another strategy where a random gene is selected and inserted to a random location in the genome, causing the other genes to move a single space.
-In scramble mutation, location of a collection of randomly selected genes are scrambled, while in inversion mutation serialized location of a set of genes are inverted.
-
-GA also have many different recombination operators for each representation.
-For binary and integer representation one-point crossover and \textit{N}-point-crossover are the most frequently used.
-These two operators work by dividing the parent genome at one or multiple random points and combining them to create an offspring.
-Uniform-crossover \cite{sywerda1989} is another method which works by treating each gene independently and making a random choice to which parent it should inherit from.
-Recombination for floating-point representation can use the same operators like binary and integer, and when it does it is termed as discreet recombination.
-Another type is intermediate or arithmetic recombination where the offspring do not just receive a part of their parent genome, but instead, their genomes are derived from their parent using an arithmetic formula.
-Permutation representation has many interesting recombination operators, out of which partially mapped crossover was first proposed by Goldsberg and Lingle \cite{goldberg1985} for the traveling salesman problem and since then it has become one of the most widely used operators for adjacency type problems.
-Other useful operators for permutation representation are Edge crossover, Order crossover and Cycle crossover, where their name provides more or less an appropriate description of their operation.
-
-In regards to parent selection the most commonly used process by GA is fitness proportion selection, where the selection probability of a parent depends on the absolute fitness value of the individual compared to the absolute fitness values of the rest of the population.
-A fitness value is evaluated from the evaluation or the fitness function.
-Introduced by Holland \cite{holland1975} this procedure has a few problems.
-Premature convergence being one where individuals that are a lot better than the rest take over the entire population.
-Also when fitness values are all very close, there is almost no selection pressure in evolution of the fittest.
-Inspired by the observed drawbacks of fitness proportion selection a method was proposed by Baker \cite{baker1987} termed as Ranking selection.
-This procedure preserves a constant selection pressure by sorting the population on the basis of fitness, and then allocating selection probabilities to individuals according to their rank.
-Both of the above mentioned selection procedures requires knowledge of the entire population.
-But when the population size is very large Tournament selection is an effective process \cite{eiben2003}.
-In this case a randomized pre-selection is done over the large population and then they are ranked according to their fitness value and selected as parent.
-
-Genetic Algorithms are one of the most effective strategy used in the field of evolutionary computation to solve optimization problems.
-Then again there are limitations.
-When the solution set of a problem do not have a gnomic representation, genetic algorithms cannot play any role in improving it.
-So the set of optimization problems to which GA can be applied is not universal.
-
-\subsubsection{Evolutionary Strategies}
-The key important property of the set of algorithms termed as ``Evolutionary Strategy" is \textbf{self-adaptation} of strategy parameters.
-The  parameters of Evolutionary Algorithm are included in the chromosomes and they co-evolve with the solution set while running the algorithm.
-To summarize these set of algorithms, they usually have real-valued vectors, their recombination process is discrete or intermediary, their mutation process uses Gaussian perturbation while parent selection is uniform random.
-In terms of their attribute feature they are fast and good optimizer for real-valued optimization.
-
-\subsubsection{Evolutionary Programming}
-The primary objective of evolutionary programming was to generate artificial intelligence by simulating evolution as a learning process \cite{fogel1966}.
-Capability of a system to adapt its behavior to meet some specified goal in the environment was considered as intelligence.
-Fogel used finite state machines as predictors and evolved them.
-Usually representation for evolutionary programming is with real-valued vectors.
-Its parent selection is deterministic, where each parent creates one offspring via mutation.
-There is no recombination operator for evolutionary programming.
-Mutation is applied with Gaussian perturbation.
-While survivor selection is probabilistic.
-
-\subsubsection{Genetic Programming}
-Genetic programming is typically applied to machine learning tasks such as prediction and classification.
-Its attribute feature behaves similar to neural network and usually has huge populations of solution combination.
-The algorithm itself is a very slow process.
-These sets of algorithms use non-linear chromosomes such as trees and graphs (data structures).
-Mutation is mostly avoided for genetic programming.
-Recombination operators work by exchanging subtrees.
-Mutation if applied will be a random changing process in the tree.
-Parent selection process is usually fitness proportional while the survivor selection process is usually replacement of generations.
-From a technical point of view, genetic programming is simply a variant of genetic algorithm working with a different data structure: the chromosomes are trees.
-
-\subsection{Artificial Life}
 Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
@@
 This includes some large-scale online systems, such as collaborative tagging or social bookmarking systems.
-
-The following definition of Complex Adaptive System is comprehensive.
-
-\begin{quote}
-\textsl{``A Complex Adaptive System (CAS) is a dynamic network of many agents (which may represent cells, species, individuals, firms, nations) acting in parallel, constantly acting and reacting to what the other agents are doing.
-The control of a CAS tends to be highly dispersed and decentralized.
-If there is to be any coherent behavior in the system, it has to arise from competition and cooperation among the agents themselves.
-The overall behavior of the system is the result of a huge number of decisions made every moment by many individual agents." - John H.
-Holland}
-\end{quote}
-
-Holland also provided some common kernel of similarities and dissimilarities between different complex adaptive systems in \textsl{Adaptation in Natural and Artificial Systems} \cite{holland1975}:
-
-\begin{enumerate}
-	\item \textsl{``All complex adaptive system involve large number of parts undergoing a kaleidoscopic array of simultaneous non linear interactions."} As the behavior of the whole system is non-linear, the usual mathematical techniques of linear approximation such as, linear regression, normal coordinates, mean field approaches, and the like make little progress in the analysis of complex adaptive systems.
-As because different interactions between agents are simultaneous, parallel computing is helpful in term of simulating and analyzing these systems.
-	\item \textsl{``The impact of these systems in human affairs center on the aggregate behavior, the behavior of the whole."}
-	\item \textsl{``The interactions evolve over time, as the parts adapt in an attempt to survive in the environment provided by the other parts."}
-	\item \textsl{``Complex adaptive systems anticipate."}
-\end{enumerate}
 
@@
 
-\subsection{Conclusion}
-This section discusses evolutionary computation, the field that takes concepts from evolutionary biology to solve and optimize problems in compute science.
-It also discusses the interdisciplinary field Artificial life where scientist discuss diverse knowledge from biology, economics, physics and use computer science to simulate and analyze life as it is in nature.
-The discussion of this section is expected to provide a base upon which the following sections will begin construction of the core idea of this thesis.
-
 \section{The Inspiration: Mimicry}
@@
 
-\subsection{History}
 Henry W.
@@
 
-\subsection{Conclusion}
 Mimicry is one of the most fascinating cases of evolutionary biology.
@@
 
-\begin{quote}
-\textsl{``Modeling, it should be clear is an art form.
-It depends on the experience and taste of the modeler.
-In this it is much like cartooning.
-The modeler (cartoonist) must decide which features to make salient (exaggerate), and which features to eliminate (avoid), in order to answer the questions (make the political point)" - John H.
-Holland \cite{holland1996}.}
-\end{quote}
-
-\subsection{Introduction}
 %Entire section until past work needs to be revised when the model has been fully described.
@@
 
-\subsection{The Prey: Mimics and Models}
-
-\subsubsection{Pattern representation by Cellular Automata}
+\subsection{The Prey: Models and Mimics}
+
 Only the significant characteristics which are required for a successful model of mimicry is implemented.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.60]{../tex/images/predators-40}
-	\caption[A population of predators]{A population of 40 predators distributed over the environment.}
-	\label{fig:predators-40}
-\end{figure}
-
 The screen shot in figure \ref{fig:predators-40} is from the simulation with only 40 predator species.
@@
 
-\subsection{Conclusion}
 This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
@@
 
-\subsection{Introduction}
 It is always a challenge to extract and analyze data from an Artificial Life simulation.
@@
 	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
-\end{figure}
-
-\subsection{Initial configuration with four prey species}
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
-  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}
-  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}
-  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}
-  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 4 prey species}
-\label{tab:config-table-4-prey}
-\end{table}
-
-This run of the simulation has been initialized with four prey species with very different CA pattern configuration.
-The predator reproduction interval has been increased to 1400, while the minimum memory size has been increased to 4 instead of 2 as the predator is expected to memorize four different species of prey before starting to make intelligent decision about consuming them.
-The rest of the parameters remain the same as from the experiment in section \ref{subsec:init-conf-2prey}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey}
-	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
-	\label{fig:plot-4-prey}
-\end{figure}
-
-By observing the graph in figure \ref{fig:plot-4-prey} we can see the two rings of unpalatable species (CA Rule 55, 110) which was put at the initial state of the simulation has dominated after 10000 iterations.
-CA rule 55 has taken over all other species while CA 110 is following it (represented with dotted curve).
-Also the palatable prey species with similar patterns to CA rule 55 and 110 are taking full advantage of their deceiving pattern and increasing their population (represented with line curve).
-The two palatable set of patterns CA Rule 190 and 30 are unable to dominate the population.
-Different other mimicry rings are present in the simulation as we can observe from the graph of number of rings verses simulation time in figure \ref{fig:ringSize10k-4Prey}.
-The total number of rings reached somewhere near 37 while most of them have comparatively low representative population.
-Batesian mimicry is in full effect in this simulated environment.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey}
-	\caption[Number of mimicry rings (4 prey species)]{Number of mimicry rings, initialized with 4 prey species.}
-	\label{fig:ringSize10k-4Prey}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\label{fig:screenshot-simTime11K-4Prey}
-	\includegraphics[scale=0.55]{../tex/images/simTime11K-4Prey}
-	\caption[Graphical representation of the model (simulation time: 11200)]{Graphical representation of the model initialized with 4 prey species, simulation time: 11200.}
-\end{figure}
-
-\subsection{Increased initial population with four prey species}
-
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 4 prey species with increased population}
-\label{tab:config-table-4-more-prey}
-\end{table}
-
-In this run of the simulation some significant parameters have been updated.
-First one is the initial population of prey species.
-It has been increased from 50 to 150 for each of the prey species, while increasing the overall population from 200 to 600.
-Secondly, predator population has been increased from 10 to 20.
-Thirdly, predator demise age has been increased from 2500 to 7000 while their reproduction interval has been increased from 1400 to 2500.
-Increasing predator demise age can have an interesting effect, as the longer a predator is present in a simulation, the longer it will be making intelligent decision in terms of consuming its prey and there will be increased selection pressure from the entire population of predators.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10K-4MorePrey}
-	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
-	\label{fig:plot-4-more-prey}
-\end{figure}
-
-Some very interesting diversity of mimicry rings can be observed in the simulation for updating these parameters.
-The unpalatable rings and their deceptive counterparts (palatable prey with similar pattern) still have their dominance.
-We can observe CA Rule 55 and 190 are the highest in number of population.
-Interestingly enough CA Rule 30 and 110 which started as palatable prey species has also taken dominance in the simulation, following 55 and 190.
-The unpalatable counter part of CA Rule 30 and 110 are also following the palatable population.
-
-The total number of rings have increased much in this run compared to the previous one.
-To summarize the results of this experiment, we can observe, increased diversity of prey population and much more interaction between predator and prey.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4MorePrey}
-	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
-	\label{fig:ringSize10k-4MorePrey}
 \end{figure}
@@
 
-\subsection{Initial configuration with single prey species}
-Until now all experiments have been initialized with multiple prey species.
-The following set of experiments have been initialized with only a single prey species, for both cases of unpalatable and palatable.
-
-\subsubsection{Unpalatable}
-\label{subsubsec:single-prey-unpalatable}
-
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
-  																									& 216 & \multicolumn{2}{c|}{10} \\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 1 prey species unpalatable.}
-\label{tab:config-table-1-prey-unpalatable}
-\end{table}
-
-This configuration has only one unpalatable species, one in each of the 216 cells, equally distributed all over the environment.
-Also have a set of 10 predators.
-Their minimum memory configuration has been set to 2 as any value below 2 will not help the Hopfield Network Memory to differentiate between two patterns.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-1Prey-unp}
-	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
-	\label{fig:plot-1-prey-unp}
-\end{figure}
-
-From figure \ref{fig:plot-1-prey-unp}, it can be observed, the initial set of unpalatable species is dominant as expected.
-The palatable population mimicking that set is following it.
-A bunch of other rings with majority of unpalatable species have been reproduced through mutation.
-Mainly because the initial population started with a bunch of unpalatable species, so their reproduced generation have similar behavior as well.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-1Prey-unp}
-	\caption[Number of mimicry rings (1 prey species unpalatable)]{Number of mimicry rings, initialized with 1 prey species unpalatable.}
-	\label{fig:ringSize8k-1-Prey-unp}
-\end{figure}
-
-\subsubsection{Palatable}
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}} 
-  																									& 216 & \multicolumn{2}{c|}{8} \\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 1 prey species palatable.}
-\label{tab:config-table-1-prey-palatable}
-\end{table}
-
-This configuration is set exactly as according to section \ref{subsubsec:single-prey-unpalatable} but with a single set of palatable species.
-The population of predators have been reduced from 10 to 8 to avoid elimination of all prey species as it happened in case of section \ref{subsec:init-only-palatable-species}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-1Prey-p}
-	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
-	\label{fig:plot-1-prey-p}
-\end{figure}
-
-From the initial palatable population we see a bunch of palatable rings created.
-Major difference from section \ref{subsubsec:single-prey-unpalatable} is the total number of prey population created.
-For the unpalatable species in section \ref{subsubsec:single-prey-unpalatable}, total prey population reach above 12 thousand.
-But for palatable species total population reach nearly above 5000 prey species, as when the preys are palatable there is more consumption from predators.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-1Prey-p}
-	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
-	\label{fig:ringSize8k-1-Prey-p}
-\end{figure}
-
 \subsection{Analysis of Batesian Mimicry}
@@
 
-\subsection{Conclusion}
-\label{subsec:result-conclusion}
+\section{Conclusion}
+\label{section:conclusion}
 Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
@@
 
-\section{Future Work: Application}
-\label{section:application}
-
-The goal of this thesis is to investigate whether the evolution of mimicry can be used in a problem solving scenario similar to evolutionary programming or genetic algorithm as it is used to optimize solutions using mathematical functions.
-Predator-prey co-evolution has also been used for solving interesting problems \cite{hillis1990}, giving better result than conventional methodologies.
-
-The biggest challenge faced while searching for the appropriate problem to be optimized is the idea of associating palatability with CA pattern with which the prey species has been represented.
-If we consider the CA pattern to be a certain solution to a problem then the set of 2D CA pattern among which the prey species vary could be considered as the solution set of the problem.
-And if we consider that the predator species are responsible for selecting the appropriate pattern based on their palatability, then we can consider palatability as the criteria for selection of the pattern (or the evaluation/fitness function for the case of Evolutionary Programming/Genetic Algorithm).
-If the predator associates the CA pattern with palatability then it does not make any sense of having a mimic in the solution space as mimics will have the same pattern with opposite palatability.
-So using the evolution of mimicry to solve an optimization problem is futile if we try conventional problems which already can be solved with the help of evolutionary programming or genetic algorithm.
-
-So the kind of problems we should be looking for applying the evolution of mimicry, are the ones which cannot be solved with conventional evolutionary methods.
-We should be looking for a problem where the idea of deception can be useful in term of solving it.
-An interesting analogy is with anti-virus and virus software.
-If we consider anti-virus to be predator and virus (mimic) to be prey species, then the objective of a virus would be to look like a regular virus free program (model) to get pass an anti-virus software.
-In this way by mimicking a regular program a virus can get pass any anti-virus software available in the market.
-To successfully implement this software we need to create a virus program which can evolve itself to pretend like a regular program (virus free).
-The environment will be the operating system itself where all the programs reside.
-It is worth noting the fact that this objective is malicious for the computer industry, which makes it less significant to pursue.
-
-\section{Conclusion}
-\label{section:conclusion}
 If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
-As mentioned in section \ref{subsec:result-conclusion} this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
+As mentioned previously this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
 Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
@@
 
-But considering Artificial Life as a subject where we essentially learn from nature, its behaviors, and use that knowledge to find better solution to existing problems in the field of computer science then this thesis has not been completely successful.
-We have not been able to find the appropriate problem solving scenario for which the natural process of mimicry can be applied.
-
-Humans came to understand the concept of biological evolution and its significance when it was first proposed by Charles Darwin in 1859 in his book \textsl{On the Origin of Species} \cite{darwin1859}.
-Nearly 200 years later Alan Turing was the first who thought over creating machines which are capable of evolving itself (Section \ref{subsubsec:evo-comp-history}).
-Eventually in 1975 John Holland was able to make the most applicable use of the process of evolution to solve problems in computer science by his invention of Genetic Algorithms.
-The time for this invention was appropriate as the field of computer science was in its burgeoning state.
-Over the next couple of decades computers became one of most useful and important machinery in human history.
-Genetic Algorithms became popular as well because of increased capability of computers in term of speed and complexity.
-
-Even though we do not have any problem solving application for the evolutionary process of mimicry at this point, it does not imply that this study will not be useful in the future to give us solution to an important problem in computer science or any other field for that matter.
-The simulation presented in this thesis, itself, consists of building blocks of knowledge such as Hopfield Network and Cellular Automata.
-Maybe to use mimicry to solve a problem, other diverse building blocks are necessary which has not yet been invented.
-
-The objective of any research is to look for \textsl{unexplored} territory to find new \textsl{knowledge}, \textsl{understanding} or \textsl{explanation}.
-From the research presented in this thesis we certainly get new \textsl{understanding} of the capability of computer science to emulate natures behavior.
-We also get to \textsl{explore} a new model for the evolutionary process of  mimicry.
-In addition to that, the model provides us with better \textsl{explanation} and \textsl{understanding} of nature, while enforcing some existing \textsl{knowledge} with greater support (section \ref{subsec:result-mullerian-mimicry}).
-
 \bibliographystyle{apalike}

### 2016-02-25 docs/paper/Paper.tex
Updates to the inspiration section

@@
 \subsubsection{Definitions of Mimicry}
-The following account on the definition of Mimicry is mostly extracted from Wickler's \textit{Mimicry in plants and animals} \cite{wickler1986}.
-
-According to Wickler the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following
-
-\begin{quote}
-\textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
-\end{quote}
-
-The following more sophisticated definition was provided at the international Zoological Congress in Washington, 1963,
-
-\begin{quote}
-\textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
-\end{quote}
-
 The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}.
@@
 \begin{itemize}
-	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".} This increases the probability that a predator will affect both parties concerned.
-Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
-	\item \textsl{``that the imitators are always the more defenseless".} On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
-	\item \textsl{``that the imitators are always less numerous in individuals".} What is meant here is that the deceived animal should encounter the mimic less often than the model.
-This is true when the deceived animal must learn to recognize model and mimic and when positive and negative experiences carry equal weight.
-But it is known from various learning experiments that when an animal has learned about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences.
-Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces.
-When the deceptive animal possesses an innate reaction to the model, the number of mimics can be virtually unlimited.
-	\item \textsl{``that the imitators differ from the bulk of their allies".} The most remarkable cases of mimicry are those where close relatives form divergent models.
-It is nevertheless highly possible that groups of closely related species may be similar mimics of the same model.
-Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry.
-	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} This criteria, like the previous one is aimed at defining mimicry as a special adaptation.
-But if one of two closely related species both of which are poisonous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
+	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
+	\item \textsl{``that the imitators are always the more defenseless".}
+	\item \textsl{``that the imitators are always less numerous in individuals".}
+	\item \textsl{``that the imitators differ from the bulk of their allies".}
+	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} 
 \end{itemize}
@@
 We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=5]{../tex/images/CA_rule30s}
-	\caption[Cellular Automata]{Cellular Automata Rule 30.
-	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
-	\label{fig:cellular-automata-rule-30}
-\end{figure}
 

### 2016-02-25 docs/paper/Paper.tex
\cite has been changed to \citep

@@
 
-\gls{al} has been described by Taylor, also as a tool for biological inquiry \cite{taylor1993}.
+\gls{al} has been described by Taylor, also as a tool for biological inquiry \citep{taylor1993}.
 While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
@@
 Most of the experiments are attempts to direct an artificial evolutionary process toward the production of \gls{rna} molecules with specific catalytic properties.
-The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \cite{neumann1966}.
+The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \citep{neumann1966}.
 He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties.
@@
 \paragraph{Criteria}
-Echo has been constructed based on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \cite{holland1996}.
+Echo has been constructed based on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \citep{holland1996}.
 
@@
 	\item The architecture of the Echo model should be flexible enough so that other well-studied mathematical models of particular \textsl{CAS} can be incorporated whenever required.
-Among other models the significant ones include, Dawkins' \textsl{biological arms race} \cite{dawkins1990} and Brower's \textsl{survival of mimics} \cite{brower1988} from ecology; Wicksell's \textsl{Triangle} \cite{marimon1989} and \textsl{overlapping generation models} \cite{anderson1989} in economics; the \textsl{prisoner's dilemma game} \cite{axelrod1984} in political science; Holland's \textsl{two-Armed bandits} \cite{holland1975} in operational research and Perelson's \textsl{antigen-body matching} \cite{perelson1999} in immunology.
+Among other models the significant ones include, Dawkins' \textsl{biological arms race} \citep{dawkins1990} and Brower's \textsl{survival of mimics} \citep{brower1988} from ecology; Wicksell's \textsl{Triangle} \citep{marimon1989} and \textsl{overlapping generation models} \citep{anderson1989} in economics; the \textsl{prisoner's dilemma game} \citep{axelrod1984} in political science; Holland's \textsl{two-Armed bandits} \citep{holland1975} in operational research and Perelson's \textsl{antigen-body matching} \citep{perelson1999} in immunology.
 	\item As mathematical analysis provides the surest route to arrive at a valid generalization point, most aspects of the Echo model should be amenable to mathematical analysis. 
@@
 In developing Echo using the above set of criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \cite{hraber1997} is more from an ecological perspective and has been discussed in the following.
+Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \citep{hraber1997} is more from an ecological perspective and has been discussed in the following.
 
@@
 As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators.
-Wickler \cite{wickler1986} expresses,
+Wickler \citep{wickler1986} expresses,
 \begin{quote}
@@
 	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
-\cite{bates1862}}
+\citep{bates1862}}
 	\label{fig:batesian-butterfly}
@@
 \subsubsection{Definitions of Mimicry}
-The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}.
+The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \citep{poulton1890colours}.
 The clauses are presented in the following:
@@
 
-According to Wickler \cite{wickler1986}, these five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
+According to Wickler \citep{wickler1986}, these five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
 But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.
@@
 
-According to Huheey \cite{huheey1988} \textsl{``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution" \cite{muller1879}.} In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
+According to Huheey \citep{huheey1988} \textsl{``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution" \citep{muller1879}.} In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
 Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species.
@@
 But recently Brower discovered that the viceroy is actually just as noxious as the monarch, making this a case of Mullerian mimicry.
-\cite{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
+\citep{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
 	\label{fig:mullerian-butterfly}
@@
 \label{subsec:evolutionary-dynamics-of-mimicry}
-The dynamics of mimicry has been investigated by Turner \cite{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
+The dynamics of mimicry has been investigated by Turner \citep{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
 
@@
 Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another.
-Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \cite{gould1977}}.
+Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \citep{gould1977}}.
 
@@
 \textsl{``According to punctuated equilibrium, therefore, evolution is not more or less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories.
-Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \cite{eldredge1972}.
-The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \cite{turner1988}}
+Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \citep{eldredge1972}.
+The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \citep{turner1988}}
 
@@
 
-To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \cite{turner1988}, which was originated by Poulton \cite{poulton1912} and Nicholson \cite{nicholson1927}, termed as the \textbf{two stage model}.
+To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}.
 This theory states that mimicry normally arises in two steps.
-A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \cite{sheppard1972} \cite{ford1964}.
+A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \citep{sheppard1972} \citep{ford1964}.
 This two-stage theory has been applied for the explanation of Mullerian mimicry as well.
@@
 \paragraph{Formation of Mimicry Rings}
-In regards to the formation of mimicry ring Turner \cite{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns.
+In regards to the formation of mimicry ring Turner \citep{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns.
 Different level of variation of these two parameter can give us very different formation of mimicry ring evolution.
@@
 One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
-And this figure is more than 40 years old as it has been taken from Wilcker \cite{wickler1986}, published in 1968.
+And this figure is more than 40 years old as it has been taken from Wilcker \citep{wickler1986}, published in 1968.
 It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.
-Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \cite{cott1957}.
+Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \citep{cott1957}.
 
@@
 Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string.
-The predator will be equipped with a Hopfield network \cite{hopfield1982}, to be able to have pattern recognition capability.
+The predator will be equipped with a Hopfield network \citep{hopfield1982}, to be able to have pattern recognition capability.
 The process of evolution will of course be running at the genetic level.
@@
 
-The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \cite{grogono2003}.
+The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \citep{grogono2003}.
 
@@
 Various models of mimicry has been simulated and explored.
-The model by Turner \cite{turner1996} and the mathematical model of Huheey \cite{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.
-
-Sherratt \cite{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations.
+The model by Turner \citep{turner1996} and the mathematical model of Huheey \citep{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.
+
+Sherratt \citep{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations.
 The model's predators are deterministic, in that they have a fixed behavioral strategy over their lifetime, and cannot learn from experience.
@@
 The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble.
-Their initial work \cite{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
-
-On 2003 \cite{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble.
+Their initial work \citep{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
+
+On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble.
 Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics.
@@
 
-Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \cite{franks2004}.
+Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \citep{franks2004}.
 Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
@@
 %Explain more about the first model by Franks and Noble
-The \textbf{first} model by Franks and Noble \cite{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
+The \textbf{first} model by Franks and Noble \citep{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
 Each individual had a single gene: a value representing their external appearance or phenotype.
@@
 
-The \textbf{second} model by Franks and Noble \cite{franks2003} is based on two working hypothesis:
+The \textbf{second} model by Franks and Noble \citep{franks2003} is based on two working hypothesis:
 
@@
 \paragraph{Predator}
-Similar to Turner's stochastic model \cite{turner_et_al1984},  predators were modeled with a Monte Carlo reinforcement learning system.
+Similar to Turner's stochastic model \citep{turner_et_al1984},  predators were modeled with a Monte Carlo reinforcement learning system.
 The predator's experience of each phenotype was represented by an attack probability, which was initialized to ambivalence at 0.5.
@@
 
-In contrary to the stochastic model \cite{turner_et_al1984},  predators would generalize on the basis of experience.
+In contrary to the stochastic model \citep{turner_et_al1984},  predators would generalize on the basis of experience.
 A set of probability formula was used to come up with the current probability to consume a prey species based on its palatability and the previous probability of consumption based on experience using generalization rate and the Euclidean distance between the experienced phenotype and the consumed prey phenotype.
@@
 \textsl{``The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
-Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them." \cite{franks2003}}
+Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them." \citep{franks2003}}
 \end{quote}
@@
 \subsection{FormAL Framework}
-The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \cite{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
 The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}".
@@
 Franks and Noble have used different models to diversify species.
-In \cite{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
+In \citep{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
 Here the distance of one phenotype from another represents their level of similarity.
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsubsec:echo} \cite{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsubsec:echo} \citep{hraber1997}.
 
@@
 Punctuated equilibrium has been defined in section \ref{subsec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism.
-Also Turner \cite{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
+Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
 The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry.
@@
 
-This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \cite{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \citep{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
 
@@
 \textit{Hebb's postulate of learning} is the oldest and most famous of all learning rules; it is named in honor of the neuropsychologist Donald Hebb(1949).
-Hebb's book \textit{The Organization of Behavior} \cite{hebb1949} states the following:
+Hebb's book \textit{The Organization of Behavior} \citep{hebb1949} states the following:
 
@@
 Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
-This model can also be considered as a complex adaptive system similar to Holland's work on Echo \cite{holland1996}.
-The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \cite{holland1996} are present in this model.
+This model can also be considered as a complex adaptive system similar to Holland's work on Echo \citep{holland1996}.
+The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \citep{holland1996} are present in this model.
 Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}.
@@
 
-To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \cite{holland1996}.
+To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \citep{holland1996}.
 He choose to use the term `Internal Model' to refer to the mechanism for anticipation.
@@
 As mentioned in section \ref{subsec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
-From the second work of Franks and Noble \cite{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
+From the second work of Franks and Noble \citep{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
@@
 Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
-This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsubsec:reflection-of-punctuated-equilibrium}) \cite{turner1988}.
+This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsubsec:reflection-of-punctuated-equilibrium}) \citep{turner1988}.
 

### 2016-02-25 docs/paper/Paper.tex
Before removing all tables

@@
 Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.
-
-Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science.
-In contrast to that, in Artificial Life scientist take concepts from biology, specially evolutionary biology and genetics and implement into computer science.
-
-Christopher G.
-Langton is considered as one of the founders of the field of Artificial Life.
-He invented the term while organizing the first `\textsl{International Conference on the Synthesis and Simulation of Living Systems'} at the Los Alamos National Laboratory in 1987.
-
-In defining Artificial Life Langton states the following,
-
-\begin{quote}
-\textsl{`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature.
-Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts.
-The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."}
-\end{quote}
-
-\gls{al} has been described by Taylor, also as a tool for biological inquiry \citep{taylor1993}.
+The objective of this paper is to present an agent based artificial life model for simulating the natural process of the evolution of mimicry.
+
+According to Langton, Artificial Life is `\textsl{Life made by Man rather than by Nature'}.
+Taylor also defines it as a tool for biological inquiry \citep{taylor1993}.
 While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
-\textsl{Wetware} artificial life systems are the most similar to natural life and indeed are actually derived from natural life.
-Most of the experiments are attempts to direct an artificial evolutionary process toward the production of \gls{rna} molecules with specific catalytic properties.
 The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \citep{neumann1966}.
 He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties.
-\textsl{Hardware systems} at the organism level can deal with an organism's sensory and nervous system, its body and its environment.
-Even though an organism's nervous system is usually considered as fantastically complex, the other interesting complex components can be its geometric, mechanical, dynamical or thermal properties.
-
-\subsubsection{Complex Adaptive System}
-\label{subsubsec:complex-adaptive-system}
-\gls{cas} are special cases of complex systems.
-They are complex as they are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.
-Examples of complex adaptive systems include the stock market, social insect and ant colonies, the biosphere and the ecosystem, the brain and the immune system, the cell and the developing embryo, manufacturing businesses and any human social group-based endeavor in a cultural and social system such as political parties or communities.
-This includes some large-scale online systems, such as collaborative tagging or social bookmarking systems.
-
-\subsubsection{Echo}
-\label{subsubsec:echo}
+
+Being a special case of complex systems, \gls{cas} are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.
 Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
@@
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
-Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described in section \ref{subsubsec:complex-adaptive-system}.
-
-\paragraph{Criteria}
-Echo has been constructed based on a set of criterion. The following is a short summary on it extracted from Holland's \textsl{Hidden Order: How Adaptation Builds Complexity} \citep{holland1996}.
-
-\begin{itemize}
-	\item Simplicity is considered as the first and foremost criterion.
-Instead of emulating a real system Echo is more of a thought experiment.
-Simplicity is attained by carefully constraining agent interaction and also giving the agents only a primitive internal model.
-	\item Actions and interaction of each agent in echo has been designed to be part of a wide range of \textsl{CAS} setting.
-Their mobility is also part of a wide range of geographical setting.
-Input to the environment which is considered as a stimuli or resource, can also be diversified.
-	\item Fitness of each agent, is an evolving criterion.
-Instead of considering fitness as an external exogenous factor, it should be dependent on the context provided by the site and other agents.
-The fitness value, instead of being a constant should evolve along with the system.
-	\item \textsl{``The primitive mechanisms in Echo should have ready counter parts in all \textsl{CAS}"}.
-Interpretation of results from the Echo model should be direct and ready-made.
-As simulation is nothing but manipulation of numbers and symbols, it is always possible to make fanciful and deceiving interpretation of them, taking the opportunity to prove one's point.
-So by applying primitive mechanism for interpretation it is possible to avoid misinterpretation.
-Another advantage is with the help of interpretations, selected mechanisms can be shown to be sufficient to generate the phenomenon of interest.
-Even though simulation cannot establish that a given mechanism is actually present, but it can establish its sufficiency or plausibility.
-	\item The architecture of the Echo model should be flexible enough so that other well-studied mathematical models of particular \textsl{CAS} can be incorporated whenever required.
-Among other models the significant ones include, Dawkins' \textsl{biological arms race} \citep{dawkins1990} and Brower's \textsl{survival of mimics} \citep{brower1988} from ecology; Wicksell's \textsl{Triangle} \citep{marimon1989} and \textsl{overlapping generation models} \citep{anderson1989} in economics; the \textsl{prisoner's dilemma game} \citep{axelrod1984} in political science; Holland's \textsl{two-Armed bandits} \citep{holland1975} in operational research and Perelson's \textsl{antigen-body matching} \citep{perelson1999} in immunology.
-	\item As mathematical analysis provides the surest route to arrive at a valid generalization point, most aspects of the Echo model should be amenable to mathematical analysis. 
-\end{itemize}
-
-In developing Echo using the above set of criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber titled ``The Ecology of Echo" \citep{hraber1997} is more from an ecological perspective and has been discussed in the following.
-
-\paragraph{Organization}
-As Echo is an agent-based model, it has a collection of agents distributed in a two dimensional site which contains resources.
-Agents in Echo have freedom and flexibility to move around in this environment.
-These agents are capable of replicating themselves, while also having the capability of making complex interactions.
-Interactions include combat, trading and mating.
-
-\subparagraph{Resources and Sites}
-Resource in a site of Echo form its very foundation.
-They are represented by letters (a,b,c,d).
-Everything in Echo is constructed by combining these letters as strings.
-These resources are treated much like an `atom' and by combining them as a molecular string, agents are constructed.
-Geographically, Echo is a collection of interconnected sites.
-Each site contains a fountain which is the source of resource for the agents in Echo.
-The amount of resource available in each site varies in time.
-A site with no resource can be compared to a `desert' while another site with increased availability of letters can be a water spring or a pond.
-
-\subparagraph{Agents}
-\textsl{``Agents have a genome that is roughly analogous to a single chromosome in an haploid species"}.
-An agents \textsl{tag} is an external phenotype of its respective genotype (such as color).
-Agents have internal conditions or rules of interaction, which are genetically represented and they encode the agents internal preferences, behavioral rules and so forth.
-So interactions between multiple agents occur based on their conditions (rules for interactions) and tags (appearance).
-This results in sophisticated interaction between agents such as deception (mimicry, bluffing) and in-transitivities.
-\textsl{``The six (external) tag and (internal) condition genes possessed by every agent are the offense tag, defense tag, mating tag, combat condition, trade condition and mating condition"}.
-These genes are used to determine what sort of interaction between agents will take place and also the outcome of their interaction.
-
-Agents have two ways of reproduction, one being self replication, while the other is by interaction between a pair of agents.
-
-\subparagraph{Replication}
-The replication process for agents is asexual reproduction.
-An agent needs to collect sufficient resource to start the self-replication process.
-After replication, the newly created agent receives a fraction of its parent's resource.
-Spontaneous mutation is applied to the gene for this process, where different mutation rate is applied to different parts of the gene.
-
-\subparagraph{Interactions}
-There are diverse interactions between agents consisting of combat, trading and mating.
-Agents need to be in the same location in site for any interaction to take place.
-Testing for which selection of interaction to take place, is always conducted in the order of combat, trade and mating.
-
-\subparagraph{Combat}
-The interaction of combat is analogous to real world antagonistic behavior, where one agent is killed resulting in the survivor agent to receive all its resource.
-Depending on each agent's offense and defense tag and the tag prefixes, the winner is decided.
-A \textsl{combat matrix} is also calculated with the genome of individual agents, which helps in calculating the winner.
-
-\subparagraph{Trading}
-When two agents are chosen to interact and they do not engage in combat, they are given the opportunity to trade and mate.
-Trading and mating are very much a mutual agreement between agents compared to combat, which is more of a destructive process.
-\textsl{``Agents A and B will trade if A's trading condition is a prefix of B's offense tag and vice versa"}.
-Trading takes place for excess resources between agents, where excess is defined as the amount which the agent possess above the amount required for a replication process, plus some reserves.
-The value of the reserve is controlled with the help of a simulation parameter.
-A deceptive process is introduced here while trading takes place, when an agent might not have excess resource but will still be engaged in trade, as it is not possible for the other agent to know the resource of its opposite interactor.
-
-\subparagraph{Mating}
-Only if two agents find each other suitable, they will engage in the mating process.
-Suitability for mating is decided on certain conditions based on the mating tag of individual agents.
-A form of two point crossover takes place to perform the mating action and produce diverse new agents.
-
-\paragraph{Discussion of Results}
-The Echo model has good resemblance with natural ecosystem.
+Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described by Holland \citep{holland1996}.
+
+In developing Echo using Holland's criterion, a step by step approach has been taken.
+Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, and having a good resemblance with natural ecosystem.
 It has stable patterns of interactions among genetic variants, or trophic networks.
@@
 
-Two separate experiments are done with the above simulation to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
+Two separate experiments were done to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
 To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature.
@@
 This allowed comparison of Echo diversity patterns with empirical patterns of species abundance.
-
-Preston's canonical log normal distribution is the most widely accepted formalization of the relative commonness and rarity of species.
-The species-area scaling relation is also an important ecological pattern.
-The theory of island biography is predicted on species-area relations.
-In conservation biology, this relation has been used to predict the effects of different reserve size, with species diversity.
-Although the species-area relation can be derived from Preston's canonical log-normal distribution, a satisfactory explanation of the processes that regulate this relation has not been advanced.
-
-Now the question is, does Echo exhibit the robust ecological phenomenon of Preston curve and species area scaling relation?
-For Preston's curve plot, the data show, qualitatively the pattern of genome abundances in Echo population resembles the general patterns found in biological systems, although some differences are observed.
-But for species area curve some discrepancy was observed between the expected result and the observed values.
-Several factors were raised for this discrepancy.
-One was the choice of the simulation parameter.
-Second being the definition of different species in Echo as agents having different genome is considered from different species.
-Another factor being the balance between rates of speciation and extinction of population.
-
-Finally to answer the above question, it has been concluded that, Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.
+As result of the comparison Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.
 
@@
 
-\subsubsection{Definitions of Mimicry}
-The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \citep{poulton1890colours}.
-The clauses are presented in the following:
-
-\begin{itemize}
-	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
-	\item \textsl{``that the imitators are always the more defenseless".}
-	\item \textsl{``that the imitators are always less numerous in individuals".}
-	\item \textsl{``that the imitators differ from the bulk of their allies".}
-	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} 
-\end{itemize}
-
-According to Wickler \citep{wickler1986}, these five requirements, if fulfilled, indeed increase the probability that any given case of mimicry will be correctly diagnosed.
-But such supplementary clauses cannot be used as a definition of mimicry in general, though this is unfortunately often attempted.
-
 \subsection{Mullerian Mimicry}
@@
 
-According to Huheey \citep{huheey1988} \textsl{``Mullerian mimicry is normally viewed as a system of mutual warning coloration arising from the convergence of two or more warningly colored species, though two closely related species could also be Mullerian mimics through parallel evolution" \citep{muller1879}.} In Muller's view, predation load on each species are reduced when their warning signals are shared or converged.
-Naive young predators create the most impact in learning predation as they start their life with no knowledge or experience over the prey species.
-For cases like these, all unpalatable species should benefit from mutual advertising.
-If mutation gives opportunity for a single unpalatable prey to resemble a warningly colored species, it is expected to be more likely to survive predation than if the change was in opposite direction.
-Predators surviving on warningly colored species need to generalize; meaning if similar patterns signal unpalatability, predators recognition rate becomes much higher.
-Thus, variation in color pattern is tolerated, and mutations leading to even poor resemblance provides some protection.
-
-It is worth observing the fact that Mullerian mimicry is not deception, as it is to the predator's advantage to be able to recognize all deterrent and noxious species.
-Preys resemblance does not have to be close enough to cause misidentification on the part of the predator, but merely similar enough to remind it of a bitter past experience with similar prey.
-As Huheey continues \textsl{``Thus although there is selection for convergence to perhaps the most common, average pattern, or more likely the one associated with the most deterrence (both from the intensity of the traumatic stimuli and the frequency of predators receiving them), the convergence need not be rapid or precise.
-Indeed, the resemblance among Mullerian mimics is often not close, and the existence of very close mimics raises doubts that the mimicry is Mullerian."}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.75]{../tex/images/BatesMimButter}
-	\caption[A very well-known example of mimicry, the viceroy butterfly]{A very well-known example of mimicry is the viceroy butterfly (top) which has a pattern very similar to the unpalatable monarch butterfly (bottom).
-It was considered for a long time that this is an ideal example of Batesian mimicry.
-But recently Brower discovered that the viceroy is actually just as noxious as the monarch, making this a case of Mullerian mimicry.
-\citep{brower1991} Image source: \href{http://en.wikipedia.org/wiki/Mullerian_mimicry}{Wikipedia}}
-	\label{fig:mullerian-butterfly}
-\end{figure}
-
 \subsection{Evolutionary Dynamics of Mimicry}
@@
 
-On this issue Turner states,
-
-\textsl{``According to punctuated equilibrium, therefore, evolution is not more or less both gradual and continual, as has been supposed for most purposes in most post-Darwinian theories.
-Rather, most morphological change is held to take place within geologically short periods, separated by vastly longer periods of comparative stasis \citep{eldredge1972}.
-The rapid, large changes all occur during speciation, that is to say during the branching of the evolutionary tree (cladogenesis);" \citep{turner1988}}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.5]{../tex/images/Punctuated-equilibrium}
-	\caption[Punctuated equilibrium vs.
-phyletic gradualism]{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism.
-Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
-	\label{fig:punctuated-equilibrium}
-\end{figure}
-
 To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}.
@@
 Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.
-
-\paragraph{Formation of Mimicry Rings}
-In regards to the formation of mimicry ring Turner \citep{turner1988} has given a theory which takes into account the level of protection of different rings of butterfly species and their difference in phenotypic warning patterns.
-Different level of variation of these two parameter can give us very different formation of mimicry ring evolution.
-The cases are considered below.
-
-\begin{itemize}
-	\item If we imagine two different rings of similar warning patterns in one single habitat, similar enough that the envelop of protection afforded to one gives some protection to the more extreme variant of the other (in a simplified language, suppose that predators that have sampled species A sometimes avoid the more extreme members of species B because they mistake them as A), then these two species are subject to natural protection for mutual convergence of their patterns.
-Eventually they will form a rather accurate Mullerian mimicry ring.
-	\item By contrast, if the two species have patterns so dissimilar that predators encountering one never imagine that it might be the other (the envelop of protection do not overlap the other species' phenotype distribution), then there is no selection whatever for convergence, and the two patterns will remain distinct indefinitely.
- \item But mutations of color patterns are occurring all the time.
-Suppose that species B happens to produce a mutation whose pattern falls within the envelop of protection afforded to species A.
-The mimicry need not be perfect, but if it is good enough, the mutation will have an advantage and will spread.
-In this way species B may, by a single mutation, become a Mullerian mimic of species A; in other word species B may switch from one Mullerian mimicry ring to another.
-Clearly, if the mimicry is not perfect, the two patterns will then gradually converge, making the resemblance ever closer.
-\end{itemize}
 
@@
 
-%Entire section until past work needs to be revised when the model has been fully described.
-The objective of this thesis is to design an agent based artificial life model for simulating the natural process of the evolution of mimicry.
-
-There are mainly two species of agents.
+The agent based artificial life model for simulating the evolution of mimicry, presented in this paper has mainly two species of agents.
 These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry.
 We represent evolution of pattern for the model and the mimic with the help of \gls{ca}.
-Cellular Automata can be easily represented by simple rules, which can be expressed as a binary string.
+\gls{ca} can be easily represented by simple rules, which can be expressed as a binary string.
 The predator will be equipped with a Hopfield network \citep{hopfield1982}, to be able to have pattern recognition capability.
@@
 
+\subsubsection{Models by Franks and Noble}
+\label{subsubsec:models-by-frank-and-noble}
 The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble.
@@
 
-On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble.
-Accordingly theory suggests that all Mullerian mimics in an ecosystem should converge into one large ring, while this convergence will be encouraged by presence of Batesian mimics.
-So an evolutionary simulation to observe the above mentioned phenomenon has been presented in this piece of work.
-
-Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics in their work on \citep{franks2004}.
-Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
-In this model prey colorations are free to evolve.
-This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.
-
-\subsubsection{Models by Franks and Noble}
-\label{subsubsec:models-by-frank-and-noble}
-%Explain more about the first model by Franks and Noble
-The \textbf{first} model by Franks and Noble \citep{franks2002} is where \textsl{``multiple species are preyed upon by a single abstract predator; the appearance of each prey species can evolve but their palatability is fixed"}.
-Each individual had a single gene: a value representing their external appearance or phenotype.
-The phenotypes are constrained to a ring of values from 1-20 (where 20 and 1 are neighbors).
-The distance of one phenotype from another represents their levels of similarity.
-
-A single abstract predator was modeled with a simple reinforcement learning system.
-The predator's experience of each phenotype was represented by a score, which would be maintained by probability to consume the next prey species depending on similarity or difference in phenotype.
-
-The existence of mimetic effect were measured with the initial and final distances between prey species' phenotypes.
-Three experiments were noted.
-Firstly, with one palatable and one unpalatable species.
-For this Batesian mimicry was evolved.
-For the second experiment, with two unpalatable species, Mullerian mimicry was evolved if the two prey species have some initial resemblance.
-Experiment 3 was carried out with two unpalatable and one palatable species, where the phenotype of the palatable species moved towards that of one of the unpalatable species, which is in other words Batesian Mimicry.
-
-The \textbf{second} model by Franks and Noble \citep{franks2003} is based on two working hypothesis:
+On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble. This \textbf{second} model is based on two working hypothesis:
 
@@
 
-%\subsubsection{Model Description}
-\paragraph{Prey}
-Similar to the first model this also contains a population of prey species each having an appearance and palatability level.
-Different species of prey were each assigned a fixed palatability level on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
-Palatable species have values greater than 0.5, and unpalatable species have values lower than 0.5.
-Each prey species have used two genes with values compositely representing their external appearance or phenotype.
-Both of these genes were constrained to values from 1 - 200.
-The Euclidean distance of one phenotype from another represented their level of similarity.
-
-\paragraph{Predator}
-Similar to Turner's stochastic model \citep{turner_et_al1984},  predators were modeled with a Monte Carlo reinforcement learning system.
-The predator's experience of each phenotype was represented by an attack probability, which was initialized to ambivalence at 0.5.
-After eating prey of a particular phenotype, the predator would make a post-attack update of the relevant probability according to the palatability of the prey consumed.
-The predator would use its experience of different prey appearances to help it decide on whether or not to attack at the next opportunity.
-
-In contrary to the stochastic model \citep{turner_et_al1984},  predators would generalize on the basis of experience.
-A set of probability formula was used to come up with the current probability to consume a prey species based on its palatability and the previous probability of consumption based on experience using generalization rate and the Euclidean distance between the experienced phenotype and the consumed prey phenotype.
-
-%Explain the results for the second model by Franks and Noble
-\paragraph{Results}
-According to the first experiment, which started with 20 unpalatable prey species, hypothesis 1 of a single large mimicry ring was not established.
-There was existence of multiple mimicry rings of very different frequency (population).
-Second experiment was carried out with some palatable species along with the unpalatable ones which was able to reach conditions of Batesian mimicry also with less mimicry rings, where hypothesis 2 borne out.
-It can be observed that,
-
-\begin{quote}
-\textsl{``The presence of Batesian mimics would provide positive selection pressure on mutants and would, therefore, increase the probability that they would evolve an initial resemblance to another unpalatable species.
-Also, Batesian pressure on mimicry rings has the potential to push one ring into the range of another, helping to bridge a large phenotypic difference between them." \citep{franks2003}}
-\end{quote}
+Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics \citep{franks2004}.
+Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
+In this model prey colorations are free to evolve.
+This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.
 
@@
 
-\begin{table}[h]
-	\centering
-	\setlength\tabcolsep{2pt}
-	\begin{tabular}{| p{2.2cm} | c | c | c | c | c | c | c | c |}
-	  \hline
-	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
-	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
-	  \hline
-	\end{tabular}
-	\caption{Cellular Automata rule}
-	\label{tab:cellular-automata-rule}
-\end{table}
-
-In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
-As figure \ref{fig:cellular-automata-rule-30} is a rule 30 cellular automata, the eight bit binary representation of 30 would be the genetic representation for this pattern.
-Generation of automata pattern from this binary string can be considered analogous to the complex pathway between the genotype and the phenotype that exists in all living organism.
-
 \subsubsection{Species diversity}
@@
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
-Similar efforts of multiple mutation rate at varying location has been used in developing Echo as mentioned in section \ref{subsubsec:echo} \citep{hraber1997}.
+Similar efforts of multiple mutation rate at varying location has been used in developing Echo \citep{hraber1997}.
 
@@
 The first eight bits represent the rule, which is used to generate Cellular Automata pattern.
-The next two bits are used to represent palatability of the organism explained detail in section \ref{subsubsec:genetic-palatability-representation}.
+The next two bits are used to represent palatability of the organism.
 The next six bits is the magnitude of the force with which mobility of the organism is calculated.
@@
 \label{subsubsec:reflection-of-punctuated-equilibrium}
-Punctuated equilibrium has been defined in section \ref{subsec:evolutionary-dynamics-of-mimicry} as the evolutionary process that is more inclined to cladogenesis instead of gradualism.
+Punctuated equilibrium is more inclined to cladogenesis instead of gradualism.
 Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
@@
 Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
-The learning procedure used for this memory is Hebbian Learning.
-
-\paragraph{Hebbian Learning}
-\textit{Hebb's postulate of learning} is the oldest and most famous of all learning rules; it is named in honor of the neuropsychologist Donald Hebb(1949).
-Hebb's book \textit{The Organization of Behavior} \citep{hebb1949} states the following:
-
-\begin{quote}
-\textsl{``When an axon of cell A is near enough to excite a cell B and repeatedly or persistently takes part in firing it, some growth process or metabolic changes take place in one or both cells such that A's efficiency as one of the cells firing B is increased."}
-\end{quote}
+The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}.
 
@@
 The Hebbian learning rule represents a purely feed-forward, unsupervised learning.
-The rule implements the interpretation of the classic \textit{Hebb's postulate of learning} stated above.
-
-The rule states that if the cross product of output and input, or correlation term \(o_ix_j\) is positive, this results in an increase of weight \(w_{ij}\); otherwise the weight decreases.
-It can be seen that the output is strengthened in turn for each input presented.
-Therefore, frequent input patterns will have most influence at the neuron's weight vector and will eventually produce the largest output.
 
@@
 
-	\item \textit{Outputting.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
+	\item \textit{Output.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
 	\begin{equation}
@@
 After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored.
-Algorithm \ref{algo:algorithm-attack-prey} and \ref{algo:algorithm-attemptToKill} explains the process in every detail.
-
-\begin{algorithm}[h]
-	\caption{Algorithm for attacking Prey species}
-	\label{algo:algorithm-attack-prey}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\IF {Predator has reached Minimum attack age}
-				\STATE $preyToAttack \gets$ select random prey species from the same cell.
-				\IF {$currentMemorySize < MinimumMemorySize$}
-					\STATE $attemptToKill(preyToAttack);$ \COMMENT {Function defined in algorithm \ref{algo:algorithm-attemptToKill}}
-				\ELSE
-					\STATE recognize $preyToAttack$ pattern from memory.
-					\IF {prey is not recognized or prey is palatable}
-						\STATE $attemptToKill(preyToAttack)$
-					\ELSE 
-						\STATE Prey is recognized as unpalatable, so release it back into environment.
-					\ENDIF
-				\ENDIF
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[h]
-	\caption{$attemptToKill(preyToAttack)$}
-	\label{algo:algorithm-attemptToKill}
-	\begin{algorithmic}
-		\STATE Kill $preyToAttack$.
-		\IF {Memory size $< MaxMemorySize$}
-			\STATE Associate $preyToAttack$ pattern and palatability and store into memory.
-			\STATE Recalculate Hopfield Memory Weights using Hebbian Learning outer product rule.
-		\ENDIF
-	\end{algorithmic}	
-\end{algorithm}
 
@@
 
-\begin{algorithm}[h]
-	\caption{Algorithm for updating position of the Predator species}
-	\label{algo:algorithm-movement-predator}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\STATE $forceMagnitude \gets convertToDecimal(genome[0-3])$
-			\STATE Get list of sorted neighborhood cells. Sorted by population of prey species.
-			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
-			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-The screen shot in figure \ref{fig:predators-40} is from the simulation with only 40 predator species.
-It is presented to show the behavior of predator species in the simulation, in absence of any prey species.
-It can be observed the predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
+The predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
 This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
@@
 This is the minimum age a predator has to reach before starting to involve itself for reproduction.
-This parameter has been set to 500 iterations during the result and analysis section of the thesis.
+This parameter has been set to 500 iterations.
 The second parameter is \textsl{``Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
@@
 Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.
-
-\begin{algorithm}[h]
-	\caption{Algorithm for reproduction of the Predator species}
-	\label{algo:algorithm-reproduction-predator}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\STATE $capableToReproduce \gets$ true or false depending on the 5th bit of the genome, and maturity on reproduction age.
-			\IF {$capableToReproduce == true$ and $currentCellPopulationOfPredators > 1$ } 
-				\STATE $anotherPredator \gets$ Select random predator from same cell.
-				\IF {$anotherPredator$ is alive and $capableToReproduce$ and also reached reproduction maturity age}
-					\STATE Perform genetic cross over and mutation to create new genome.
-					\STATE Create new predator with new genome and zero memory, and release into environment.
-					\STATE Record reproduction time for both predators.
-				\ENDIF
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
 
@@
 The model has its \textit{flow} as it progresses in time.
-Also there is \textit{diversity} of prey species in the environment (\ref{subsubsec:species-diversity}).
-
-To explain internal model for a complex adaptive system Holland has used specifically the example of evolution of mimicry \citep{holland1996}.
-He choose to use the term `Internal Model' to refer to the mechanism for anticipation.
-Predators in this model anticipate the bitter taste of prey, by making intelligent decisions for consuming them.
-This mechanism for anticipation can be considered as the property of \textit{internal model} for this specific study.
+Also there is \textit{diversity} of prey species in the environment.
 
@@
 
-It is always a challenge to extract and analyze data from an Artificial Life simulation.
 Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place.
@@
 Only the 8 most populous rings are presented in the graphs with population verses simulation time.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey-generated-prey}
-	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
-	\label{fig:plot-2-prey-generated-prey}
-\end{figure}
-
-Figure \ref{fig:plot-2-prey-generated-prey} is the same experimental data of figure \ref{fig:plot-2-prey} but with only the newly generated ring of prey species.
-The initialized dominant population of CA rule 110 and 30, both palatable and unpalatable has been eliminated from this graph to observe the newly created rings.
-In this plot, among the population of new patterns the unpalatable ones dominate (CA Rule 14, 26, 94).
-Also the palatable counterpart of the unpalatable population is increasing their number.
-Species with \textsl{un-mimicked} palatable pattern is very few in number.
 

### 2016-02-25 docs/paper/Paper.tex
Images and algorithms removed

@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
-	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
-\citep{bates1862}}
-	\label{fig:batesian-butterfly}
-\end{figure}
-
 \subsection{Mullerian Mimicry}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/cells-front}
-	\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
-	\label{tab:3-d-environment-images}
-\end{figure}
-
 \subsubsection{Mobility}
@@
 Otherwise, Newton's law is used to obtain the \(acceleration\), which is integrated to obtain the new \(velocity\) and new \(position\).
-
-\begin{algorithm}
-	\caption{Algorithm for updating movement of the Agents}
-	\label{algo:algorithm-movement-agents}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\STATE $accelaration \gets ForceFactor * force - Friction * velocity$
-			\STATE $velocity \gets DT*accelaration$ \COMMENT{DT is considered as Differential Time Set}
-			\STATE $deltaPos \gets DT*velocity$
-			\STATE $position \gets position + deltaPos$
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
-
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
-		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
-		Friction & 5 & The friction constant used for motion calculations.\\ \hline
-		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
-	\hline
-\end{tabular}
-\caption{Parameters to control mobility of agents.}
-\label{tab:mobility-control-parameters}
-\end{table}
-
-Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.
 
@@
 If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least.
-Algorithm \ref{algo:algorithm-movement-prey} explains in detail.
-
-\begin{algorithm}[h]
-	\caption{Algorithm for updating position of the Prey species}
-	\label{algo:algorithm-movement-prey}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
-			\STATE Get list of neighborhood cells, sorted by population of prey species.
-			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
-			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
 
@@
 So there is two point mutation for the genome.
-
-\begin{algorithm}[h]
-	\caption{Algorithm for reproduction of the Prey species}
-	\label{algo:algorithm-reproduction-prey}
-	\begin{algorithmic}
-		\FOR{each step in time}
-			\STATE $capableToReproduce \gets$ true or false depending on the 17th bit of the genome, and maturity on reproduction age.
-			\IF {$capableToReproduce == true$ and $currentCellPopulation > 1$ } 
-				\STATE $anotherPrey \gets$ Select random prey from same cell.
-				\IF {$anotherPrey$ is alive and $capableToReproduce$ and of similar $pattern$ and $palatability$}
-					\STATE Perform genetic cross over and mutation to create new genome.
-					\STATE Create new prey with new genome, and release into environment.
-					\STATE Record reproduction time for both prey.
-				\ENDIF
-			\ENDIF
-		\ENDFOR
-	\end{algorithmic}
-\end{algorithm}
 
@@
 \label{subsec:init-conf-6-prey}
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
-  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}} 
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule57}}    
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 6 prey species.}
-\label{tab:config-table-6-prey}
-\end{table}
 
@@
 As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate.
-In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}.
-In this experiment, the value of `Minimum Memory Configuration' is 6, which is rather a large number.
+In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10.
+Also the value of `Minimum Memory Configuration' is 6, which is rather a large number.
 So there could be possibility of wrong recognition by Hopfield memory.
 Then again this phenomenon is common if we consider behavior of predators in nature.
-It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{subsec:mullerian-mimicry}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-6Prey}
-	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
-	\label{fig:ringSize10k-6-Prey}
-\end{figure}
+It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes effect.
 
@@
 \label{subsec:init-conf-only-unp}
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
-  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 4 prey species all unpalatable.}
-\label{tab:config-table-4-prey-unpalatable}
-\end{table}
 
 To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species.
-After finding different anomalous behavior of predator recognition capability in section \ref{subsec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
+After finding different anomalous behavior of predator recognition capability in the previous section for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
 As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-4Prey-unp}
-	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
-	\label{fig:ringSize10k-4-Prey-unp}
-\end{figure}
-
 This experiment is an ideal scenario for observing Mullerian mimicry.
@@
 
-\begin{table}[h]
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
-  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
-  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 4 prey species all palatable.}
-\label{tab:config-table-4-prey-palatable}
-\end{table}
-
-The parameters for this simulation has been set exactly the same as in table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point.
+The parameters for this simulation has been set exactly the same as the previous section, except all the species are palatable at this point.
 All predator configuration has also been set to exactly same as before.
 
-The results for the configuration in table \ref{tab:config-table-4-prey-palatable} can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
+The results can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
 By analyzing details we can see, around simulation time 500 all population of species come to a steady downfall as at this point initial predator species reach its' age for consumption.
@@
 It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
-Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{subsec:init-only-palatable-species}).
+Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time.
 This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
@@
 \label{subsec:result-mullerian-mimicry}
-Effects of Mullerian mimicry can be observed best for the experiment in section \ref{subsec:init-conf-only-unp}.
-For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
+Effects of Mullerian mimicry can be observed best for the experiment initialized with only unpalatable prey species.
+We initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
 The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four.
@@
 But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
-It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsubsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.
+It can be concluded that our results are consistent with those of Franks and Noble \citep{franks2003}, that multiple Mullerian mimics do not converge into one large ring.
 
@@
 Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
-This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsubsec:reflection-of-punctuated-equilibrium}) \citep{turner1988}.
+This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium \citep{turner1988}.
 
@@
 If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry.
-From the sections of \ref{subsec:result-batesian-mimicry} and \ref{subsec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
+We can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
 

### 2016-02-26 docs/paper/Paper.tex
12 pages...!!!

@@
 In developing Echo using Holland's criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, and having a good resemblance with natural ecosystem.
-It has stable patterns of interactions among genetic variants, or trophic networks.
-It consists of different levels of resources along with relative species abundance.
-Even different cataclysmic events such as meteor, drought and so fourth are introduced.
-Also several isolation effects are observed where a number of sites are allowed to evolve independently.
-In addition to that Echo contains interesting flow of resources.
-
-Two separate experiments were done to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
-To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature.
-The objective is to compare these naturally occurring ecosystems with Echo.
-The ecological patterns are the Preston  curve and the species-area scaling relation.
-This allowed comparison of Echo diversity patterns with empirical patterns of species abundance.
-As result of the comparison Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.
+Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, having a good resemblance with natural ecosystem.
 
@@
 As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators.
-Wickler \citep{wickler1986} expresses,
-\begin{quote}
-\textsl{``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they `act a part'.
-An actor is a mime, and so the representation of a false warning pattern was called \textit{mimicry}.
-Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."}
-\end{quote}
+
 In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.
@@
 It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.
-
-Mimicry is one of the most fascinating cases of evolutionary biology.
-This phenomenon has been studied extensively as infinite number of evidence exists in nature.
-One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
-And this figure is more than 40 years old as it has been taken from Wilcker \citep{wickler1986}, published in 1968.
-It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.
-Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \citep{cott1957}.
 
@@
 While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}".
-We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.
 
@@
 A cell is a three dimensional cubical section of the hyperspace.
-Accordingly in table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
+Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
 The size of a cell is evaluated from the entire world size.
@@
 The pattern represents palatability of the prey species, at least to the predator.
-To store this new pattern into memory, each predator is equipped with a Hopfield Network Memory.
 Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
-The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}.
-
-The following \textit{general learning rule} is adopted in neural network studies: \textit{The weight vector} \( \textbf{w}_i = [w_{i1} \> w_{i2} \> ...
-\> w_{in}]^t \) \textit{increases in proportion to the product of input} \textbf{x} \textit{and learning signal r}.
-The learning signal r is in general a function of \(\textbf{w}_i,\textbf{x}\), and sometimes of the teacher's signal \(d_i\).
-Thus we have,
-\begin{equation}
-	r = r(\textbf{w}_i,\textbf{x},d_i)
-%\label{eq:}
-\end{equation}
-The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
-\begin{equation}
-	\Delta\textbf{w}_i(t)=cr[\textbf{w}_i(t),\textbf{x}(t),d_i(t)]\textbf{x}(t)
-%\label{eq:}
-\end{equation}
-when c is a positive number called the \textit{learning constant} that determines the rate of learning.
-
-For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
-\begin{equation}
-	r \overset{\Delta}{=} f(\textbf{w}_i^t \textbf{x})
-%\label{eq:}
-\end{equation}
-The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
-\begin{equation}
-	\Delta\textbf{w}_i = cf(\textbf{w}_i^t \textbf{x})\textbf{x}
-%\label{eq:}
-\end{equation}
-The single weight \( w_{ij} \) is adapted using the following increment:
-\begin{equation}
-	\Delta\textit{w}_{ij} = cf(\textbf{w}_i^t \textbf{x})x_j
-%\label{eq:}
-\end{equation}
-This can be written briefly as 
-\begin{equation}
-	\Delta\textit{w}_{ij} = c o_i x_j, \> \text{for} \> j = 1, 2, ..., n
-%\label{eq:}
-\end{equation}
-Here, \(\textbf{o}\) is the output vector.
-The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning.
-The Hebbian learning rule represents a purely feed-forward, unsupervised learning.
-
-Training for Hopfield Network used for predator's memory is done by Hebbian Learning.
-Initially the weights are all set to zero.
+The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}, which represents a purely feed-forward, unsupervised learning.
+Initially the weights of the Hopfield Network are all set to zero.
 Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern.
@@
 The outer vector matrix of all the patterns are summed to come up with the final weight matrix.
-Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
-\begin{equation}
-w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
-%\label{eq:}
-\end{equation}
-\[
-w_{ij} = 0, i = j
-\]
-where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
-
-\subsubsection{Design of Memory with Hopfield Network}
-
-\paragraph{Hopfield Network}
-
-Algorithm for the Hopfield model is described in the following:
-
-\begin{enumerate}
-	\item \textit{Learning.} Let \( \boldsymbol{\xi}_1, \boldsymbol{\xi}_2, ..., \boldsymbol{\xi}_{\mu} \) denote a known set of N-dimensional fundamental memories.
-Use the outer-product rule (i.e.
-Hebb's postulate of learning) to compute the synaptic weights of the network as
-	\begin{equation}
-		w_{ji} =
-			\begin{cases}
-				\frac{1}{N} \sum_{\mu=1}^{M}\xi_{\mu,j}\xi_{\mu,i}	& j \neq i \\
-				0																										& j = i 
-			\end{cases}
-	%\label{eq:}
-	\end{equation}
-	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\).
-The elements of the vector \( \boldsymbol{\xi}_\mu \) equal \(\pm 1\) (bipolar).
-Once they are computed, the synaptic weights are kept fixed.
-
-	\item \textit{Initialization.} Let \( \boldsymbol{\xi}_{probe} \) denote an unknown N-dimensional input vector (probe) presented to the network. The algorithm is initialized by setting
-	\begin{equation}
-		x_j(0) = \xi_{j,probe}, \> j = 1,...,N
-	%\label{eq:}
-	\end{equation}
-	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).
-
-	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
-	\begin{equation}
-		x_j(n+1)=sgn \Bigg(\sum_{i=1}^{N} w_{ji}x_i(n) \Bigg), \> j = 1,2, ..., N
-	%\label{eq:}
-	\end{equation}
-	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.
-
-	\item \textit{Output.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
-	\begin{equation}
-		\boldsymbol{y} = \boldsymbol{x}_{fixed}
-	\label{eq:}
-	\end{equation}
-	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
-\end{enumerate}
 
@@
 The predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
-This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
+This behavior of predator has been designed to enforce the predatory capabilities of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
 
@@
 		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
-		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern.
-Usually the network reaches a steady state before that.
-But this restriction is to avoid infinite loop in case the network never reaches a steady state.
-\\ \hline
+		Hopfield Maximum Iterations & 20 & Maximum number of iterations to recognize a pattern and to avoid infinite loop in case the network never reaches a steady state. \\ \hline
 		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
@@
 
-If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
-As mentioned previously this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
-Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
-
-If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry.
-We can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
-
 \bibliographystyle{apalike}

### 2016-02-26 docs/paper/Paper.tex
Updating predator table

@@
 \begin{table}[h]
+\small
 \centering
@@
 As for this simulation we are considering heliconius butterfly, the representation of their wing pattern is with the help of cellular automata.
-So basically every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.
-
-%More content needs to be added for cellular automata.
-\paragraph{Cellular Automata}
-
-Cellular automata are computer generated patterns applying very simple rules.
-First invented by Jon von Neuman and later extended by Stephen Wolfram, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules.
+So every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.
 We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
@@
 But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species.
-So that is why we have two separate mutation rate while reproducing prey species.
+That is why we have two separate mutation rate while reproducing prey species.
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
@@
 \begin{table}[h]
+	\small
 	\centering
@@
 			\textbf{Gene (Index 8 to 9)} &	\textbf{Palatable} \\ \hline
-			00									& True 			\\ \hline
-			01									& True 			\\ \hline
-			10									& False 		\\ \hline
-			11									& False 		\\
+			00 or 01						& True 			\\ \hline
+			10 or 11						& False 		\\
 		\hline
@@
 A set of parameters are defined to control predators' population and learning ability in the environment.
-Details of these parameters are given in table \ref{tab:predator-control-parameters}.
+Details of which are in table \ref{tab:predator-control-parameters}.
 
@@
 As soon as a predator reaches its attack age it selects random prey species around its vicinity and starts attacking them.
-This attack process also involves recognition of prey pattern, which is at the heart of mimicry simulation for this research.
+This attack process also involves recognition of prey pattern.
 Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive.
-The ``Hopfield Minimum Memory Size" (default value in table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
+The ``Hopfield Minimum Memory Size" is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
 After a predator is born, it start attacking prey without any caution.
@@
 If the pattern is not recognized predator will try to consume it and in the process will store its palatability and pattern into memory.
-
 In this way the predator memory is limited to \textsl{``Hopfield Maximum Memory Size"}.
@@
 Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.
-
-When the above two conditions are met, meaning the predator reaches its age for reproduction and also crosses its age interval, it randomly select another predator residing in the same cell.
-If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species is born which also resides on the same cell and initializes with zero memory configuration.
-Similarly when the new born predator reaches its maturity of reproductive age and if it is capable of reproduction then the process iterates itself.
 
@@
 The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability.
-Data is stored at every instance of time of the simulation keeping an interval of 10 iterations.
+Data is stored for time interval of 10 iterations.
 As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
@@
 As mentioned in table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
-After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment.
-At this point its memory size is zero.
-As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank.
-No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species.
-When catching a prey if its memory tells that it is palatable, it will consume that prey.
-Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.
-
-Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
+Based on the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
 So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern currently captured and the patterns stored in memory.
@@
 % Put the image
-\begin{figure}[h]
+\begin{figure*}[t!]
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
+	\includegraphics[width=0.7\textwidth]{../tex/images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
 	\label{fig:plot-2-prey}
-\end{figure}
+\end{figure*}
 
@@
 Two prey species are considered to be in a ring if their CA pattern have a Hamming distance within 10 bits.
-This parameter is mentioned in table \ref{tab:ring-report-control-parameters}.
 Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve.
@@
 The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
-	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
-	\label{fig:plot-2-prey-5k}
-\end{figure}
-
-The plot of figure \ref{fig:plot-2-prey-5k} is from the same experiment as of figure \ref{fig:plot-2-prey}, but only up to 5000 iterations.
-By closely observing the graph of figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches the maturity for consuming prey species (effect of the parameter `Minimum Attack Age' from table \ref{tab:config-table-2-prey}).
-At around time 1000 the prey population starts reproducing as the population increases (controlled by `Reproduction Age Limit' from table \ref{tab:config-table-2-prey}).
-At the same time different other species of prey gets to be born with mutated CA patterns.
-There is a straight drop of prey population at time 2000, when all the prey species with which the simulation was initialized come to its demise age (controlled by `Prey Demise Age' at table \ref{tab:config-table-2-prey}).
-Over time the population of CA Rule 30 dominates the population (figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
+Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
 Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.).
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
+	\includegraphics[width=0.4\textwidth]{../tex/images/ringSize10k-2Prey}
 	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
@@
 
-The screen shot in figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation.
-The red agents are predators while the black agents with different textured patterns are the prey species.
-According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.
-
-%Screenshot of the simulation
-\begin{figure}[h]
-	\centering
-	\label{fig:screenshot-simTime7600-2-prey}
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime7600}
-	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
-\end{figure}
-
 \subsection{Initial population with six prey species}
@@
 As previously mentioned this number is always set in accordance with the initial number of different prey configuration.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-6Prey}
-	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
-	\label{fig:plot-6-prey}
-\end{figure}
-
-With the above set of parameters we receive the plot of figure \ref{fig:plot-6-prey}.
 An enormous diversity of species can be observed from this experiment.
 In addition to the six prey species with which the simulation starts, the total number of mimicry rings reach nearly 50.
-Observing the top 8 as presented in the plot of figure \ref{fig:plot-6-prey}, effects of Batesian mimicry is obvious.
-Unpalatable CA Rule 190 and 30 dominates the population.
-Similarly unpalatable CA Rule 105 is also dominant.
-But after 10000 iterations CA Rule 55 seems to have higher population than 105 even though 55 is a \textsl{palatable} set of species.
-This anomaly could be the reason for storing large number of patterns in the predator Hopfiled memory.
-As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate.
-In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10.
-Also the value of `Minimum Memory Configuration' is 6, which is rather a large number.
-So there could be possibility of wrong recognition by Hopfield memory.
-Then again this phenomenon is common if we consider behavior of predators in nature.
-It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes effect.
 
@@
 
-To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species.
-After finding different anomalous behavior of predator recognition capability in the previous section for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four.
+To further observe the effects of mimicry ring we initialize the simulation with all four unpalatable prey species.
 As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species.
@@
 
-\begin{figure}[h]
+\begin{figure*}[t]
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-4Prey-unp}
+	\includegraphics[width=0.7\textwidth]{../tex/images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
 	\label{fig:plot-4-prey-unp}
-\end{figure}
+\end{figure*}
 
@@
 This experiment is an ideal scenario for observing Mullerian mimicry.
-As mentioned in section \ref{subsec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population.
+Mullerian mimicry occurs between multiple species of unpalatable prey population.
 From the second work of Franks and Noble \citep{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
-By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we get the following plot.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime6k-4Prey-unp-1-mem}
-	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.
-Minimum Memory size reduced to one.}
-	\label{fig:plot-4-prey-unp-1-mem}
-\end{figure}
-
-Running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring.
-As it can be observed in figure \ref{fig:plot-4-prey-unp-1-mem} all four unpalatable prey population have a very dominant presence in the simulation.
+By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we run the simulation for 6000 iterations, and there was no sign for all prey population to converge into one large ring.
+All four unpalatable prey population have a very dominant presence in the simulation.
 Even though predator minimum memory has been reduced to only one pattern, different population of predators become familiar with different prey patterns, which results in the existence of multiple Mullerian mimicry ring instead of a single one.
 
-\subsection{Initial configuration with only palatable species}
-\label{subsec:init-only-palatable-species}
-
-The parameters for this simulation has been set exactly the same as the previous section, except all the species are palatable at this point.
-All predator configuration has also been set to exactly same as before.
-
-The results can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations.
-By analyzing details we can see, around simulation time 500 all population of species come to a steady downfall as at this point initial predator species reach its' age for consumption.
-Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction.
-At iteration time 2000 there is a sudden drop of prey population because the initial population of prey have reached its demise age at this point.
-By this time the population of unpalatable species mutated from the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey come to its demise.
-Predator population, from the beginning of the simulation has taken a very dominant effect.
-As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keep increasing in a geometric rate.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey-p}
-	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
-	\label{fig:plot-4-prey-p}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey-p}
-	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
-	\label{fig:ringSize8k-4-Prey-p}
-\end{figure}
-
-Observation of mimicry rings also tell us about the results we have seen in the plot of figure \ref{fig:plot-4-prey-p}.
-The number of rings keep increasing but comes to a sudden drop around simulation time 7000 and goes to zero.
+In contrast when the simulation was initiated with only palatable species all population of prey have reached its demise at nearly 7000 iterations.
 

### 2016-02-26 docs/paper/Paper.tex
10 pages!! Finally

@@
 
-\begin{table}[h!]
+\begin{table}[h]
+\small
 \centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
+\begin{tabular}{| l | c |}
 	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
-		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
-		Hopfield Maximum Iterations & 20 & Maximum number of iterations to recognize a pattern and to avoid infinite loop in case the network never reaches a steady state. \\ \hline
-		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
-		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
-		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
-		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
-		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
-		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
+		\textbf{Parameter} & \textbf{Value} \\ \hline
+		Minimum Memory Size & 2 to 6 \\ \hline
+		Maximum Memory Size & 10 \\ \hline 
+		Hopfield Maximum Iterations & 20 \\ \hline
+		Attack Age & 500 \\ \hline
+		Attack Interval & 100 \\ \hline
+		Genome Mutation rate & 0.3 \\ \hline
+		Reproduction Age Limit & 500 \\ \hline
+		Reproduction Interval & 1000 to 3000 \\ \hline
+		Demise Age & 2000 to 7000 \\
 	\hline
 \end{tabular}
-\caption{Parameters to control predator population and pattern recognition capability.}
-\label{tab:predator-control-parameters}
+\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
+\label{tab:predator-genome}
 \end{table}
 
-This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
+This model has been designed to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
 Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{../tex/images/simTime10k-2Prey}
+	\includegraphics[width=0.75\textwidth]{../tex/images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
@@
 
-\begin{figure*}[t]
+\begin{figure*}[t!]
 	\centering
-	\includegraphics[width=0.7\textwidth]{../tex/images/simTime8k-4Prey-unp}
+	\includegraphics[width=0.75\textwidth]{../tex/images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}

### 2016-02-26 docs/paper/Paper.tex
9 Pages! Phew!!

@@
 A novel agent based, artificial life model, for the evolution of mimicry is presented.
-This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network.
+This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network.
 A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
 These agents are classified into categories of predator and prey species.
-Genome of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented.
+Genome of prey species control their mobility and palatability, while 2D CA is used to represent a pattern, where the rule to generate the CA is also genetically represented.
 Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators.
@@
 Being a special case of complex systems, \gls{cas} are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.
-Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations.
-Echo provides a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+Echo \citep{hraber1997} is a class of simulation model for \gls{cas}, providing a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
 Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
-Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described by Holland \citep{holland1996}.
-
-In developing Echo using Holland's criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, having a good resemblance with natural ecosystem.
+Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of \gls{cas} described by Holland \citep{holland1996}.
 
@@
 Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies, after 10 years of research in the Brazilian rain forest.
-For the next hundred years, it simulated heated discussion among all groups of people, scientists, philosophers, theologians, teachers and amateur naturalists.
 Bates collected ninety-four pieces of butterfly.
@@
 The dynamics of mimicry has been investigated by Turner \citep{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
-
-\paragraph{Punctuated Equilibrium}
-In evolutionary biology, punctuated equilibrium is the theory which proposes that most sexually reproducing species will remain in an extended state called \textit{stasis} while experiencing little evolutionary change for most of their geological history.
-When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis.
-Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another.
-Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \citep{gould1977}}.
-
-\paragraph{Phyletic Gradualism}
-In contrast to punctuated equilibrium, phyletic gradualism states that species continue to adapt to new environmental and biological selection pressures over the course of their history, gradually becoming new species.
-Phyletic gradualism holds that a species population changes gradually; that is there is no clear line of demarcation between an ancestral species and a descendant species unless a splitting (cladogenetic) event occurs or the gradually-changing lineage is divided arbitrarily.
-During this process, evolution occurs at a smooth, steady and incremental (but not necessarily constant and slow) rate on a geological time scale.
-
-To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}.
+He came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}.
 This theory states that mimicry normally arises in two steps.
@@
 
-The agent based artificial life model for simulating the evolution of mimicry, presented in this paper has mainly two species of agents.
-These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry.
+Our model initializes three kinds of agents.
+These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
 We represent evolution of pattern for the model and the mimic with the help of \gls{ca}.
@@
 The predator will be equipped with a Hopfield network \citep{hopfield1982}, to be able to have pattern recognition capability.
-The process of evolution will of course be running at the genetic level.
+The process of evolution will be occurring at the genetic level.
 
@@
 
-The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \citep{grogono2003}.
+Similar to the \textsl{Laws and Life} project by Peter Grogono \citep{grogono2003} the environment is designed as three dimensional, while the space will be of toroidal nature.
 
@@
 
-On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble. This \textbf{second} model is based on two working hypothesis:
+On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed which is based on two working hypothesis:
 
@@
 
-Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics \citep{franks2004}.
-Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded.
-In this model prey colorations are free to evolve.
-This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.
-
 \subsection{FormAL Framework}
 The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
-The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}".
-While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}".
+In FormAL, an \textbf{Agent} is a simulated organism.
+It is designed simply, but with capabilities of reproduction using genetic information and modification of genome between generations.
+There is also interaction between agents while being able to survive and reproduce in a challenging environment.
 
-\subsubsection{Agents}
-In FormAL, an \textbf{Agent} is a simulated organism. It is designed simply, but with the following qualities:
-
-\begin{itemize}
-	\item It has behaviors to be able to reproduce itself using genetic information.
-	\item Capable of modifying the structure of genome between generations.
-	\item Able to interact with other agents.
-	\item And also to survive and reproduce in a challenging environment.
-\end{itemize}
-
-\subsubsection{Spatial representation of the environment}
-The framework consists of a three dimensional visual environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.
-
-\paragraph{Space}
-The space of the environment is a three-dimensional lattice of discrete points.
+The framework consists of a three dimensional visual environment where agents get complete freedom of movement defined from their genetic representation.
+The \textbf{space} of the environment is a three-dimensional lattice of discrete points.
 The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
 \(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in table \ref{tab:environment-control-parameters}).
-
-\paragraph{Time}
-Time, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.
-
-\paragraph{Cell}
+\textbf{Time}, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.
 The entire three dimensional toroidal environment is divided in multiple cells.
-A cell is a three dimensional cubical section of the hyperspace.
+A \textbf{cell} is a three dimensional cubical section of the hyperspace.
 Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
@@
 \centering
-\begin{tabular}{| p{1.5cm} | >{\centering} p{1.6cm} | p{4cm} |}
+\begin{tabular}{| l | c |}
 	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
-		World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
-		Cell Size & \( World Size\) / \(ISize \) & Size of each cell\\ \hline
-		Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
+		\textbf{Parameter} & \textbf{Value} \\ \hline
+		ISize: Number of cell in single dimension & 6 \\ \hline
+		World Size: Size of a single dimension & 20 \\ \hline
+		Cell Size & \( World Size\) / \(ISize \) \\ \hline
+		Total Number of Cells & \( ISize^3  = 216\)\\ 
 	\hline
@@
 
-Only the significant characteristics which are required for a successful model of mimicry is implemented.
-As for this simulation we are considering heliconius butterfly, the representation of their wing pattern is with the help of cellular automata.
-So every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.
+For this simulation the preys are heliconius butterfly and the representation of their wing pattern is with the help of cellular automata (CA).
+Every prey organism contains a genetic representation of CA with which the predator will identify the prey and store its level of palatability in memory.
 We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
+Prey's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
+Each of this 256 values have a unique CA pattern associated with it.
+When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.
 
@@
 \label{subsubsec:species-diversity}
-Franks and Noble have used different models to diversify species.
-In \citep{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
-Here the distance of one phenotype from another represents their level of similarity.
-
-To use CA as prey pattern, an agent's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
-Each of this 256 values have a unique CA pattern associated with it.
-When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.
-
 With CA based pattern representation, population of prey species with a specific CA pattern can be grouped as one single species.
@@
 The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}.
-The first eight bits represent the rule, which is used to generate Cellular Automata pattern.
+The first eight bits represent the rule, which is used to generate CA pattern.
 The next two bits are used to represent palatability of the organism.
 The next six bits is the magnitude of the force with which mobility of the organism is calculated.
-The 17th bit is used to evaluate reproduction capability of the organism, depending on which the prey species is either capable or not capable to participate in reproduction.
+The 17th bit is used to evaluate reproduction capability of the organism.
 
@@
 \label{subsubsec:genetic-palatability-representation}
-The palatability of each prey species is fixed and has been represented with 2 bits of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:
-
-\begin{table}[h]
-	\small
-	\centering
-	\begin{tabular}{|c|c|}
-		\hline
-			\textbf{Gene (Index 8 to 9)} &	\textbf{Palatable} \\ \hline
-			00 or 01						& True 			\\ \hline
-			10 or 11						& False 		\\
-		\hline
-	\end{tabular}
-	\caption{Genetic representation of palatability}
-	\label{tab:genetic-representation-palatability}
-\end{table}
-
-This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \citep{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.
+The palatability of each prey species is fixed and has been represented with 2 bits (index 8 to 9) of the genome giving it a range of 0 to 3 with four levels of palatability.
+For the combinations of 00 and 01 palatability is true, while for 10 and 11 it is false.
 
@@
 If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least.
+This implementation is to have a conglomerate behavior of all prey species, while running away from predators.
 
@@
 Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}.
-If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it.
-Now the other prey also needs to be genetically capable of reproduction and needs to reach its age limit.
+If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it, given it is also capable of reproduction.
 A new genome is created from the existing genome of the two prey by applying single point crossover operation.
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1cm} | p{5cm} |}
+\begin{tabular}{| l | c |}
 	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
-		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
-		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
-		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
-		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
-		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
+		\textbf{Parameter} & \textbf{Value}\\ \hline
+		Prey Size in the 3D FormAL environment & 2 to 5 \\ \hline
+		Reproduction age limit & 100 \\ \hline
+		Reproduction interval & 1000 \\ \hline
+		Pattern Mutation Rate & 0.05 \\ \hline
+		Genome Mutation Rate & 0.5 \\ \hline
+		Demise Age & 2000 \\
 	\hline
@@
 Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction.
-In addition to it, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
+In addition, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
 Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
-So every new predator species gets to born with zero memory and with no inheritance from parents.
+Every new predator is born with zero memory and with no inheritance from parents.
 A set of parameters are defined to control predators' population and learning ability in the environment.
@@
 Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern.
-As Hopfield is a feedback network, the output of the network is also the input.
 The outer vector matrix of all the patterns are summed to come up with the final weight matrix.
@@
 \caption{Distribution and purpose of each gene of the 5 bit predator genome.}
-\label{tab:predator-genome}
+\label{tab:predator-control-parameters}
 \end{table}
@@
 As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
-Parameters are mentioned in table \ref{tab:ring-report-control-parameters}.
-
-\begin{table}[h]
-\small
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
-		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
-		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
-	\hline
-\end{tabular}
-\caption{Parameters to mimicry ring report.}
-\label{tab:ring-report-control-parameters}
-\end{table}
+Mimicry Ring Hamming distance between patterns is 10 \% of the pattern size.
 
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
+  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule60}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule61}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule62}}\\
   \hline

### 2016-02-26 docs/paper/Paper.tex
Finally 8 pages :-D

@@
 \subsubsection{Genome}
-The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}.
+The Genome of the prey species consists of 17 bits.
 The first eight bits represent the rule, which is used to generate CA pattern.
@@
 The 17th bit is used to evaluate reproduction capability of the organism.
-
-\begin{table}[h]
-\small
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{|c|c|c|c|}
-	\hline
-		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
-		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
-\end{tabular}
-\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
-\label{tab:prey-genome}
-\end{table}
 
@@
 The ``Hopfield Minimum Memory Size" is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
-After a predator is born, it start attacking prey without any caution.
+After a predator is born, it starts attacking prey without any caution.
 But after every attack the predator will store its pattern and palatability level inside its memory.
@@
 
-\subsubsection{Genome}
-Each predator has a 5 bits genome as explained in table \ref{tab:predator-genome}.
+\paragraph{Genome}
+Each predator has a 5 bits genome.
 The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment.
@@
 
-\begin{table}[h]
-\small
-\centering
-\begin{tabular}{|c|c|}
-	\hline
-		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
-				 1101					   &					1						 		\\ \hline
-\end{tabular}
-\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
-\label{tab:predator-genome}
-\end{table}
+\paragraph{Mobility}
+Movement behavior of a predator is calculated from its genome.
+The first 4 bit converted to decimal is the magnitude of force (varying from 0-15) with which it will move towards the maximum crowd of prey present within its neighborhood.
+If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells with a constant mobile behavior.
+This behavior of predator has been designed to increase predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
 
-\subsubsection{Mobility and reproduction capability}
-Movement behavior of a predator is calculated from its genome.
-The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of prey present within its neighborhood.
-So magnitude of movement of a predator varies within a range of 0-15 units.
-If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells.
-A predator chooses the neighborhood cell which contains the least number of predators.
-When the neighborhood contains zero predators, it would select any one of them randomly and move towards that cell.
-
-The predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species.
-This behavior of predator has been designed to enforce the predatory capabilities of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
-
-\subsubsection{Reproduction process}
+\paragraph{Reproduction process}
 The  fifth gene of the predator is used to represent their capability of reproduction.
@@
 The reproduction process for predators is similar to prey species.
-As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability takes effect in the reproductive process from one generation to another.
-
-There are two control parameters that effect the reproduction of predator species.
-The first is \textsl{``Reproduction Age Limit"}.
-This is the minimum age a predator has to reach before starting to involve itself for reproduction.
-This parameter has been set to 500 iterations.
-The second parameter is \textsl{``Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species.
-This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment.
-Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.
+As the learning capability of predators do not have any genetic representation.
+Similar to the prey the predator also have the \textsl{``Reproduction Interval"} and the \textsl{``Reproduction Age Limit"} which is the minimum age it has to reach before starting to mate.
+Using these parameters we can control the population of predators and by which we also control the rate of predation on prey species.
 
@@
 \end{tabular}
-\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
+\caption{Parameters to control predator population and pattern recognition capability.}
 \label{tab:predator-control-parameters}
@@
 The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability.
-Data is stored for time interval of 10 iterations.
+Data is stored at time interval of 10 iterations.
 As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
@@
 The genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents.
-As mentioned earlier the genome mutation rate has been separated from the pattern mutation rate to bring more control to the number of mimicry rings generated.
 
 Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500.
-But in the later experiments predator demise age has been increased to 5000 iterations.
 Predators in this simulation generate selection pressure for the evolution of mimicry.
-So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid.
-But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.
+So the longer a predator is present in the simulation it will be making intelligent decisions.
+Using this rate of demise for predator we were able to create successful mimetic population of prey species.
 
@@
 That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.
-
-The memory configuration size for predators is a very interesting parameter.
-The minimum memory size is directly associated with the number of prey species with which we initiate the simulation.
-Otherwise evolution of mimicry is not observed.
-As mentioned in table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species.
-Based on the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory.
-So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern currently captured and the patterns stored in memory.
 
@@
 
-%Put the number of rings picture:
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.4\textwidth]{../tex/images/ringSize10k-2Prey}
-	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
-	\label{fig:ringSize10k-2Prey}
-\end{figure}
-
-Observing from figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
+The number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
 A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
@@
 
-\subsection{Initial population with six prey species}
-\label{subsec:init-conf-6-prey}
-
-To evaluate the simulation at a more complex level we increase the prey population to 900, consisting of 6 different species with very different pattern configuration.
-To boost predator-prey interaction we also increase the number of predator population to 30.
-Predator reproduction interval has been set comparatively lower in this simulation to 2000 iterations.
-As the initial population of prey species is very high, over time we are expecting even larger number of prey species.
-If predator population does not increase at similar rate there might be a prey population explosion were predator will have no effect on providing selection pressure for the evolution of mimicry.
-So that is why predator population control parameter has been set to this level.
-For memory configuration, the minimum number is set to 6, meaning the predator will have to store 6 different prey pattern configuration before starting to make intelligent decision about consuming them.
-As previously mentioned this number is always set in accordance with the initial number of different prey configuration.
-An enormous diversity of species can be observed from this experiment.
-In addition to the six prey species with which the simulation starts, the total number of mimicry rings reach nearly 50.
+To evaluate the simulation at a more complex level we increased the prey population to 900, consisting of 6 different species with very different pattern configuration.
+To boost predator-prey interaction we also increased the number of predator population to 30.
+This resulted in an enormous diversity of species where the total number of mimicry rings reached nearly 50.
 
@@
 The population of unpalatable species have prevailed.
-After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed with the most population.
+After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed.
 All of their palatable counter parts are also increasing their population deceiving the predators.
-We observe the effect of the simulation up to 8000 iterations instead of 10000 as the total number of prey species increases at an enormous rate in this simulation within very short period of time.
-As most of the species are unpalatable, predators mostly do not get the opportunity to consume, causing a much lower prey death rate.
 
@@
 Mullerian mimicry occurs between multiple species of unpalatable prey population.
-From the second work of Franks and Noble \citep{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
+From Franks and Noble \citep{franks2003}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
 But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
@@
 All four unpalatable prey population have a very dominant presence in the simulation.
-Even though predator minimum memory has been reduced to only one pattern, different population of predators become familiar with different prey patterns, which results in the existence of multiple Mullerian mimicry ring instead of a single one.
+Even after reducing predator minimum memory to one pattern, different population of predators become familiar with different prey patterns, which resulted in the existence of multiple Mullerian mimicry ring instead of a single one.
 
@@
 
-\subsection{Analysis of Batesian Mimicry}
-\label{subsec:result-batesian-mimicry}
+\subsection{Analysis}
 For all possible initial conditions, Batesian mimicry has taken effect.
 It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
-Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time.
-This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction.
-So from this analysis it can be concluded that the model under discussion have successfully simulated the evolution of Batesian mimicry.
-
-\subsection{Analysis of Mullerian Mimicry}
-\label{subsec:result-mullerian-mimicry}
-Effects of Mullerian mimicry can be observed best for the experiment initialized with only unpalatable prey species.
+Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species.
 We initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
@@
 Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
-In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings.
-Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population.
+In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings and their shift in population.
 This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium \citep{turner1988}.

### 2016-02-26 docs/paper/Paper.tex
Hopefully final commit before sending

@@
 Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.
-The objective of this paper is to present an agent based artificial life model for simulating the natural process of the evolution of mimicry.
+The objective of this paper is to present an agent based artificial life model for simulating this natural process of the evolution of mimicry.
 
@@
 
-Being a special case of complex systems, \gls{cas} are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience.
-Echo \citep{hraber1997} is a class of simulation model for \gls{cas}, providing a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
-Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes.
-Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of \gls{cas} described by Holland \citep{holland1996}.
+Being a special case of complex systems, \gls{cas} are diverse and are made up of multiple interconnected elements, and adaptive as they have the capacity to change and learn from experience.
+Echo \citep{hraber1997} is a class of simulation model of \gls{cas}, providing a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
+Each agent has simple capabilities: offense, defense, trading and mate selection, defined by a set of chromosomes.
+Even though these capabilities are defined simply, they provide a rich set of variations illustrating the four kernel properties of \gls{cas} described by Holland \citep{holland1996}.
 
@@
 
-Our model initializes three kinds of agents.
+Our model initializes with three kinds of agents.
 These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
@@
 Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
-The size of a cell is evaluated from the entire world size.
-And the total number of cell is calculated as \(ISize^3 = 216\).
+The size of a cell is evaluated from the entire world size and the total number of cell is calculated as \(ISize^3 = 216\).
 
@@
 The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
-The \(force\) component is calculated from agent's mobility gene.
-And it is used to compute agent's \(acceleration\).
+The \(force\) component is calculated from agent's mobility gene and it is used to compute agent's \(acceleration\).
 If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion.
@@
 Each of this 256 values have a unique CA pattern associated with it.
-When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.
+When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two patterns we evaluate the hamming distance between their linear representation.
 
@@
 And by restricting inter species reproduction we can control the diversity of patterns.
-But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species.
+But there is mutation applied when similar species mate with each other, so new species born out of generations of existing species.
 That is why we have two separate mutation rate while reproducing prey species.
-One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
+One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome.
 Similar efforts of multiple mutation rate at varying location has been used in developing Echo \citep{hraber1997}.
@@
 
-\subsubsection{Genetic representation of palatability}
+\subsubsection{Palatability gene}
 \label{subsubsec:genetic-palatability-representation}
@@
 
-\subsubsection{Interaction between other Prey and Predators}
+\subsubsection{Interaction}
 The prey have been defined to have many conglomerate behavior in the environment.
@@
 Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}.
-If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it, given it is also capable of reproduction.
-A new genome is created from the existing genome of the two prey by applying single point crossover operation.
+If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it, given the other prey is also capable of reproduction.
+A prey is created from the existing genome of the two prey by applying single point crossover operation.
 Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in table \ref{tab:prey-control-parameters}.
@@
 Each input pattern consists of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
-The \textit{m} by \textit{n} pattern configuration will be serialized by putting all row vectors in one single row sequentially.
+The \textit{m} by \textit{n} pattern configuration is serialized by putting all row vectors in one single row sequentially.
 
@@
 The ``Hopfield Minimum Memory Size" is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
-After a predator is born, it starts attacking prey without any caution.
+When a predator is born, it starts attacking prey without any caution.
 But after every attack the predator will store its pattern and palatability level inside its memory.
@@
 
-\paragraph{Reproduction process}
+\paragraph{Reproduction}
 The  fifth gene of the predator is used to represent their capability of reproduction.
 Depending on its binary value a predator in the simulation will or will not be able to reproduce.
-The reproduction process for predators is similar to prey species.
-As the learning capability of predators do not have any genetic representation.
+The reproduction process for predators is similar to prey species as the learning capability of predators do not have any genetic representation.
 Similar to the prey the predator also have the \textsl{``Reproduction Interval"} and the \textsl{``Reproduction Age Limit"} which is the minimum age it has to reach before starting to mate.
@@
 
+% Put the image
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.77\textwidth]{../tex/images/simTime10k-2Prey}
+	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
+	\label{fig:plot-2-prey}
+\end{figure*}
+
 \subsection{Initial configuration with two prey species}
@@
 
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.77\textwidth]{../tex/images/simTime8k-4Prey-unp}
+	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\label{fig:plot-4-prey-unp}
+\end{figure*}
+
 The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
@@
 
-% Put the image
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.75\textwidth]{../tex/images/simTime10k-2Prey}
-	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
-	\label{fig:plot-2-prey}
-\end{figure*}
-
 The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations.
 With the initial configuration in the above table we can observe that multiple rings of prey population have been created.
-Two prey species are considered to be in a ring if their CA pattern have a Hamming distance within 10 bits.
-Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve.
+Two prey species are considered to be in a ring if their CA pattern have Hamming distance within 10 bits.
+Population of palatable species have been represented with line curve while population of unpalatable species have been presented with dotted curve.
 Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population.
@@
 
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.75\textwidth]{../tex/images/simTime8k-4Prey-unp}
-	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
-	\label{fig:plot-4-prey-unp}
-\end{figure*}
-
 The results according to figure \ref{fig:plot-4-prey-unp} are much expected.
@@
 The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four.
-So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern.
+So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable of memorizing only a single pattern.
 But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.

### 2016-02-29 docs/paper/Paper.tex
Hopefully the final version

@@
 Taylor also defines it as a tool for biological inquiry \citep{taylor1993}.
-While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level.
+While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, \textsl{Software systems} which work at the cellular level and \textsl{Hardware systems} which works at the organism level.
 The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \citep{neumann1966}.
@@
 These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
-We represent evolution of pattern for the model and the mimic with the help of \gls{ca}.
+We represent evolution of pattern for the model and the mimic with the help of \gls{ca} \citep{Wolfram2002}.
 \gls{ca} can be easily represented by simple rules, which can be expressed as a binary string.
-The predator will be equipped with a Hopfield network \citep{hopfield1982}, to be able to have pattern recognition capability.
+The predator will be equipped with a Hopfield network \citep{hopfield1982}, to have pattern recognition capability.
 The process of evolution will be occurring at the genetic level.
@@
 \subsection{FormAL Framework}
-The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for modeling the evolution of mimicry.
+The \textsl{``FormAL framework"} is a collection of concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for this model.
 In FormAL, an \textbf{Agent} is a simulated organism.
@@
 
-The framework consists of a three dimensional visual environment where agents get complete freedom of movement defined from their genetic representation.
-The \textbf{space} of the environment is a three-dimensional lattice of discrete points.
-The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
-\(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in table \ref{tab:environment-control-parameters}).
+The framework consists of a three dimensional world where agents get complete freedom of movement defined from their genetic representation.
+This toroidal \textbf{space} is a three-dimensional lattice of discrete points, divided in multiple cells, which can be visualized.
+A \textbf{cell} is a three dimensional cubical section of the hyperspace.
+The purpose of the cells is to avoid expensive distance calculations.
+As two agents are considered \textsl{``close"} to interact when they are in the same cell and \textsl{``distant"} otherwise.
 \textbf{Time}, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.
-The entire three dimensional toroidal environment is divided in multiple cells.
-A \textbf{cell} is a three dimensional cubical section of the hyperspace.
-Accordingly in Table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment.
-The size of a cell is evaluated from the entire world size and the total number of cell is calculated as \(ISize^3 = 216\).
-
-\begin{table}[h]
-\small
-\centering
-\begin{tabular}{| l | c |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} \\ \hline
-		ISize: Number of cell in single dimension & 6 \\ \hline
-		World Size: Size of a single dimension & 20 \\ \hline
-		Cell Size & \( World Size\) / \(ISize \) \\ \hline
-		Total Number of Cells & \( ISize^3  = 216\)\\ 
-	\hline
-\end{tabular}
-\caption{Parameters to control the environment.}
-\label{tab:environment-control-parameters}
-\end{table}
 
@@
 Each of this 256 values have a unique CA pattern associated with it.
+In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
 When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two patterns we evaluate the hamming distance between their linear representation.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[scale=1]{images/CARule30}
+	\caption[Cellular Automata]{Cellular Automata Rule 30}
+	\label{fig:cellular-automata-rule-30}
+\end{figure}
+
+\begin{table}[h!]
+	\small
+	\centering
+	\setlength\tabcolsep{2pt}
+	\begin{tabular}{| p{3cm} | c | c | c | c | c | c | c | c |}
+	  \hline
+	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
+	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
+	  \hline
+	\end{tabular}
+	\caption{Cellular Automata rule}
+	\label{tab:cellular-automata-rule}
+\end{table}
 
@@
 In addition, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
-Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network.
+Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as we could not find a suitable encoding for the genetic representation of Hopfield Network.
 Every new predator is born with zero memory and with no inheritance from parents.
-A set of parameters are defined to control predators' population and learning ability in the environment.
-Details of which are in table \ref{tab:predator-control-parameters}.
+A set of parameters are defined to control predators' population and learning ability in the environment (table \ref{tab:predator-control-parameters}).
 
@@
 \paragraph{Genome}
-Each predator has a 5 bits genome.
-The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment.
-The last bit controls reproduction capability of each species.
+Each predator has a 5 bits genome. The first 4 bits are for mobility, while the last bit controls reproduction capability of each species.
 
@@
 The first 4 bit converted to decimal is the magnitude of force (varying from 0-15) with which it will move towards the maximum crowd of prey present within its neighborhood.
+Number of bit are less than prey (6 bits) to reduce their maximum speed.
 If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells with a constant mobile behavior.
@@
 
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.75\textwidth]{images/simTime10k-2Prey}
+	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
+	\label{fig:plot-2-prey}
+\end{figure*}
+
 \section{The Results}
@@
 
-% Put the image
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.77\textwidth]{../tex/images/simTime10k-2Prey}
-	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
-	\label{fig:plot-2-prey}
-\end{figure*}
-
 \subsection{Initial configuration with two prey species}
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
+\begin{tabular}{| p{1.75cm} | m{1.75cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
   \hline
@@
    														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{images/CARule110}} & 108 
   														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
+  					 									& {\parbox{1.75cm}{Rule30\\ (Unpalatable)}}& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule30}}  & 108 
   					 									& \multicolumn{2}{c|}{}\\ \hline
@@
   						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
-  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
+  \multirow{2}{*}{\parbox{1.75cm}{Mutation\\ Rate}} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
   						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
   Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
-  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+  {\parbox{1.75cm}{Minimum\\ Attack Age}}	& \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  \multirow{2}{*}{\parbox{1.75cm}{Memory\\ Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 \end{table}
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[width=0.77\textwidth]{../tex/images/simTime8k-4Prey-unp}
-	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
-	\label{fig:plot-4-prey-unp}
-\end{figure*}
 
@@
 Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation.
-The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die accept their natural cause of death, that is to reach their demise age.
+The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die except their natural cause of death, that is to reach their demise age.
 So predator population can explode very easily.
 That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.
+
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[width=0.73\textwidth]{images/simTime8k-4Prey-unp}
+	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
+	\label{fig:plot-4-prey-unp}
+\end{figure*}
 
@@
 Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population.
-The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.
+The simulation was initiated with two prey species having CA rule of 110 and 30 and being palatable and unpalatable respectively.
 Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule60}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule61}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.40]{../tex/images/CARule62}}\\
+  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule60}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule61}} 
+  				& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule62}}\\
   \hline
@@
 This resulted in an enormous diversity of species where the total number of mimicry rings reached nearly 50.
+Details of this result can be found in \citep{mohiulThesis2011}.
 
@@
 
-In contrast when the simulation was initiated with only palatable species all population of prey have reached its demise at nearly 7000 iterations.
+In contrast when the simulation was initiated with only palatable species all population of prey have reached its demise at nearly 7000 iterations, details of which can be found in \citep{mohiulThesis2011}.
 

### 2016-02-29 docs/paper/Paper.tex
Final Changes

@@
 The framework consists of a three dimensional world where agents get complete freedom of movement defined from their genetic representation.
-This toroidal \textbf{space} is a three-dimensional lattice of discrete points, divided in multiple cells, which can be visualized.
+This toroidal \textbf{space} is a 3D lattice of discrete points, divided in multiple cells, which can be visualized.
 A \textbf{cell} is a three dimensional cubical section of the hyperspace.
@@
 Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population.
-The simulation was initiated with two prey species having CA rule of 110 and 30 and being palatable and unpalatable respectively.
+The simulation was initiated with two prey species having CA rule of 110 and 30, being palatable and unpalatable respectively.
 Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.

### 2016-04-21 docs/paper/Paper.tex
Camera Ready Version

@@
 An explanation for this was provided by Fritz Muller in 1878.
-Like Bates, Muller observed and caught butterflies in Brazil.
 When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
@@
 For this simulation the preys are heliconius butterfly and the representation of their wing pattern is with the help of cellular automata (CA).
-Every prey organism contains a genetic representation of CA with which the predator will identify the prey and store its level of palatability in memory.
-We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
-Prey's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255.
-Each of this 256 values have a unique CA pattern associated with it.
+Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state, with which the predator will identify the prey and store its level of palatability in memory.
+We choose CA as it can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
+This 8 bit genome has a decimal range between 0 to 255, having each of this value associated to a unique CA pattern.
 In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{images/simTime10k-2Prey}
+	\includegraphics[resolution=300]{images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
@@
 	\centering
-	\includegraphics[width=0.73\textwidth]{images/simTime8k-4Prey-unp}
+	\includegraphics[resolution=300]{images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 The simulation was initiated with two prey species having CA rule of 110 and 30, being palatable and unpalatable respectively.
+Rule 110 and 30 has been used as their phenotype is distinctly different from each other and Hopfield Network will easily distinguish them.
 Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
@@
 
-In contrast when the simulation was initiated with only palatable species all population of prey have reached its demise at nearly 7000 iterations, details of which can be found in \citep{mohiulThesis2011}.
+In contrast when the simulation was initiated with only palatable species all population of prey were consumed by predators at nearly 7000 iterations, details of which can be found in \citep{mohiulThesis2011}.
 

### 2016-04-21 docs/paper/Paper.tex
Final Camera ready version

@@
 The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
-The \(force\) component is calculated from agent's mobility gene and it is used to compute agent's \(acceleration\).
+The \(force\) component is calculated from agent's mobility gene, based on which some agents are faster/slower than others, and it is used to compute agent's \(acceleration\).
 If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion.
@@
 For this simulation the preys are heliconius butterfly and the representation of their wing pattern is with the help of cellular automata (CA).
-Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state, with which the predator will identify the prey and store its level of palatability in memory.
+Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state.
+With this pattern the predator will identify the prey and store its level of palatability in memory.
 We choose CA as it can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
-This 8 bit genome has a decimal range between 0 to 255, having each of this value associated to a unique CA pattern.
+This 8 bit genome has a decimal range between 0 to 255.
+Each of this value is associated to a unique CA pattern.
 In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
-When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two patterns we evaluate the hamming distance between their linear representation.
+To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
 
@@
 	\centering
-	\includegraphics[scale=1]{images/CARule30}
+	\includegraphics{images/CARule30-large}
 	\caption[Cellular Automata]{Cellular Automata Rule 30}
@@
 \label{subsubsec:species-diversity}
-With CA based pattern representation, population of prey species with a specific CA pattern can be grouped as one single species.
-And by restricting inter species reproduction we can control the diversity of patterns.
-But there is mutation applied when similar species mate with each other, so new species born out of generations of existing species.
-That is why we have two separate mutation rate while reproducing prey species.
+Using CA based pattern representation, population of prey species with a specific pattern can be grouped as one single species.
+Also by restricting inter species reproduction we can control the diversity of patterns.
+But mutation is applied when similar species mate with each other, so new species born out of generations of existing species.
+That is why we have two separate mutation rate for reproduction of prey species.
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome.
@@
 \subsubsection{Genome}
-The Genome of the prey species consists of 17 bits.
+The Genome of prey species consists of 17 bits.
 The first eight bits represent the rule, which is used to generate CA pattern.
-The next two bits are used to represent palatability of the organism.
-The next six bits is the magnitude of the force with which mobility of the organism is calculated.
+Next two bits are used to represent palatability of the organism.
+Following six bits are the magnitude of force with which mobility of the organism is calculated.
 The 17th bit is used to evaluate reproduction capability of the organism.
@@
 The mutations that are favored, helps the mimics to survive while the unfavored ones fail to persist.
-It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene.
+It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene, thus following the evolutionary process of punctuated equilibrium.
 
@@
 But after every attack the predator will store its pattern and palatability level inside its memory.
-As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next species.
-It will try to recognize the pattern and if found palatable, prey will be consumed.
+As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next prey species.
+It will try to recognize the pattern and if found palatable, the prey will be consumed.
 Otherwise prey will be thrown back into the environment.
@@
 \paragraph{Genome}
-Each predator has a 5 bits genome. The first 4 bits are for mobility, while the last bit controls reproduction capability of each species.
+Each predator has a 5 bit genome. The first 4 bits are for mobility, while the last bit controls reproduction capability of each species.
 
@@
 The first 4 bit converted to decimal is the magnitude of force (varying from 0-15) with which it will move towards the maximum crowd of prey present within its neighborhood.
-Number of bit are less than prey (6 bits) to reduce their maximum speed.
+Number of bits are less than prey (6 bits) to reduce their maximum speed.
 If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells with a constant mobile behavior.
@@
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.40]{images/CARule110}} & 108 
+   														& \multicolumn{2}{c|}{\parbox[c][2.4em][c]{2cm}{Predator \\ configuration}} \\ \hline
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics{images/CARule110}} & 108 
   														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& {\parbox{1.75cm}{Rule30\\ (Unpalatable)}}& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule30}}  & 108 
+  					 									& {\parbox{1.75cm}{Rule30\\ (Unpalatable)}}& \parbox[c][2.4em][c]{2.1em}{\includegraphics{images/CARule30}}  & 108 
   					 									& \multicolumn{2}{c|}{}\\ \hline
@@
   Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
-  {\parbox{1.75cm}{Minimum\\ Attack Age}}	& \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
+  {\parbox[c][2.3em][c]{1.75cm}{Minimum\\ Attack Age}}	& \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
   \multirow{2}{*}{\parbox{1.75cm}{Memory\\ Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
@@
 A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
-For example if we take a look at the set of pattern genotype with very different phenotype in table \ref{tab:diff-in-pattern}.
+For example if we take a look at the set of almost similar pattern genotype with vastly different phenotype in table \ref{tab:diff-in-pattern}.
 
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule60}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule61}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.35]{images/CARule62}}\\
+  Pattern & \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule60}} 
+  				& \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule61}} 
+  				& \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule62}}\\
   \hline

### 2016-05-27 docs/abstract_1page/abstract.tex
Initial commit for the 1 page abstract

--- 2016-04-21 docs/paper/Paper.tex
@@
 \maketitle
-
-\begin{abstract}
-A novel agent based, artificial life model, for the evolution of mimicry is presented.
-This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network.
-A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
-These agents are classified into categories of predator and prey species.
-Genome of prey species control their mobility and palatability, while 2D CA is used to represent a pattern, where the rule to generate the CA is also genetically represented.
-Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators.
-Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry.
-They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
-Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved.
-Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
-\end{abstract}
 
@@
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics{images/CARule30-large}
-	\caption[Cellular Automata]{Cellular Automata Rule 30}
-	\label{fig:cellular-automata-rule-30}
-\end{figure}
-
-\begin{table}[h!]
-	\small
-	\centering
-	\setlength\tabcolsep{2pt}
-	\begin{tabular}{| p{3cm} | c | c | c | c | c | c | c | c |}
-	  \hline
-	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
-	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
-	  \hline
-	\end{tabular}
-	\caption{Cellular Automata rule}
-	\label{tab:cellular-automata-rule}
-\end{table}
-
 \subsubsection{Species diversity}
@@
 So there is two point mutation for the genome.
-
-\begin{table}[h]
-\small
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| l | c |}
-	\hline
-		\textbf{Parameter} & \textbf{Value}\\ \hline
-		Prey Size in the 3D FormAL environment & 2 to 5 \\ \hline
-		Reproduction age limit & 100 \\ \hline
-		Reproduction interval & 1000 \\ \hline
-		Pattern Mutation Rate & 0.05 \\ \hline
-		Genome Mutation Rate & 0.5 \\ \hline
-		Demise Age & 2000 \\
-	\hline
-\end{tabular}
-\caption{Parameters to control prey population and visibility.}
-\label{tab:prey-control-parameters}
-\end{table}
 
@@
 
-\begin{table}[h]
-\small
-\centering
-\begin{tabular}{| l | c |}
-	\hline
-		\textbf{Parameter} & \textbf{Value} \\ \hline
-		Minimum Memory Size & 2 to 6 \\ \hline
-		Maximum Memory Size & 10 \\ \hline 
-		Hopfield Maximum Iterations & 20 \\ \hline
-		Attack Age & 500 \\ \hline
-		Attack Interval & 100 \\ \hline
-		Genome Mutation rate & 0.3 \\ \hline
-		Reproduction Age Limit & 500 \\ \hline
-		Reproduction Interval & 1000 to 3000 \\ \hline
-		Demise Age & 2000 to 7000 \\
-	\hline
-\end{tabular}
-\caption{Parameters to control predator population and pattern recognition capability.}
-\label{tab:predator-control-parameters}
-\end{table}
-
 This model has been designed to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
@@
 Also there is \textit{diversity} of prey species in the environment.
-
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[resolution=300]{images/simTime10k-2Prey}
-	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
-	\label{fig:plot-2-prey}
-\end{figure*}
 
@@
 \label{subsec:init-conf-2prey}
-% Put the table here
-\begin{table}[h]
-\small
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{| p{1.75cm} | m{1.75cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
-  \hline
-   														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox[c][2.4em][c]{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics{images/CARule110}} & 108 
-  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& {\parbox{1.75cm}{Rule30\\ (Unpalatable)}}& \parbox[c][2.4em][c]{2.1em}{\includegraphics{images/CARule30}}  & 108 
-  					 									& \multicolumn{2}{c|}{}\\ \hline
-  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
-  \multirow{2}{*}{\parbox{1.75cm}{Mutation\\ Rate}} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
-  {\parbox[c][2.3em][c]{1.75cm}{Minimum\\ Attack Age}}	& \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{1.75cm}{Memory\\ Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
-   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-\end{tabular}
-\caption{Agent configuration of 2 prey species}
-\label{tab:config-table-2-prey}
-\end{table}
 
@@
 
-\begin{figure*}[t!]
-	\centering
-	\includegraphics[resolution=300]{images/simTime8k-4Prey-unp}
-	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
-	\label{fig:plot-4-prey-unp}
-\end{figure*}
-
 The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations.
@@
 For example if we take a look at the set of almost similar pattern genotype with vastly different phenotype in table \ref{tab:diff-in-pattern}.
-
-%CARule table
-\begin{table}[h]
-\small
-\centering
-\setlength\tabcolsep{2pt}
-\begin{tabular}{|l|c|c|c|}
-  \hline
-  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule60}} 
-  				& \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule61}} 
-  				& \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule62}}\\
-  \hline
-\end{tabular}
-\caption{Difference in prey pattern genotype and phenotype}
-\label{tab:diff-in-pattern}
-\end{table}
 
@@
 It can be concluded that our results are consistent with those of Franks and Noble \citep{franks2003}, that multiple Mullerian mimics do not converge into one large ring.
+These claims can only be made within the limits of this simulation.
 

### 2016-05-29 docs/abstract_1page/abstract.tex
Final version

@@
 
-%Introductory Section
-\section{Introduction}
-\label{section:introduction}
-
 %A few paragraphs are required to bring an appropriate introduction.
@@
 
-According to Langton, Artificial Life is `\textsl{Life made by Man rather than by Nature'}.
-Taylor also defines it as a tool for biological inquiry \citep{taylor1993}.
-While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, \textsl{Software systems} which work at the cellular level and \textsl{Hardware systems} which works at the organism level.
-The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \citep{neumann1966}.
-He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties.
-
-Being a special case of complex systems, \gls{cas} are diverse and are made up of multiple interconnected elements, and adaptive as they have the capacity to change and learn from experience.
-Echo \citep{hraber1997} is a class of simulation model of \gls{cas}, providing a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites.
-Each agent has simple capabilities: offense, defense, trading and mate selection, defined by a set of chromosomes.
-Even though these capabilities are defined simply, they provide a rich set of variations illustrating the four kernel properties of \gls{cas} described by Holland \citep{holland1996}.
-
-\section{The Inspiration: Mimicry}
-\label{section:mimicry}
-
 Henry W.
-Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies, after 10 years of research in the Brazilian rain forest.
-Bates collected ninety-four pieces of butterfly.
-He grouped them according to their similar appearance.
+Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies.
 He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families.
-Out of the ninety four species, sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.
-
-\subsection{Batesian Mimicry}
 Even though Heliconiids are conspicuously colored, they are extremely abundant.
@@
 Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature.
-Also because of this phenomenon other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.
-
-Repulsive animals, such as heliconiids are very conspicuously colored.
-Having this noticeable property, they are easily recalled by predators.
-Their wing pattern works as a warning to predators.
-Once a predator has the knowledge of their inedible and unpalatable property, they would probably never attempt to try it again.
-As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators.
-
+Other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.
 In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.
 
-\subsection{Mullerian Mimicry}
-\label{subsec:mullerian-mimicry}
 Bates was not able to explain some phenomena of mimicry.
@@
 When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
-Because of predator's limited memory, all these species still lose their number even after being inedible.
-So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different family also tend to evolve to have similar appearance.
+Because of the predator's limited memory, all these species still lose their number even after being inedible.
+So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different families also tend to evolve to have similar appearance.
 This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.
-
-\subsection{Evolutionary Dynamics of Mimicry}
-\label{subsec:evolutionary-dynamics-of-mimicry}
-The dynamics of mimicry has been investigated by Turner \citep{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.
-He came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}.
-This theory states that mimicry normally arises in two steps.
-A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \citep{sheppard1972} \citep{ford1964}.
-This two-stage theory has been applied for the explanation of Mullerian mimicry as well.
-
-\subsubsection{Mimicry Ring}
-Any theory of Mullerian mimicry has to take into account the phenomenon of the coexistence of multiple mimicry rings.
-If we examine the local butterfly fauna in any area of the world, we will find that between all the aposomatic (warningly colored and defended) species present there are normally only a limited number of different patterns, normally far smaller than the number of species.
-Each cluster of species, all sharing a common pattern, is termed as Mullerian mimicry ring.
-Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.
-
 Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.
-It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.
-
-%Chapter describing the model
-\section{The Model: Evolution of Mimicry}
-\label{section:model}
 
@@
 These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
-We represent evolution of pattern for the model and the mimic with the help of \gls{ca} \citep{Wolfram2002}.
-\gls{ca} can be easily represented by simple rules, which can be expressed as a binary string.
-The predator will be equipped with a Hopfield network \citep{hopfield1982}, to have pattern recognition capability.
-The process of evolution will be occurring at the genetic level.
-
-The choice of Hopfield Network memory for a predator can be considered appropriate as the number of patterns which can be recognized by this network is inversely proportional to the accuracy of recall.
-As more patterns are memorized, Hopfield network tends to make more errors.
-This behavior will be appropriate for the simulation of Mullerian mimicry.
-Mullerian mimicry happens because of limited memory of the predators.
-Because of this limited memory, multiple inedible butterflies seems to converge to a single ring.
-
-Similar to the \textsl{Laws and Life} project by Peter Grogono \citep{grogono2003} the environment is designed as three dimensional, while the space will be of toroidal nature.
-
-\subsection{Past Work}
-Various models of mimicry has been simulated and explored.
-The model by Turner \citep{turner1996} and the mathematical model of Huheey \citep{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.
-
-Sherratt \citep{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations.
-The model's predators are deterministic, in that they have a fixed behavioral strategy over their lifetime, and cannot learn from experience.
-For both cryptic and conspicuous prey, each predator has fixed policy of either attacking or avoiding.
-
-\subsubsection{Models by Franks and Noble}
-\label{subsubsec:models-by-frank-and-noble}
-The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble.
-Their initial work \citep{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.
-
-On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed which is based on two working hypothesis:
-
-\begin{enumerate}
-	\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
-	\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
-\end{enumerate}
-
-Although there are many mathematical and stochastic models of mimicry in the biological literature, this model gives attention to the evolution of mimicry ring phenomenon from an artificial life perspective.
-
-\subsection{FormAL Framework}
-The \textsl{``FormAL framework"} is a collection of concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for this model.
-In FormAL, an \textbf{Agent} is a simulated organism.
-It is designed simply, but with capabilities of reproduction using genetic information and modification of genome between generations.
-There is also interaction between agents while being able to survive and reproduce in a challenging environment.
-
-The framework consists of a three dimensional world where agents get complete freedom of movement defined from their genetic representation.
-This toroidal \textbf{space} is a 3D lattice of discrete points, divided in multiple cells, which can be visualized.
-A \textbf{cell} is a three dimensional cubical section of the hyperspace.
-The purpose of the cells is to avoid expensive distance calculations.
-As two agents are considered \textsl{``close"} to interact when they are in the same cell and \textsl{``distant"} otherwise.
-\textbf{Time}, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.
-
-\subsubsection{Mobility}
-An agent's position is calculated once during each step of update in time.
-The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components.
-The \(force\) component is calculated from agent's mobility gene, based on which some agents are faster/slower than others, and it is used to compute agent's \(acceleration\).
-If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion.
-Otherwise, Newton's law is used to obtain the \(acceleration\), which is integrated to obtain the new \(velocity\) and new \(position\).
-
-\subsection{The Prey: Models and Mimics}
-
-For this simulation the preys are heliconius butterfly and the representation of their wing pattern is with the help of cellular automata (CA).
-Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state.
-With this pattern the predator will identify the prey and store its level of palatability in memory.
-We choose CA as it can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
-This 8 bit genome has a decimal range between 0 to 255.
-Each of this value is associated to a unique CA pattern.
-In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
-To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
-
-\subsubsection{Species diversity}
-\label{subsubsec:species-diversity}
-Using CA based pattern representation, population of prey species with a specific pattern can be grouped as one single species.
-Also by restricting inter species reproduction we can control the diversity of patterns.
-But mutation is applied when similar species mate with each other, so new species born out of generations of existing species.
-That is why we have two separate mutation rate for reproduction of prey species.
-One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome.
-Similar efforts of multiple mutation rate at varying location has been used in developing Echo \citep{hraber1997}.
-
-\subsubsection{Genome}
-The Genome of prey species consists of 17 bits.
-The first eight bits represent the rule, which is used to generate CA pattern.
-Next two bits are used to represent palatability of the organism.
-Following six bits are the magnitude of force with which mobility of the organism is calculated.
-The 17th bit is used to evaluate reproduction capability of the organism.
-
-\subsubsection{Reflection of punctuated equilibrium}
-\label{subsubsec:reflection-of-punctuated-equilibrium}
-Punctuated equilibrium is more inclined to cladogenesis instead of gradualism.
-Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
-The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry.
-As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
-Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation.
-The mutations that are favored, helps the mimics to survive while the unfavored ones fail to persist.
-It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene, thus following the evolutionary process of punctuated equilibrium.
-
-\subsubsection{Palatability gene}
-\label{subsubsec:genetic-palatability-representation}
-The palatability of each prey species is fixed and has been represented with 2 bits (index 8 to 9) of the genome giving it a range of 0 to 3 with four levels of palatability.
-For the combinations of 00 and 01 palatability is true, while for 10 and 11 it is false.
-
-\subsubsection{Interaction}
-The prey have been defined to have many conglomerate behavior in the environment.
-Prey interaction with other prey species and with predators make the evolution of mimicry possible.
-Mobility of prey species and their reproduction capability are two important behaviors which result from interaction.
-
-\paragraph{Mobility}
-The mobility genes of the prey consist of 6 bits.
-These six bits are used to calculate the force with which each prey try to move towards any neighborhood cell.
-The algorithm sorts all neighboring cell descending to the number of prey species.
-Then it selects the cell which contains the highest number of prey with zero predator.
-If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least.
-This implementation is to have a conglomerate behavior of all prey species, while running away from predators.
-
-\paragraph{Reproduction}
-Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}.
-If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it, given the other prey is also capable of reproduction.
-A prey is created from the existing genome of the two prey by applying single point crossover operation.
-Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in table \ref{tab:prey-control-parameters}.
-So there is two point mutation for the genome.
-
-\subsection{Predator}
-
-Predators in the system are designed to provide selection pressure to \textit{models} and \textit{mimics} for the evolution of mimicry.
-Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction.
-In addition, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
-Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as we could not find a suitable encoding for the genetic representation of Hopfield Network.
-Every new predator is born with zero memory and with no inheritance from parents.
-A set of parameters are defined to control predators' population and learning ability in the environment (table \ref{tab:predator-control-parameters}).
-
-\subsubsection{Learning}
-The objective of a predator's interaction with prey is always to consume it.
-But based on the prey's pattern and palatability, the predator will either be able to consume it or throw it back to the environment.
-At this event the predator needs to learn the pattern with which the prey has been represented.
-The pattern represents palatability of the prey species, at least to the predator.
-Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
-The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}, which represents a purely feed-forward, unsupervised learning.
-Initially the weights of the Hopfield Network are all set to zero.
-Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern.
-The outer vector matrix of all the patterns are summed to come up with the final weight matrix.
-
-%This section needs to use similar variables as mentioned in the above section on Hopfield Network.
-\paragraph{Input to memory}
-Each prey contains an evolving cellular automata which is represented by a binary genome.
-This two dimensional pattern is serialized to be available as a one dimensional binary array, which is taken as input for any predator organism trying to interact with the prey.
-This binary representation of the pattern gets converted to a bipolar representation.
-Each input pattern consists of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension).
-The \textit{m} by \textit{n} pattern configuration is serialized by putting all row vectors in one single row sequentially.
-
-\paragraph{Predator attack algorithm}
-As soon as a predator reaches its attack age it selects random prey species around its vicinity and starts attacking them.
-This attack process also involves recognition of prey pattern.
-Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive.
-The ``Hopfield Minimum Memory Size" is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species.
-When a predator is born, it starts attacking prey without any caution.
-But after every attack the predator will store its pattern and palatability level inside its memory.
-As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next prey species.
-It will try to recognize the pattern and if found palatable, the prey will be consumed.
-Otherwise prey will be thrown back into the environment.
-If the pattern is not recognized predator will try to consume it and in the process will store its palatability and pattern into memory.
-In this way the predator memory is limited to \textsl{``Hopfield Maximum Memory Size"}.
-After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored.
-
-\paragraph{Genome}
-Each predator has a 5 bit genome. The first 4 bits are for mobility, while the last bit controls reproduction capability of each species.
-
-\paragraph{Mobility}
-Movement behavior of a predator is calculated from its genome.
-The first 4 bit converted to decimal is the magnitude of force (varying from 0-15) with which it will move towards the maximum crowd of prey present within its neighborhood.
-Number of bits are less than prey (6 bits) to reduce their maximum speed.
-If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells with a constant mobile behavior.
-This behavior of predator has been designed to increase predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.
-
-\paragraph{Reproduction}
-The  fifth gene of the predator is used to represent their capability of reproduction.
-Depending on its binary value a predator in the simulation will or will not be able to reproduce.
-The reproduction process for predators is similar to prey species as the learning capability of predators do not have any genetic representation.
-Similar to the prey the predator also have the \textsl{``Reproduction Interval"} and the \textsl{``Reproduction Age Limit"} which is the minimum age it has to reach before starting to mate.
-Using these parameters we can control the population of predators and by which we also control the rate of predation on prey species.
+We represent evolution of pattern for the model and the mimic with the help of \gls{ca}, as \gls{ca} can be easily represented by simple rules.
+Each predator is equipped with a Hopfield network, which gives it pattern recognition capability.
+The process of evolution occurs at the genetic level.
 
@@
 Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
-This model can also be considered as a complex adaptive system similar to Holland's work on Echo \citep{holland1996}.
-The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \citep{holland1996} are present in this model.
-Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}.
-Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them.
-We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome.
-The model has its \textit{flow} as it progresses in time.
-Also there is \textit{diversity} of prey species in the environment.
-
-\section{The Results}
-\label{section:results}
+This model can also be considered as a complex adaptive system similar to Holland's work on Echo.
 
 Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place.
-This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
+This evaluation can be made with the number of different mimicry rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
 Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.
 
-\subsection{Mimicry Ring Reports}
-The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability.
-Data is stored at time interval of 10 iterations.
-As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot.
-Mimicry Ring Hamming distance between patterns is 10 \% of the pattern size.
+For all possible initial conditions, Batesian mimicry been found to take effect.
+From the population data sets it has been observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
+Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species.
 
-\subsection{Initial configuration with two prey species}
-\label{subsec:init-conf-2prey}
-
-The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation.
-This test has been done with two sets of prey species with very different Cellular Automata pattern and with opposite palatability and equal population.
-To control reproduction of the prey species their age limit has been set to 100 iterations into the time the species were alive.
-And the reproduction interval was set to 1000 iterations.
-
-Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation.
-The genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents.
-
-Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500.
-Predators in this simulation generate selection pressure for the evolution of mimicry.
-So the longer a predator is present in the simulation it will be making intelligent decisions.
-Using this rate of demise for predator we were able to create successful mimetic population of prey species.
-
-Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation.
-The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die except their natural cause of death, that is to reach their demise age.
-So predator population can explode very easily.
-That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.
-
-The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations.
-With the initial configuration in the above table we can observe that multiple rings of prey population have been created.
-Two prey species are considered to be in a ring if their CA pattern have Hamming distance within 10 bits.
-Population of palatable species have been represented with line curve while population of unpalatable species have been presented with dotted curve.
-Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population.
-The simulation was initiated with two prey species having CA rule of 110 and 30, being palatable and unpalatable respectively.
-Rule 110 and 30 has been used as their phenotype is distinctly different from each other and Hopfield Network will easily distinguish them.
-Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable.
-Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.).
-CA Rule 110 was initialized as a set of palatable species.
-
-We can observe from the above result that the evolution of mimicry has taken effect.
-A population of mimics were successfully able to exceed the population of other prey species, and the reason being, avoidance by predators of prey pattern similar to unpalatable ones.
-We can conclude that Batesian mimicry has taken effect in the simulation.
-
-The number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations.
-A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented.
-For example if we take a look at the set of almost similar pattern genotype with vastly different phenotype in table \ref{tab:diff-in-pattern}.
-
-All the patterns in table \ref{tab:diff-in-pattern} have a genetic bit difference of 1.
-So by a single mutation there can be three different set of phenotype for a child organism from its parent.
-This is largely the reason for the increased number of mimicry rings created in the simulation.
-Only the 8 most populous rings are presented in the graphs with population verses simulation time.
-
-To evaluate the simulation at a more complex level we increased the prey population to 900, consisting of 6 different species with very different pattern configuration.
-To boost predator-prey interaction we also increased the number of predator population to 30.
-This resulted in an enormous diversity of species where the total number of mimicry rings reached nearly 50.
-Details of this result can be found in \citep{mohiulThesis2011}.
-
-\subsection{Initial configuration with only unpalatable species}
-\label{subsec:init-conf-only-unp}
-
-To further observe the effects of mimicry ring we initialize the simulation with all four unpalatable prey species.
-As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species.
-Rest of the parameters remain quite unchanged.
-
-The results according to figure \ref{fig:plot-4-prey-unp} are much expected.
-The population of unpalatable species have prevailed.
-After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed.
-All of their palatable counter parts are also increasing their population deceiving the predators.
-
-This experiment is an ideal scenario for observing Mullerian mimicry.
-Mullerian mimicry occurs between multiple species of unpalatable prey population.
-From Franks and Noble \citep{franks2003}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium.
-But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them.
-By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we run the simulation for 6000 iterations, and there was no sign for all prey population to converge into one large ring.
-All four unpalatable prey population have a very dominant presence in the simulation.
-Even after reducing predator minimum memory to one pattern, different population of predators become familiar with different prey patterns, which resulted in the existence of multiple Mullerian mimicry ring instead of a single one.
-
-In contrast when the simulation was initiated with only palatable species all population of prey were consumed by predators at nearly 7000 iterations, details of which can be found in \citep{mohiulThesis2011}.
-
-\subsection{Analysis}
-For all possible initial conditions, Batesian mimicry has taken effect.
-It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
-Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species.
-We initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
-The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four.
-So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable of memorizing only a single pattern.
-But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings.
-It can be concluded that our results are consistent with those of Franks and Noble \citep{franks2003}, that multiple Mullerian mimics do not converge into one large ring.
-These claims can only be made within the limits of this simulation.
-
-\section{Conclusion}
-\label{section:conclusion}
-Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
-In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings and their shift in population.
-This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium \citep{turner1988}.
-
-\bibliographystyle{apalike}
-\bibliography{references}
-
+Analyzing the results tell us that we have successfully been able to simulate the evolution of mimicry.
+In addition, this model provides a more accurate simulation of the fascinating natural process of mimicry rings and their shift in population.
+It also verifies the explanation of the evolution of mimicry with punctuated equilibrium.
 \printglossaries
 \phantomsection \label{acronyms}
-
 \end{document}

### 2016-06-09 docs/poster/poster.tex
Poster initial commit

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a0,portrait]{a0poster}

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

\usepackage{graphicx} % Required for including images
\graphicspath{{figures/}} % Location of the graphics files
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures

\begin{document}

%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into two boxes:
% The first is 75% wide and houses the title, subtitle, names, university/organization and contact information
% The second is 25% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit

\begin{minipage}[b]{0.75\linewidth}
\veryHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\\\ % Title
\huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
\huge Engineering \& Computer Science, Concordia University\\[0.4cm] % University/organization
\Large \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\includegraphics[width=20cm]{logo.jpg}\\
\end{minipage}

\vspace{1cm} % A bit of extra whitespace between the header and poster content

%----------------------------------------------------------------------------------------

\begin{multicols}{2} % This is how many columns your poster will be broken into, a portrait poster is generally split into 2 columns

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\color{Navy} % Navy color for the abstract

\begin{abstract}

A novel agent based, artificial life model, for the evolution of mimicry is presented. This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network. A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations. These agents are classified into categories of predator and prey species. Genome of prey species control their mobility and palatability, while 2D CA is used to represent a pattern, where the rule to generate the CA is also genetically represented. Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators. Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry. They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability. Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved. Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.

\end{abstract}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the introduction

\section*{Introduction}

Mimicry is a process of deception. It is an evolutionary process with the help of which organisms survive by deceiving its predator. But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable. Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species. The objective of this paper is to present an agent based artificial life model for simulating this natural process of the evolution of mimicry.

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content

%----------------------------------------------------------------------------------------
%	The Inspiration: Mimicry
%----------------------------------------------------------------------------------------

\section*{The Inspiration: Mimicry}
\subsection*{Batesian Mimicry}
Henry W. Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies. He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families. Even though Heliconiids are conspicuously colored, they are extremely abundant. They are also slow in mobility. Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature. Other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection. In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.

\begin{center}\vspace{1cm}
\includegraphics[width=0.5\linewidth]{Batesplate_ArM.jpg}
\captionof{figure}{\color{Green} Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row)}
\end{center}\vspace{1cm}

\subsection*{Mullerian Mimicry}
Bates was not able to explain some phenomena of mimicry. Occasionally two inedible unrelated butterfly species are amazingly similar in appearance. An explanation for this was provided by Fritz Muller in 1878. When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid. Because of the predator's limited memory, all these species still lose their number even after being inedible. So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different families also tend to evolve to have similar appearance. This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller. Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.

\section*{The Model: Evolution of Mimicry}

Our model initializes with three kinds of agents. These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}. We represent evolution of pattern for the model and the mimic with the help of \textbf{CA}, as \textbf{CA} can be easily represented by simple rules. Each predator is equipped with a Hopfield network, which gives it pattern recognition capability. The process of evolution occurs at the genetic level.

\begin{center}\vspace{1cm}
\includegraphics[width=0.1\linewidth]{CARule30-large.jpg}
\captionof{figure}{\color{Green} Cellular Automata Rule 30}
\end{center}\vspace{1cm}

This model has been designed to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo.

\begin{center}\vspace{1cm}
\includegraphics[width=0.5\linewidth]{simTime7600.jpg}
\captionof{figure}{\color{Green} Graphical representation of the model, simulation time: 7600}
\end{center}\vspace{1cm}

\section*{The Results}

Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place. This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species. Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.

\subsection*{Initial configuration with two prey species}

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{simTime10k-2Prey.png}
\captionof{figure}{\color{Green} Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
\end{center}\vspace{1cm}

\subsection*{Initial configuration with only unpalatable species}

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{simTime8k-4Prey-unp.png}
\captionof{figure}{\color{Green} Population distribution of mimicry rings, initialized with 4 prey species all unpalatable}
\end{center}\vspace{1cm}

\subsection*{Analysis}
\begin{itemize}
\item Batesian mimicry has taken effect as it can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
\item Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species. We initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance. 
\end{itemize}
%----------------------------------------------------------------------------------------
%	CONCLUSIONS
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out

\section*{Conclusions}
\begin{itemize}
\item Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry.
\item This model provides a more accurate simulation of the fascinating natural process of mimicry rings and their shift in population. 
\item This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
\end{itemize}

\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

%----------------------------------------------------------------------------------------

\end{multicols}
\end{document}

### 2016-06-28 docs/poster/poster.tex
Poster and Slides

@@
 
-\documentclass[a0,portrait]{a0poster}
+\documentclass[a0,landscape]{a0poster}
+\usepackage[paperwidth=93in, paperheight=36in, textwidth=87in, textheight=30in, scale=2]{geometry}
 
@@
 \graphicspath{{figures/}} % Location of the graphics files
+
+\usepackage{multirow}
+%Middle allignment in tables.
+\usepackage{array}
+
 \usepackage{booktabs} % Top and bottom rules for table
@@
 \usepackage{wrapfig} % Allows wrapping text around tables and figures
+\usepackage{natbib}
+\usepackage{fancytikzposter}
 
@@
 
-% The header is divided into two boxes:
-% The first is 75% wide and houses the title, subtitle, names, university/organization and contact information
-% The second is 25% wide and houses a logo for your university/organization or a photo of you
-% The widths of these boxes can be easily edited to accommodate your content as you see fit
-
-\begin{minipage}[b]{0.75\linewidth}
-\veryHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\\\ % Title
-\huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
-\huge Engineering \& Computer Science, Concordia University\\[0.4cm] % University/organization
-\Large \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
+\begin{minipage}[b]{0.85\linewidth}
+\VERYHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\[0.5cm] % Title
+\Huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
+\Huge Engineering \& Computer Science, Concordia University\\[0.5cm] % University/organization
+\huge \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
 \end{minipage}
 %
-\begin{minipage}[b]{0.25\linewidth}
-\includegraphics[width=20cm]{logo.jpg}\\
+\begin{minipage}[b]{0.19\linewidth}
+\includegraphics[width=30cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
 \end{minipage}
@@
 
-\begin{multicols}{2} % This is how many columns your poster will be broken into, a portrait poster is generally split into 2 columns
+\begin{multicols}{5} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more
+
+\tikz[remember picture,overlay,opacity=.1]{
+  \node at(current page.center){\includegraphics[height=\textheight]{monarch.jpg}};
+}
 
@@
 
-\begin{abstract}
+\section*{Abstract}
 
-A novel agent based, artificial life model, for the evolution of mimicry is presented.
-This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network.
-A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
-These agents are classified into categories of predator and prey species.
+\begin{itemize}
+	\item A novel agent based, artificial life model, for the evolution of mimicry is presented.
+	\item This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network.
+	\item A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
+	\item Agents are classified into categories of predator and prey species.
 Genome of prey species control their mobility and palatability, while 2D CA is used to represent a pattern, where the rule to generate the CA is also genetically represented.
-Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators.
-Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry.
-They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability.
-Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved.
+	\item Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved.
 Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
-
-\end{abstract}
+\end{itemize}
 
@@
 
-\color{SaddleBrown} % SaddleBrown color for the introduction
-
-\section*{Introduction}
-
-Mimicry is a process of deception.
-It is an evolutionary process with the help of which organisms survive by deceiving its predator.
-But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable.
-Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species.
-The objective of this paper is to present an agent based artificial life model for simulating this natural process of the evolution of mimicry.
-
-\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
+\color{SaddleBrown}
 
@@
 \subsection*{Batesian Mimicry}
-Henry W.
-Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies.
-He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families.
-Even though Heliconiids are conspicuously colored, they are extremely abundant.
-They are also slow in mobility.
-Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature.
-Other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.
-In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.
 
 \begin{center}\vspace{1cm}
-\includegraphics[width=0.5\linewidth]{Batesplate_ArM.jpg}
+\includegraphics[width=0.5\linewidth]{Batesplate_ArM.png}
 \captionof{figure}{\color{Green} Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row)}
@@
 
+\begin{itemize}
+	\item Henry W. Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies.
+	\item He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families.
+	\item Even though Heliconiids are conspicuously colored, they are extremely abundant and slow in mobility.
+Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature.
+	\item Other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.
+	\item In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.
+\end{itemize}
+
+\color{DarkSlateGray}
 \subsection*{Mullerian Mimicry}
-Bates was not able to explain some phenomena of mimicry.
-Occasionally two inedible unrelated butterfly species are amazingly similar in appearance.
-An explanation for this was provided by Fritz Muller in 1878.
-When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
-Because of the predator's limited memory, all these species still lose their number even after being inedible.
-So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different families also tend to evolve to have similar appearance.
-This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.
+\begin{itemize}
+	\item Occasionally two inedible unrelated butterfly species are amazingly similar in appearance. An explanation for this was provided by Fritz Muller in 1878. 
+	\item When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid.
+	\item Because of the predator's limited memory, all these species still lose their number even after being inedible. 
+	\item So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different families also tend to evolve to have similar appearance. 
+	\item This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.
 Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.
+\end{itemize}
 
+\color{SaddleBrown} 
 \section*{The Model: Evolution of Mimicry}
 
-Our model initializes with three kinds of agents.
-These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
-We represent evolution of pattern for the model and the mimic with the help of \textbf{CA}, as \textbf{CA} can be easily represented by simple rules.
-Each predator is equipped with a Hopfield network, which gives it pattern recognition capability.
-The process of evolution occurs at the genetic level.
+\begin{itemize}
+	\item Our model initializes with three kinds of agents. These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator}.
+	\item We represent evolution of pattern for the model and the mimic with the help of \textbf{CA}, as \textbf{CA} can be easily represented by simple rules.
+	\item Each predator is equipped with a Hopfield network, which gives it pattern recognition capability. The process of evolution occurs at the genetic level.
+\end{itemize}
+
+\color{DarkSlateGray}
+\subsection*{The Prey: Models and Mimics}
+
+\begin{itemize}
+	\item Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state.
+	\item With this pattern the predator will identify the prey and store its level of palatability in memory. 
+	\item We choose CA as it can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied. 
+	\item In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'. 
+	\item To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
+\end{itemize}
 
 \begin{center}\vspace{1cm}
-\includegraphics[width=0.1\linewidth]{CARule30-large.jpg}
+\includegraphics[width=0.1\linewidth]{CARule30-large.png}
 \captionof{figure}{\color{Green} Cellular Automata Rule 30}
+\label{fig:cellular-automata-rule-30}
 \end{center}\vspace{1cm}
 
-This model has been designed to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}.
-Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results.
-This model can also be considered as a complex adaptive system similar to Holland's work on Echo.
+\color{SaddleBrown} 
+\subsubsection*{Reflection of punctuated equilibrium}
+\label{subsubsec:reflection-of-punctuated-equilibrium}
+
+\begin{itemize}
+	\item Punctuated equilibrium is more inclined to cladogenesis instead of gradualism.
+Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
+	\item The design of the model also follows Turner's explanation in terms of evolving mimicry.
+As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
+\end{itemize}
+
+\color{SaddleBrown} 
+\subsection*{Predator}
+
+\begin{itemize}
+	\item Predators in the system are designed to provide selection pressure to \textit{models} and \textit{mimics} for the evolution of mimicry. 
+	\item These agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species.
+	\item Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as we could not find a suitable encoding for the genetic representation of Hopfield Network.
+	\item Every new predator is born with zero memory and with no inheritance from parents.
+\end{itemize}
+
+\color{DarkSlateGray}
+\subsubsection*{Learning}
+
+\begin{itemize}
+	\item The objective of a predator's interaction with prey is always to consume it.
+But based on the prey's pattern and palatability, the predator will either be able to consume it or throw it back to the environment.
+	\item At this event the predator needs to learn the pattern with which the prey has been represented. The pattern represents palatability of the prey species, at least to the predator. 
+	\item Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one.
+	\item The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}, which represents a purely feed-forward, unsupervised learning. 
+\end{itemize}
 
 \begin{center}\vspace{1cm}
-\includegraphics[width=0.5\linewidth]{simTime7600.jpg}
+\includegraphics[width=0.5\linewidth]{simTime7600.png}
 \captionof{figure}{\color{Green} Graphical representation of the model, simulation time: 7600}
@@
 
+\color{DarkSlateGray}
 \section*{The Results}
 
-Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place.
-This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
-Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.
+\begin{itemize}
+	\item Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place.
+	\item This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species.
+	\item Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.
+\end{itemize}
 
@@
 
+\color{SaddleBrown} 
 \subsection*{Analysis}
@@
 %----------------------------------------------------------------------------------------
-
-\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out
-
+\color{DarkSlateGray}
 \section*{Conclusions}
@@
 
-\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content
+ % Set the color back to DarkSlateGray for the rest of the content
 
@@
 %----------------------------------------------------------------------------------------
-
-\nocite{*} % Print all references regardless of whether they were cited in the poster or not
+\color{SaddleBrown} 
+%\nocite{*} % Print all references regardless of whether they were cited in the poster or not
 \bibliographystyle{plain} % Plain referencing style
-\bibliography{sample} % Use the example bibliography file sample.bib
+\bibliography{references} % Use the example bibliography file sample.bib
 

### 2016-06-29 docs/poster/poster.tex
Poster update

@@
 
-\tikz[remember picture,overlay,opacity=.1]{
-  \node at(current page.center){\includegraphics[height=\textheight]{monarch.jpg}};
+\tikz[remember picture,overlay,opacity=.3]{
+  \node at(current page.center){\includegraphics[width=\textwidth]{butterflies-mobile.jpg}};
 }
@@
 	\item A novel agent based, artificial life model, for the evolution of mimicry is presented.
-	\item This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA), while behaviors of pattern recognition is configured with Hopfield Network.
-	\item A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations.
+	\item This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata (CA) \citep{Wolfram2002}, while behaviors of pattern recognition is configured with Hopfield Network.
+	\item A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations \citep{grogono2003}.
 	\item Agents are classified into categories of predator and prey species.
@@
 	\item This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller. 
-Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.
+	\item Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage.
 \end{itemize}
@@
 
+\begin{center}\vspace{1cm}
+\includegraphics[width=0.50\linewidth]{CA_rule30s.png}
+\captionof{figure}{\color{Green} Cellular Automata Rule 30 (Image Credit: Wikipedia)}
+\label{fig:cellular-automata-rule-30}
+\end{center}\vspace{1cm}
+
 \color{DarkSlateGray}
@@
 	\item With this pattern the predator will identify the prey and store its level of palatability in memory. 
-	\item We choose CA as it can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied. 
-	\item In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'. 
+	\item We choose CA as its decimal rule can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
 	\item To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
 \end{itemize}
-
-\begin{center}\vspace{1cm}
-\includegraphics[width=0.1\linewidth]{CARule30-large.png}
-\captionof{figure}{\color{Green} Cellular Automata Rule 30}
-\label{fig:cellular-automata-rule-30}
-\end{center}\vspace{1cm}
 
@@
 Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism.
-	\item The design of the model also follows Turner's explanation in terms of evolving mimicry.
-As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene.
+	\item The design of this model also follows Turner's explanation in terms of evolving mimicry.
+	\item New CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene. 
 \end{itemize}
+
+\begin{center}\vspace{1cm}
+\includegraphics[width=0.5\linewidth]{simTime7600.png}
+\captionof{figure}{\color{Green} Graphical representation of the model, simulation time: 7600}
+\end{center}\vspace{1cm}
 
@@
 
-\begin{center}\vspace{1cm}
-\includegraphics[width=0.5\linewidth]{simTime7600.png}
-\captionof{figure}{\color{Green} Graphical representation of the model, simulation time: 7600}
-\end{center}\vspace{1cm}
-
 \color{DarkSlateGray}
@@
 
-\subsection*{Initial configuration with two prey species}
-
 \begin{center}\vspace{1cm}
@@
 \captionof{figure}{\color{Green} Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
-\end{center}\vspace{1cm}
-
-\subsection*{Initial configuration with only unpalatable species}
-
-\begin{center}\vspace{1cm}
-\includegraphics[width=0.8\linewidth]{simTime8k-4Prey-unp.png}
-\captionof{figure}{\color{Green} Population distribution of mimicry rings, initialized with 4 prey species all unpalatable}
+\label{fig:2prey-species}
 \end{center}\vspace{1cm}
@@
 \begin{itemize}
-\item Batesian mimicry has taken effect as it can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
-\item Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species.
+\item Batesian mimicry has taken effect as it can be observed (figure \ref{fig:2prey-species}) that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart.
+\item Effects of Mullerian mimicry can also be observed best for the experiment initialized with only unpalatable prey species (figure \ref{fig:unpalatable-species}).
 We initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance.
 \end{itemize}
+
+\begin{center}\vspace{1cm}
+\includegraphics[width=0.8\linewidth]{simTime8k-4Prey-unp.png}
+\captionof{figure}{\color{Green} Population distribution of mimicry rings, initialized with 4 prey species all unpalatable}
+\label{fig:unpalatable-species}
+\end{center}\vspace{1cm}
+
 %----------------------------------------------------------------------------------------

### 2016-06-29 docs/poster/poster.tex
Poster final version

@@
 
-\tikz[remember picture,overlay,opacity=.3]{
+\tikz[remember picture,overlay,opacity=.2]{
   \node at(current page.center){\includegraphics[width=\textwidth]{butterflies-mobile.jpg}};
@@
 	\item We choose CA as its decimal rule can be easily represented with the help of a binary genome and evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
-	\item To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
+	\item To store in Hopfield memory we take a linear representation of this 2-D pattern.
+	\item To find similarity between two patterns we calculate the hamming distance between their linear representations.
 \end{itemize}

### 2016-07-12 docs/slides_conference/mimicry.tex
Poster and Slides
Slide Update

--- 2011-01-14 docs/slides_shortened/mimicry.tex
@@
 
-\subsection{Evolutionary Dynamics}
-
-\frame
-{
-	\frametitle{Evolutionary Dynamics}
-	\framesubtitle{Punctuated Equilibrium}
-
-	Most sexually reproducing species remain:
-	\begin{itemize}
-		\item extended state of \textit{stasis}.
-		\item Little evolutionary change in most geological history.
-	\end{itemize}
-
-	Cladogenesis:
-	\begin{itemize}
-		\item Process of speciation.
-		\item One split into two distinct species.
-		\item In geological time:
-			\begin{itemize}
-				\item Discontinuous change
-				\item Not gradual transformation
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{Evolutionary Dynamics}
-	\framesubtitle{Phyletic Gradualism}
-
-	\begin{itemize}
-		\item Continued adaptation to new environmental and biological selection pressure.
-		\item Gradually becoming new species.
-	\end{itemize}
-
-	Phyletic gradualism holds,
-	\begin{itemize}
-		\item Species population changes gradually.
-		\item No clear demarcation between ancestral and descendant species.
-		\item Gradually changing lineage is divided arbitrarily.
-		\item Evolution is 
-			\begin{itemize}
-				\item smooth
-				\item steady
-				\item incremental
-				\item but not necessary constant and slow rate in geological time scale.
-			\end{itemize}
-	\end{itemize}
-}
-
 \frame

### 2016-07-12 docs/slides_conference/model.tex
Poster and Slides
Slide Update

--- 2011-01-14 docs/slides_shortened/model.tex
@@
 
-\subsection{Past Work}
-
-\frame
-{
-	\frametitle{The Model}
-	\framesubtitle{Past Work}
-
-	\begin{itemize}
-		\item Turner (1996) and Huheey (1988):
-			\begin{itemize}
-				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
-				\item Predator: Simple Monte Carlo learning or mathematical approach.
-			\end{itemize}
-		\item Sherratt (2002):
-			\begin{itemize}
-				\item Co-evolving predator and prey population.
-				\item Predators:
-				\begin{itemize}
-					\item deterministic
-					\item cannot learn from experience.
-					\item attack policy is fixed, either attack or avoid.
-				\end{itemize}
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{Franks and Noble}
-	\framesubtitle{Working hypothesis}
-
-	\begin{enumerate}
-		\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
-		\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
-	\end{enumerate}
-}
-
-\frame
-{
-	\frametitle{Franks and Noble}
-	\framesubtitle{Prey and Predator}
-
-\begin{itemize}
-	\item Prey:
-		\begin{itemize}
-			\item Appearance and palatability.
-			\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
-			\item Two genes representing external appearance, using values between 1 to 200.
-			\item Euclidean distance between values represents similarity.
-		\end{itemize}	
-	\item Predator:
-		\begin{itemize}
-			\item Monte Carlo reinforcement learning system.
-			\item Decision for consumption of prey:
-			\begin{itemize}
-				\item Use: set of probability formula.
-				\item Dependence on phenotype.
-			\end{itemize}
-		\end{itemize}
-\end{itemize}
-
-}
-
-\frame
-{
-	\frametitle{Franks and Noble}
-	\framesubtitle{Result}
-
-	\begin{itemize}
-		\item Hypothesis 1 of a single large ring did was not established.
-		\item Hypothesis 2 is established.
-		\item \textbf{Observation:}
-			\begin{itemize}
-				\item Batesian mimics provide pressure on mutants.
-				\item Batesian pressure on mimicry rings push one into the range of another.
-			\end{itemize}
-	\end{itemize}
-}
-
 \subsection{FormAL}
@@
 	\frametitle{FormAL Framework}
-	\framesubtitle{Environment}
-
-	Environment is 3D, complete freedom of movement defined from genetic representation.
-	\begin{itemize}
-		\item \textbf{Space:}
-			\begin{itemize}
-				\item 3D Lattice of discreet points.
-				\item \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\).
-				\item \(S\) is a universal constant, small positive number. Value is 20, \(World Size\) parameter. 
-			\end{itemize}
-		\item \textbf{Time:}
-			\begin{itemize}
-				\item Integer value, increases in discreet steps. 
-				\item Each agent updates itself in each time step.
-			\end{itemize}
-		\item \textbf{Cell:}
-			\begin{itemize}
-				\item Entire environment is divided into multiple cells.
-				\item A 3D cubical section of the hyperspace.
-				\item \(ISize\) parameter kept at 6. Total \(ISize^3 = 216\) cells.
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
 	\framesubtitle{Environment - Visual representation - Front}
@@
 	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{FormAL Framework}
-	\framesubtitle{Agent Mobility}
-
-	\begin{itemize}
-		\item Position is calculated in each step in time.
-		\item Vector components: \(position\), \(force\), \(acceleration\) and \(velocity\).
-		\item \(force\) is calculated from the mobility genes.
-		\item Newton's law of motion, used to calculate \(acceleration\) when \(force\) is not zero.
-		\item \(acceleration\) is integrated to obtain \(velocity\) and new \(position\).
-	\end{itemize}
-
 }
@@
 
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Mobility}
-
-	\begin{itemize}
-		\item Mobility gene: 6 bits. 
-		\item Use: calculate the magnitude of force for mobility.
-		\item Direction:
-			\begin{itemize}
-				\item Towards collection of maximum prey species in a cell.
-				\item Away from concentration of predators.
-				\item Move towards the selected cell with the magnitude of force calculated.
-			\end{itemize}
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Prey: Mimics and Models}
-	\framesubtitle{Reproduction}
-
-	\begin{itemize}
-		\item Begins at ``Reproductive Age"
-		\item Capability is decided on 17th bit gene.
-		\item Mate selection is random, but within same cell.
-		\item Mate needs to be
-			\begin{itemize}
-				\item similar species
-				\item genetically capable to reproduce
-				\item reached maturity 
-			\end{itemize}
-		\item Reproduction process:
-			\begin{itemize}
-				\item Single point crossover.
-				\item Two point mutation: different rates
-					\begin{itemize}
-						\item \textit{Pattern Mutation Rate}
-						\item \textit{Genome Mutation Rate}
-					\end{itemize}
-			\end{itemize}
-	\end{itemize}
-}
-
 \subsection{Predator}
@@
 }
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Genome}
-
-	\begin{table}
-	\centering
-	\begin{scriptsize}
-	\begin{spacing}{1.5}
-	\begin{tabular}{|c|c|}
-		\hline
-			\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
-					 1101					   &					1						 		\\ \hline
-	\end{tabular}
-	\end{spacing}
-	\end{scriptsize}
-	\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
-	\label{tab:predator-genome}
-	\end{table}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Mobility}
-
-	\begin{itemize}
-		\item Magnitude of force of movement: 4 bits of genome.
-		\item Direction: number of prey species present in a neighboring cell.
-		\item Move towards the cell with least number of predator and most number of prey.
-		\item Result: Predators are distributed all over the environment.
-		\item Increases agent's predatory behavior.
-	\end{itemize}
-}
-
-\frame
-{
-	\frametitle{The Predator}
-	\framesubtitle{Reproduction process}
-
-	\begin{itemize}
-		\item Reproduction age: begins.
-		\item Reproduction age interval: which is difference in time between two reproduction activity.
-		\item Capability: 5th gene.
-		\item Selection: another predator from same cell which satisfy above conditions.
-		\item Perform genome crossover and mutation: create new predator.
-		\item New predator initialized with zero memory.
-	\end{itemize}
-}

### 2016-07-12 docs/slides_conference/result.tex
Poster and Slides
Slide Update

--- 2011-01-14 docs/slides_shortened/result.tex
@@
 
-\frame
-{
-	\frametitle{Two Prey Species}
-	\framesubtitle{Population vs. Time (5k)}
-
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime5k-2Prey}
-		\caption{Population distribution of mimicry rings (2 prey species, 5k iterations)}
-		\label{fig:plot-2-prey-5k}
-	\end{figure}
-}
-
-\frame
-{
-	\frametitle{Two Prey Species}
-	\framesubtitle{Number of Mimicry Rings}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.30]{../tex/images/ringSize10k-2Prey}
-		\caption{Number of mimicry rings, initialized with 2 prey species.}
-		\label{fig:ringSize10k-2Prey}
-	\end{figure}	
-}
-
-\frame
-{
-	\frametitle{Generated Prey Species}
-	\framesubtitle{Population vs. Time (10k)}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime10k-2Prey-generated-prey}
-		\caption{Population distribution of generated mimicry rings (2 prey species)}
-		\label{fig:plot-2-prey-generated-prey}
-	\end{figure}
-}
-
-%-----------------------------
-%----- Four Prey Species ------
-%-----------------------------
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Increased Population}
-
-	\begin{table}[H]
-	\centering
-	\begin{tiny}
-	\begin{spacing}{1.5}	
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{\multirow{4}{*}{\textbf{20 \(\uparrow\)}}} \\ \cline{2-4}
-	  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  	 & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}  & \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& \textbf{150 \(\uparrow\)} & \multicolumn{2}{c|}{}\\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{\textbf{2500 \(\uparrow\)}} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{\textbf{7000 \(\uparrow\)}} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{spacing}	
-	\end{tiny}
-	\caption{Agent configuration of 4 prey species with increased population}
-	\label{tab:config-table-4-more-prey}
-	\end{table}
-
-}
-
-\frame
-{
-	\frametitle{Four Prey Species}
-	\framesubtitle{Increased Population\\ Population vs. Time (10k)}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.25]{../tex/images/simTime10K-4MorePrey}
-		\caption{Population distribution of mimicry rings (4 prey species, increased population)}
-		\label{fig:plot-4-more-prey}
-	\end{figure}	
-}
-
 %-----------------------------
@@
 
-%-----------------------------
-%----- Palatable Species ------
-%-----------------------------
-\frame
-{
-	\frametitle{Only Palatable Species}
-	\framesubtitle{Initial Configuration}
-
-	\begin{table}[H]
-	\centering
-	\begin{spacing}{1.5}
-	\begin{tiny}
-	\begin{tabular}{|l|l|c|c|l|c|}
-	  \hline
-	   														&\multicolumn{3}{c|}{Prey configuration} 																	
-	   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
-	  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule110}} 
-	  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-	  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule30}}  
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule55}}    
-	  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-	  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.30]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
-	  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
-	  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
-	  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
-	  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
-	  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
-	  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-	  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
-	   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
-	\end{tabular}
-	\end{tiny}
-	\end{spacing}
-	\caption{Agent configuration of 4 prey species all palatable.}
-	\label{tab:config-table-4-prey-palatable}
-	\end{table}
-
-}
-
-\frame
-{
-	\frametitle{Only Palatable Species}
-	\framesubtitle{Population vs. Time (7k)}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.25]{../tex/images/simTime10k-4Prey-p}
-	\caption{Population distribution of mimicry rings (4 prey species all palatable)}
-	\label{fig:plot-4-prey-p}
-\end{figure}
-}
-
-\frame
-{
-	\frametitle{Only Palatable Species}
-	\framesubtitle{Number of Mimicry Rings}
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[scale=0.3]{../tex/images/ringSize10k-4Prey-p}
-		\caption{Number of mimicry rings (4 prey species all palatable)}
-		\label{fig:ringSize8k-4-Prey-p}
-	\end{figure}
-}
-
 \subsection{Analysis}

### 2016-07-13 docs/poster - smaller/poster.tex
Poster smaller

--- 2016-06-29 docs/poster/poster.tex
@@
 
-\documentclass[a0,landscape]{a0poster}
-\usepackage[paperwidth=93in, paperheight=36in, textwidth=87in, textheight=30in, scale=2]{geometry}
+\documentclass[a0,portrait]{a0poster}
+\usepackage[paperwidth=36in, paperheight=59in, textwidth=30in, textheight=53in, scale=2]{geometry}
 
@@
 \begin{minipage}[b]{0.85\linewidth}
-\VERYHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\[0.5cm] % Title
-\Huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
-\Huge Engineering \& Computer Science, Concordia University\\[0.5cm] % University/organization
-\huge \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
+\veryHuge \color{NavyBlue} \textbf{Modeling the Evolution of Mimicry} \color{Black}\\[0.5cm] % Title
+\huge \textbf{Mohiul Islam \& Peter Grogono}\\[0.5cm] % Author(s)
+\huge Engineering \& Computer Science, Concordia University\\[0.5cm] % University/organization
+\large \texttt{moh\_i@encs.concordia.ca \& grogono@cse.concordia.ca}\\
 \end{minipage}
@@
 \begin{minipage}[b]{0.19\linewidth}
-\includegraphics[width=30cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
+\includegraphics[width=20cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
 \end{minipage}
@@
 
-\begin{multicols}{5} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more
+\begin{multicols}{2} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more
 

### 2016-07-13 docs/journal-paper/Paper.tex
Journal paper

\documentclass[letterpaper]{article}
\usepackage{natbib}
%\usepackage{natbib}
%Graphics package
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.jpg,.pdf}
%For multirow feature to draw tables
\usepackage{multirow}
%Middle allignment in tables.
\usepackage{array}
%For Mathematics
\usepackage{amsmath}
\numberwithin{equation}{section}
%Float package used to specify positioning
\usepackage{float}
%Depth of upto four in sections.
%\setcounter{secnumdepth}{3}
\usepackage{algorithmic}
\usepackage{algorithm}

%For hyper referencing
\usepackage[colorlinks={true},linkcolor={black},citecolor={black},urlcolor={black}]{hyperref}
%In case you use the package hyperref to create a PDF, the links to tables or figures will point to the caption of the table or figure, which is always below the table or figure itself. Therefore the table or figure will not be visible, if it is above the pointer and one has to scroll up in order to see it. If you want the link point to the top of the image you can use the package hypcap with:
\usepackage[all]{hypcap}

\usepackage[acronym]{glossaries}
\makeglossaries
\input{acronym}

\title{Modeling the Evolution of Mimicry}
\author{Mohiul Islam$^{1}$ \and Peter Grogono$^{1}$ \\
\mbox{}\\
$^1$Concordia University  \\
moh\_i@encs.concordia.ca \\
grogono@cse.concordia.ca}

\begin{document}
\maketitle

\begin{abstract}
A novel agent based, artificial life model, for the evolution of mimicry is presented. This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network. A visual three dimensional toroidal cube is used to construct a universe in which agents have complete freedom of mobility, genetic representation of behavior and reproduction capability to evolve new behaviors in successive generations. These agents are classified into categories of predator and prey species. Genome of prey species control their mobility and palatability, while 2D Cellular Automata (CA) is used to represent a pattern, where the rule to generate the CA is also genetically represented. Through evolution, successive generations of prey species develop new patterns to represent them both visually and to the predators. Predators are agents with the primary purpose of providing selection pressure for the evolution of mimicry. They are equipped with Hopfield Network memory to recognize new CA pattern and make intelligent decisions to consume the prey based on their level of palatability. Using the above construction of ideas, successful emulation of the natural process of mimicry is achieved. Also complex behavior pattern of Batesian and Mullerian mimicry is simulated and studied.
\end{abstract}

%Introductory Section
\section{Introduction}
\label{section:introduction}

%A few paragraphs are required to bring an appropriate introduction.
Mimicry is a process of deception. It is an evolutionary process with the help of which organisms survive by deceiving its predator. But this deception happens only if the environment contains similar appearing noxious organisms which the predators find unpalatable. Palatable organisms mimic the unpalatable ones through the process of evolution for survival of its species. The objective of this paper is to present an agent based artificial life model for simulating the natural process of the evolution of mimicry.

According to Langton, Artificial Life is `\textsl{Life made by Man rather than by Nature'}. Taylor also defines it as a tool for biological inquiry \citep{taylor1993}. While providing a brief survey over different AL models he talks about \textsl{Wetware systems} which work at the molecular level, the \textsl{Software systems} which work at the cellular level and the \textsl{Hardware systems} which works at the organism level. The initial contribution of \textsl{software systems} in artificial life was from John von Neumann when he designed the first artificial-life model (without referring to it as such), the famous self-reproducing, computation-universal cellular automata \citep{neumann1966}. He tried to understand the fundamental properties of living systems, especially self-reproduction and the evolution of complex adaptive structures, by constructing simple formal systems that exhibit those properties.

Being a special case of complex systems, \gls{cas} are diverse and made up of multiple interconnected elements and adaptive as they have the capacity to change and learn from experience. Echo is a class of simulation model for complex adaptive system, designed primarily for gedanken experiments rather than precise simulations. Echo provides a population of evolving, reproducing agents distributed over a geography, with different inputs of renewable resources at various sites. Each agent has simple capabilities - offense, defense, trading and mate selection - defined by a set of chromosomes. Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described by Holland \citep{holland1996}.

In developing Echo using Holland's criterion, a step by step approach has been taken. Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, and having a good resemblance with natural ecosystem. It has stable patterns of interactions among genetic variants, or trophic networks. It consists of different levels of resources along with relative species abundance. Even different cataclysmic events such as meteor, drought and so fourth are introduced. Also several isolation effects are observed where a number of sites are allowed to evolve independently. In addition to that Echo contains interesting flow of resources.

Two separate experiments were done to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo. To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature. The objective is to compare these naturally occurring ecosystems with Echo. The ecological patterns are the Preston  curve and the species-area scaling relation. This allowed comparison of Echo diversity patterns with empirical patterns of species abundance. As result of the comparison Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.

\section{The Inspiration: Mimicry}
\label{section:mimicry}

Henry W. Bates first published in 1862 his findings about the similarities and dissimilarities between Heliconiinae and Ithomiinae butterflies, after 10 years of research in the Brazilian rain forest. For the next hundred years, it simulated heated discussion among all groups of people, scientists, philosophers, theologians, teachers and amateur naturalists. Bates collected ninety-four pieces of butterfly. He grouped them according to their similar appearance. He found butterflies having similar appearance, exhibiting morphological features which point to completely different species even families. Out of the ninety four species, sixty seven are now classified as Ithomiinae, while twenty seven of them are Heliconiinae.

\subsection{Batesian Mimicry}
Even though Heliconiids are conspicuously colored, they are extremely abundant. They are also slow in mobility. Still predators in the surrounding area, mostly insectivorous birds do not prey on them, because of their inedible and unpalatable nature. Also because of this phenomenon other edible and palatable species such as ithomiinae and pieridae, pretend to be heliconiids and thus enjoy protection.

Repulsive animals, such as heliconiids are very conspicuously colored. Having this noticeable property, they are easily recalled by predators. Their wing pattern works as a warning to predators. Once a predator has the knowledge of their inedible and unpalatable property, they would probably never attempt to try it again. As this is true, if any organism within close family and species, but being edible and having a deceptive resemblance to those conspicuously colored species will be avoided by the predators. Wickler \citep{wickler1986} expresses,
\begin{quote}
\textsl{``Such unpalatable appearing and yet edible animals thus possess a false warning pattern, they `act a part'. An actor is a mime, and so the representation of a false warning pattern was called \textit{mimicry}. Since Bates was the first to point out this phenomenon, it has received the name \textit{Batesian Mimicry} in his honor."}
\end{quote}
In general, the animal which is avoided by predator for unpalatable behavior is called the \textbf{model} and the imitating animal is called the \textbf{mimic}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \citep{bates1862}}
	\label{fig:batesian-butterfly}
\end{figure}

\subsection{Mullerian Mimicry}
\label{subsec:mullerian-mimicry}
Bates was not able to explain some phenomena of mimicry. Occasionally two inedible unrelated butterfly species are amazingly similar in appearance. An explanation for this was provided by Fritz Muller in 1878. Like Bates, Muller observed and caught butterflies in Brazil. When there are multiple inedible species it is hard for predators to recognize each of them to know which one to consume and which one to avoid. Because of predator's limited memory, all these species still lose their number even after being inedible. So to save this loss, and to prevent more sacrifice of their own kind, inedible species from different family also tend to evolve to have similar appearance. This phenomena is referred to as Mullerian Mimicry in the name of Fritz Muller.

\subsection{Evolutionary Dynamics of Mimicry}
\label{subsec:evolutionary-dynamics-of-mimicry}
The dynamics of mimicry has been investigated by Turner \citep{turner1988}, where he states that the evolution of mimicry can be explained best by the process of punctuated equilibrium instead of phyletic gradualism.

\paragraph{Punctuated Equilibrium}
In evolutionary biology, punctuated equilibrium is the theory which proposes that most sexually reproducing species will remain in an extended state called \textit{stasis} while experiencing little evolutionary change for most of their geological history. When evolution occurs it is localized in rare, rapid events of branching speciation, called cladogenesis. Cladogenesis is the process by which species split into two distinct species, rather than one species gradually transforming into another. Thus, \textsl{``punctuated equilibria is a model for discontinuous tempos of change (in) the process of speciation and the deployment of species in geological time" \citep{gould1977}}.

\paragraph{Phyletic Gradualism}
In contrast to punctuated equilibrium, phyletic gradualism states that species continue to adapt to new environmental and biological selection pressures over the course of their history, gradually becoming new species. Phyletic gradualism holds that a species population changes gradually; that is there is no clear line of demarcation between an ancestral species and a descendant species unless a splitting (cladogenetic) event occurs or the gradually-changing lineage is divided arbitrarily. During this process, evolution occurs at a smooth, steady and incremental (but not necessarily constant and slow) rate on a geological time scale.

To explain the dynamic evolutionary process of mimicry, Turner came up with a synthetic theory \citep{turner1988}, which was originated by Poulton \citep{poulton1912} and Nicholson \citep{nicholson1927}, termed as the \textbf{two stage model}. This theory states that mimicry normally arises in two steps. A comparative large mutation achieves a good approximate resemblance to the model; it is followed by gradual evolutionary changes that refine the resemblance, in many cases to a high degree of perfection \citep{sheppard1972} \citep{ford1964}. This two-stage theory has been applied for the explanation of Mullerian mimicry as well.

\subsubsection{Mimicry Ring}
Any theory of Mullerian mimicry has to take into account the phenomenon of the coexistence of multiple mimicry rings. If we examine the local butterfly fauna in any area of the world, we will find that between all the aposomatic (warningly colored and defended) species present there are normally only a limited number of different patterns, normally far smaller than the number of species. Each cluster of species, all sharing a common pattern, is termed as Mullerian mimicry ring. Thus, in the rain forest of South and Central America, most of the long-winged butterflies (ithomiids, danaids, and heliconids) belong to one of only five different rings.

Like Batesian mimicry, Mullerian mimicry can evolve in two stages: the mutational, one way convergence stage followed by the gradual, mutual convergence stage. It is worth mentioning that in the first stage only the less protected species can adopt the pattern of the better protected species; mutations in the other direction is not favored.

Mimicry is one of the most fascinating cases of evolutionary biology. This phenomenon has been studied extensively as infinite number of evidence exists in nature. One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it. And this figure is more than 40 years old as it has been taken from Wilcker \citep{wickler1986}, published in 1968. It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless. Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \citep{cott1957}.

%Chapter describing the model
\section{The Model: Evolution of Mimicry}
\label{section:model}

The agent based artificial life model for simulating the evolution of mimicry, presented in this paper has mainly two species of agents. These agents have properties and behavior similar to the \textbf{model}, the \textbf{mimic} and the \textbf{predator} in the evolution of mimicry. We represent evolution of pattern for the model and the mimic with the help of \gls{ca}. \gls{ca} can be easily represented by simple rules, which can be expressed as a binary string. The predator will be equipped with a Hopfield network \citep{hopfield1982}, to be able to have pattern recognition capability. The process of evolution will of course be running at the genetic level.

The choice of Hopfield Network memory for a predator can be considered appropriate as the number of patterns which can be recognized by this network is inversely proportional to the accuracy of recall. As more patterns are memorized, Hopfield network tends to make more errors. This behavior will be appropriate for the simulation of Mullerian mimicry. Mullerian mimicry happens because of limited memory of the predators. Because of this limited memory, multiple inedible butterflies seems to converge to a single ring.

The environment is designed as three dimensional, while the space will be of toroidal nature. This idea has been taken from the \textsl{Laws and Life} project by Peter Grogono \citep{grogono2003}.

\subsection{Past Work}
Various models of mimicry has been simulated and explored. The model by Turner \citep{turner1996} and the mathematical model of Huheey \citep{huheey1988} tend to focus on the selective pressure on prey brought about by the particular learning abilities of the predator, and employ simple Monte Carlo or mathematical approaches.

Sherratt \citep{sherratt2002} provides an innovative perspective on the evolution of warning signals by considering co-evolving predator and prey populations. The model's predators are deterministic, in that they have a fixed behavioral strategy over their lifetime, and cannot learn from experience. For both cryptic and conspicuous prey, each predator has fixed policy of either attacking or avoiding.

\subsubsection{Models by Franks and Noble}
\label{subsubsec:models-by-frank-and-noble}
The latest work on modeling evolution of warning signals and mimicry with individual based simulation is done by Franks and Noble. Their initial work \citep{franks2002} seems to focus on putting some conditions of mimetic evolution in an individual based model with multiple species preyed upon by a single abstract predator, where the appearance of each prey species can evolve but their palatability is fixed.

On 2003 \citep{franks2003} another model for the origin of mimicry ring has been proposed by Franks and Noble. This \textbf{second} model is based on two working hypothesis:

\begin{enumerate}
	\item \textsl{All of the Mullerian mimics in a given ecosystem should eventually converge into one large ring in order to gain maximum protection.}
	\item \textsl{If the Mullerian mimics do not converge into one large ring, then the presence of Batesian mimics could entice them to do so, by influencing the rings to converge.}
\end{enumerate}

Although there are many mathematical and stochastic models of mimicry in the biological literature, this model gives attention to the evolution of mimicry ring phenomenon from an artificial life perspective.

Franks and Noble continue to test the influence on mimicry ring evolution by Batesian mimics \citep{franks2004}. Usually mathematical models of mimicry has fixed prey coloration and appearances, which enables a comparison of predation rates to demonstrate the level of protection a mimic might be afforded. In this model prey colorations are free to evolve. This phenomenon is used to examine the effect of Batesian mimicry on Mullerian mimics and mimicry rings.

\subsection{FormAL Framework}
The \textsl{``FormAL framework"} is a collection of ideas and concepts taken from Peter Grogono's \gls{formal} project \citep{grogono2003} and are used to build a framework for modeling the evolution of mimicry. The primary goal of the FormAL project was ``\textit{To study the emergence of complexity}". While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}". We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.

\subsubsection{Agents}
In FormAL, an \textbf{Agent} is a simulated organism. It is designed simply, but with the following qualities:

\begin{itemize}
	\item It has behaviors to be able to reproduce itself using genetic information.
	\item Capable of modifying the structure of genome between generations.
	\item Able to interact with other agents.
	\item And also to survive and reproduce in a challenging environment.
\end{itemize}

\subsubsection{Spatial representation of the environment}
The framework consists of a three dimensional visual environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.

\paragraph{Space}
The space of the environment is a three-dimensional lattice of discrete points. The coordinate of each point in space is of the form \((x,y,z) \in \Sigma^3\), where \(\Sigma\) be the set \(\{0, 1, ..., S-1\}\). \(S\) is a universal constant being a small positive integer, which in this simulation has been kept at 20 (the value of the \(World Size\) parameter in table \ref{tab:environment-control-parameters}).

\paragraph{Time}
Time, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.

\paragraph{Cell}
The entire three dimensional toroidal environment is divided in multiple cells. A cell is a three dimensional cubical section of the hyperspace. Accordingly in table \ref{tab:environment-control-parameters} \(ISize\) is the parameter that controls the number of cells in the environment. The size of a cell is evaluated from the entire world size. And the total number of cell is calculated as \(ISize^3 = 216\).

\begin{table}[h]
\centering
\begin{tabular}{| p{1.5cm} | >{\centering} p{1.6cm} | p{4cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		ISize & 6 & Number of cell in single dimension of the 3-D toroidal cube\\ \hline
		World Size & 20 & Size of a single dimension of the 3-D toroidal cube\\ \hline
		Cell Size & \( World Size\) / \(ISize \) & Size of each cell\\ \hline
		Total Number of Cells & \( ISize^3  = 216\) & Total number of cells in the environment\\ 
	\hline
\end{tabular}
\caption{Parameters to control the environment.}
\label{tab:environment-control-parameters}
\end{table}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/cells-front}
	\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
	\label{tab:3-d-environment-images}
\end{figure}

\subsubsection{Mobility}
An agent's position is calculated once during each step of update in time. The agents \(position\), \(force\), \(acceleration\) and \(velocity\) are all vector components. The \(force\) component is calculated from agent's mobility gene. And it is used to compute agent's \(acceleration\). If the \(force\) and \(velocity\) are both zero, then the agent has no effect in motion. Otherwise, Newton's law is used to obtain the \(acceleration\), which is integrated to obtain the new \(velocity\) and new \(position\).

\begin{algorithm}
	\caption{Algorithm for updating movement of the Agents}
	\label{algo:algorithm-movement-agents}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $accelaration \gets ForceFactor * force - Friction * velocity$
			\STATE $velocity \gets DT*accelaration$ \COMMENT{DT is considered as Differential Time Set}
			\STATE $deltaPos \gets DT*velocity$
			\STATE $position \gets position + deltaPos$
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
		Friction & 5 & The friction constant used for motion calculations.\\ \hline
		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
	\hline
\end{tabular}
\caption{Parameters to control mobility of agents.}
\label{tab:mobility-control-parameters}
\end{table}

Algorithm \ref{algo:algorithm-movement-agents} explains the calculation of mobility of each agent at each time step of the simulation, while table \ref{tab:mobility-control-parameters} contains the values of the parameters used to apply to this algorithm.

\subsection{The Prey: Models and Mimics}

Only the significant characteristics which are required for a successful model of mimicry is implemented. As for this simulation we are considering heliconius butterfly, the representation of their wing pattern is with the help of cellular automata. So basically every prey organism will contain a genetic representation of cellular automata with which the predator will identify the prey and store its level of palatability in memory.

%More content needs to be added for cellular automata.
\paragraph{Cellular Automata}

Cellular automata are computer generated patterns applying very simple rules. First invented by Jon von Neuman and later extended by Stephen Wolfram, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules. We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.

\subsubsection{Species diversity}
\label{subsubsec:species-diversity}
Franks and Noble have used different models to diversify species. In \citep{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity. Here the distance of one phenotype from another represents their level of similarity.

To use CA as prey pattern, an agent's genome is constructed as an 8 bit binary value with a decimal range between 0 to 255. Each of this 256 values have a unique CA pattern associated with it. When storing this pattern in Hopfield memory we take a linear representation of this 2-D pattern, while to consider similarity between two pattern we evaluate the hamming distance between their linear representation.

With CA based pattern representation, population of prey species with a specific CA pattern can be grouped as one single species. And by restricting inter species reproduction we can control the diversity of patterns. But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species. So that is why we have two separate mutation rate while reproducing prey species. One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}). Similar efforts of multiple mutation rate at varying location has been used in developing Echo \citep{hraber1997}.

\subsubsection{Genome}
The Genome of the prey species consists of 17 bits as presented in table \ref{tab:prey-genome}. The first eight bits represent the rule, which is used to generate Cellular Automata pattern. The next two bits are used to represent palatability of the organism. The next six bits is the magnitude of the force with which mobility of the organism is calculated. The 17th bit is used to evaluate reproduction capability of the organism, depending on which the prey species is either capable or not capable to participate in reproduction.

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{|c|c|c|c|}
	\hline
		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
\label{tab:prey-genome}
\end{table}

\subsubsection{Reflection of punctuated equilibrium}
\label{subsubsec:reflection-of-punctuated-equilibrium}
Punctuated equilibrium is more inclined to cladogenesis instead of gradualism. Also Turner \citep{turner1988} emphasizes on punctuated equilibrium to describe the evolution of mimicry instead of phyletic gradualism. The design of the model under discussion also follows Turner's explanation in terms of evolving mimicry. As it can be observed, new CA patterns evolve from existing ones in prey population just by a single mutation in the pattern gene. Mimics do not follow a gradual process of evolution to look close to models but rather the change happens randomly through a single step mutation. The mutations that are favored, helps the mimics to survive while the unfavored ones fail to persist. It can be observed later in table \ref{tab:diff-in-pattern} how CA patterns of prey species can have vastly different configuration for a unit change in their representative gene.

\subsubsection{Genetic representation of palatability}
\label{subsubsec:genetic-palatability-representation}
The palatability of each prey species is fixed and has been represented with 2 bits of the genome giving it a range of 0 to 3 with four levels of palatability. The combinations are as follows:

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|}
		\hline
			\textbf{Gene (Index 8 to 9)} &	\textbf{Palatable} \\ \hline
			00									& True 			\\ \hline
			01									& True 			\\ \hline
			10									& False 		\\ \hline
			11									& False 		\\
		\hline
	\end{tabular}
	\caption{Genetic representation of palatability}
	\label{tab:genetic-representation-palatability}
\end{table}

This representation in table \ref{tab:genetic-representation-palatability} is unlike Franks and Noble \citep{franks2003} where palatability level has been used on a scale between zero and one (least to most palatable), where 0.5 is neutrally palatable.

\subsubsection{Interaction between other Prey and Predators}
The prey have been defined to have many conglomerate behavior in the environment. Prey interaction with other prey species and with predators make the evolution of mimicry possible. Mobility of prey species and their reproduction capability are two important behaviors which result from interaction.

\paragraph{Mobility}
The mobility genes of the prey consist of 6 bits. These six bits are used to calculate the force with which each prey try to move towards any neighborhood cell. The algorithm sorts all neighboring cell descending to the number of prey species. Then it selects the cell which contains the highest number of prey with zero predator. If all the neighboring cells contain predators, then the algorithm sorts the neighboring cells descending on the number of predators and chooses the one which contains the least. Algorithm \ref{algo:algorithm-movement-prey} explains in detail.

\begin{algorithm}[h]
	\caption{Algorithm for updating position of the Prey species}
	\label{algo:algorithm-movement-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
			\STATE Get list of neighborhood cells, sorted by population of prey species.
			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\paragraph{Reproduction}
Every prey species starts reproducing when it reaches the \textsl{``Reproductive age limit"}. If it is capable of reproducing, which is decided based on its 17th bit gene, the prey will randomly select another prey species with similar pattern and palatability from the same cell and mate with it. Now the other prey also needs to be genetically capable of reproduction and needs to reach its age limit. A new genome is created from the existing genome of the two prey by applying single point crossover operation. Mutation is performed separately on the pattern gene and the rest of the genome, with two different rates to control them using the values in table \ref{tab:prey-control-parameters}. So there is two point mutation for the genome.

\begin{algorithm}[h]
	\caption{Algorithm for reproduction of the Prey species}
	\label{algo:algorithm-reproduction-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $capableToReproduce \gets$ true or false depending on the 17th bit of the genome, and maturity on reproduction age.
			\IF {$capableToReproduce == true$ and $currentCellPopulation > 1$ } 
				\STATE $anotherPrey \gets$ Select random prey from same cell.
				\IF {$anotherPrey$ is alive and $capableToReproduce$ and of similar $pattern$ and $palatability$}
					\STATE Perform genetic cross over and mutation to create new genome.
					\STATE Create new prey with new genome, and release into environment.
					\STATE Record reproduction time for both prey.
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Prey Size & 2 to 5 & Size of the prey species in the 3D FormAL  environment.\\ \hline
		Reproduction age limit & 100 & Minimum number of iterations or time steps a prey species need to be present in the simulation to get reproduction capability\\ \hline
		Reproduction interval & 1000 & Number of iterations a prey need to wait before reproducing again.\\ \hline
		Pattern Mutation Rate & 0.05 & Rate of Mutation of the pattern genome.\\ \hline
		Genome Mutation Rate & 0.5 & Rate of mutation of the rest of the genome excluding the pattern gene.\\ \hline
		Demise Age & 2000 & Age at which the prey species will be removed from the environment.\\
	\hline
\end{tabular}
\caption{Parameters to control prey population and visibility.}
\label{tab:prey-control-parameters}
\end{table}

\subsection{Predator}

Predators in the system are designed to provide selection pressure to \textit{models} and \textit{mimics} for the evolution of mimicry. Similar to prey species, they are agents in the FormAL environment capable of mobility and reproduction. In addition to it, these agents are equipped with Hopfield Network Memory to be able to learn and recognize patterns of the prey species. Their mobility and reproduction capability are controlled at the genetic level, while their memory is not genetically controlled, as it was not possible to come up with a genetic representation for Hopfield Network. So every new predator species gets to born with zero memory and with no inheritance from parents. A set of parameters are defined to control predators' population and learning ability in the environment. Details of these parameters are given in table \ref{tab:predator-control-parameters}.

\subsubsection{Learning}
The objective of a predator's interaction with prey is always to consume it. But based on the prey's pattern and palatability, the predator will either be able to consume it or throw it back to the environment. At this event the predator needs to learn the pattern with which the prey has been represented. The pattern represents palatability of the prey species, at least to the predator. To store this new pattern into memory, each predator is equipped with a Hopfield Network Memory. Every time a new interaction is made by the predator its memory is initialized with all the existing pattern that has already been encountered and the new one. The learning procedure used for this memory is Hebbian Learning \citep{hebb1949}.

The following \textit{general learning rule} is adopted in neural network studies: \textit{The weight vector} \( \textbf{w}_i = [w_{i1} \> w_{i2} \> ... \> w_{in}]^t \) \textit{increases in proportion to the product of input} \textbf{x} \textit{and learning signal r}. The learning signal r is in general a function of \(\textbf{w}_i,\textbf{x}\), and sometimes of the teacher's signal \(d_i\). Thus we have, 
\begin{equation}
	r = r(\textbf{w}_i,\textbf{x},d_i)
%\label{eq:}
\end{equation}
The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
\begin{equation}
	\Delta\textbf{w}_i(t)=cr[\textbf{w}_i(t),\textbf{x}(t),d_i(t)]\textbf{x}(t)
%\label{eq:}
\end{equation}
when c is a positive number called the \textit{learning constant} that determines the rate of learning.

For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
\begin{equation}
	r \overset{\Delta}{=} f(\textbf{w}_i^t \textbf{x})
%\label{eq:}
\end{equation}
The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
\begin{equation}
	\Delta\textbf{w}_i = cf(\textbf{w}_i^t \textbf{x})\textbf{x}
%\label{eq:}
\end{equation}
The single weight \( w_{ij} \) is adapted using the following increment:
\begin{equation}
	\Delta\textit{w}_{ij} = cf(\textbf{w}_i^t \textbf{x})x_j
%\label{eq:}
\end{equation}
This can be written briefly as 
\begin{equation}
	\Delta\textit{w}_{ij} = c o_i x_j, \> \text{for} \> j = 1, 2, ..., n
%\label{eq:}
\end{equation}
Here, \(\textbf{o}\) is the output vector. The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning. The Hebbian learning rule represents a purely feed-forward, unsupervised learning.

Training for Hopfield Network used for predator's memory is done by Hebbian Learning. Initially the weights are all set to zero. Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern. As Hopfield is a feedback network, the output of the network is also the input. The outer vector matrix of all the patterns are summed to come up with the final weight matrix. Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
\begin{equation}
w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
%\label{eq:}
\end{equation}
\[
w_{ij} = 0, i = j
\]
where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.

\subsubsection{Design of Memory with Hopfield Network}

\paragraph{Hopfield Network}

Algorithm for the Hopfield model is described in the following:

\begin{enumerate}
	\item \textit{Learning.} Let \( \boldsymbol{\xi}_1, \boldsymbol{\xi}_2, ..., \boldsymbol{\xi}_{\mu} \) denote a known set of N-dimensional fundamental memories. Use the outer-product rule (i.e. Hebb's postulate of learning) to compute the synaptic weights of the network as 
	\begin{equation}
		w_{ji} =
			\begin{cases}
				\frac{1}{N} \sum_{\mu=1}^{M}\xi_{\mu,j}\xi_{\mu,i}	& j \neq i \\
				0																										& j = i 
			\end{cases}
	%\label{eq:}
	\end{equation}
	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\). The elements of the vector \( \boldsymbol{\xi}_\mu \) equal \(\pm 1\) (bipolar). Once they are computed, the synaptic weights are kept fixed.

	\item \textit{Initialization.} Let \( \boldsymbol{\xi}_{probe} \) denote an unknown N-dimensional input vector (probe) presented to the network. The algorithm is initialized by setting
	\begin{equation}
		x_j(0) = \xi_{j,probe}, \> j = 1,...,N
	%\label{eq:}
	\end{equation}
	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).

	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
	\begin{equation}
		x_j(n+1)=sgn \Bigg(\sum_{i=1}^{N} w_{ji}x_i(n) \Bigg), \> j = 1,2, ..., N
	%\label{eq:}
	\end{equation}
	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.

	\item \textit{Output.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
	\begin{equation}
		\boldsymbol{y} = \boldsymbol{x}_{fixed}
	\label{eq:}
	\end{equation}
	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
\end{enumerate}

%This section needs to use similar variables as mentioned in the above section on Hopfield Network.
\paragraph{Input to memory}
Each prey contains an evolving cellular automata which is represented by a binary genome. This two dimensional pattern is serialized to be available as a one dimensional binary array, which is taken as input for any predator organism trying to interact with the prey. This binary representation of the pattern gets converted to a bipolar representation. Each input pattern consists of \(\textit{m} \times \textit{n} = \textit{mn}\) components, each component representing one pixel of the pattern (\textit{m} and \textit{n} representing each dimension). The \textit{m} by \textit{n} pattern configuration will be serialized by putting all row vectors in one single row sequentially.

\paragraph{Predator attack algorithm}
As soon as a predator reaches its attack age it selects random prey species around its vicinity and starts attacking them. This attack process also involves recognition of prey pattern, which is at the heart of mimicry simulation for this research. Two parameters have been defined to limit predator memorization and recognition process as both of these processes are computationally expensive. The ``Hopfield Minimum Memory Size" (default value in table \ref{tab:predator-control-parameters}) is the number of memory a predator needs to store before making intelligent decisions about attacking a new prey species. After a predator is born, it start attacking prey without any caution. But after every attack the predator will store its pattern and palatability level inside its memory. As soon as it reaches the minimum memory size, it will start making intelligent decision about attacking the next species. It will try to recognize the pattern and if found palatable, prey will be consumed. Otherwise prey will be thrown back into the environment. If the pattern is not recognized predator will try to consume it and in the process will store its palatability and pattern into memory.

In this way the predator memory is limited to \textsl{``Hopfield Maximum Memory Size"}. After reaching this memory predator will not store any more new pattern but will try to associate with the existing ones it has already stored.

\subsubsection{Genome}
Each predator has a 5 bits genome as explained in table \ref{tab:predator-genome}. The first 4 bits represent its mobility and magnitude of the force component with which it moves around the environment. The last bit controls reproduction capability of each species.

\begin{table}[h]
\centering
\begin{tabular}{|c|c|}
	\hline
		\textbf{Mobility(4)} & \textbf{Reproduction(1)} \\ \hline
				 1101					   &					1						 		\\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 5 bit predator genome.}
\label{tab:predator-genome}
\end{table}

\subsubsection{Mobility and reproduction capability}
Movement behavior of a predator is calculated from its genome. The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of prey present within its neighborhood. So magnitude of movement of a predator varies within a range of 0-15 units. If no prey is present in the neighborhood then this force is active in trying to keep predators distributed all over the cells. A predator chooses the neighborhood cell which contains the least number of predators. When the neighborhood contains zero predators, it would select any one of them randomly and move towards that cell.

The predators are distributed all over the cells with a constant mobile behavior to switch to another neighboring cell depending on the one containing the least number of predator and also most number of prey species. This behavior of predator has been designed to enforce the predatory behavior of these agents and also to have increased predator prey interaction in the simulation in terms of one agent chasing the other for survival of species.

\subsubsection{Reproduction process}
The  fifth gene of the predator is used to represent their capability of reproduction.  Depending on its binary value a predator in the simulation will or will not be able to reproduce. The reproduction process for predators is similar to prey species. As the learning capability of predators do not have any genetic representation, only the mobility behavior and reproduction capability takes effect in the reproductive process from one generation to another.

There are two control parameters that effect the reproduction of predator species. The first is \textsl{``Reproduction Age Limit"}. This is the minimum age a predator has to reach before starting to involve itself for reproduction. This parameter has been set to 500 iterations. The second parameter is \textsl{``Reproduction Interval"} which has been varied in the simulation from 1000 to 3000 iteration depending on the population of palatable prey species. This is a very important parameter for the simulation as it determines the overall predator population and its rate of increment. Depending on this value we can control the rate of predation on prey species, which on the other hand controls the rate of mimetic behavior of the overall prey population.

When the above two conditions are met, meaning the predator reaches its age for reproduction and also crosses its age interval, it randomly select another predator residing in the same cell. If this random predator is capable to reproduce depending on its 5th gene, then with a random single point crossover and mutation a new predator species is born which also resides on the same cell and initializes with zero memory configuration. Similarly when the new born predator reaches its maturity of reproductive age and if it is capable of reproduction then the process iterates itself.

\begin{table}[h!]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Minimum Memory Size & 2 to 6 & Minimum number of patterns stored in memory before predators start making intelligent decisions.\\ \hline
		Maximum Memory Size & 10 & Maximum number of patterns to be stored in memory. Limited to reduce processing time. \\ \hline 
		Hopfield Maximum Iterations & 20 & Maximum number of iterations for Hopfield Network to recognize a pattern. Usually the network reaches a steady state before that. But this restriction is to avoid infinite loop in case the network never reaches a steady state. \\ \hline
		Attack Age & 500 & minimum age a predator needs to reach to be able to attack prey species.  \\ \hline
		Attack Interval & 100 & Interval of time which needs to pass before a predators attacks its next prey. \\ \hline
		Genome Mutation rate & 0.3 & Mutation rate for the 5 bit genome of the predators representing their mobility and pattern recognition capability. \\ \hline
		Reproduction Age Limit & 500 & Minimum age a predator needs to reach before engaging in reproduction.\\ \hline
		Reproduction Interval & 1000 to 3000 & Interval of time a predator needs to pass between two reproduction process.\\ \hline
		Demise Age & 2000 to 7000 & Age at which a predator is considered as dead.\\
	\hline
\end{tabular}
\caption{Parameters to control predator population and pattern recognition capability.}
\label{tab:predator-control-parameters}
\end{table}

This model has been designed from a practical point of view; to come up with efficient results and achieve the main objective, \textit{evolution of mimicry}. Creation and transformation of different mimicry ring and also the dynamics of it has been integrated to achieve interesting results. This model can also be considered as a complex adaptive system similar to Holland's work on Echo \citep{holland1996}. The seven basics of a complex adaptive system which are: Aggregation, Tagging, Nonlinearity, Flow, Diversity, Internal Models and Building blocks \citep{holland1996} are present in this model. Individual components of this model such as the different types of agents and their properties can be considered as \textit{building blocks}. Each prey species are \textit{tagged} with individual pattern and palatability with which predators recognize them. We are providing different properties, behaviors and goals to the agents but setting them free in the environment to observe their \textit{aggregate} behavior, resulting in \textit{non-linear} or unpredictable outcome. The model has its \textit{flow} as it progresses in time. Also there is \textit{diversity} of prey species in the environment.

\section{The Results}
\label{section:results}

Data and analysis in this simulation has been concentrated on evaluating whether evolution of mimicry has taken place. This evaluation can be made with the number of different rings that has been created and the size of each of those rings along with the population of palatable and unpalatable species. Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.

\subsection{Mimicry Ring Reports}
The mimicry ring reports consist entirely of the population of prey species categorized according to pattern and palatability. Data is stored at every instance of time of the simulation keeping an interval of 10 iterations. As the number of rings that get generated reaches as many as 50 or more, and all the population of ring do not last for the entire simulation, so while storing data we have taken the most populous of the surviving 8 rings to plot. Parameters are mentioned in table \ref{tab:ring-report-control-parameters}.

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Mimicry Ring Hamming Distance & 10 \% of the Pattern Size & If the Hamming distance between the pattern of the model and the mimic is 10 \% the size of the pattern then they are considered within the same ring.\\ \hline
		Number of Rings to report & 8 & This value is the number of most populous rings that are included in the report.\\
	\hline
\end{tabular}
\caption{Parameters to mimicry ring report.}
\label{tab:ring-report-control-parameters}
\end{table}

\subsection{Initial configuration with two prey species}
\label{subsec:init-conf-2prey}
% Put the table here
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
  					 									& \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

The set of parameters in table \ref{tab:config-table-2-prey} were carefully selected to be the initial condition for this run of the simulation. This test has been done with two sets of prey species with very different Cellular Automata pattern and with opposite palatability and equal population. To control reproduction of the prey species their age limit has been set to 100 iterations into the time the species were alive. And the reproduction interval was set to 1000 iterations.

Pattern mutation rate has been set to a minimal level of 0.05 as by increasing this variable it is possible to increase the size of the number of mimicry rings present in the simulation. The genome mutation rate controls the rate at which genome of the child prey species will deviate from their parents. As mentioned earlier the genome mutation rate has been separated from the pattern mutation rate to bring more control to the number of mimicry rings generated.

Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500. But in the later experiments predator demise age has been increased to 5000 iterations. Predators in this simulation generate selection pressure for the evolution of mimicry. So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid. But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.

Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation. The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die accept their natural cause of death, that is to reach their demise age. So predator population can explode very easily. That is why their population is controlled in a restrictive manner with the help of high reproduction age limit and reproduction age interval.

The memory configuration size for predators is a very interesting parameter. The minimum memory size is directly associated with the number of prey species with which we initiate the simulation. Otherwise evolution of mimicry is not observed. As mentioned in table \ref{tab:predator-control-parameters} the minimum memory size is the number of prey species predator would consume before starting to make decisive consumption of prey species. After the initial birth of a predator and when the minimum attack age is crossed, it starts consuming prey species present in its vicinity without making any judgment. At this point its memory size is zero. As long as the minimum memory size is not reached predators will blindly consume prey species and insert their CA pattern and associated palatability into its Hopfield memory bank. No later than the minimum memory size has been reached, predators will start making intelligent decision about consuming its prey species. When catching a prey if its memory tells that it is palatable, it will consume that prey. Otherwise if memory recognizes it to be unpalatable predator will certainly let it go.

Now as we know the behavior of Hopfield memory, a recognition result will always be achieved depending on the similarity of the patterns stored in memory. So when minimum memory size has been reached the predator will always make a decision based on the similarity of the prey pattern currently captured and the patterns stored in memory.

% Put the image
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure}

The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations. With the initial configuration in the above table we can observe that multiple rings of prey population have been created. Two prey species are considered to be in a ring if their CA pattern have a Hamming distance within 10 bits. This parameter is mentioned in table \ref{tab:ring-report-control-parameters}. Population of palatable species has been represented with line curve while population of unpalatable species has been presented with dotted curve. Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population. The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
	\label{fig:plot-2-prey-5k}
\end{figure}

The plot of figure \ref{fig:plot-2-prey-5k} is from the same experiment as of figure \ref{fig:plot-2-prey}, but only up to 5000 iterations. By closely observing the graph of figure \ref{fig:plot-2-prey-5k}, we could see the population of two species have started dropping at around time 500 when the initial predator population reaches the maturity for consuming prey species (effect of the parameter `Minimum Attack Age' from table \ref{tab:config-table-2-prey}). At around time 1000 the prey population starts reproducing as the population increases (controlled by `Reproduction Age Limit' from table \ref{tab:config-table-2-prey}). At the same time different other species of prey gets to be born with mutated CA patterns. There is a straight drop of prey population at time 2000, when all the prey species with which the simulation was initialized come to its demise age (controlled by `Prey Demise Age' at table \ref{tab:config-table-2-prey}). Over time the population of CA Rule 30 dominates the population (figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable. Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.). CA Rule 110 was initialized as a set of palatable species.

We can observe from the above result that the evolution of mimicry has taken effect. A population of mimics were successfully able to exceed the population of other prey species, and the reason being, avoidance by predators of prey pattern similar to unpalatable ones. We can conclude that Batesian mimicry has taken effect in the simulation.

%Put the number of rings picture:
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

Observing from figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 27 rings at the end of 10000 iterations. A small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented. For example if we take a look at the set of pattern genotype with very different phenotype in table \ref{tab:diff-in-pattern}.

%CARule table
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{|l|c|c|c|}
  \hline
  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
  \hline
\end{tabular}
\caption{Difference in prey pattern genotype and phenotype}
\label{tab:diff-in-pattern}
\end{table}

All the patterns in table \ref{tab:diff-in-pattern} have a genetic bit difference of 1. So by a single mutation there can be three different set of phenotype for a child organism from its parent. This is largely the reason for the increased number of mimicry rings created in the simulation. Only the 8 most populous rings are presented in the graphs with population verses simulation time.

The screen shot in figure \ref{fig:screenshot-simTime7600-2-prey} is for one instance of time of the simulation. The red agents are predators while the black agents with different textured patterns are the prey species. According to their behavior most of the prey species are flocking together in a group while also being chased by the predators, whose sole purpose is to consume prey species.

%Screenshot of the simulation
\begin{figure}[h]
	\centering
	\label{fig:screenshot-simTime7600-2-prey}
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime7600}
	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
\end{figure}

\subsection{Initial population with six prey species}
\label{subsec:init-conf-6-prey}
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}} 
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule57}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 6 prey species.}
\label{tab:config-table-6-prey}
\end{table}

To evaluate the simulation at a more complex level we increase the prey population to 900, consisting of 6 different species with very different pattern configuration. To boost predator-prey interaction we also increase the number of predator population to 30. Predator reproduction interval has been set comparatively lower in this simulation to 2000 iterations. As the initial population of prey species is very high, over time we are expecting even larger number of prey species. If predator population does not increase at similar rate there might be a prey population explosion were predator will have no effect on providing selection pressure for the evolution of mimicry. So that is why predator population control parameter has been set to this level. For memory configuration, the minimum number is set to 6, meaning the predator will have to store 6 different prey pattern configuration before starting to make intelligent decision about consuming them. As previously mentioned this number is always set in accordance with the initial number of different prey configuration.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-6Prey}
	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
	\label{fig:plot-6-prey}
\end{figure}

With the above set of parameters we receive the plot of figure \ref{fig:plot-6-prey}. An enormous diversity of species can be observed from this experiment. In addition to the six prey species with which the simulation starts, the total number of mimicry rings reach nearly 50. Observing the top 8 as presented in the plot of figure \ref{fig:plot-6-prey}, effects of Batesian mimicry is obvious. Unpalatable CA Rule 190 and 30 dominates the population. Similarly unpalatable CA Rule 105 is also dominant. But after 10000 iterations CA Rule 55 seems to have higher population than 105 even though 55 is a \textsl{palatable} set of species. This anomaly could be the reason for storing large number of patterns in the predator Hopfiled memory. As we know that the number of patterns stored in Hopfiled network is inversely proportional to its recognition rate. In this simulation memory size is controlled by the `Maximum Memory Configuration' which is set to 10 in table \ref{tab:config-table-6-prey}. In this experiment, the value of `Minimum Memory Configuration' is 6, which is rather a large number. So there could be possibility of wrong recognition by Hopfield memory. Then again this phenomenon is common if we consider behavior of predators in nature. It is definitely hard for a single predator to memorize multiple poisonous patterns and because of which Mullerian mimicry takes an effect as mentioned in section \ref{subsec:mullerian-mimicry}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-6Prey}
	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
	\label{fig:ringSize10k-6-Prey}
\end{figure}

\subsection{Initial configuration with only unpalatable species}
\label{subsec:init-conf-only-unp}
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all unpalatable.}
\label{tab:config-table-4-prey-unpalatable}
\end{table}

To further observe the effects of mimicry ring we initialize the simulation with all unpalatable prey species. After finding different anomalous behavior of predator recognition capability in section \ref{subsec:init-conf-6-prey} for increased number of diverse prey species; for this experiment the initial number of species have been reduced from six to four. As explained earlier the minimum memory configuration is also set to four in accordance to the initial number of prey species. Rest of the parameters remain quite unchanged.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-4Prey-unp}
	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:plot-4-prey-unp}
\end{figure}

The results according to figure \ref{fig:plot-4-prey-unp} are much expected. The population of unpalatable species have prevailed. After nearly 8000 iterations we can see unpalatable species of CA rule 55, 110, 30 and 190 have prevailed with the most population. All of their palatable counter parts are also increasing their population deceiving the predators. We observe the effect of the simulation up to 8000 iterations instead of 10000 as the total number of prey species increases at an enormous rate in this simulation within very short period of time. As most of the species are unpalatable, predators mostly do not get the opportunity to consume, causing a much lower prey death rate.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-4Prey-unp}
	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
	\label{fig:ringSize10k-4-Prey-unp}
\end{figure}

This experiment is an ideal scenario for observing Mullerian mimicry. As mentioned in section \ref{subsec:mullerian-mimicry}, Mullerian mimicry occurs between multiple species of unpalatable prey population. From the second work of Franks and Noble \citep{franks2003} mentioned in section \ref{subsubsec:models-by-frank-and-noble}, we note that multiple Mullerian mimicry rings are expected to converge into one large ring through the evolutionary process of punctuated equilibrium. But in this experiment as the predator's `Minimum Memory Configuration' is set to four, all predators have the capability to recognize four prey patterns before starting to make intelligent decision of consuming them. By setting `Minimum Memory Configuration' to one, also increasing `Predator Demise Age' to 7000 and decreasing predator's `Reproduction Age Interval' to 1500, we get the following plot.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime6k-4Prey-unp-1-mem}
	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable. Minimum Memory size reduced to one.}
	\label{fig:plot-4-prey-unp-1-mem}
\end{figure}

Running the simulation for 6000 iterations there was no sign for all prey population to converge into one large ring. As it can be observed in figure \ref{fig:plot-4-prey-unp-1-mem} all four unpalatable prey population have a very dominant presence in the simulation. Even though predator minimum memory has been reduced to only one pattern, different population of predators become familiar with different prey patterns, which results in the existence of multiple Mullerian mimicry ring instead of a single one.

\subsection{Initial configuration with only palatable species}
\label{subsec:init-only-palatable-species}

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all palatable.}
\label{tab:config-table-4-prey-palatable}
\end{table}

The parameters for this simulation has been set exactly the same as in table \ref{tab:config-table-4-prey-unpalatable} except all the species are palatable at this point. All predator configuration has also been set to exactly same as before.

The results for the configuration in table \ref{tab:config-table-4-prey-palatable} can be observed in figure \ref{fig:plot-4-prey-p} where all population of prey species have reached its demise at nearly 7000 iterations. By analyzing details we can see, around simulation time 500 all population of species come to a steady downfall as at this point initial predator species reach its' age for consumption. Around simulation time 1000 all population of prey species start increasing steadily because they reach their maturity level of reproduction. At iteration time 2000 there is a sudden drop of prey population because the initial population of prey have reached its demise age at this point. By this time the population of unpalatable species mutated from the palatable ones start increasing, and slowly around time 7000 and onwards the entire population of prey come to its demise. Predator population, from the beginning of the simulation has taken a very dominant effect. As all the species are palatable, predator's consumption and reproduction rate is extremely high and it keep increasing in a geometric rate.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey-p}
	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey-p}
	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

Observation of mimicry rings also tell us about the results we have seen in the plot of figure \ref{fig:plot-4-prey-p}. The number of rings keep increasing but comes to a sudden drop around simulation time 7000 and goes to zero.

\subsection{Analysis of Batesian Mimicry}
\label{subsec:result-batesian-mimicry}
For all possible initial conditions, Batesian mimicry has taken effect. It can be observed that for every ring of unpalatable species there is an existence of the palatable ring racing to reach the population count of its unpalatable counterpart. Also when the initial population starts with a set of only palatable species we can observe that the total population vanishes within very short period of time (section \ref{subsec:init-only-palatable-species}). This effect can be explained with the fact that the palatable population does not have any models to mimic, and it reaches extinction. So from this analysis it can be concluded that the model under discussion have successfully simulated the evolution of Batesian mimicry.

\subsection{Analysis of Mullerian Mimicry}
\label{subsec:result-mullerian-mimicry}
Effects of Mullerian mimicry can be observed best for the experiment in section \ref{subsec:init-conf-only-unp}. For that case, we initialized the model with 4 rings of unpalatable species with no palatable ones and after nearly 10K iterations, all of the initial unpalatable rings have survived with dominance. The cause of this behavior can be explained by the minimum number of patterns that each predator can store in memory, which was set to four. So this parameter was reduced to one to observe whether it is possible to converge all different unpalatable rings into one large ring, when predators are capable to memorizing only a single pattern. But as it turned out, the phenomena of ``a single large ring" does not occur because different predators recognize different patterns resulting in multiple divergent Mullerian mimicry rings. It can be concluded that our results are consistent with those of Franks and Noble (section \ref{subsubsec:models-by-frank-and-noble}), that multiple Mullerian mimics do not converge into one large ring.

\section{Conclusion}
\label{section:conclusion}
Analysis of the results tell us that we have successfully been able to simulate the evolution of mimicry. In addition to that, this model provides a more accurate simulation of the fascinating natural process of mimicry rings. Not only does this model simulates mimicry with the initialized population but also it provides possibility of creating diverse new rings and their shift in population. This model also verifies the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium (section \ref{subsubsec:reflection-of-punctuated-equilibrium}) \citep{turner1988}.

If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature. As mentioned previously this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium. Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.

If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry. From the sections of \ref{subsec:result-batesian-mimicry} and \ref{subsec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.

\bibliographystyle{apalike}
\bibliography{references}

\printglossaries
\phantomsection \label{acronyms}

\end{document}

### 2016-10-20 docs/journal-paper/Paper.tex
Journal paper

@@
-\documentclass[letterpaper]{article}
-\usepackage{natbib}
-%\usepackage{natbib}
+\documentclass{article}
+\usepackage[paper=letterpaper,margin=0.9in]{geometry}
+\usepackage[numbers]{natbib}
 %Graphics package
@@
 
-\title{Modeling the Evolution of Mimicry}
-\author{Mohiul Islam$^{1}$ \and Peter Grogono$^{1}$ \\
+\newcommand{\footremember}[2]{%
+   \footnote{#2}
+    \newcounter{#1}
+    \setcounter{#1}{\value{footnote}}%
+}
+\newcommand{\footrecall}[1]{%
+    \footnotemark[\value{#1}]%
+}
+
+\title{A Model for the Evolution of Mimicry}
+\author{Mohiul Islam\footremember{contactAuthor}{Contact Author} \footremember{address}{Faculty of Engineering and Computer Science, Concordia University, Montreal, Canada, H3G 1M8.
+moh\_i@encs.concordia.ca (M.I.), grogono@cse.concordia.ca (P.G.)} \qquad Peter Grogono\footrecall{address} \\
 \mbox{}\\
-$^1$Concordia University  \\
-moh\_i@encs.concordia.ca \\
-grogono@cse.concordia.ca}
+Concordia University}
+\date{\vspace{-5ex}}
 
@@
 \begin{abstract}
-A novel agent based, artificial life model, for the evolution of mimicry is presented.
+An agent based, artificial life model, for the evolution of mimicry is presented.
 This model is a predator-prey co-evolution scenario where pattern representation phenotype is simulated with Cellular Automata, while behaviors of pattern recognition is configured with Hopfield Network.
@@
 \end{abstract}
-
+\newpage
 %Introductory Section
@@
 Even though these capabilities are simple and defined simply, they provide a rich set of variations illustrating the four kernel properties of complex adaptive systems described by Holland \citep{holland1996}.
-
-In developing Echo using Holland's criterion, a step by step approach has been taken.
-Among these steps of improvement, the work by Hraber \citep{hraber1997} is more from an ecological perspective, and having a good resemblance with natural ecosystem.
-It has stable patterns of interactions among genetic variants, or trophic networks.
-It consists of different levels of resources along with relative species abundance.
-Even different cataclysmic events such as meteor, drought and so fourth are introduced.
-Also several isolation effects are observed where a number of sites are allowed to evolve independently.
-In addition to that Echo contains interesting flow of resources.
-
-Two separate experiments were done to observe whether species abundance pattern can be used to find ecologically plausible behavior in Echo.
-To make a falsifiable comparison with biological systems, two ecological patterns are considered, each of which has similar quantitative properties in many different ecosystems that exist in nature.
-The objective is to compare these naturally occurring ecosystems with Echo.
-The ecological patterns are the Preston  curve and the species-area scaling relation.
-This allowed comparison of Echo diversity patterns with empirical patterns of species abundance.
-As result of the comparison Echo showed good quantitative agreement with naturally occurring species abundance distribution and species area scaling relation.
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
+	\includegraphics[width=0.5\textwidth]{images/Batesplate_ArM}
 	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row).
@@
 
-Mimicry is one of the most fascinating cases of evolutionary biology.
-This phenomenon has been studied extensively as infinite number of evidence exists in nature.
-One hundred years after Bates first clearly defined the concept, a review of literature listed 1,500 papers arguing for or against it.
-And this figure is more than 40 years old as it has been taken from Wilcker \citep{wickler1986}, published in 1968.
-It is almost impossible to survey all the known examples of Mimicry, and this would in any case be pointless.
-Then again many examples can be found in Cott's \textit{Adaptive Coloration in Animals} \citep{cott1957}.
-
 %Chapter describing the model
@@
 While the principal behind it was ``\textit{not to include a variable in an agent unless the variable is genetically controlled (or, at least, genetically influenced)}".
-We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.
+We will see that this principal was not completely established in simulating mimicry as it was not possible to come up with a suitable encoding for genetic representation of Hopfield Network which was used as a pattern recognizer for the predator species.
 
@@
 \subsubsection{Spatial representation of the environment}
-The framework consists of a three dimensional visual environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.
+The framework consists of a three dimensional environment where agents of the individual based simulation gets complete freedom of movement defined from their genetic representation.
+This toroidal cube can be visualized to provide intuition into the agents' behavior.
 
@@
 \centering
-\begin{tabular}{| p{1.5cm} | >{\centering} p{1.6cm} | p{4cm} |}
+\begin{tabular}{| c | c | l |}
 	\hline
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/cells-front}
+	\includegraphics[width=0.5\textwidth]{images/cells-front}
 	\caption[Three dimensional representation of the environment]{Three dimensional representation of the environment divided in cells. Presence of different species of agents inside.}
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
+\begin{tabular}{| c | c | p{10cm} |}
 	\hline
@@
 Cellular automata are computer generated patterns applying very simple rules.
-First invented by Jon von Neuman and later extended by Stephen Wolfram, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules.
+First invented by Jon von Neuman and later extended by Stephen Wolfram \citep{Wolfram2002}, this field of study has created a lot of enthusiasm in the evolution of complexity with blocks of simplicity, in this case rules.
 We choose cellular automata as it can be easily represented with the help of a binary genome and then evolutionary operations on the genomic representation, such as mutation and crossover can easily be applied.
+
+Every prey organism contain a binary genetic representation of CA which generates a fully developed pattern of size 16 by 16 bits from its initial state.
+With this pattern the predator will identify the prey and store its level of palatability in memory.
+This 8 bit genome has a decimal range between 0 to 255.
+Each of this value is associated to a unique CA pattern.
+In generating the pattern of figure \ref{fig:cellular-automata-rule-30}, the genetic representation would be the `New state of center cell'.
+To store in Hopfield memory we take a linear representation of this 2-D pattern and to find similarity between two patterns we calculate hamming distance between their linear representations.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[resolution=300]{images/CARule30-large}
+	\caption[Cellular Automata]{Cellular Automata Rule 30}
+	\label{fig:cellular-automata-rule-30}
+\end{figure}
+
+\begin{table}[h!]
+	\small
+	\centering
+	\setlength\tabcolsep{2pt}
+	\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
+	  \hline
+	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
+	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
+	  \hline
+	\end{tabular}
+	\caption{Cellular Automata rule}
+	\label{tab:cellular-automata-rule}
+\end{table}
 
@@
 In \citep{franks2002} they have used linear difference in number ``constrained to a 'ring' of values  from 1-20 (where 20 and 1 are neighbors)" to distinguish species diversity.
-Here the distance of one phenotype from another represents their level of similarity.
+The distance of one phenotype from another represents their level of similarity.
 
@@
 And by restricting inter species reproduction we can control the diversity of patterns.
-But there is mutation applied when similar species mate with each other, so new species do born out of generations of existing species.
-So that is why we have two separate mutation rate while reproducing prey species.
+But there is mutation applied when similar species mate with each other, so new species born out of generations of existing species.
+That is why we have two separate mutation rate while reproducing prey species.
 One being the ``Pattern Mutation Rate" (default values are mentioned in table \ref{tab:prey-control-parameters}) with which we control mutation of the first 8 bits of the genome while the ``Genome Mutation Rate" is used to control mutation of rest of the 9 bit genome (table \ref{tab:prey-genome}).
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1cm} | p{5cm} |}
+\begin{tabular}{| c | c | p{11cm} |}
 	\hline
@@
 
-The following \textit{general learning rule} is adopted in neural network studies: \textit{The weight vector} \( \textbf{w}_i = [w_{i1} \> w_{i2} \> ...
-\> w_{in}]^t \) \textit{increases in proportion to the product of input} \textbf{x} \textit{and learning signal r}.
-The learning signal r is in general a function of \(\textbf{w}_i,\textbf{x}\), and sometimes of the teacher's signal \(d_i\).
-Thus we have,
-\begin{equation}
-	r = r(\textbf{w}_i,\textbf{x},d_i)
-%\label{eq:}
-\end{equation}
-The increment of the weight vector \(\textbf{w}_i\) produced by the learning step at time t according to the general learning rule is,
-\begin{equation}
-	\Delta\textbf{w}_i(t)=cr[\textbf{w}_i(t),\textbf{x}(t),d_i(t)]\textbf{x}(t)
-%\label{eq:}
-\end{equation}
-when c is a positive number called the \textit{learning constant} that determines the rate of learning.
-
-For Hebbian learning rule the learning signal is equal simply to the neuron's output. We have
-\begin{equation}
-	r \overset{\Delta}{=} f(\textbf{w}_i^t \textbf{x})
-%\label{eq:}
-\end{equation}
-The increment \(\Delta\textbf{w}_i\) of the weight vector becomes
-\begin{equation}
-	\Delta\textbf{w}_i = cf(\textbf{w}_i^t \textbf{x})\textbf{x}
-%\label{eq:}
-\end{equation}
-The single weight \( w_{ij} \) is adapted using the following increment:
-\begin{equation}
-	\Delta\textit{w}_{ij} = cf(\textbf{w}_i^t \textbf{x})x_j
-%\label{eq:}
-\end{equation}
-This can be written briefly as 
-\begin{equation}
-	\Delta\textit{w}_{ij} = c o_i x_j, \> \text{for} \> j = 1, 2, ..., n
-%\label{eq:}
-\end{equation}
-Here, \(\textbf{o}\) is the output vector.
-The learning rule requires the weight initialization at small random values around \( \textbf{w}_i = \textbf{0}\) prior to learning.
-The Hebbian learning rule represents a purely feed-forward, unsupervised learning.
-
-Training for Hopfield Network used for predator's memory is done by Hebbian Learning.
-Initially the weights are all set to zero.
-Using Hebbian rule, the outer product of the input - output vector pairs are calculated for each pattern.
-As Hopfield is a feedback network, the output of the network is also the input.
-The outer vector matrix of all the patterns are summed to come up with the final weight matrix.
-Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
-\begin{equation}
-w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
-%\label{eq:}
-\end{equation}
-\[
-w_{ij} = 0, i = j
-\]
-where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
-
 \subsubsection{Design of Memory with Hopfield Network}
-
-\paragraph{Hopfield Network}
-
-Algorithm for the Hopfield model is described in the following:
-
-\begin{enumerate}
-	\item \textit{Learning.} Let \( \boldsymbol{\xi}_1, \boldsymbol{\xi}_2, ..., \boldsymbol{\xi}_{\mu} \) denote a known set of N-dimensional fundamental memories.
-Use the outer-product rule (i.e.
-Hebb's postulate of learning) to compute the synaptic weights of the network as
-	\begin{equation}
-		w_{ji} =
-			\begin{cases}
-				\frac{1}{N} \sum_{\mu=1}^{M}\xi_{\mu,j}\xi_{\mu,i}	& j \neq i \\
-				0																										& j = i 
-			\end{cases}
-	%\label{eq:}
-	\end{equation}
-	where \(w_{ji}\) is the synaptic weight from neuron \(i\) to neuron \(j\).
-The elements of the vector \( \boldsymbol{\xi}_\mu \) equal \(\pm 1\) (bipolar).
-Once they are computed, the synaptic weights are kept fixed.
-
-	\item \textit{Initialization.} Let \( \boldsymbol{\xi}_{probe} \) denote an unknown N-dimensional input vector (probe) presented to the network. The algorithm is initialized by setting
-	\begin{equation}
-		x_j(0) = \xi_{j,probe}, \> j = 1,...,N
-	%\label{eq:}
-	\end{equation}
-	where \( x_j(0) \) is the state of neuron \(j\) at time \(n = 0\) and \( \xi_{j,probe} \) is the \(j\)th element of the probe \( \boldsymbol{\xi}_{probe} \).
-
-	\item \textit{Iterate Until Convergence.} Update the elements of state vector \( \boldsymbol{x}(n) \) asynchronously (i.e., randomly and once at a time) according to the rule
-	\begin{equation}
-		x_j(n+1)=sgn \Bigg(\sum_{i=1}^{N} w_{ji}x_i(n) \Bigg), \> j = 1,2, ..., N
-	%\label{eq:}
-	\end{equation}
-	Repeat the iteration until the state vector \( \boldsymbol{x} \) remains unchanged.
-
-	\item \textit{Output.} Let \( \boldsymbol{x}_{fixed} \) denote the fixed point (stable state) computed at the end of the step 3, The resulting output vector \( \boldsymbol{y} \) of the network is
-	\begin{equation}
-		\boldsymbol{y} = \boldsymbol{x}_{fixed}
-	\label{eq:}
-	\end{equation}
-	Step 1 is the storage phase, and steps 2 through 4 constitute the retrieval phase.
-\end{enumerate}
 
@@
 Movement behavior of a predator is calculated from its genome.
-The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force at which it will move towards the maximum crowd of prey present within its neighborhood.
+The first 4 bits of the genome are converted from binary to decimal to determine the magnitude of force with which it will move towards the maximum crowd of prey present within its neighborhood.
+Number of bits are less than prey (6 bits) to reduce their maximum speed.
 So magnitude of movement of a predator varies within a range of 0-15 units.
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
+\begin{tabular}{| p{3cm} | c | p{10cm} |}
 	\hline
@@
 Also it can be established whether Batesian Mimicry and Mullerian Mimicry have taken effect by analyzing the data set of these populations.
+These results were initially presented at \citep{mohiulThesis2011} and later some has been published in \citep{mohiulAlifexv}.
 
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | >{\centering} p{1cm} | p{5cm} |}
+\begin{tabular}{| p{3cm} | c | p{8cm} |}
 	\hline
@@
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
+\begin{tabular}{| p{3.5cm} | p{3.5cm} | p{1cm} | p{.5cm} | p{2.5cm} | p{1cm} |}
   \hline
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule110}} & 108 
   														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
-  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
+  					 									& Rule30 (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics{images/CARule30}}  & 108 
   					 									& \multicolumn{2}{c|}{}\\ \hline
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 Initial population of predator species has been set to 10 which is in accordance with the prey population in the simulation.
-The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die accept their natural cause of death, that is to reach their demise age.
+The reason for such low number of predator is, unlike prey species which are consumed by predators, there is no cause for the predator species to die except their natural cause of death, that is to reach their demise age.
 So predator population can explode very easily.
@@
 % Put the image
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
+\begin{figure*}[t!]
+	\centering
+	\includegraphics[resolution=300]{images/simTime10k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
 	\label{fig:plot-2-prey}
-\end{figure}
+\end{figure*}
 
@@
 Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population.
-The simulation was initiated with two prey species having CA rule of 30 and 110 and being palatable and unpalatable consecutively.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
+The simulation was initiated with two prey species having CA rule of 110 and 30 and being palatable and unpalatable respectively.
+
+\begin{figure*}[h]
+	\centering
+	\includegraphics[resolution=300]{images/simTime5k-2Prey}
 	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
 	\label{fig:plot-2-prey-5k}
-\end{figure}
+\end{figure*}
 
@@
 %Put the number of rings picture:
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
+\begin{figure*}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{images/ringSize10k-2Prey}
 	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
 	\label{fig:ringSize10k-2Prey}
-\end{figure}
+\end{figure*}
 
@@
   CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
-  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
-  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
+  Pattern & \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule60}} 
+  				& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule61}} 
+  				& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule62}}\\
   \hline
@@
 	\label{fig:screenshot-simTime7600-2-prey}
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime7600}
+	\includegraphics[width=0.5\textwidth]{images/simTime7600}
 	\caption[Graphical representation of the model (simulation time: 7600)]{Graphical representation of the model, simulation time: 7600.}
@@
 \label{subsec:init-conf-6-prey}
-\begin{table}[h]
+\begin{table}[H]
 \centering
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
+\begin{tabular}{| p{3.5cm} | p{3.5cm} | p{1cm} | p{.5cm} | p{2.5cm} | p{1cm} |}
   \hline
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
+  					 									& Rule30  (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
+  					 									& Rule55  (Palatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}} 
+  					 									& Rule190 (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule190}} 
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule57}}    
+  					 									& Rule57  (Palatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule57}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule105 (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-6Prey}
+	\includegraphics[resolution=300]{images/simTime10k-6Prey}
 	\caption[Population distribution of mimicry rings (6 prey species)]{Population distribution of mimicry rings, initialized with 6 prey species.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-6Prey}
+	\includegraphics[width=0.5\textwidth]{images/ringSize10k-6Prey}
 	\caption[Number of mimicry rings (6 prey species)]{Number of mimicry rings, initialized with 6 prey species.}
@@
 \label{subsec:init-conf-only-unp}
-\begin{table}[h]
+\begin{table}[H]
 \centering
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
+\begin{tabular}{| p{3.5cm} | p{3.5cm} | p{1cm} | p{.5cm} | p{2.5cm} | p{1cm} |}
   \hline
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
+  					 									& Rule30  (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
+  					 									& Rule55  (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule190 (Unpalatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
   Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
-  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
+  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
    																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime8k-4Prey-unp}
+	\includegraphics[resolution=300]{images/simTime8k-4Prey-unp}
 	\caption[Population distribution of mimicry rings(4 prey species all unpalatable)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize8k-4Prey-unp}
+	\includegraphics[width=0.5\textwidth]{images/ringSize8k-4Prey-unp}
 	\caption[Number of mimicry rings (4 prey species all unpalatable)]{Number of mimicry rings, initialized with 4 prey species all unpalatable.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime6k-4Prey-unp-1-mem}
+	\includegraphics[resolution=300]{images/simTime6k-4Prey-unp-1-mem}
 	\caption[Population distribution of mimicry rings(4 prey, all unpalatable but reduced predator memory)]{Population distribution of mimicry rings, initialized with 4 prey species all unpalatable.
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \centering
 \setlength\tabcolsep{2pt}
-\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
+\begin{tabular}{| p{3.5cm} | p{3.5cm} | p{1cm} | p{.5cm} | p{2.5cm} | p{1cm} |}
   \hline
    														&\multicolumn{3}{c|}{Prey configuration} 																	
-   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator \\ configuration}} \\ \hline
-  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
+   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
+  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule110}} 
   																									& 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
-  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
+  					 									& Rule30  (Palatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule30}}  
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
+  					 									& Rule55  (Palatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule55}}    
   					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
-  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
+  					 									& Rule190 (Palatable)& \parbox[c][2em][c]{2.3em}{\includegraphics[resolution=300]{images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
   \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey-p}
+	\includegraphics[resolution=300]{images/simTime10k-4Prey-p}
 	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4Prey-p}
+	\includegraphics[width=0.5\textwidth]{images/ringSize10k-4Prey-p}
 	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
@@
 
-If we consider the field of Artificial Life as a tool for biological inquiry then the model presented in this thesis was successful in terms of providing good insight in terms of understanding better the evolutionary process of mimicry as it happens in nature.
-As mentioned previously this model gives us verification of the theory of Turner in explaining the evolution of mimicry with punctuated equilibrium.
-Also it enforces findings from the work of Franks and Noble that multiple Mullerian mimics do not converge into one large ring.
-
-If we consider Artificial Life as the study where we simulate natural processes to further extend capabilities in the field of computer science, then also this thesis is a success in making an appropriate emulation of the evolutionary process of mimicry.
-From the sections of \ref{subsec:result-batesian-mimicry} and \ref{subsec:result-mullerian-mimicry} we can conclude that the complex behavior of Batesian and Mullerian mimicry can be simulated with this model.
-
-\bibliographystyle{apalike}
+\bibliographystyle{apa-good}
 \bibliography{references}
